### 2019-03-14 paper.tex
add abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{AP Codes: Low Overhead Erasure Code Using Approximate Recovery}

\author{Huayi J}

\maketitle

\begin{abstract}
    Erasure codes are commonly used in large-scale data storage systems.
    Current erasure code schemes use an extra number of parity disks to tolerate multiple disk failures, which is expensive because it is very rare for multiple disks to be corrupted at the same time.
    We present AP (short for Approximation) codes that can approximately tolerate disk-level failures with little additional storage overhead for files such as video.

    Video data such as autopilot or security monitoring occupies a large amount of storage space, however the current erasure code scheme does not take into account the redundant information and fault tolerance contained in the video data.
    For encoded video data, errors at different segments have different effects on the decoding quality of the video. We only apply parity blocks to key data segments in the video. By allowing the loss of certain non-critical data segments, we can approximately tolerate disk failures with little additional storage overhead.    
\end{abstract}

\begin{IEEEkeywords}
    Erasure Codes, Approximate Storage, Video Storage, Low Overhead
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-03-18 paper.tex
Finish ABSTRACT and most INTRODUCTION

@@
 \usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithm}
 \usepackage{algorithmic}
@@
 \usepackage{xcolor}
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{subfigure}
+\usepackage{ntheorem}
+\usepackage{enumerate}
+\usepackage[bottom]{footmisc}
+\usepackage{soul}
+
+\usepackage[T1]{fontenc}
+\usepackage{mathptmx}
+\soulregister\cite7
+\soulregister\ref7
+\pagestyle{plain}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{AP Codes: Low Overhead Erasure Code Using Approximate Recovery}
-
-\author{Huayi J}
+\title{\LARGE{Approximate Code: A cost-effective erasure code for multimedia applications in cloud storage systems}\\
+}
+\author{\IEEEauthorblockN{Huayi Jin$^1$}
+}
 
@@
 \begin{abstract}
-    Erasure codes are commonly used in large-scale data storage systems.
-    Current erasure code schemes use an extra number of parity disks to tolerate multiple disk failures, which is expensive because it is very rare for multiple disks to be corrupted at the same time.
-    We present AP (short for Approximation) codes that can approximately tolerate disk-level failures with little additional storage overhead for files such as video.
+Erasure codes are commonly used to ensure data reliability in cloud storage systems, where multimedia data produced by live video, autopilot, social media and security monitoring occupies large amounts of space.
+Typical erasure codes, such as Reed-Solomon (RS) codes, use several parity disks to fully recover failure disks. 
+However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the multimedia data, which results in multiple complete parity disks being excessive.
 
-    Video data such as autopilot or security monitoring occupies a large amount of storage space, however the current erasure code scheme does not take into account the redundant information and fault tolerance contained in the video data.
-    For encoded video data, errors at different segments have different effects on the decoding quality of the video.
-We only apply parity blocks to key data segments in the video.
-By allowing the loss of certain non-critical data segments, we can approximately tolerate disk failures with little additional storage overhead.
+Therefore, we propose Approximate Codes for multimedia data, which significantly reduce storage overhead by reducing the verification of redundant data.
+Approximate Codes provide complete recovery when fewer disks fail, and approximate recovery (recover most data) in the event of multiple disk failures.
+To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
+The results show that compared with the typical high-reliability erasure code scheme, Approximate Codes reduce the storage cost by 7.64\% at the expense of reasonable video quality loss probability.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-    Erasure Codes, Approximate Storage, Video Storage, Low Overhead
+    Erasure Codes, Approximate Storage, Multimedia, Cloud Storage
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Currently, many cloud storage systems use erasure codes to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud.
+It is known that erasure codes provide much lower storage overhead and write bandwidth than replication with the same fault tolerance.
 
-\section{Ease of Use}
+Typical erasure codes schemes generate k check disks for a group of disks by calculation, which can tolerate any k disk failures in the group, such as RS-based code (RS, LRC), or XOR-based code (...).
+Other erasure codes (SD, STAIR) use the parity blocks to tolerate sector failures in addition to disk-level fault tolerance.
 
-\subsection{Maintaining the Integrity of the Specifications}
+In cloud storage systems, erasure code schemes are essential for multimedia applications.
+Applications such as the video industry, autonomous driving, social media, and security monitoring generate numerous data each day while consuming large amounts of storage resources.
+This makes it extremely expensive to guarantee multimedia data availability through replication scheme.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+Existing erasure codes are designed to completely recover corrupted data and use at least 3 additional check disks [] to ensure data availability.
+These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of multimedia applications can tolerate a certain amount of data loss.
+For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive.
+In addition, even if the multimedia data suffers a certain loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+We also find that multimedia data is typically encoded and stored to save space, while the encoded multimedia data stream is non-uniformly sensitive to data loss, which makes it unsuitable to provide uniform fault tolerance using conventional erasure codes.
+Image coding algorithms such as JPEG convert pixels to the frequency domain, making some data segments more important than others, while video coding algorithms such as H264 only store key frames (I frame) completely, so that other frames need to rely on them for calculation.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+Therefore, we propose Approximate Codes for multimedia data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors.
+In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of n disks where m disks are dedicated to coding and another s sectors encoded for the first strip.
+This allows the data of the first stripe to tolerate any m+s disk corruption, so we specifically store important segments of multimedia data here.
+With an appropriate data distribution scheme, non-critical data segments will still retain (n-m-s)/(n-m) data when any m+s disks are lost, which makes recovery schemes such as interpolated or superpixel still effective.
+The approximate code provides two recovery modes, full recovery and approximate recovery.
+The former applies to no more than m disk corruptions and recovers all data, the latter applies to no more than m+s disk corruptions and retains important data.
 
@@
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{IEEEtrans}
+\bibliography{paper}
 

### 2019-03-20 paper.tex
version 0.1

@@
 
-\title{\LARGE{Approximate Code: A cost-effective erasure code for multimedia applications in cloud storage systems}\\
+\title{\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\
 }
@@
 \begin{abstract}
-Erasure codes are commonly used to ensure data reliability in cloud storage systems, where multimedia data produced by live video, autopilot, social media and security monitoring occupies large amounts of space.
-Typical erasure codes, such as Reed-Solomon (RS) codes, use several parity disks to fully recover failure disks. 
-However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the multimedia data, which results in multiple complete parity disks being excessive.
+Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
+Typical erasure codes, such as Reed-Solomon (RS) codes or RAID use several parity disks to fully recover failure disks. 
+However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.
 
-Therefore, we propose Approximate Codes for multimedia data, which significantly reduce storage overhead by reducing the verification of redundant data.
+Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
 Approximate Codes provide complete recovery when fewer disks fail, and approximate recovery (recover most data) in the event of multiple disk failures.
 To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
-The results show that compared with the typical high-reliability erasure code scheme, Approximate Codes reduce the storage cost by 7.64\% at the expense of reasonable video quality loss probability.
+The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.
+
 \end{abstract}
@@
 
-Typical erasure codes schemes generate k check disks for a group of disks by calculation, which can tolerate any k disk failures in the group, such as RS-based code (RS, LRC), or XOR-based code (...).
+Typical erasure codes schemes generate k parity disks for a group of disks by calculation, which can tolerate any k disk failures in the group, such as RS-based code (RS, LRC), or XOR-based code (...).
 Other erasure codes (SD, STAIR) use the parity blocks to tolerate sector failures in addition to disk-level fault tolerance.
 
-In cloud storage systems, erasure code schemes are essential for multimedia applications.
-Applications such as the video industry, autonomous driving, social media, and security monitoring generate numerous data each day while consuming large amounts of storage resources.
-This makes it extremely expensive to guarantee multimedia data availability through replication scheme.
+Video data consumes massive space in cloud storage systems, and this trend is exacerbated as applications demand increased resolution and frame rates.
+Using multiple copies to ensure video data security will generate storage cost that are several times larger than the original data, which is obviously too expensive, while erasure codes can significantly reduce this cost.
 
-Existing erasure codes are designed to completely recover corrupted data and use at least 3 additional check disks [] to ensure data availability.
-These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of multimedia applications can tolerate a certain amount of data loss.
+Existing erasure codes are designed to completely recover corrupted data and use at least 3 additional parity disks [] to ensure data availability.
+These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of video applications can tolerate a certain amount of data loss.
 For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive.
-In addition, even if the multimedia data suffers a certain loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
+In addition, even if the video data suffers a certain loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
 
-We also find that multimedia data is typically encoded and stored to save space, while the encoded multimedia data stream is non-uniformly sensitive to data loss, which makes it unsuitable to provide uniform fault tolerance using conventional erasure codes.
-Image coding algorithms such as JPEG convert pixels to the frequency domain, making some data segments more important than others, while video coding algorithms such as H264 only store key frames (I frame) completely, so that other frames need to rely on them for calculation.
+We also find that video data is usually stored after being encoded to save space, while the encoded video data stream is non-uniformly sensitive to data loss, which makes it inappropriate to provide uniform fault tolerance using conventional erasure codes.
+With the motion compensation mechanism, common video coding algorithms such as H.264 only needs to store the complete content of key frames and a little part of other frames, which makes other frames rely on the key frames for computation while decoding.
 
-Therefore, we propose Approximate Codes for multimedia data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of n disks where m disks are dedicated to coding and another s sectors encoded for the first strip.
-This allows the data of the first stripe to tolerate any m+s disk corruption, so we specifically store important segments of multimedia data here.
-With an appropriate data distribution scheme, non-critical data segments will still retain (n-m-s)/(n-m) data when any m+s disks are lost, which makes recovery schemes such as interpolated or superpixel still effective.
+Therefore, we propose Approximate Codes for video data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors.
+In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first strip.
+This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there.
+With an appropriate data distribution scheme, non-critical data segments will still retain $(n-m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes recovery schemes such as interpolated or superpixel still effective.
 The approximate code provides two recovery modes, full recovery and approximate recovery.
-The former applies to no more than m disk corruptions and recovers all data, the latter applies to no more than m+s disk corruptions and retains important data.
+The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.
+
+\section{Related Work and Our Motivation}
+\subsection{Existing Erasure Codes}
+
+\subsection{Video Encoding}
+Video data is compressed using various formats to reduce storage costs.
+Lossy compression is a common method because it provides a much lower compression ratio than lossless compression while ensuring a tolerable loss of video quality, so we focus on this type of algorithm.
+Currently, H.264 is one of the most popular advanced algorithms in this type of work.
+H.264 is widely used on video sites such as YouTube because of its higher compression ratio and lower complexity than its predecessor.
+
+\subsection{Approximate Storage}
+\subsection{Our Motivation}
+
+\section{Approximate Code}
+\subsection{Design of Approximate Code}
+\subsection{Encoding and Decoding Processes}
+\subsection{Proof of Correctness}
+\subsection{Properties of Approximate Code}
 

### 2019-03-23 paper.tex
version 0.2: add in section 2

@@
 Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
-Typical erasure codes, such as Reed-Solomon (RS) codes or RAID use several parity disks to fully recover failure disks. 
+Typical erasure codes, such as Reed-Solomon (RS) codes or XOR-based codes use several parity disks to fully recover failure disks. 
 However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.
@@
 
-Typical erasure codes schemes generate k parity disks for a group of disks by calculation, which can tolerate any k disk failures in the group, such as RS-based code (RS, LRC), or XOR-based code (...).
+Typical erasure codes schemes can be divided into two categories such as RS-based code (RS, LRC), or XOR-based code (...).
 Other erasure codes (SD, STAIR) use the parity blocks to tolerate sector failures in addition to disk-level fault tolerance.
@@
 
-Existing erasure codes are designed to completely recover corrupted data and use at least 3 additional parity disks [] to ensure data availability.
+Existing erasure codes are designed to completely recover corrupted data.
+Typical configurations use triple disk failure tolerant arrays (3DFTS), such as Windows Azure [], which requires at least 3 parity disks.
 These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of video applications can tolerate a certain amount of data loss.
@@
 This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there.
-With an appropriate data distribution scheme, non-critical data segments will still retain $(n-m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes recovery schemes such as interpolated or superpixel still effective.
-The approximate code provides two recovery modes, full recovery and approximate recovery.
+With an appropriate data distribution scheme, non-critical data segments will still retain $(n-2m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes
+recovery schemes such as interpolated or superpixel still effective.
+The approximate codes provide two recovery modes, full recovery and approximate recovery.
 The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.
@@
 \section{Related Work and Our Motivation}
+Video data can be classified into hot data and cold data, the former requiring high availability and reliability, which often relies on expensive replication approach.
+The latter's storage usually uses erasure codes schemes, because cold data far exceeds hot data, and erasure codes can guarantee its reliability with low monetary overhead.
+However, existing erasure code schemes do not consider the characteristics of video data and are not specifically designed for them.
+
+Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
+For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
+Therefore, the encoded video data has an ununiform degree of importance, that is, it is tolerable that some of those less important data losses because the user is hard to detect.
+
+This section then introduces the relevant background and our motivation.
+
 \subsection{Existing Erasure Codes}
+RS/LRC/CLAY/SD/STAIR…
+XOR-based
+RS-based
+RAID6
+MSR
+
+\subsection{Approximate Storage}
+Approximate Storage loosen the requirement of storage reliability by allowing some quality loss of specific data, which recently receives more attentions since data centers are trading off the limited resource budget with the costly reliability requirements of ever-increasing data.
 
 \subsection{Video Encoding}
-Video data is compressed using various formats to reduce storage costs.
-Lossy compression is a common method because it provides a much lower compression ratio than lossless compression while ensuring a tolerable loss of video quality, so we focus on this type of algorithm.
-Currently, H.264 is one of the most popular advanced algorithms in this type of work.
-H.264 is widely used on video sites such as YouTube because of its higher compression ratio and lower complexity than its predecessor.
+For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
+Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.
 
-\subsection{Approximate Storage}
+H.264 is one of the advanced algorithms for this type of work.
+This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
+For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
+
 \subsection{Our Motivation}
@@
 
+\section{Evaluation}
+\subsection{An Evaluation methodology}
+\subsubsection{Erasure Codes in Our Comparisons}
+\subsubsection{Platforms and Configurations}
+\subsubsection{Metrics}
+\subsubsection{Parameters and Assumption in Our Evaluation}
+
+\subsection{Results}
+\subsection{Analysis}
+Illustrate why Approximate Code achieve high reliability with low cost
+\section{Conclusion}
 \section*{Acknowledgment}

### 2019-03-25 paper.tex
version 0.2.2 merge and add test figure

@@
 For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an ununiform degree of importance, that is, it is tolerable that some of those less important data losses because the user is hard to detect.
+Therefore, the encoded video data has an uneven degree of importance, that is, it is tolerable that some of those less important data losses because the users are hard to detect.
+On the other hand, loss of important data will have more serious consequences.
 
@@
 
-\subsection{Video Encoding}
+\subsection{Video Storage}
 For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
@@
 \subsection{Our Motivation}
+Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
+However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
+Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
+To solve these two problems, we propose a new erasure code called approximation code.
+It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.
 
 \section{Approximate Code}
+In a system of $n$ disks, each disk can be divided into multiple sectors.
+We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a chunk.
+The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{TEST-chunk-sector} .
+We also use the term symbol in coding theory to refer to sectors.
+Since each strip is independent of the entire system, we only consider a single strip.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.4\textwidth]{photo/TEST-chunk-sector.JPG}
+\caption{TEST--A sample of chunk and sector}
+\label{TEST-chunk-sector}
+\end{figure}
+
+In the $n$ chunks of each stripe, we use $m$ parity chunks, and there are $s \times t$ additional symbols in the remaining $n-m$ chunks for encoding.
+Our goal is to provide different reliability for important and general data, so we assume that normal data can tolerate damage of up to $m$ chunks, while important data can tolerate damage of up to $m+s$ chunks.
+Figure \ref{TEST-apcode-74222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-74222.JPG}
+\caption{TEST--A sample of Approximate Code with n = 7, r = 4, m = 2, t=2 and s = 2.}
+\label{TEST-apcode-74222}
+\end{figure}
+
 \subsection{Design of Approximate Code}

### 2019-03-25 paper.tex
version 0.2.1 add motivation

--- 2019-03-23 paper.tex
@@
 \subsection{Our Motivation}
+Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
+However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
+Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
+To solve these two problems, we propose a new erasure code called approximation code.
+It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.
 
 \section{Approximate Code}
+
 \subsection{Design of Approximate Code}

### 2019-03-25 paper.tex
version 0.2.2.0

--- 2019-03-25 paper.tex
@@
 For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an uneven degree of importance, that is, it is tolerable that some of those less important data losses because the users are hard to detect.
-On the other hand, loss of important data will have more serious consequences.
+Therefore, the encoded video data has an ununiform degree of importance, that is, it is tolerable that some of those less important data losses because the user is hard to detect.
 
@@
 \subsection{Our Motivation}
-Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
-First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
-However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
-Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
-To solve these two problems, we propose a new erasure code called approximation code.
-It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.
 

### 2019-03-25 paper.tex
version 0.3.1 code design but with errors

--- 2019-03-25 paper.tex
@@
 Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
-Typical erasure codes, such as Reed-Solomon (RS) codes or XOR-based codes use several parity disks to fully recover failure disks. 
+Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to fully recover failure disks. 
 However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.
@@
 \subsection{Existing Erasure Codes}
-RS/LRC/CLAY/SD/STAIR…
+RS/LRC/CLAY/SD/STAIR???
+
 XOR-based
+
 RS-based
+
 RAID6
+
 MSR
@@
 \subsection{Our Motivation}
-Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+Based on Table [], the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
 First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
@@
 Our goal is to provide different reliability for important and general data, so we assume that normal data can tolerate damage of up to $m$ chunks, while important data can tolerate damage of up to $m+s$ chunks.
-Figure \ref{TEST-apcode-74222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
+Figure \ref{TEST-apcode-75222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
 \begin{figure}[ht]
 \centering
-\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-74222.JPG}
-\caption{TEST--A sample of Approximate Code with n = 7, r = 4, m = 2, t=2 and s = 2.}
-\label{TEST-apcode-74222}
+\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-75222.JPG}
+\caption{TEST--A sample of Approximate Code with n = 7, r = 5, m = 2, t=2 and s = 2.}
+\label{TEST-apcode-75222}
 \end{figure}
@@
 \subsection{Design of Approximate Code}
+We label $n$ disks from $D_0$ to $D_{n-1}$.
+Among them, $D_{n-m}$ to $D_{n-1}$ are parity disks.
+We label the data disks with $d_{i,j}$, the important data parity sectors with $x_{i,j}$ and the normal parity check sectors with $y_{i,j}$.
+The following equation represents the method to calculate $x_{i,j}$, $y_{i,j}(i<t)$ and $y_{i,j}(i \geqslant t)$
+
+\begin{equation}
+    x_{i,j} = \sum_{k=0}^{n-m-s-1} \alpha_k^{j+1} d_{i,k}
+\end{equation}
+\begin{equation}
+    \mathop{y_{i,j}}\limits_{i<t} = \sum_{k=0}^{n-m-s-1} \alpha_k^{s+j+1} d_{i,k}
+\end{equation}
+
 \subsection{Encoding and Decoding Processes}

### 2019-03-26 paper.tex
version 0.3.2 add pictures and equations

@@
 recovery schemes such as interpolated or superpixel still effective.
-The approximate codes provide two recovery modes, full recovery and approximate recovery.
+The Approximate Codes provide two recovery modes, full recovery and approximate recovery.
 The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.
@@
 \section{Approximate Code}
+In this section, we introduce the design of Approximate Codes and its properties through a simple example.
+In order to be general and easy to describe, we use fewer data blocks and more parity blocks (resulting in greater storage overhead).
+A more optimized parameter selection scheme for practical applications will be introduced in XXX.
+
+\subsection{Design of Approximate Code}
 In a system of $n$ disks, each disk can be divided into multiple sectors.
@@
 
-In the $n$ chunks of each stripe, we use $m$ parity chunks, and there are $s \times t$ additional symbols in the remaining $n-m$ chunks for encoding.
-Our goal is to provide different reliability for important and general data, so we assume that normal data can tolerate damage of up to $m$ chunks, while important data can tolerate damage of up to $m+s$ chunks.
-Figure \ref{TEST-apcode-75222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
-\begin{figure}[ht]
+In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
+Our design assumes that the parameters  $(n, m, s,t)$ are user-defined configurable parameters so the constructor of the Approximate Code will be determined by these 4 parameters.
+For convenience, we label $h=n-m-s$ as the number of columns of important data.
+We choose the value of $r$ according to equation $r=s+h$, which will be explained in \ref{Data Distribution}.
+Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$,$m = 2$ , $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
+
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-75222.JPG}
-\caption{TEST--A sample of Approximate Code with n = 7, r = 5, m = 2, t=2 and s = 2.}
-\label{TEST-apcode-75222}
+\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
+\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data.
+In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
+\label{apcode-7222-v2}
 \end{figure}
 
-\subsection{Design of Approximate Code}
-We label $n$ disks from $D_0$ to $D_{n-1}$.
-Among them, $D_{n-m}$ to $D_{n-1}$ are parity disks.
-We label the data disks with $d_{i,j}$, the important data parity sectors with $x_{i,j}$ and the normal parity check sectors with $y_{i,j}$.
-The following equation represents the method to calculate $x_{i,j}$, $y_{i,j}(i<t)$ and $y_{i,j}(i \geqslant t)$
+\subsubsection{Encoding Process}
+We explain the encoding process through Figure \ref{apcode-7222-v2}, which shows the two encoding phases of Approximate Codes.
 
-\begin{equation}
-    x_{i,j} = \sum_{k=0}^{n-m-s-1} \alpha_k^{j+1} d_{i,k}
+\textbf{Phase 1:} Encode important data sectors based on Galois Field (GF).
+Phase 1 generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF.
+For example, $q_{0,0} = \alpha_0 d_{0,0} + \alpha_1 d_{0,1} + \alpha_2 d_{0,2}$ and 
+$q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$
+
+\textbf{Phase 2:} Generate $m$ parity chunks from $h+s$ chunks consist of data sectors and important parity sectors.
+
+ , $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$
+
+\begin{equation}\label{q_ij}
+    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
 \end{equation}
 \begin{equation}
-    \mathop{y_{i,j}}\limits_{i<t} = \sum_{k=0}^{n-m-s-1} \alpha_k^{s+j+1} d_{i,k}
+    \mathop{p_{i,j}}\limits_{i<t} = 
+    \sum_{k=0}^{h-1} \alpha_k^{s+j+1} d_{i,k} +
+    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j+1} q_{i,l}
+\end{equation}
+\begin{equation}
+    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
+    \sum_{k=0}^{n-m-1} \alpha_k^{s+j+1} d_{i,k}
 \end{equation}
 
-\subsection{Encoding and Decoding Processes}
 \subsection{Proof of Correctness}
+\subsection{Data Distribution}\label{Data Distribution}
 \subsection{Properties of Approximate Code}

### 2019-03-27 paper.tex
version 0.3.2.1

@@
 In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
-Our design assumes that the parameters  $(n, m, s,t)$ are user-defined configurable parameters so the constructor of the Approximate Code will be determined by these 4 parameters.
-For convenience, we label $h=n-m-s$ as the number of columns of important data.
-We choose the value of $r$ according to equation $r=s+h$, which will be explained in \ref{Data Distribution}.
-Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$,$m = 2$ , $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
+Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
+Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
+The relevant instructions will be shown in \ref{Data Distribution}.
+Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
+
+Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
 
@@
 \subsubsection{Encoding Process}
-We explain the encoding process through Figure \ref{apcode-7222-v2}, which shows the two encoding phases of Approximate Codes.
+The encoding process can be divided into two phases: important coding phase and global coding phase. We us RS code to generate both important parity sectors and global parity sectors.
 
-\textbf{Phase 1:} Encode important data sectors based on Galois Field (GF).
-Phase 1 generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF.
-For example, $q_{0,0} = \alpha_0 d_{0,0} + \alpha_1 d_{0,1} + \alpha_2 d_{0,2}$ and 
-$q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$
+\emph{Phase 1} Encode important data sectors based on Galois Field (GF) and generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF.
+According to Figure \ref{apcode-7222-v2}, Phase 1 use RS(5,3).
+For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$
 

### 2019-03-27 paper.tex
'frameinterpolation2'

@@
 
+\subsection{Video Frame Recovery: Frame Interpolation}
+In the circumstance of data loss, it's common to lose some frames and then the video is not complete.
+One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates.
+Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.
+
+Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames.
+This is a technique that can model natural motion within a video, and generate frames according to this modelling.
+Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
+Optical flow is commonly addressed in the video frame interpolation problem.
+Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene.
+Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.
+
+Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{b1}\cite{b2}\cite{b3}.
+These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color.
+Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation.
+In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{b6}\cite{b7}.
+Among them, a multi-scale network\cite{b4} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{b5} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.
+
+All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
+However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames.
+Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.
+
 \subsection{Our Motivation}
@@
 \section*{Acknowledgment}
-
+\begin{thebibliography}{00}
+\bibitem{b1} Piotr Didyk, Pitchaya Sitthi-Amorn, William T. Freeman, Fr¨¦do Durand, Wojciech Matusik
+Joint View Expansion and Filtering for Automultiscopic 3D Displays
+ACM Transactions on Graphics 32(6) (Proceedings SIGGRAPH Asia 2013, Hong Kong), 2013
+\bibitem{b2} Neal Wadhwa, Michael Rubinstein, Fr¨¦do Durand, and William T.
+Freeman.
+2013.
+Phase-based video motion processing.
+ACM Trans.
+Graph.
+32, 4, Article 80 (July 2013), 10 pages.
+DOI: https://doi.org/10.1145/2461912.2461966
+\bibitem{b3} Meyer, Simone et al. ¡°Phase-based frame interpolation for video.¡± 2015 IEEE Conference on Computer Vision and Pattern Recognition (CVPR) (2015): 1410-1418.
+\bibitem{b4} Joost van Amersfoort, Joost $\&$ Shi, Wenzhe $\&$ Acosta, Alejandro $\&$ Massa, Francisco $\&$ Totz, Johannes $\&$ Wang, Zehan $\&$ Caballero, Jose.
+(2017).
+Frame Interpolation with Multi-Scale Deep Loss Functions and Generative Adversarial Networks.
+\bibitem{b5} Niklaus, Simon $\&$ Liu, Feng. (2018). Context-aware Synthesis for Video Frame Interpolation.
+\bibitem{b6} Fischer, Philipp et al. ¡°FlowNet: Learning Optical Flow with Convolutional Networks.¡± 2015 IEEE International Conference on Computer Vision (ICCV) (2015): 2758-2766.
+\bibitem{b7} Ilg, Eddy Mayer, Nikolaus Saikia, Tonmoy Keuper, Margret Dosovitskiy, Alexey Brox, Thomas. (2016). FlowNet 2.0: Evolution of Optical Flow Estimation with Deep Networks.
+\end{thebibliography}
 \bibliographystyle{IEEEtrans}
-\bibliography{paper}
 

### 2019-03-27 paper.tex
version 0.3.2.2

--- 2019-03-27 paper.tex
@@
 
-\usepackage[T1]{fontenc}
-\usepackage{mathptmx}
+%\usepackage[T1]{fontenc}
+%\usepackage{mathptmx}
 \soulregister\cite7
@@
 Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
-
 Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
 
-\begin{figure}[t]
+\begin{figure}[ht]
 \centering
@@
 
+A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
+\hl{Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section }\ref{evaluation}.
+
 \subsubsection{Encoding Process}
-The encoding process can be divided into two phases: important coding phase and global coding phase. We us RS code to generate both important parity sectors and global parity sectors.
+The encoding process can be divided into two phases: important coding phase and global coding phase.
 
-\emph{Phase 1} Encode important data sectors based on Galois Field (GF) and generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF.
-According to Figure \ref{apcode-7222-v2}, Phase 1 use RS(5,3).
-For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$
-
-\textbf{Phase 2:} Generate $m$ parity chunks from $h+s$ chunks consist of data sectors and important parity sectors.
-
- , $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$
-
+In \emph{phase 1}, we use RS$(h+s,h)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$.
+The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF).
+For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
+As shown in the blod box in Figure \ref{apcode-7222-v2}, we use RS(5,3) in this phase.
 \begin{equation}\label{q_ij}
@@
 \end{equation}
-\begin{equation}
+
+In \emph{phase 2}, we use RS$(n,n-m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors.
+The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
+Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
+For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
+As shown in orange chunks in Figure \ref{apcode-7222-v2}, we use RS(7,5) in this phase.
+
+\begin{equation}\label{p_ij_1}
     \mathop{p_{i,j}}\limits_{i<t} = 
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{p_ij_2}
     \mathop{p_{i,j}}\limits_{i \geqslant t} = 
@@
 
-\section{Evaluation}
+\section{Evaluation}\label{evaluation}
 \subsection{An Evaluation methodology}

### 2019-03-28 paper.tex
version 0.4 change to ACM format

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+%\documentclass[conference]{IEEEtran}
+\documentclass[sigconf]{acmart}
+
 \usepackage{cite}
@@
 
+\usepackage{booktabs}
+
 %\usepackage[T1]{fontenc}
 %\usepackage{mathptmx}
-\soulregister\cite7
-\soulregister\ref7
-\pagestyle{plain}
+%\soulregister\cite7
+%\soulregister\ref7
+%\pagestyle{plain}
 
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 }
-\author{\IEEEauthorblockN{Huayi Jin$^1$}
-}
+\author{Huayi Jin$^1$}
 
@@
 
-\begin{IEEEkeywords}
+\begin{keywords}
     Erasure Codes, Approximate Storage, Multimedia, Cloud Storage
-\end{IEEEkeywords}
+\end{keywords}
 
@@
 
+\textcolor{red}
+{Sixth paragraph:
+Contribution of this paper, typically two or three contributions,
+(1)	Propose a novel code Approximate Code
+(2)	Give some mathematical proof to demonstrate the correctness of Approximate Code
+(3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}
+
+\begin{table*}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & Computational Complexity \\ \hline
+RS Code & any m disks & m disks & high & high & high \\ \hline
+LRC Code & up to m disks & m global disks and r local disks & high & medium & medium \\ \hline
+MSR Code & any m disks & m disks & medium & low & very high \\ \hline
+Raid 6 & 2 & 2 & low & high & low \\ \hline
+SD Code & m disks and s sectors & m disks and s sectors & low & low & low \\ \hline
+Approximate Code(Important) & m+s disks & m disks and s sectors & high & high & medium to high \\ \hline
+Approximate Code(Ordinary) & m disks & m disks and s sectors & high & high & medium to high \\ \hline
+\end{tabular}
+\end{table*}
+
+\textcolor{red}
+{Seventh paragraph:
+organization of the paper}
+
 \section{Related Work and Our Motivation}
@@
 \subsection{Existing Erasure Codes}
-RS/LRC/CLAY/SD/STAIR???
 
-XOR-based
+\textcolor{red}{Here we give some introduction to existing erasure codes
+Specifically, we need to illustrate the existing erasure codes for video applications in detail.
+Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}
 
-RS-based
-
-RAID6
-
-MSR
-
-\subsection{Approximate Storage}
-Approximate Storage loosen the requirement of storage reliability by allowing some quality loss of specific data, which recently receives more attentions since data centers are trading off the limited resource budget with the costly reliability requirements of ever-increasing data.
-
-\subsection{Video Storage}
+\subsection{Video Storage}\label{video storage}
 For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
 Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
+\caption{A sample of GOPs in H.264}
+\label{H264-IPB}
+\end{figure}
 
@@
 For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
+
+\textcolor{red}{Something about H.264\dots}
+
+\subsection{Approximate Storage}
+Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
+
+It loosens the requirement of storage reliability by allowing some quality loss of specific data.
+Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
+The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices.
+Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
+
+However, it is too naive to store data in approximate storage units indiscriminately.
+Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
+To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
+
+In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
+An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable.
+In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.
 
@@
 Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
-Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
+Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
+\includegraphics[width=0.45\textwidth]{photo/apcode-7222-v5.PDF}
 \caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data.
 In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
-\label{apcode-7222-v2}
+\label{apcode-7222-v5}
 \end{figure}
@@
 For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
-As shown in the blod box in Figure \ref{apcode-7222-v2}, we use RS(5,3) in this phase.
+As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(5,3) in this phase.
 \begin{equation}\label{q_ij}
@@
 For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
-As shown in orange chunks in Figure \ref{apcode-7222-v2}, we use RS(7,5) in this phase.
+As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(7,5) in this phase.
 
@@
 \end{equation}
+
+\subsubsection{Decoding Process}
+The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover
 
@@
 
-\bibliographystyle{IEEEtrans}
-\bibliography{paper}
-
 \end{document}

### 2019-03-28 paper.tex
Update paper.tex

--- 2019-03-27 paper.tex
@@
 
-%\usepackage[T1]{fontenc}
-%\usepackage{mathptmx}
+\usepackage[T1]{fontenc}
+\usepackage{mathptmx}
 \soulregister\cite7
@@
 Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
-Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to fully recover failure disks. 
-However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.
+Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to equally back up all data.
+However, this is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to the ignorance of redundant information inside the data, which results in multiple complete parity disks being excessive.
 
 Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
-Approximate Codes provide complete recovery when fewer disks fail, and approximate recovery (recover most data) in the event of multiple disk failures.
+Approximate Codes provide complete recovery when fewer disks fail, and ensure approximate recovery (recover most data) in the event of multiple disk failures.
 To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
@@
 For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive.
-In addition, even if the video data suffers a certain loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
+In addition, even if the video data suffers a certain amount of loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
 
@@
 For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an uneven degree of importance, that is, it is tolerable that some of those less important data losses because the users are hard to detect.
+Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
 On the other hand, loss of important data will have more serious consequences.
@@
 
-\subsection{Approximate Storage}
-Approximate Storage loosen the requirement of storage reliability by allowing some quality loss of specific data, which recently receives more attentions since data centers are trading off the limited resource budget with the costly reliability requirements of ever-increasing data.
-
-\subsection{Video Storage}
+\subsection{Video Storage}\label{video storage}
 For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
 Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
+\caption{A sample of GOPs in H.264}
+\label{H264-IPB}
+\end{figure}
 
@@
 For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
+
+\subsection{Approximate Storage}
+Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
+
+It loosens the requirement of storage reliability by allowing some quality loss of specific data.
+Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
+The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices.
+Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
+
+However, it is too naive to store data in approximate storage units indiscriminately.
+Related research [] shows that this can lead to unacceptable data pollution.
+To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
+
+In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
+An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable.
+In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.
+
+\subsection{Video Frame Recovery: Frame Interpolation}
+In the circumstance of data loss, it's common to lose some frames and then the video is not complete.
+One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates.
+Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.
+
+Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames.
+This is a technique that can model natural motion within a video, and generate frames according to this modelling.
+Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
+Optical flow is commonly addressed in the video frame interpolation problem.
+Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene.
+Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.
+
+Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{didyk2013joint}\cite{wadhwa2013phase}\cite{meyer2015phase}.
+These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color.
+Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation.
+In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{dosovitskiy2015flownet}\cite{ilg2017flownet}.
+Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.
+
+All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
+However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames.
+Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.
 
@@
 Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
-Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
+Figure \ref{apcode-7222-v4} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
+\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v4.PDF}
 \caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data.
 In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
-\label{apcode-7222-v2}
+\label{apcode-7222-v4}
 \end{figure}

### 2019-03-28 ApproximareCode.tex
change the fucking format from IEEE to ACM

--- 2019-03-28 paper.tex
@@
-%\documentclass[conference]{IEEEtran}
 \documentclass[sigconf]{acmart}
-
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{subfigure}
-\usepackage{ntheorem}
-\usepackage{enumerate}
-\usepackage[bottom]{footmisc}
-\usepackage{soul}
-
-\usepackage{booktabs}
-
-%\usepackage[T1]{fontenc}
-%\usepackage{mathptmx}
-%\soulregister\cite7
-%\soulregister\ref7
-%\pagestyle{plain}
 
@@
 
-\title{\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\
-}
-\author{Huayi Jin$^1$}
+\title{Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems}
 
-\maketitle
+\author{Huayi Jin}
 
@@
 The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.
-
 \end{abstract}
 
-\begin{keywords}
-    Erasure Codes, Approximate Storage, Multimedia, Cloud Storage
-\end{keywords}
+%
+% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+% Please copy and paste the code instead of the example below.
+%
+\keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}
+
+\maketitle
 
@@
 A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
-\hl{Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section }\ref{evaluation}.
+\textcolor{red}{Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section }\ref{evaluation}.
 
@@
 \section{Conclusion}
-\section*{Acknowledgment}
+
+%
+% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
+% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
+\begin{acks}
+To Robert, for the bagels and explaining CMYK and color spaces.
+\end{acks}
+
+%
+% The next two lines define the bibliography style to be used, and the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{ApproximareCode}
 

### 2019-03-29 paper.tex
Update paper.tex

@@
 To solve these two problems, we propose a new erasure code called approximation code.
-It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.
+It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.
 
@@
 In this section, we introduce the design of Approximate Codes and its properties through a simple example.
-In order to be general and easy to describe, we use fewer data blocks and more parity blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in XXX.
+For convenience of description and without loss of generalizability, we first use fewer data blocks and more parity blocks (resulting in greater storage overhead) and a more optimized parameter selection scheme for practical applications will be introduced later in XXX.
 

### 2019-03-30 ApproximareCode.tex
version 0.4.1

@@
 \author{Huayi Jin}
+
+%-------------------------ATTANTION-------------------------%
+%                                                           %
+% red words should be removed or rewrite in later version   %
+% blue words need to be perfected or filled                 %
+%                                                           %
+%-----------------------------------------------------------%
 
@@
 \section{Approximate Code}
-In this section, we introduce the design of Approximate Codes and its properties through a simple example.
-In order to be general and easy to describe, we use fewer data blocks and more parity blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in XXX.
+In this section, we introduce the design of Approximate Codes and its properties through a few simple examples.
+In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead).
+A more optimized parameter selection scheme for practical applications will be introduced in \textcolor{blue}{XXXXX}.
 
@@
 In a system of $n$ disks, each disk can be divided into multiple sectors.
-We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a chunk.
+We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a \emph{chunk}.
 The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{TEST-chunk-sector} .
@@
 \includegraphics[width=0.4\textwidth]{photo/TEST-chunk-sector.JPG}
-\caption{TEST--A sample of chunk and sector}
+\caption{\textcolor{blue}{TEST--}A sample of chunk and sector}
 \label{TEST-chunk-sector}
@@
 
-In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
-Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
-Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
-The relevant instructions will be shown in \ref{Data Distribution}.
-Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
+In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
+We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-7222-v5}.
+For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
+Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in \ref{Data Distribution}.
+
+Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
 Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.45\textwidth]{photo/apcode-7222-v5.PDF}
-\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data.
-In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
+\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange blocks) and 4 other sectors (red blocks) are designed for encoding important data.
+In this example, there are 6 sectors (dark blue blocks) for important data and 15 sectors (light blue blocks) for normal data.}
 \label{apcode-7222-v5}
@@
 
-A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
-\textcolor{red}{Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section }\ref{evaluation}.
+\textcolor{red}{A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
+Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section XXXXX}.
 
-\subsubsection{Encoding Process}
-The encoding process can be divided into two phases: important coding phase and global coding phase.
+In general, Approximate Code performs extra parities on important data.
+Since our design guarantees the important data, the important parity and the normal data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
+Therefore, EC methods such as RS-based codes, XOR-based codes or MSR codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.
 
-In \emph{phase 1}, we use RS$(h+s,h)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$.
+\subsection{Encoding and Decoding Process}
+
+The encoding process can be divided into two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (G-Phase). . .
+
+In \emph{I-Phase}, $s$ groups of important parity sectors are generated
+
+The decoding process can be divided into two modes: the approximate recovery mode (A-model) and the full recovery mode (F-model). . .
+
+\textcolor{blue}{We introduce RS-based and XOR-based Approximate Code due to space limitations}
+\subsubsection{RS-based Approximate Code}
+
+In \emph{phase 1}, we use RS$(h,s)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$.
 The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF).
-For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
-As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(5,3) in this phase.
+For example, $q_{1,1} = \alpha_0 d_{1,0} + \alpha_1 d_{1,1} + \alpha_2 d_{1,2}$.
+As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(3,2) in this phase.
 \begin{equation}\label{q_ij}
-    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
+    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j} d_{i,k}
 \end{equation}
 
-In \emph{phase 2}, we use RS$(n,n-m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors.
+In \emph{phase 2}, we use RS$(n-m,m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors.
 The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
 Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
-For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
-As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(7,5) in this phase.
+For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.
+As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(5,2) in this phase.
 
@@
     \mathop{p_{i,j}}\limits_{i<t} = 
-    \sum_{k=0}^{h-1} \alpha_k^{s+j+1} d_{i,k} +
-    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j+1} q_{i,l}
+    \sum_{k=0}^{h-1} \alpha_k^{s+j} d_{i,k} +
+    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j} q_{i,l}
 \end{equation}
@@
     \mathop{p_{i,j}}\limits_{i \geqslant t} = 
-    \sum_{k=0}^{n-m-1} \alpha_k^{s+j+1} d_{i,k}
+    \sum_{k=0}^{n-m-1} \alpha_k^{s+j} d_{i,k}
 \end{equation}
@@
 \subsubsection{Decoding Process}
-The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover
+The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover.
 

### 2019-03-30 ApproximareCode.tex
version 4.1

--- 2019-03-28 ApproximareCode.tex
@@
 
-\begin{table*}[]
+\begin{table*}[ht]
 \centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & Computational Complexity \\ \hline
-RS Code & any m disks & m disks & high & high & high \\ \hline
-LRC Code & up to m disks & m global disks and r local disks & high & medium & medium \\ \hline
-MSR Code & any m disks & m disks & medium & low & very high \\ \hline
-Raid 6 & 2 & 2 & low & high & low \\ \hline
-SD Code & m disks and s sectors & m disks and s sectors & low & low & low \\ \hline
-Approximate Code(Important) & m+s disks & m disks and s sectors & high & high & medium to high \\ \hline
-Approximate Code(Ordinary) & m disks & m disks and s sectors & high & high & medium to high \\ \hline
+\caption{Summary on Various Erasure Codes}
+\begin{tabular}{@{}cccccc@{}}
+\toprule
+Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \midrule
+RS($k,r$) Code & any $r$ disks & $r$ disks & high & high & high \\
+LRC($k,l,r$) Code & $r+1$ to $r+l$ disks & $l+r$ disks & high & medium & medium \\
+MSR($k,r$) Code & any $m$ disks & $m$ disks & medium & low & very high \\
+Raid 6 & 2 & 2 & low & high & low \\
+SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Ordinary Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \bottomrule
 \end{tabular}
@@
 \centering
-\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
+\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
 \caption{A sample of GOPs in H.264}
@@
 \section{Approximate Code}
-In this section, we introduce the design of Approximate Codes and its properties through a simple example.
-In order to be general and easy to describe, we use fewer data blocks and more parity blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in XXX.
+In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
+In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead).
+A more optimized parameter selection scheme for practical applications will be introduced in \ref{evaluation}.
 

### 2019-03-30 ApproximareCode.tex
version 0.4.2.1 a little change

--- 2019-03-30 ApproximareCode.tex
@@
 
-\begin{table*}[]
+\begin{table*}[ht]
 \centering
+\caption{Summary on Various Erasure Codes}
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
-Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & Computational Complexity \\ \hline
-RS Code & any m disks & m disks & high & high & high \\ \hline
-LRC Code & up to m disks & m global disks and r local disks & high & medium & medium \\ \hline
-MSR Code & any m disks & m disks & medium & low & very high \\ \hline
+Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
+RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
+MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
 Raid 6 & 2 & 2 & low & high & low \\ \hline
-SD Code & m disks and s sectors & m disks and s sectors & low & low & low \\ \hline
-Approximate Code(Important) & m+s disks & m disks and s sectors & high & high & medium to high \\ \hline
-Approximate Code(Ordinary) & m disks & m disks and s sectors & high & high & medium to high \\ \hline
+SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Ordinary Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
 \end{tabular}
@@
 \section{Approximate Code}
-In this section, we introduce the design of Approximate Codes and its properties through a few simple examples.
+In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
 In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in \textcolor{blue}{XXXXX}.
+A more optimized parameter selection scheme for practical applications will be introduced in Section \ref{evaluation}.
 
@@
 
-The encoding process can be divided into two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (G-Phase). . .
+The encoding process can be divided into two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). . .
 

### 2019-03-30 ApproximareCode.tex

--- 2019-03-30 ApproximareCode.tex
@@
 
+\subsection{Video Frame Recovery: Frame Interpolation}
+In the circumstance of data loss, it's common to lose some frames and then the video is not complete.
+One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates.
+Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.
+
+Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames.
+This is a technique that can model natural motion within a video, and generate frames according to this modelling.
+Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
+Optical flow is commonly addressed in the video frame interpolation problem.
+Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene.
+Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.
+
+Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{didyk2013joint}\cite{wadhwa2013phase}\cite{meyer2015phase}.
+These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color.
+Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation.
+In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{dosovitskiy2015flownet}\cite{ilg2017flownet}.
+Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.
+
+All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
+However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames.
+Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.
+
 \subsection{Our Motivation}
@@
 In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
-In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead).
+For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
 A more optimized parameter selection scheme for practical applications will be introduced in \ref{evaluation}.

### 2019-03-30 ApproximareCode.tex

--- 2019-03-30 ApproximareCode.tex
@@
 In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
-In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in Section \ref{evaluation}.
+For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
+A more optimized parameter selection scheme for practical applications will be introduced in \ref{evaluation}.
 

### 2019-03-30 ApproximateCode.tex
version 0.4.5

--- 2019-03-30 ApproximareCode.tex
@@
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage{subfigure}
 
@@
 \begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Ordinary Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
 \end{tabular}
@@
 
+\textcolor{red}{We define I frames are our important data}
+
 \subsection{Video Frame Recovery: Frame Interpolation}
+\textcolor{red}{Add something related to the former subsection}
+
+\textcolor{blue}{In the circumstance of video approximate storage, it's common to lose some minor data making the video incomplete...}
+
 In the circumstance of data loss, it's common to lose some frames and then the video is not complete.
@@
 
-All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
+\textcolor{blue}{All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
 However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames.
-Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.
+Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.}
 
@@
 Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.
+Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
-\begin{figure}[htbp]
+We then define the set of sectors as follows:
+\begin{itemize}
+    \item Important data sector set $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$
+    \item Minor data sector set $D_M=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < n-m \}$
+    \item Important parity sector set $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$
+    \item Global parity sector set $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$
+\end{itemize}
+
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{photo/apcode-7222-v5.PDF}
-\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange blocks) and 4 other sectors (red blocks) are designed for encoding important data.
-In this example, there are 6 sectors (dark blue blocks) for important data and 15 sectors (light blue blocks) for normal data.}
+
+\subfigure[sector label and encoding process]{
+    \includegraphics[width=0.32\textwidth]{photo/apcode-7222-v5.PDF}
+    \label{apcode-7222-v5-a}
+}
+\subfigure[sector sets]{
+    \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
+    \label{apcode-7222-v5-b}
+}
+\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and 4 other sectors (red set $Q$) are designed for encoding important data.
+In this example, there are 6 sectors (dark blue set $D_I$) for important data and 15 sectors (light blue set $D_M$) for minor data.}
 \label{apcode-7222-v5}
@@
 In general, Approximate Code performs extra parities on important data.
-Since our design guarantees the important data, the important parity and the normal data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
+Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
 Therefore, EC methods such as RS-based codes, XOR-based codes or MSR codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.
@@
 \subsection{Encoding and Decoding Process}
+In this section, we use Figure \ref{apcode-7222-v5} to illustrate the encoding and decoding process of Approximate Code(7,2,2,2).
 
-The encoding process can be divided into two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). . .
+The encoding process consists of two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). 
+The \emph{I-Phase} is expressed as two red arrows in the blod box, where $Q$ is generated to verify $D_I$, and
+the \emph{G-Phase} is expressed as a yellow triangle arrow, where $G$ is generated to verify $D_I$, $D_M$ and $Q$.
 
-In \emph{I-Phase}, $s$ groups of important parity sectors are generated
+The decoding process provides two modes: the approximate recovery mode and the full recovery mode.
+When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data.
+It should be noted that in the calculation of $G$ in \emph{G-Phase} and in the decoding process in full recovery mode, we consider $D_I$, $D_M$ and $Q$ as the same, so the minimum coding unit is chunk.
+When the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.
 
-The decoding process can be divided into two modes: the approximate recovery mode (A-model) and the full recovery mode (F-model). . .
-
-\textcolor{blue}{We introduce RS-based and XOR-based Approximate Code due to space limitations}
+\textcolor{blue}{We then introduce RS-based and XOR-based Approximate Code}
 \subsubsection{RS-based Approximate Code}
 
-In \emph{phase 1}, we use RS$(h,s)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$.
+In \emph{I-Phase}, we use RS(3,2) to encode 3 groups of important data sectors and generate 2 groups of parity sectors labeled with $q_{i,j}$.
 The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF).
+The coding coefficient matrix is transformed from the Vandermonde matrix by elementary transformation.
+\textcolor{blue}{Coding matrix?}
+
+\iffalse
+\begin{equation}
+\begin{pmatrix} 
+1&  1&  1\\
+\alpha_0 & \alpha_1 & \alpha_2 \\
+\alpha_0^2+\alpha_3^2+\alpha_4^2*\alpha_0 & \alpha_1^2 +\alpha_3^2+\alpha_4^2*\alpha_1 & \alpha_2^2+\alpha_3^2+\alpha_4^2*\alpha_2  \\
+\alpha_0^3+\alpha_3^3+\alpha_4^3*\alpha_0 & \alpha_1^3 +\alpha_3^3+\alpha_4^3*\alpha_1 & \alpha_2^3+\alpha_3^3+\alpha_4^3*\alpha_2  \\
+\end{pmatrix} 
+\end{equation}
+\fi
+
 For example, $q_{1,1} = \alpha_0 d_{1,0} + \alpha_1 d_{1,1} + \alpha_2 d_{1,2}$.
-As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(3,2) in this phase.
 \begin{equation}\label{q_ij}
@@
 
-In \emph{phase 2}, we use RS$(n-m,m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors.
+In \emph{I-Phase}, we use RS(5,2) to generate 2 parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors.
 The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
-Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
 For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.
-As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(5,2) in this phase.
 
@@
     \sum_{k=0}^{h-1} \alpha_k^{s+j} d_{i,k} +
-    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j} q_{i,l}
+    \sum_{k=0}^{s-1} \alpha_{k+h}^{s+j} q_{i,k}
 \end{equation}
@@
 
-\subsubsection{Decoding Process}
-The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover.
+The full recovery decoding process of RS-based Approximate Code is obvious since it is the same as the decoding process of RS(5,2).
+For the approximate decoding process, there are 4 independent equations that can tolerate any 4 disk failures because the coding coefficient matrix is full rank.
 
@@
 \subsection{Data Distribution}\label{Data Distribution}
+
 \subsection{Properties of Approximate Code}
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{ApproximareCode}
+\bibliography{ApproximateCode}
 

### 2019-03-31 ApproximateCode.test.tex
First draft of Approximate Code, Version1

--- 2019-03-30 ApproximateCode.tex
@@
 %                                                           %
-% red words should be removed or rewrite in later version   %
-% blue words need to be perfected or filled                 %
+% orange words show the content that requires to be add     %
+% blue words need to be perfected or changed                %
+% gray words are the placeholder which is easy to fill      %
 %                                                           %
@@
 
-\textcolor{red}
+\textcolor{orange}
 {Sixth paragraph:
@@
 (3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}
+
+\textcolor{orange}
+{Seventh paragraph:
+organization of the paper}
+
+\textcolor{gray}{
+    hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello
+}
 
@@
 
-\textcolor{red}
-{Seventh paragraph:
-organization of the paper}
-
 \section{Related Work and Our Motivation}
@@
 
-\textcolor{red}{Here we give some introduction to existing erasure codes
+\textcolor{orange}{Here we give some introduction to existing erasure codes
 Specifically, we need to illustrate the existing erasure codes for video applications in detail.
 Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}
+
+\textcolor{gray}{
+    hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello
+}
 
@@
 
-\textcolor{red}{Something about H.264\dots}
+\textcolor{orange}{Something about H.264\dots}
+
+\textcolor{gray}{
+    hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello
+}
 
@@
 
-\textcolor{red}{We define I frames are our important data}
+\textcolor{orange}{We define I frames are our important data}
 
 \subsection{Video Frame Recovery: Frame Interpolation}
-\textcolor{red}{Add something related to the former subsection}
+\textcolor{orange}{Add something related to the former subsection}
 
@@
 We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a \emph{chunk}.
-The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{TEST-chunk-sector} .
+The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{chunk-sector} .
 We also use the term symbol in coding theory to refer to sectors.
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/TEST-chunk-sector.JPG}
-\caption{\textcolor{blue}{TEST--}A sample of chunk and sector}
-\label{TEST-chunk-sector}
+\includegraphics[width=0.35\textwidth,height=40mm]{photo/chunk-sector.JPG}
+\caption{A sample of chunks and sectors}
+\label{chunk-sector}
 \end{figure}
@@
 In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
-We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-7222-v5}.
+We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522}.
 For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
-Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in \ref{Data Distribution}.
 
-Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
+Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
+Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
@@
 \begin{itemize}
-    \item Important data sector set $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$
-    \item Minor data sector set $D_M=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < n-m \}$
-    \item Important parity sector set $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$
-    \item Global parity sector set $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$
+    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector set.
+    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector set.
+    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector set. 
+    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector set.
 \end{itemize}
@@
 \centering
-
 \subfigure[sector label and encoding process]{
-    \includegraphics[width=0.32\textwidth]{photo/apcode-7222-v5.PDF}
-    \label{apcode-7222-v5-a}
+    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
+    \label{apcode-72522-a}
 }
@@
     \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
-    \label{apcode-7222-v5-b}
+    \label{apcode-72522-b}
 }
-\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and 4 other sectors (red set $Q$) are designed for encoding important data.
-In this example, there are 6 sectors (dark blue set $D_I$) for important data and 15 sectors (light blue set $D_M$) for minor data.}
-\label{apcode-7222-v5}
+\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and each chunk has 5 sectors.
+In this example, there are 6 sectors (dark blue set $D_I$) for important data, 15 sectors (light blue set $D_M$) for minor data and 4 other sectors (red set $Q$) are designed for encoding important data.}
+\label{apcode-72522}
 \end{figure}
 
-\textcolor{red}{A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
-Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section XXXXX}.
-
-In general, Approximate Code performs extra parities on important data.
-Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
-Therefore, EC methods such as RS-based codes, XOR-based codes or MSR codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.
-
 \subsection{Encoding and Decoding Process}
-In this section, we use Figure \ref{apcode-7222-v5} to illustrate the encoding and decoding process of Approximate Code(7,2,2,2).
+In this section, we use Figure \ref{apcode-72522} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
 
@@
 When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data.
-It should be noted that in the calculation of $G$ in \emph{G-Phase} and in the decoding process in full recovery mode, we consider $D_I$, $D_M$ and $Q$ as the same, so the minimum coding unit is chunk.
 When the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.
+
+It should be noted that in the calculation of $G$ in \emph{G-Phase} and in the decoding process in full recovery mode, we consider $D_I$, $D_M$ and $Q$ as the same, and the minimum coding unit is chunk.
+That is, when we do not distinguish the importance of the data($s,t = 0$), the Approximate Code is a typical $m$ disk redundancy code.
+
+In general, Approximate Code performs extra parities on important data.
+Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
+Therefore, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.
 
@@
 In \emph{I-Phase}, we use RS(3,2) to encode 3 groups of important data sectors and generate 2 groups of parity sectors labeled with $q_{i,j}$.
-The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF).
+The calculation of $q_{i,j}$ are defined by equation (\ref{q_ij}), where $\alpha_k$ is the coefficient in Galois Field (GF).
 The coding coefficient matrix is transformed from the Vandermonde matrix by elementary transformation.
-\textcolor{blue}{Coding matrix?}
 
-\iffalse
+\textcolor{orange}{Coding matrix like below?}
+
 \begin{equation}
@@
 \end{equation}
-\fi
 
@@
 In \emph{I-Phase}, we use RS(5,2) to generate 2 parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors.
-The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
+The calculation of $p_{i,j}$ are defined by equation (\ref{p_ij_1}) and (\ref{p_ij_2}).
 For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.
@@
 
-\subsection{Proof of Correctness}
-\subsection{Data Distribution}\label{Data Distribution}
+\subsubsection{ XOR-based Approximate Code}
+\textcolor{orange}{It is difficult to design XOR-based codes that m=2,s=1.
+Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails.
+However, the desgin of m=1 is easy, because we only use horizontal parity blocks.
+}
+
+\textcolor{orange}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them.
+This might be too complex but its correctness is easy to proof.}
+
+\textcolor{gray}{
+    hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello
+}
+
+\subsection{\textcolor{orange}{Proof of Correctness}}
+
+\subsection{Intermediate Layer}\label{Intermediate Layer}
+Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is needed to preprocess the data.
+In our design, the middle layer performs automatic data identification and data distribution, implementing \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.
+
+\subsubsection{Data Identification}
+For H.264 video data, we define I frames as important data, and P frames and B frames as minor data based on the analysis in the \ref{video storage}.
+In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
+We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space.
+The feasibility of this definition will be confirmed in \ref{evaluation}.
+
+\subsubsection{Data Distribution}
+Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames.
+Therefore, we store data in units of GOPs.
+Our main purpose is to store I frames and other frames separately.
+For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame.
+In the following description, we no longer consider such data especially and simply refer to them as I-frames.
+Our data distribution algorithm is as follows:
+
+\textcolor{orange}{Need to draw an algorithm table from the following description}
+
+1. Calculate the important data ratio of each GOP in a stripe, and remember that the highest one is $\omega_{max}$.
+
+2. Adjust $t$ to find the important rate $\omega_{act}$ closest to $\omega_{max}$
+
+3. Divide each GOP into two parts: $\omega_{act}$: $1-\omega_{act}$.
+
+4. Store the former in $D_I$, the latter in $D_M$.
+
+In this regard, the decoding process is as follows:
+
+1. Read the entire strip and find the nmrst parameter of the strip record
+
+2. Calculate $\omega_{act}$ based on parameters
+
+3. Read the $I$ frame from $D_I$ until the next I frame is encountered
+
+4. Calculate the length read in 3, multiply by $(1-\omega_{act})/\omega_{act}$ , and read this length in $D_M$.
+
+5. Combine I frames with other frames.
+The data distribution scheme is shown in the figure \ref{Data-distribution-v2}.
+
+\textcolor{blue}{Some description about the figure...}
+
+\textcolor{gray}{
+    hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello hello
+}
+Our approach can be applied to a variety of other data types.
+In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.35\textwidth]{photo/Data-distribution-v2.PDF}
+\caption{1}
+\label{Data-distribution-v2}
+\end{figure}
 
@@
 \section{Evaluation}\label{evaluation}
+\begin{table}[ht]
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Efficiency\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
+(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
+(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
+(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
+(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
+(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
+(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
+(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
+(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
+(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
+(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
+\end{tabular}
+\end{table}
 \subsection{An Evaluation methodology}

### 2019-03-31 ApproximateCode.tex
First draft of Approximate Code, Version1

@@
 %                                                           %
-% red words should be removed or rewrite in later version   %
-% blue words need to be perfected or filled                 %
+% red words show the content that requires to be add        %
+% blue words need to be perfected or changed                %
 %                                                           %
@@
 In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
-We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-7222-v5}.
+We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522}.
 For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
-Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in \ref{Data Distribution}.
 
-Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
+\textcolor{blue}{Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in ...}
+
+Based on the above definition, our design has 4 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
+Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
@@
 In \emph{I-Phase}, we use RS(3,2) to encode 3 groups of important data sectors and generate 2 groups of parity sectors labeled with $q_{i,j}$.
-The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF).
+The calculation of $q_{i,j}$ are defined by equation (\ref{q_ij}), where $\alpha_k$ is the coefficient in Galois Field (GF).
 The coding coefficient matrix is transformed from the Vandermonde matrix by elementary transformation.
-\textcolor{blue}{Coding matrix?}
 
-\iffalse
+\textcolor{red}{Coding matrix like below?}
+
 \begin{equation}
@@
 
-\subsection{Proof of Correctness}
-\subsection{Data Distribution}\label{Data Distribution}
+\subsubsection{ XOR-based Approximate Code}
+\textcolor{red}{It is difficult to design XOR-based codes that m=2,s=1.
+Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails.
+However, the desgin of m=1 is easy, because we only use horizontal parity blocks.
+}
+
+\textcolor{red}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them.
+This might be too complex but its correctness is easy to proof.}
+
+\subsection{\textcolor{red}{Proof of Correctness}}
+
+\subsection{Intermediate Layer}\label{Intermediate Layer}
+Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is needed to preprocess the data.
+In our design, the middle layer performs automatic data identification and data distribution, implementing \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.
+
+\subsubsection{Data Identification}
+For H.264 video data, we define I frames as important data, and P frames and B frames as minor data based on the analysis in the \ref{video storage}.
+In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
+We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space.
+The feasibility of this definition will be confirmed in \ref{evaluation}.
+
+\subsubsection{Data Distribution}
+Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames.
+Therefore, we store data in units of GOPs.
+Our main purpose is to store I frames and other frames separately.
+For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame.
+In the following description, we no longer consider such data especially and simply refer to them as I-frames.
+Our data distribution algorithm is as follows:
+
+\textcolor{red}{Need to draw an algorithm table from the following description}
+
+1. Calculate the important data ratio of each GOP in a stripe, and remember that the highest one is $\omega_{max}$.
+
+2. Adjust $t$ to find the important rate $\omega_{act}$ closest to $\omega_{max}$
+
+3. Divide each GOP into two parts: $\omega_{act}$: $1-\omega_{act}$.
+
+4. Store the former in $D_I$, the latter in $D_M$.
+
+In this regard, the decoding process is as follows:
+
+1. Read the entire strip and find the nmrst parameter of the strip record
+
+2. Calculate $\omega_{act}$ based on parameters
+
+3. Read the $I$ frame from $D_I$ until the next I frame is encountered
+
+4. Calculate the length read in 3, multiply by $(1-\omega_{act})/\omega_{act}$ , and read this length in $D_M$.
+
+5. Combine I frames with other frames.
+The data distribution scheme is shown in the figure \ref{Data-distribution-v2}.
+
+\textcolor{blue}{Some description about the figure...}
+
+Our approach can be applied to a variety of other data types.
+In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.35\textwidth]{photo/Data-distribution-v2.PDF}
+\caption{1}
+\label{Data-distribution-v2}
+\end{figure}
 

### 2019-04-01 ApproximateCode.tex
Version 1.0.0

@@
 \usepackage{subfigure}
+\usepackage{algorithm}
+%\usepackage{algorithmic}
+\usepackage{algpseudocode}
+\usepackage{amsmath}
+\usepackage{graphics}
+\usepackage{epsfig}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
+\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm
 
@@
 %                                                           %
-% red words show the content that requires to be add        %
+% orange words show the content that requires to be add     %
 % blue words need to be perfected or changed                %
+% gray words are the placeholder which is easy to fill      %
 %                                                           %
@@
 Therefore, we propose Approximate Codes for video data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first strip.
+In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first stripe.
 This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there.
@@
 (3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}
+
+\textcolor{orange}
+{Seventh paragraph:
+organization of the paper}
+
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
+
+\section{Related Work and Our Motivation}
+Video data can be classified into hot data and cold data, the former requiring high availability and reliability, which often relies on expensive replication approach.
+The latter's storage usually uses erasure codes schemes, because cold data far exceeds hot data, and erasure codes can guarantee its reliability with low monetary overhead.
+However, existing erasure code schemes do not consider the characteristics of video data and are not specifically designed for them.
+
+Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
+For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
+Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
+On the other hand, loss of important data will have more serious consequences.
+
+This section then introduces the relevant background and our motivation.
+
+\subsection{Existing Erasure Codes}
+
+\textcolor{orange}{Here we give some introduction to existing erasure codes
+Specifically, we need to illustrate the existing erasure codes for video applications in detail.
+Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}
+
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
 
@@
 
-\textcolor{red}
-{Seventh paragraph:
-organization of the paper}
-
-\section{Related Work and Our Motivation}
-Video data can be classified into hot data and cold data, the former requiring high availability and reliability, which often relies on expensive replication approach.
-The latter's storage usually uses erasure codes schemes, because cold data far exceeds hot data, and erasure codes can guarantee its reliability with low monetary overhead.
-However, existing erasure code schemes do not consider the characteristics of video data and are not specifically designed for them.
-
-Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
-For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
-On the other hand, loss of important data will have more serious consequences.
-
-This section then introduces the relevant background and our motivation.
-
-\subsection{Existing Erasure Codes}
-
-\textcolor{red}{Here we give some introduction to existing erasure codes
-Specifically, we need to illustrate the existing erasure codes for video applications in detail.
-Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}
-
 \subsection{Video Storage}\label{video storage}
@@
 
-\textcolor{red}{Something about H.264\dots}
+\textcolor{orange}{Something about H.264\dots}
+
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+    }
 
@@
 We also use the term symbol in coding theory to refer to sectors.
-Since each strip is independent of the entire system, we only consider a single strip.
+Since each stripe is independent of the entire system, we only consider a single stripe.
 
@@
 
-\textcolor{blue}{Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$ and the relevant instructions will be shown in ...}
-
-Based on the above definition, our design has 4 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
+Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
 Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
-We then define the set of sectors as follows:
+We then define the area of sectors as follows:
 \begin{itemize}
-    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector set.
-    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector set.
-    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector set. 
-    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector set.
+    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector area.
+    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector area.
+    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector area. 
+    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector area.
 \end{itemize}
@@
 }
-\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and each chunk has 5 sectors.
-In this example, there are 6 sectors (dark blue set $D_I$) for important data, 15 sectors (light blue set $D_M$) for minor data and 4 other sectors (red set $Q$) are designed for encoding important data.}
+\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange area $G$) and each chunk has 5 sectors.
+In this example, there are 6 sectors (dark blue area $D_I$) for important data, 15 sectors (light blue area $D_M$) for minor data and 4 other sectors (red area $Q$) are designed for encoding important data.}
 \label{apcode-72522}
@@
 
-\textcolor{red}{Coding matrix like below?}
+\textcolor{orange}{Coding matrix like below?}
 
@@
 \subsubsection{ XOR-based Approximate Code}
-\textcolor{red}{It is difficult to design XOR-based codes that m=2,s=1.
+\textcolor{orange}{It is difficult to design XOR-based codes that m=2,s=1.
 Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails.
@@
 
-\textcolor{red}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them.
+\textcolor{orange}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them.
 This might be too complex but its correctness is easy to proof.}
 
-\subsection{\textcolor{red}{Proof of Correctness}}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
+\subsection{\textcolor{orange}{Proof of Correctness}}
+\textcolor{orange}{I am not quite clear what to write here, our proof of correctness is organized in encoding and decoding process}
 
 \subsection{Intermediate Layer}\label{Intermediate Layer}
-Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is needed to preprocess the data.
-In our design, the middle layer performs automatic data identification and data distribution, implementing \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.
+Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is necessary to preprocess the data.
+In our design, the middle layer performs automatic data identification and data distribution.
+It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.
 
@@
 
-\subsubsection{Data Distribution}
+\subsubsection{Data Distribution and Reorganization}
 Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames.
@@
 In the following description, we no longer consider such data especially and simply refer to them as I-frames.
-Our data distribution algorithm is as follows:
+We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size.
+We also define $\omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}$ as the actual important rate the code can provide.
+Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.
 
-\textcolor{red}{Need to draw an algorithm table from the following description}
+\begin{algorithm}[htb] 
+\caption{Data Distribution Algorithm} 
+\label{alg-data-dist} 
+\begin{algorithmic}[1]
 
-1. Calculate the important data ratio of each GOP in a stripe, and remember that the highest one is $\omega_{max}$.
+\Require A stripe of video data.
+\Ensure $D_I$ and $D_M$.
 
-2. Adjust $t$ to find the important rate $\omega_{act}$ closest to $\omega_{max}$
+\State Divide video data into several GOPs;
+\State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
+\State Adjust $t$ to find the closest $\omega_{act}$ to $\omega_{max}$;
+\Repeat 
+\State Divide each GOP into two parts: $\omega_{act}$ and $1-\omega_{act}$;
+\State Store the former in $D_I$, the latter in $D_M$;
+\Until All GOPs are classified;
+\end{algorithmic} 
+\end{algorithm}
 
-3. Divide each GOP into two parts: $\omega_{act}$: $1-\omega_{act}$.
+\begin{algorithm}[htb] 
+\caption{Data Reorganization Algorithm} 
+\label{alg-data-reor} 
+\begin{algorithmic}[1] 
+\Require $D_I$ and $D_M$;
+\Ensure A stripe of video data;
+\State Find the parameter $(n,m,r,s,t)$ and calculate $\omega_{act}$.
+\Repeat
+\State Read an I frame from $D_I$ and record its length as $l$.
+\State Read $l \times \frac{1-\omega_{act}}{\omega_{act}}$ in $D_M$ and combine two parts.
+\Until All blocks are read.
+\end{algorithmic} 
+\end{algorithm}
 
-4. Store the former in $D_I$, the latter in $D_M$.
+The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
+For example, Data 3 is represnted by blue, and its key segment (10\%) and part of minor segment (10\%) are settled in $D_I$.
+The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$.
+This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time.
+Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.
 
-In this regard, the decoding process is as follows:
-
-1. Read the entire strip and find the nmrst parameter of the strip record
-
-2. Calculate $\omega_{act}$ based on parameters
-
-3. Read the $I$ frame from $D_I$ until the next I frame is encountered
-
-4. Calculate the length read in 3, multiply by $(1-\omega_{act})/\omega_{act}$ , and read this length in $D_M$.
-
-5. Combine I frames with other frames.
-The data distribution scheme is shown in the figure \ref{Data-distribution-v2}.
-
-\textcolor{blue}{Some description about the figure...}
-
-Our approach can be applied to a variety of other data types.
-In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].
-
-\begin{figure}[h]
+\begin{figure}[htb]
 \centering
-\includegraphics[width=0.35\textwidth]{photo/Data-distribution-v2.PDF}
-\caption{1}
+\includegraphics[width=0.4\textwidth]{photo/Data-distribution-v2.pdf}
+\caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area.
+Here for each data segment, $\omega_1=15\%$, $\omega_2=20\%$ and $\omega_3=10\%$, so the $\omega_{max}=20\%$.}
 \label{Data-distribution-v2}
@@
 
+In addition, our approach can be applied to a variety of other data types.
+In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].
+
 \subsection{Properties of Approximate Code}
 
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \section{Evaluation}\label{evaluation}
-\begin{table}[ht]
+
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
+\begin{table}[htbp]
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{table}
+
 \subsection{An Evaluation methodology}
+
 \subsubsection{Erasure Codes in Our Comparisons}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \subsubsection{Platforms and Configurations}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \subsubsection{Metrics}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
 \subsubsection{Parameters and Assumption in Our Evaluation}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
 
 \subsection{Results}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \subsection{Analysis}
-Illustrate why Approximate Code achieve high reliability with low cost
+\textcolor{orange}{Illustrate why Approximate Code achieve high reliability with low cost}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
 \section{Conclusion}
 
-%
-% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
-% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
+
 \end{acks}
 
-%
-% The next two lines define the bibliography style to be used, and the bibliography file.
 \bibliographystyle{ACM-Reference-Format}

### 2019-04-06 ApproximateCode.tex
Version 2

@@
 \begin{abstract}
-Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
-Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to equally back up all data.
-However, this is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to the ignorance of redundant information inside the data, which results in multiple complete parity disks being excessive.
+Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space.
+Meanwhile, to ensure the data reliability, distributed file systems usually use erasure code redundant data.
+However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive.
+On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.
 
-Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
-Approximate Codes provide complete recovery when fewer disks fail, and ensure approximate recovery (recover most data) in the event of multiple disk failures.
-To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
-The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.
+In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy.
+Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead.
+It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures.
+To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems.
+The results show that compared with the typical high-reliability erasure code schemes, Approximate Code reduces the storage overhead by 7.64\% at the expense of reasonable probability of data quality loss.
+
 \end{abstract}

### 2019-04-06 ApproximateCode.tex
version 2.1

@@
 \section{Introduction}
-Currently, many cloud storage systems use erasure codes to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud.
-It is known that erasure codes provide much lower storage overhead and write bandwidth than replication with the same fault tolerance.
+Multimedia data consumes massive storage space in cloud storage systems, and this trend is exacerbated as applications demand higher resolution and frame rates.
+On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded.
+Rapidly growing data imposes very high requirements of reliability and availability on large-scale storage systems as well as low cost.
 
-Typical erasure codes schemes can be divided into two categories such as RS-based code (RS, LRC), or XOR-based code (...).
-Other erasure codes (SD, STAIR) use the parity blocks to tolerate sector failures in addition to disk-level fault tolerance.
+Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice.
+In contrast, cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data.
+It provides lower storage overhead and write bandwidth than replication with the same fault tolerance.
+Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud [].
+Typical erasure codes configuration use three-disk fault tolerant array (3DFTS).
+However, its overhead is still too high and is excessive because simultaneous damage of triple disks is relatively rare.
 
-Video data consumes massive space in cloud storage systems, and this trend is exacerbated as applications demand increased resolution and frame rates.
-Using multiple copies to ensure video data security will generate storage cost that are several times larger than the original data, which is obviously too expensive, while erasure codes can significantly reduce this cost.
+The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy.
+Common methods are to ensure the reliability of important data while storing the minor data on relatively unreliable media or reducing their error correction coding.
+Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data.
+For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames.
+Also, some pixel errors in the image data do not affect the information of the entire picture.
+However, the direct application of approximate storage in a cloud storage system will result in minor data being unacceptable volatile.
 
-Existing erasure codes are designed to completely recover corrupted data.
-Typical configurations use triple disk failure tolerant arrays (3DFTS), such as Windows Azure [], which requires at least 3 parity disks.
-These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of video applications can tolerate a certain amount of data loss.
-For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive.
-In addition, even if the video data suffers a certain amount of loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].
+Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
+In the scenario shown in Figure \ref{apcode-72522-v2}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
+Other $s \times t$ sectors are encoded for important data thus raise its reliability.
+Approximate Codes ensure that the important data can tolerate $m+s$ device failures while all data can tolerate $m$ device failures.
+When more than $s$ disks fails, Approximate Code recovers the important data and then transfer the surviving data to the upper layer for recovery.
+With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage that is distinguishing data importance.
 
-We also find that video data is usually stored after being encoded to save space, while the encoded video data stream is non-uniformly sensitive to data loss, which makes it inappropriate to provide uniform fault tolerance using conventional erasure codes.
-With the motion compensation mechanism, common video coding algorithms such as H.264 only needs to store the complete content of key frames and a little part of other frames, which makes other frames rely on the key frames for computation while decoding.
+This work is usually done by experienced programmers, but fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being inherently more important than others.
+For example, in the progressive transform codec (PTC) compressed image, control and run-length bits are much more important than refinement bits.
+Therefore, this work is done automatically by a system tailored to specific encodings in our design.
 
-Therefore, we propose Approximate Codes for video data that significantly reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in (Figure 1), the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding and another $s$ sectors encoded for the first stripe.
-This allows the data of the first stripe to tolerate any $m+s$ disks corruption, so we specifically store important segments of video data there.
-With an appropriate data distribution scheme, non-critical data segments will still retain $(n-2m-s)/(n-m)$ data when any $m+s$ disks are corrupted, which makes
-recovery schemes such as interpolated or superpixel still effective.
-The Approximate Codes provide two recovery modes, full recovery and approximate recovery.
-The former applies to no more than $m$ disk corruptions and recovers all data, the latter applies to no more than $m+$s disks corruptions and retains important data.
+Our work contributions include:
+\begin{enumerate}
+\item We propose an approximation code that reduces storage overhead and improves the reliability and availability of important data with an approximate strategy.
+\item We prove the mathematical correctness of the approximation code.
+\item A series of experiments show that the approximate code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
+\end{enumerate}
 
-\textcolor{orange}
-{Sixth paragraph:
-Contribution of this paper, typically two or three contributions,
-(1)	Propose a novel code Approximate Code
-(2)	Give some mathematical proof to demonstrate the correctness of Approximate Code
-(3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}
+The rest of the paper is organized as follows.
+In Section \ref{RelatedWork}, we introduce related work and our motivation.
+In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail.
+The evaluation is presented in Section \ref{Evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
 
-\textcolor{orange}
-{Seventh paragraph:
-organization of the paper}
-
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
-
-\section{Related Work and Our Motivation}
-Video data can be classified into hot data and cold data, the former requiring high availability and reliability, which often relies on expensive replication approach.
-The latter's storage usually uses erasure codes schemes, because cold data far exceeds hot data, and erasure codes can guarantee its reliability with low monetary overhead.
-However, existing erasure code schemes do not consider the characteristics of video data and are not specifically designed for them.
-
-Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
-For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
-On the other hand, loss of important data will have more serious consequences.
-
-This section then introduces the relevant background and our motivation.
+\section{Related Work and Our Motivation}\label{RelatedWork}
+This section presents background on erasure codes, related video storage methods, approximate storage, and our motivation.
 
@@
 
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.35\textwidth,height=40mm]{photo/chunk-sector.JPG}
+\caption{A sample of chunks and sectors}
+\label{chunk-sector}
+\end{figure}
+
 \textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
-
-\begin{table*}[ht]
-\centering
-\caption{Summary on Various Erasure Codes}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
-RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
-MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
-Raid 6 & 2 & 2 & low & high & low \\ \hline
-SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
-\end{tabular}
-\end{table*}
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
 
 \subsection{Video Storage}\label{video storage}
+
 For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
@@
 
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-    }
+Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
+For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
+Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
+On the other hand, loss of important data will have more serious consequences.
 
-\subsection{Approximate Storage}
-Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
-
-It loosens the requirement of storage reliability by allowing some quality loss of specific data.
-Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
-The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices.
-Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
-
-However, it is too naive to store data in approximate storage units indiscriminately.
-Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
-To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
-
-In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
-An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable.
-In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.
-
-\textcolor{orange}{We define I frames are our important data}
-
-\subsection{Video Frame Recovery: Frame Interpolation}
 \textcolor{orange}{Add something related to the former subsection}
@@
 
+\subsection{Approximate Storage}
+Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
+
+It loosens the requirement of storage reliability by allowing some quality loss of specific data.
+Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
+The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices.
+Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
+
+However, it is too naive to store data in approximate storage units indiscriminately.
+Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
+To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
+
+In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
+An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable.
+In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.
+
+\textcolor{orange}{We define I frames are our important data}
+
 \subsection{Our Motivation}
@@
 
-\section{Approximate Code}
+\section{Approximate Code}\label{ApCode}
 In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.35\textwidth,height=40mm]{photo/chunk-sector.JPG}
-\caption{A sample of chunks and sectors}
-\label{chunk-sector}
-\end{figure}
-
 In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
-We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522}.
+We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522-v2}.
 For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
@@
 Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-72522} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
+Figure \ref{apcode-72522-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
@@
 \subfigure[sector label and encoding process]{
-    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
-    \label{apcode-72522-a}
+    \includegraphics[width=0.32\textwidth]{photo/apcode-72522-v2.PDF}
+    \label{apcode-72522-v2-a}
 }
@@
     \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
-    \label{apcode-72522-b}
+    \label{apcode-72522-v2-b}
 }
@@
 In this example, there are 6 sectors (dark blue area $D_I$) for important data, 15 sectors (light blue area $D_M$) for minor data and 4 other sectors (red area $Q$) are designed for encoding important data.}
-\label{apcode-72522}
+\label{apcode-72522-v2}
 \end{figure}
@@
 \subsection{Encoding and Decoding Process}
-In this section, we use Figure \ref{apcode-72522} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
+In this section, we use Figure \ref{apcode-72522-v2} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
 
@@
 
-\section{Evaluation}\label{evaluation}
+\section{Evaluation}\label{Evaluation}
+
+\begin{table*}[ht]
+\centering
+\caption{Summary on Various Erasure Codes}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
+RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
+MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
+Raid 6 & 2 & 2 & low & high & low \\ \hline
+SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
+\end{tabular}
+\end{table*}
 
@@
 }
-\section{Conclusion}
+\section{Conclusion}\label{Conclusion}
 

### 2019-04-07 ApproximateCode.tex
version 2.1.2

@@
 Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in Figure \ref{apcode-72522-v2}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
+In the scenario shown in Figure \ref{apcode-72522-v3}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
 Other $s \times t$ sectors are encoded for important data thus raise its reliability.
@@
 In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
-We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522-v2}.
+We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522-v3}.
 For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
@@
 Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-72522-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
+Figure \ref{apcode-72522-v3} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
 
@@
 \subfigure[sector label and encoding process]{
-    \includegraphics[width=0.32\textwidth]{photo/apcode-72522-v2.PDF}
-    \label{apcode-72522-v2-a}
+    \includegraphics[width=0.32\textwidth]{photo/apcode-72522-v3.PDF}
+    \label{apcode-72522-v3-a}
 }
 \subfigure[sector sets]{
-    \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
-    \label{apcode-72522-v2-b}
+    \includegraphics[width=0.13\textwidth]{photo/DDQP.jpg}
+    \label{apcode-72522-v3-b}
 }
@@
 In this example, there are 6 sectors (dark blue area $D_I$) for important data, 15 sectors (light blue area $D_M$) for minor data and 4 other sectors (red area $Q$) are designed for encoding important data.}
-\label{apcode-72522-v2}
+\label{apcode-72522-v3}
 \end{figure}
@@
 \subsection{Encoding and Decoding Process}
-In this section, we use Figure \ref{apcode-72522-v2} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
+In this section, we use Figure \ref{apcode-72522-v3} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
 
@@
 
-\subsection{Intermediate Layer}\label{Intermediate Layer}
+\subsection{Properties of Approximate Code}
+
+We analyze the nature of the approximate code from the following aspects, and the calculation method of the relevant indicators is given in Table x.
+Low cost Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
+Important data High reliability The approximate code guarantees the fault tolerance of the important data m+s.
+Flexibility The implementation of the approximate code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the approximate code can also be used for encoding such as LRC or MSR.
+Lower recovery overhead Due to the shorter checksum chain of important data blocks, the recovery code of the approximate code in the full recovery mode is less expensive.
+
+\section{Implementation}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
+\caption{111}
+\label{fig-implementation}
+\end{figure}
+
 Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is necessary to preprocess the data.
@@
 
-\subsubsection{Data Identification}
+\subsection{Data Identification}
 For H.264 video data, we define I frames as important data, and P frames and B frames as minor data based on the analysis in the \ref{video storage}.
@@
 
-\subsubsection{Data Distribution and Reorganization}
+\subsection{Data Distribution and Reorganization}
 Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames.
@@
 \begin{algorithmic}[1] 
-
 \Require A stripe of video data.
 \Ensure $D_I$ and $D_M$.
-
 \State Divide video data into several GOPs;
@@
 
-\subsection{Properties of Approximate Code}
-
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
-\section{Evaluation}\label{Evaluation}
+\section{Evaluation}\label{evaluation}
+In our evaluation, we first compare the approximate code with the RS code and some XOR-based code to demonstrate the performance benefits of our solution.
+Since 3DFTS is a typical erase code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
+We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
+We use mathematical analysis and experiments to prove the effectiveness of the approximation code.
 
@@
 \end{table*}
-
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
 
@@
 
-\subsection{An Evaluation methodology}
+\subsection{Evaluation methodology}
 

### 2019-04-08 ApproximateCode.tex
version2.1.2

@@
 This section presents background on erasure codes, related video storage methods, approximate storage, and our motivation.
+
+\begin{table}[]
+\begin{tabular}{|c|l|}
+\hline
+Symbols & Description                          \\ \hline\hline
+$n$     & the number of chunks in a stripe     \\ \hline
+$m$     & the number of parity chunks          \\ \hline
+$r$     & the number of sectors in a chunk     \\ \hline
+$s$     & the number of columns of $D_I$       \\ \hline
+$t$     & the number of rows of $D_I$          \\ \hline
+$D_I$   & the zone of important data sectors   \\ \hline
+$D_M$   & the zone of minor data sectors       \\ \hline
+$Q$     & the zone of important parity sectors \\ \hline
+$P$     & the zone of minor parity sectors     \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage module is necessary to preprocess the data.
+Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data.
 In our design, the middle layer performs automatic data identification and data distribution.
@@
 \section{Evaluation}\label{evaluation}
-In our evaluation, we first compare the approximate code with the RS code and some XOR-based code to demonstrate the performance benefits of our solution.
-Since 3DFTS is a typical erase code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
-We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
-We use mathematical analysis and experiments to prove the effectiveness of the approximation code.
+This section introduces a series of experiments we have conducted to verify the efficiendy of the Approximate Code.
 
@@
 \subsection{Evaluation methodology}
+In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution.
+Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
+We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
+We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
 

### 2019-04-08 ApproximateCode.tex
Update ApproximateCode.tex

@@
 \subsection{Video Storage}\label{video storage}
+For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
+Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, and that is why we focus on such algorithms.
 
-For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
-Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.
+H.264 is one of the advanced algorithms for this type of work.
+This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
+For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
 
+\textcolor{orange}{Something about H.264\dots}
+
+H.264 classifies all frames into three different categories:
+\begin{enumerate}
+    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
+    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
+    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
+\end{enumerate}
+In order to prevent the circumstance where a P or B frame references another distant frame, the concept of GOP is introduced.
+A GOP consists of multiple consecutive I,P and B frames which are independent of the frames in other GOPs.
+In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}.
 \begin{figure}[ht]
@@
 
-H.264 is one of the advanced algorithms for this type of work.
-This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
-For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
-
-\textcolor{orange}{Something about H.264\dots}
-
-Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application.
-For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to.
-Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect.
-On the other hand, loss of important data will have more serious consequences.
+\subsubsection{Video Frame Recovery}
 
@@
 
-In the circumstance of data loss, it's common to lose some frames and then the video is not complete.
-One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates.
-Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.
+In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
+However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
+One of them is named video frame interpolation.
 
@@
 Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
-Optical flow is commonly addressed in the video frame interpolation problem.
-Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene.
-Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.
 
-Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{didyk2013joint}\cite{wadhwa2013phase}\cite{meyer2015phase}.
-These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color.
-Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation.
-In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{dosovitskiy2015flownet}\cite{ilg2017flownet}.
-Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.
+In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
+Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
 
-\textcolor{blue}{All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle).
-However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames.
-Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.}
+The methods are relied on the completeness of some video frame, which enhances the importance of the only intact type of frame data in commonly used H.264 standard: the I frame.
 
 \subsection{Approximate Storage}
+Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
+But not all data need high-reliability storage for its backup.
+That is when the concept of approximate storage is introduced.
 Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
 
-It loosens the requirement of storage reliability by allowing some quality loss of specific data.
+Use cases for approximate storage range from transient memory to embedded settings and mass storage cloud servers.
+Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance.
+On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints./ref{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
+
+Approximate storage loosens the requirement of storage reliability by allowing quality loss of some specific data.
 Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
-The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices.
+The critical data is still safe because they are stored and sufficiently backed up by expensive and highly reliable storage devices.
 Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
@@
 In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
-An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable.
-In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.
+An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to fail.
+In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frames depend on it.
 
-\textcolor{orange}{We define I frames are our important data}
+Considering the vital role the I frame plays in the video coding, we therefore define I frame data as the critical data of a video file.
+Although some part of P frames may play a relatively important role in the decoding process of a video, it’s importance can not exceed that of the I frames.
 

### 2019-04-08 ApproximateCode.tex
Update ApproximateCode.tex

@@
 In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
+Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
 

### 2019-04-09 ApproximateCode.tex
version2.4

@@
 \usepackage{epsfig}
+\usepackage{multirow}
+\usepackage{graphicx}
+\usepackage{subfigure}
+
 \renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
@@
 Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in Figure \ref{apcode-72522-v3}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
+In the scenario shown in Figure \ref{apcode-72522}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
 Other $s \times t$ sectors are encoded for important data thus raise its reliability.
@@
 \subsection{Design of Approximate Code}
-In a system of $n$ disks, each disk can be divided into multiple sectors.
-We focus on the $r$ sectors of the same logical position of each device, and we treat these $r$ sectors as a \emph{chunk}.
-The $r \times n$ sectors of $n$ chunks constitute a stripe, as shown in Figure \ref{chunk-sector} .
-We also use the term symbol in coding theory to refer to sectors.
-Since each stripe is independent of the entire system, we only consider a single stripe.
-
-In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks. 
-We use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows, as shown in Figure \ref{apcode-72522-v3}.
+We use Figure \ref{apcode-72522} to illustrate the construction of Approximate Code.
+In the $n$ chunks of each stripe, $m$ ones are for coding.
+In the remaining $n-m$ chunks, $s \times t$ additional sectors are for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
 For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
@@
 \begin{itemize}
-    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector area.
-    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector area.
-    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector area. 
-    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector area.
+    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector zone.
+    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector zone.
+    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector zone. 
+    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector zone.
 \end{itemize}
@@
 \subfigure[sector label and encoding process]{
-    \includegraphics[width=0.32\textwidth]{photo/apcode-72522-v3.PDF}
-    \label{apcode-72522-v3-a}
+    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
+    \label{apcode-72522-a}
 }
 \subfigure[sector sets]{
-    \includegraphics[width=0.13\textwidth]{photo/DDQP.jpg}
-    \label{apcode-72522-v3-b}
+    \includegraphics[width=0.13\textwidth]{photo/DDQG.pdf}
+    \label{apcode-72522-b}
 }
-\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are parity chunks (orange area $G$) and each chunk has 5 sectors.
-In this example, there are 6 sectors (dark blue area $D_I$) for important data, 15 sectors (light blue area $D_M$) for minor data and 4 other sectors (red area $Q$) are designed for encoding important data.}
-\label{apcode-72522-v3}
+\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are global parity chunks (orange zone $G$) and each chunk has 5 sectors.
+In this example, there are 6 sectors (dark blue zone $D_I$) for important data, 15 sectors (light blue zone $D_M$) for minor data and 4 sectors (red zone $Q$) encode important data.}
+\label{apcode-72522}
 \end{figure}
@@
 \subsection{Encoding and Decoding Process}
-In this section, we use Figure \ref{apcode-72522-v3} to illustrate the encoding and decoding process of Approximate Code$(7,2,5,2,2)$.
+We also use Figure \ref{apcode-72522} to illustrate the basic idea of encoding and decoding process of Approximate Code.
 
 The encoding process consists of two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). 
-The \emph{I-Phase} is expressed as two red arrows in the blod box, where $Q$ is generated to verify $D_I$, and
-the \emph{G-Phase} is expressed as a yellow triangle arrow, where $G$ is generated to verify $D_I$, $D_M$ and $Q$.
+The \emph{I-Phase} is expressed as two red arrows in the blod box, where $Q$ is generated to verify $D_I$, and the \emph{G-Phase} is expressed as a yellow triangle arrow, where $G$ is generated to verify $D_I$, $D_M$ and $Q$.
 
 The decoding process provides two modes: the approximate recovery mode and the full recovery mode.
-When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data.
-When the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.
+When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data, and if the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.
 
@@
 In general, Approximate Code performs extra parities on important data.
-Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are.
-Therefore, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.
+Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in several ways.
+Therefore, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can be used to construct Approximate Code.
 
-\textcolor{blue}{We then introduce RS-based and XOR-based Approximate Code}
-\subsubsection{RS-based Approximate Code}
+We then introduce two typical Approximate Code implementation schemes: RS-based and XOR-based Approximate Code.
+Different code selection of \emph{I-Phase} and \emph{G-Phase} will cause different effect.
 
-In \emph{I-Phase}, we use RS(3,2) to encode 3 groups of important data sectors and generate 2 groups of parity sectors labeled with $q_{i,j}$.
-The calculation of $q_{i,j}$ are defined by equation (\ref{q_ij}), where $\alpha_k$ is the coefficient in Galois Field (GF).
-The coding coefficient matrix is transformed from the Vandermonde matrix by elementary transformation.
+\subsection{RS-based Approximate Code}
 
-\textcolor{orange}{Coding matrix like below?}
+\begin{figure}[htp]
+\centering
+\subfigure[I-Phase]{\label{fig-Ap-RS-I}
+\begin{minipage}[b]{0.38\textwidth}
+\includegraphics[width=\textwidth]{photo/AP-RS-Iphase.pdf}
+\end{minipage}
+}
+\subfigure[G-Phase]{\label{fig-Ap-RS-G}
+\begin{minipage}[b]{0.38\textwidth}
+\includegraphics[width=\textwidth]{photo/AP-RS-Gphase.pdf}
+\end{minipage}
+}
+\subfigure[The decoding process of important data.
+$B_L$ represents the lost data vector and $B_S$ represents the surviving data vector.
+$C_L$ and $C_S$ are the coefficient matrices of $B_L$ and $B_S$ respectively.]{\label{fig-Ap-RS-en}
+\begin{minipage}[b]{0.38\textwidth}
+\includegraphics[width=\textwidth]{photo/AP-RS-Iphase-en.pdf}
+\end{minipage}
+}
+\caption{Generation Matrix of RS-based Approximate Code. 
+$D_{I0}$ to $D_{I2}$ (dark blue) are important data sectors.
+$D_{M0}$ to $D_{M4}$ (light blue) are minor data sectors.
+$Q_{0}$ and $Q_{1}$ are important parity sectors (red).
+$P_{0}$ and $P_{1}$ are global parity sectors (orange).}\label{fig-Ap-RS}
+\end{figure}
 
-\begin{equation}
-\begin{pmatrix} 
-1&  1&  1\\
-\alpha_0 & \alpha_1 & \alpha_2 \\
-\alpha_0^2+\alpha_3^2+\alpha_4^2*\alpha_0 & \alpha_1^2 +\alpha_3^2+\alpha_4^2*\alpha_1 & \alpha_2^2+\alpha_3^2+\alpha_4^2*\alpha_2  \\
-\alpha_0^3+\alpha_3^3+\alpha_4^3*\alpha_0 & \alpha_1^3 +\alpha_3^3+\alpha_4^3*\alpha_1 & \alpha_2^3+\alpha_3^3+\alpha_4^3*\alpha_2  \\
-\end{pmatrix} 
+Without loss of generality, we use Figure \ref{fig-Ap-RS} to introduce the construction method of RS-based Approximate Code with parameter ($7,2,5,2,2$).
+
+\subsubsection{Encoding and Decoding Process}
+In \emph{I-Phase}, we encode 3 groups of important data sectors $D_{I0}$ to $D_{I2}$ and generate 2 groups of parity sectors $Q_{0}$ and $Q_{1}$. 
+The calculation of $q_{i,j}$ are defined by equation (\ref{q_ij}) and shown in Figure \ref{fig-Ap-RS-I}, where $A_k$ is the coefficient in Galois Field (GF). 
+In fact, the encoding process of $Q_{0}$ and $Q_{1}$ should be considered as a special decoding case that $Q_{0}$ and $Q_{1}$ have lost.
+
+\begin{equation}\label{q_ij}
+    \{ \sum_{j=0}^{h-1} A_{k,j} d_{i,j} + \sum_{j=0}^{s-1}A_{k,j+h} q_{i,j} = 0 
+    | 0 \leqslant i < t, 0 \leqslant k < s \}
 \end{equation}
 
-For example, $q_{1,1} = \alpha_0 d_{1,0} + \alpha_1 d_{1,1} + \alpha_2 d_{1,2}$.
-\begin{equation}\label{q_ij}
-    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j} d_{i,k}
+In \emph{G-Phase}, we use RS(5,2) to generate 2 global parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors.
+The calculation of $p_{i,j}$ are defined by equation (\ref{p_ij_1}) and (\ref{p_ij_2}).
+
+\begin{equation}\label{p_ij_1}
+    \{ \sum_{j=0}^{h-1} A_{k,j} d_{i,j} + \sum_{j=0}^{s-1}A_{k,j+h} q_{i,j} = p_{i,k-s}  
+    | 0 \leqslant i < t, s \leqslant k < s+m \}
+\end{equation}
+\begin{equation}\label{p_ij_2}
+    \{ \sum_{j=0}^{h+s-1} A_{k,j} d_{i,j} = p_{i,k-s} 
+    | t \leqslant i < r, s \leqslant k < s+m \}
 \end{equation}
 
-In \emph{I-Phase}, we use RS(5,2) to generate 2 parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors.
-The calculation of $p_{i,j}$ are defined by equation (\ref{p_ij_1}) and (\ref{p_ij_2}).
-For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.
+In approximate recovery mode, assume that any $k$ chunks fail $(m < k \leqslant m+s)$.
+We reorganized important data blocks, important parity blocks, and global parity blocks into surviving blocks set $B_S$ and lost blocks set $B_L$.
+We label their corresponding coefficient matrices as $C_S$ and $C_L$, as shown in Figure \ref{fig-Ap-RS-en}.
+We use the following equation to fully recover lost blocks.
+\begin{equation*}
+    B_L = (C_L)^{-1} \times C_S \times B_S
+\end{equation*}
+Furthermore, the encoding process of $Q_0$, $Q_1$, $P_0$ and $P_1$ of important data sectors are also calcuated by this equation.
 
-\begin{equation}\label{p_ij_1}
-    \mathop{p_{i,j}}\limits_{i<t} = 
-    \sum_{k=0}^{h-1} \alpha_k^{s+j} d_{i,k} +
-    \sum_{k=0}^{s-1} \alpha_{k+h}^{s+j} q_{i,k}
-\end{equation}
-\begin{equation}\label{p_ij_2}
-    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
-    \sum_{k=0}^{n-m-1} \alpha_k^{s+j} d_{i,k}
-\end{equation}
+\subsubsection{Proof of Correctness}
+The guarantee of correctness is based on the choice of coefficients. Here we define the coefficient matrix as Vandermonde matrix.
 
-The full recovery decoding process of RS-based Approximate Code is obvious since it is the same as the decoding process of RS(5,2).
-For the approximate decoding process, there are 4 independent equations that can tolerate any 4 disk failures because the coding coefficient matrix is full rank.
+The correctness of full recovery mode of RS-based Approximate Code is obvious since it is the same as the decoding process of RS(5,2), as shown in Figure \ref{fig-Ap-RS-G}.
 
-\subsubsection{ XOR-based Approximate Code}
-\textcolor{orange}{It is difficult to design XOR-based codes that m=2,s=1.
-Codes like EVENODD or STAR cannot be used to recover the important data when 3 disks fails.
-However, the desgin of m=1 is easy, because we only use horizontal parity blocks.
-}
+In approximate recovery mode, the key to ensuring that important data can tolerate any $m+s$ block failures is to prove that any $m+s$ columns in coefficient matrix is reversible.
+According to the number of global parity block losses (from 0 to $m$), the column combination of the coefficient matrix can be divided into $m+1$ cases.
+When no global parity sectors fail, the coefficient matrix must be full rank since it is a Vandermonde matrix.
+When some of global parity sectors fail, as $C_L$ in Figure \ref{fig-Ap-RS-en}, we calculate the coefficient determinant corresponding to the lost blocks.
+By expanding the coefficient determinant by the last column, we can get a Vandermonde determinant lacking a line, which is still full rank.
 
-\textcolor{orange}{One other way to generate XOR parity sectors is to divide each sector into multiple smaller blocks and apply EVENODD or RAID6 on them.
-This might be too complex but its correctness is easy to proof.}
+\subsection{ XOR-based Approximate Code}
+We take RAID-6 code
 
@@
 
-\subsection{\textcolor{orange}{Proof of Correctness}}
-\textcolor{orange}{I am not quite clear what to write here, our proof of correctness is organized in encoding and decoding process}
-
 \subsection{Properties of Approximate Code}
 
-We analyze the nature of the approximate code from the following aspects, and the calculation method of the relevant indicators is given in Table x.
-Low cost Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-Important data High reliability The approximate code guarantees the fault tolerance of the important data m+s.
-Flexibility The implementation of the approximate code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the approximate code can also be used for encoding such as LRC or MSR.
-Lower recovery overhead Due to the shorter checksum chain of important data blocks, the recovery code of the approximate code in the full recovery mode is less expensive.
+We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table x.
+\begin{itemize}
+    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
+    \item High reliability for important data. The Approximate Code guarantees the fault tolerance of the important data $m+s$.
+    \item Flexibility.
+The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the Approximate Code can also be used for encoding such as LRC or MSR.
+\end{itemize}
 

### 2019-04-09 ApproximateCode.tex
Update ApproximateCode.tex
a glitch in the cite.

@@
 Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance.
-On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints./ref{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
+On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints.\cite{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
 

### 2019-04-09 ApproximateCode.tex
Update ApproximateCode.tex
grammar mistake

@@
 Considering the vital role the I frame plays in the video coding, we therefore define I frame data as the critical data of a video file.
-Although some part of P frames may play a relatively important role in the decoding process of a video, it’s importance can not exceed that of the I frames.
+Although some part of P frames may play a relatively important role in the decoding process of a video, its importance can not exceed that of the I frames.
 

### 2019-04-10 ApproximateCode.tex
version 2.5

--- 2019-04-09 ApproximateCode.tex
@@
 
+\iffalse
 \begin{table}[]
@@
 \end{table}
+\fi
 
@@
 
-\textcolor{orange}{Something about H.264\dots}
-
 H.264 classifies all frames into three different categories:
@@
 \subsubsection{Video Frame Recovery}
-
-\textcolor{orange}{Add something related to the former subsection}
-
-\textcolor{blue}{In the circumstance of video approximate storage, it's common to lose some minor data making the video incomplete...}
 
@@
 
+\begin{table}[ht]
+\centering 
+\caption{Comparison of fault tolerance and storage overhead between approximate storage, RS and Approximate Code}\label{tab-AS-RS-AP}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Scheme & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate\\ Storage\end{tabular} & very low & some bits & -\\ \hline
+RS(n-m,m) & $\frac{n}{n-m}$ & $m$ & $m$  \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate\\ Code($n,m,r,s,t$)\end{tabular} &
+$\frac{n \times r}{(n-m)\times r -s\times t}$ & $m+s$ & $m$\\ \hline
+\end{tabular}
+\end{table}
+
 \subsection{Our Motivation}
-Based on Table [], the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+Based on Table \ref{tab-AS-RS-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+
 First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
@@
 Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
-To solve these two problems, we propose a new erasure code called approximation code.
+Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.
+
+To solve these problems, we propose a new erasure code called Approximation Code.
 It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.
@@
 
-We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table x.
+We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
 \begin{itemize}
@@
 \includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
-\caption{111}
+\caption{Overview of Approximate Code implementation}
 \label{fig-implementation}
@@
 Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data.
-In our design, the middle layer performs automatic data identification and data distribution.
-It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.
+We call it the approximate storage layer.
+The approximate storage layer is responsible for the identification and allocation of data. It controls the EC module and implements the encoding and decoding work of the Approximate Code.
 
 \subsection{Data Identification}
-For H.264 video data, we define I frames as important data, and P frames and B frames as minor data based on the analysis in the \ref{video storage}.
+The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer.
+We focus on the latter and take video file as an example to introduce our method of automatically distinguishing importance.
+
+For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as minor data based on the analysis in section \ref{video storage}.
 In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
@@
 We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size.
-We also define $\omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}$ as the actual important rate the code can provide.
+We also define $\omega_{act}$ as the actual important rate the code can provide by equation \ref{eq-ome-act}.
+\begin{equation}\label{eq-ome-act}
+    \omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}
+\end{equation}
+
   Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.
@@
 \begin{algorithmic}[1]
-\Require A stripe of video data.
-\Ensure $D_I$ and $D_M$.
-\State Divide video data into several GOPs;
+
+\Require  $n$, $m$ and $s$ from the settings of approximate storage layer. Get the type of erasure code.
+\Ensure $D_I$, $D_M$, $Q$ and $G$.
+\While {true}
+\State Divide data into several segments (several GOPs for video data);
 \State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
@@
 \Until All GOPs are classified;
+\EndWhile
+
 \end{algorithmic} 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/Data-distribution-v2.pdf}
+\includegraphics[width=0.32 \textwidth]{photo/Data-distribution-v2.pdf}
 \caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area.
@@
 \hline
-\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Efficiency\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
 (6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline

### 2019-04-10 ApproximateCode.tex
version 3.0.1

@@
 Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space.
-Meanwhile, to ensure the data reliability, distributed file systems usually use erasure code redundant data.
-However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive.
+Meanwhile, to ensure the data reliability, distributed file systems often use erasure codes to backup data.
+However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive.
 On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.
@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems.
-The results show that compared with the typical high-reliability erasure code schemes, Approximate Code reduces the storage overhead by 7.64\% at the expense of reasonable probability of data quality loss.
+\textcolor{blue}{The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide higher reliability of important data.}
 
@@
 
+//////////////////////
+
 Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
@@
 When more than $s$ disks fails, Approximate Code recovers the important data and then transfer the surviving data to the upper layer for recovery.
-With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage that is distinguishing data importance.
 
-This work is usually done by experienced programmers, but fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being inherently more important than others.
+//////////////////////
+
+With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage, distinguishing data importance.
+This work is traditionally done by experienced programmers.
+Fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being more important than others.
 For example, in the progressive transform codec (PTC) compressed image, control and run-length bits are much more important than refinement bits.
-Therefore, this work is done automatically by a system tailored to specific encodings in our design.
+Therefore, this work can be done automatically by a system tailored to specific encodings.
 
@@
 \begin{enumerate}
-\item We propose an approximation code that reduces storage overhead and improves the reliability and availability of important data with an approximate strategy.
-\item We prove the mathematical correctness of the approximation code.
-\item A series of experiments show that the approximate code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
+\item We propose Approximation Code that reduces storage overhead and improves the reliability and availability of important data with the approximate strategy.
+\item We prove the mathematical correctness of the Approximation Code.
+\item We perform a series of experiments and show that Approximate Code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
 \end{enumerate}
 
-The rest of the paper is organized as follows.
-In Section \ref{RelatedWork}, we introduce related work and our motivation.
+The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. 
 In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
-The evaluation is presented in Section \ref{Evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
+Section \ref{Implementation} introduce the implementation of our design.
+The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
 
@@
 
-\section{Implementation}
+\section{Implementation}\label{Implementation}
 

### 2019-04-11 ApproximateCode.tex
version 3.1

@@
 Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in Figure \ref{apcode-72522}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
+In the scenario shown in Figure \ref{fig-Ap-322}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
 Other $s \times t$ sectors are encoded for important data thus raise its reliability.
@@
 \centering
-\includegraphics[width=0.35\textwidth,height=40mm]{photo/chunk-sector.JPG}
-\caption{A sample of chunks and sectors}
-\label{chunk-sector}
+\includegraphics[width=0.4\textwidth,height=40mm]{photo/chunk.pdf}
+\caption{A sample of chunks and stripes}
+\label{fig-chunk}
 \end{figure}
@@
 For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in \ref{evaluation}.
+A more optimized parameter selection scheme for practical applications will be introduced in Section \ref{evaluation}.
 
 \subsection{Design of Approximate Code}
-We use Figure \ref{apcode-72522} to illustrate the construction of Approximate Code.
-In the $n$ chunks of each stripe, $m$ ones are for coding.
-In the remaining $n-m$ chunks, $s \times t$ additional sectors are for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
-For convenience, we label $h=n-m-s$ as the number of columns of important data that is storaged in $h \times t$ blocks in our assumption.
-
-Based on the above definition, our design has 5 configurable parameters $(n, m, r, s,t)$ that uniquely determine the construction of Approximate Code.
-Figure \ref{apcode-72522-v3} shows an example of Approximate Codes with $n = 7$, $m = 2$, $r=5$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.
-
-We then define the area of sectors as follows:
-\begin{itemize}
-    \item $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$ important data sector zone.
-    \item $D_M=\{d_{i,j}|t\leqslant i < r, 0\leqslant j < n-m \}$ minor data sector zone.
-    \item $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$ important parity sector zone. 
-    \item $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$ global parity sector zone.
-\end{itemize}
+We use Figure \ref{fig-Ap-322} to illustrate the construction of Approximate Code. We focus on a system cons
 
@@
 \centering
-\subfigure[sector label and encoding process]{
-    \includegraphics[width=0.32\textwidth]{photo/apcode-72522.PDF}
-    \label{apcode-72522-a}
-}
-\subfigure[sector sets]{
-    \includegraphics[width=0.13\textwidth]{photo/DDQG.pdf}
-    \label{apcode-72522-b}
-}
-\caption{A sample of Approximate Codes $(7,2,5,2,2)$ with 7 chunks where 2 of them are global parity chunks (orange zone $G$) and each chunk has 5 sectors.
-In this example, there are 6 sectors (dark blue zone $D_I$) for important data, 15 sectors (light blue zone $D_M$) for minor data and 4 sectors (red zone $Q$) encode important data.}
-\label{apcode-72522}
+\includegraphics[width=0.4\textwidth]{photo/AP-kmha-v2.pdf}
+\caption{A sample of Approximate Codes $(3,2,2)$ with $h=2$ layers of devices, where each layer contains $k=3$ data devices and $m=2$ parity devices.}
+\label{fig-Ap-322}
 \end{figure}
@@
 \subsection{Encoding and Decoding Process}
-We also use Figure \ref{apcode-72522} to illustrate the basic idea of encoding and decoding process of Approximate Code.
-
-The encoding process consists of two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). 
-The \emph{I-Phase} is expressed as two red arrows in the blod box, where $Q$ is generated to verify $D_I$, and the \emph{G-Phase} is expressed as a yellow triangle arrow, where $G$ is generated to verify $D_I$, $D_M$ and $Q$.
-
-The decoding process provides two modes: the approximate recovery mode and the full recovery mode.
-When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data, and if the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.
-
-It should be noted that in the calculation of $G$ in \emph{G-Phase} and in the decoding process in full recovery mode, we consider $D_I$, $D_M$ and $Q$ as the same, and the minimum coding unit is chunk.
-That is, when we do not distinguish the importance of the data($s,t = 0$), the Approximate Code is a typical $m$ disk redundancy code.
-
-In general, Approximate Code performs extra parities on important data.
-Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in several ways.
-Therefore, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can be used to construct Approximate Code.
-
-We then introduce two typical Approximate Code implementation schemes: RS-based and XOR-based Approximate Code.
-Different code selection of \emph{I-Phase} and \emph{G-Phase} will cause different effect.
 
 \subsection{RS-based Approximate Code}
-
-\begin{figure}[htp]
-\centering
-\subfigure[I-Phase]{\label{fig-Ap-RS-I}
-\begin{minipage}[b]{0.38\textwidth}
-\includegraphics[width=\textwidth]{photo/AP-RS-Iphase.pdf}
-\end{minipage}
-}
-\subfigure[G-Phase]{\label{fig-Ap-RS-G}
-\begin{minipage}[b]{0.38\textwidth}
-\includegraphics[width=\textwidth]{photo/AP-RS-Gphase.pdf}
-\end{minipage}
-}
-\subfigure[The decoding process of important data.
-$B_L$ represents the lost data vector and $B_S$ represents the surviving data vector.
-$C_L$ and $C_S$ are the coefficient matrices of $B_L$ and $B_S$ respectively.]{\label{fig-Ap-RS-en}
-\begin{minipage}[b]{0.38\textwidth}
-\includegraphics[width=\textwidth]{photo/AP-RS-Iphase-en.pdf}
-\end{minipage}
-}
-\caption{Generation Matrix of RS-based Approximate Code. 
-$D_{I0}$ to $D_{I2}$ (dark blue) are important data sectors.
-$D_{M0}$ to $D_{M4}$ (light blue) are minor data sectors.
-$Q_{0}$ and $Q_{1}$ are important parity sectors (red).
-$P_{0}$ and $P_{1}$ are global parity sectors (orange).}\label{fig-Ap-RS}
-\end{figure}
-
-Without loss of generality, we use Figure \ref{fig-Ap-RS} to introduce the construction method of RS-based Approximate Code with parameter ($7,2,5,2,2$).
-
-\subsubsection{Encoding and Decoding Process}
-In \emph{I-Phase}, we encode 3 groups of important data sectors $D_{I0}$ to $D_{I2}$ and generate 2 groups of parity sectors $Q_{0}$ and $Q_{1}$. 
-The calculation of $q_{i,j}$ are defined by equation (\ref{q_ij}) and shown in Figure \ref{fig-Ap-RS-I}, where $A_k$ is the coefficient in Galois Field (GF). 
-In fact, the encoding process of $Q_{0}$ and $Q_{1}$ should be considered as a special decoding case that $Q_{0}$ and $Q_{1}$ have lost.
-
-\begin{equation}\label{q_ij}
-    \{ \sum_{j=0}^{h-1} A_{k,j} d_{i,j} + \sum_{j=0}^{s-1}A_{k,j+h} q_{i,j} = 0 
-    | 0 \leqslant i < t, 0 \leqslant k < s \}
-\end{equation}
-
-In \emph{G-Phase}, we use RS(5,2) to generate 2 global parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors.
-The calculation of $p_{i,j}$ are defined by equation (\ref{p_ij_1}) and (\ref{p_ij_2}).
-
-\begin{equation}\label{p_ij_1}
-    \{ \sum_{j=0}^{h-1} A_{k,j} d_{i,j} + \sum_{j=0}^{s-1}A_{k,j+h} q_{i,j} = p_{i,k-s}  
-    | 0 \leqslant i < t, s \leqslant k < s+m \}
-\end{equation}
-\begin{equation}\label{p_ij_2}
-    \{ \sum_{j=0}^{h+s-1} A_{k,j} d_{i,j} = p_{i,k-s} 
-    | t \leqslant i < r, s \leqslant k < s+m \}
-\end{equation}
-
-In approximate recovery mode, assume that any $k$ chunks fail $(m < k \leqslant m+s)$.
-We reorganized important data blocks, important parity blocks, and global parity blocks into surviving blocks set $B_S$ and lost blocks set $B_L$.
-We label their corresponding coefficient matrices as $C_S$ and $C_L$, as shown in Figure \ref{fig-Ap-RS-en}.
-We use the following equation to fully recover lost blocks.
-\begin{equation*}
-    B_L = (C_L)^{-1} \times C_S \times B_S
-\end{equation*}
-Furthermore, the encoding process of $Q_0$, $Q_1$, $P_0$ and $P_1$ of important data sectors are also calcuated by this equation.
-
-\subsubsection{Proof of Correctness}
-The guarantee of correctness is based on the choice of coefficients. Here we define the coefficient matrix as Vandermonde matrix.
-
-The correctness of full recovery mode of RS-based Approximate Code is obvious since it is the same as the decoding process of RS(5,2), as shown in Figure \ref{fig-Ap-RS-G}.
-
-In approximate recovery mode, the key to ensuring that important data can tolerate any $m+s$ block failures is to prove that any $m+s$ columns in coefficient matrix is reversible.
-According to the number of global parity block losses (from 0 to $m$), the column combination of the coefficient matrix can be divided into $m+1$ cases.
-When no global parity sectors fail, the coefficient matrix must be full rank since it is a Vandermonde matrix.
-When some of global parity sectors fail, as $C_L$ in Figure \ref{fig-Ap-RS-en}, we calculate the coefficient determinant corresponding to the lost blocks.
-By expanding the coefficient determinant by the last column, we can get a Vandermonde determinant lacking a line, which is still full rank.
-
-\subsection{ XOR-based Approximate Code}
-We take RAID-6 code
-
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
 
@@
 
+\section{Experimental Setup}
+
+\subsection{Evaluation methodology}
+In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution.
+Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
+We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
+We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
+
+\subsubsection{Erasure Codes in Our Comparisons}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
+\subsubsection{Platforms and Configurations}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
+\subsubsection{Metrics}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+\subsubsection{Parameters and Assumption in Our Evaluation}
+\textcolor{gray}{
+    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
+}
+
 \section{Evaluation}\label{evaluation}
@@
 
-\subsection{Evaluation methodology}
-In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution.
-Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
-We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
-We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
-
-\subsubsection{Erasure Codes in Our Comparisons}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
-\subsubsection{Platforms and Configurations}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
-\subsubsection{Metrics}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-\subsubsection{Parameters and Assumption in Our Evaluation}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
 \subsection{Results}
@@
 }
+
 \section{Conclusion}\label{Conclusion}

### 2019-04-13 ApproximateCode.tex
version 3.1.1
version 3.2 add code and Section3

@@
 Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance.
-On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints./ref{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
+On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints.
+\cite{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
 
@@
 \subsection{Design of Approximate Code}
-We use Figure \ref{fig-Ap-322} to illustrate the construction of Approximate Code. We focus on a system cons
+The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $a$. 
+The nodes are divided into $h$ layers, and in each layer, $k$ data nodes generate $r$ local parity nodes. 
+We assume that each data node is composed of multiple chunks, while important data occupies $a$ of them.
+The global parity chunks are calculated by the important data chunks from $h$ nodes between layers so they only occupy $a \times k$ nodes of storage space.
+The construction of Approximate Code(3,2,2,1/3) can be illustrated by Figure \ref{fig-Ap-322}, where $X_i$ and $Y_i$ are data nodes, $P_{X/Yi}$ are local parity nodes and $G_i$ are global parity chunks.
+In this example, global parity chunks only consume 1 node storage space.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/AP-kmha-v2.pdf}
-\caption{A sample of Approximate Codes $(3,2,2)$ with $h=2$ layers of devices, where each layer contains $k=3$ data devices and $m=2$ parity devices.}
+\includegraphics[width=0.45\textwidth]{photo/AP-kmha-v4.pdf}
+\caption{A sample of Approximate Codes $(3,2,2,1/3)$ with $h=2$ layers of devices, where each layer contains $k=3$ data devices and $r=2$ parity devices.
+The important data occupies $1/3$ of the total data node.
+Data nodes are marked as water green and the more important data is marked in darker color. Local parity nodes are marked orange and global parity chunks are marked red.}
 \label{fig-Ap-322}
@@
 
+\subsection{Encoding Process}
+The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
+
+The local encoding process takes place in the layer, where data are encoded in node level.
+In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
+
+The global encoding process is independent of the local encoding process and is only for important data.
+It is designed to encode important data across layers in the simplest way, so we use XOR to generate global parity chunks.
+The global parity chunks can be stored in another layer or other nodes. The data layer and the global parity layer can be rotated to avoid uneven distribution of data.
+
+\subsubsection{RS-based Approximate Code}
 \subsection{Encoding and Decoding Process}
-
-\subsection{RS-based Approximate Code}
+The encoding process of Approximate Code is the same
 

### 2019-04-13 Apcode_reli/Hicode/main.cpp

@@ -1,0 +1,417 @@
+//
+//  main.cpp
+//  Hicode
+//
+//  Created by HY J on 2019/3/6.
+//  Copyright © 2019 HY J. All rights reserved.
+//
+#include "main.h"
+
+
+int print_map(vector< vector<int> > diskmap){
+    for(int i = 0 ; i < diskmap.size() ; ++i){
+        for(int j= 0 ; j < diskmap[i].size() ; ++j){
+            cout<<diskmap[i][j]<<"\t";
+        }
+        cout<<endl;
+    }
+    cout<<endl;
+    return 0;
+}
+
+int diskclean(vector< vector<int> > & diskmap){
+    for(int i = 0 ; i < diskmap.size() ; ++i){
+        for(int j = 0 ; j < diskmap[0].size() ; ++j){
+            diskmap[i][j]=0;
+        }
+    }
+    diskmap[diskmap.size()-1][diskmap[0].size()-1]=-2;
+    diskmap[diskmap.size()-1][diskmap[0].size()-2]=-2;
+    return 0;
+}
+
+int index2map(vector<vector<int>> & diskmap, bool* index){
+    int a = diskmap.size();
+    int b = diskmap[0].size();
+    
+    for(int i = 0 ; i < a ; ++i){
+        for(int j = 0 ; j < b ; ++j){
+            if(i == a-1 && j >= b-2){
+                continue;
+            }
+            diskmap[i][j]=index[i * b + j];
+        }
+    }
+    return 0;
+}
+
+int disk_break_RS(vector< vector<int> > &RSmap, bool* index, int & comb_num){
+    int length;
+    length = RSmap.size() * RSmap[0].size();
+    
+    if (!hasDone(index, length, DISK_BREAK_NUM))
+    {
+        //从左到右扫描数组
+        for (int i = 0; i < length - 1; i++)
+        {
+            //找到第一个“10”组合将其变成"01"组合
+            if (index[i] && !index[i + 1])
+            {
+                index[i] = false;
+                index[i + 1] = true;
+                
+                //将"01"组合左边的1移到最左边
+                int count = 0;
+                for (int j = 0; j < i; j++)
+                {
+                    if (index[j])
+                    {
+                        index[j] = false;
+                        index[count++] = true;
+                    }
+                }
+                index2map(RSmap, index);
+                //print_map(RSmap);
+                comb_num ++;
+                break;
+            }
+        }
+        return 0;
+    }
[…]

### 2019-04-13 Apcode_reli/Hicode/main.h

@@ -1,0 +1,46 @@
+//
+//  Header.h
+//  Hicode
+//
+//  Created by HY J on 2019/3/6.
+//  Copyright © 2019 HY J. All rights reserved.
+//
+#include <vector>
+#include <iostream>
+#include <time.h>
+#include <iomanip>
+
+
+#ifndef Header_h
+#define Header_h
+#define MAX 100
+#define RATE 10 //损坏率(%)
+#define TIMES 0
+#define DISK_BREAK_NUM 6
+
+
+using namespace std;
+//This project is for Hi-code
+
+/*磁盘存储形式
+            k          m
+     -------------  -------
+     |  |  |  |  |  |  |  |
+     -------------  -------
+l    |  |  |  |  |  |  |  |
+     -------------  -------
+     |  |  |  |  |  |  |  |
+     -------------  -------
+ 
+     -------------
+ 1   |  |  |  |  |
+     -------------
+ 0表示数据正常，1表示数据损坏，-1表示无此盘。
+ */
+
+int print_map(vector< vector<int> >);
+int Comb(int n, int k);
+void printRes(bool* index, int n);
+bool hasDone(bool* index, int n, int k);
+int index2map(vector<vector<int>> & diskmap, bool* index);
+#endif /* Header_h */

### 2019-04-13 ApproximateCode.tex
version 3.3

@@
 \centering
-\includegraphics[width=0.4\textwidth,height=40mm]{photo/chunk.pdf}
+\includegraphics[width=0.3\textwidth]{photo/chunk.pdf}
 \caption{A sample of chunks and stripes}
@@
 \centering 
-\caption{Comparison of fault tolerance and storage overhead between approximate storage, RS and Approximate Code}\label{tab-AS-RS-AP}
-\begin{tabular}{|c|c|c|c|}
+\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-RS-AP}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-Scheme & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate\\ Storage\end{tabular} & very low & some bits & -\\ \hline
-RS(n-m,m) & $\frac{n}{n-m}$ & $m$ & $m$  \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate\\ Code($n,m,r,s,t$)\end{tabular} &
-$\frac{n \times r}{(n-m)\times r -s\times t}$ & $m+s$ & $m$\\ \hline
+\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
+\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
+\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
+\multicolumn{2}{|c|}{Ap-Storage}& low & very low & high \\ \hline
+\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
+ & Minor &  & medium & medium \\ \hline
 \end{tabular}
@@
 The construction of Approximate Code(3,2,2,1/3) can be illustrated by Figure \ref{fig-Ap-322}, where $X_i$ and $Y_i$ are data nodes, $P_{X/Yi}$ are local parity nodes and $G_i$ are global parity chunks.
-In this example, global parity chunks only consume 1 node storage space.
+In this example, global parity chunks only consume 1 node of storage space.
 
@@
 
-\subsection{Encoding Process}
+\subsection{Overview of the Coding Scheme}
+\subsubsection{Encoding Process}
+
 The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
-
 The local encoding process takes place in the layer, where data are encoded in node level.
 In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
-
 The global encoding process is independent of the local encoding process and is only for important data.
@@
 
-\subsubsection{RS-based Approximate Code}
-\subsection{Encoding and Decoding Process}
-The encoding process of Approximate Code is the same
+\subsubsection{Decoding Process}
+Approximate Code decodes important and minor data in different ways. Since the minor data is only encoded in local way, its decoding process is on the contrary.
+The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
+\begin{enumerate}
+\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
+\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
+\item Inter-layer check again, reconstruct using the global parity chunks.
+\end{enumerate}
+
+\subsection{Recovery Mode}
+When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}.
+If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
+
+\subsubsection{Full Recovery Mode}
+In general, our parameter settings guarantee $h<k$, so the global parity chain is shorter than the local one and has a lower reconstruct overhead.
+In addition, the global parity chunks are encoded by XOR, which results in high decoding speed.
+Therefore, important data blocks tend to recover data using global parity blocks whenever possible, which makes the Approximate Code have low overall computational overhead and reconstruction costs in \emph{full recovery mode}.
+
+\subsubsection{Approximate Recovery Mode}
+
+\subsection{RS-based Approximate Code}
+\subsection{XOR-based Approximate Code}
+
+\subsection{Fault Tolerance}
+In this section we give the fault tolerance of important and secondary data in the approximate code.
+We first prove the correctness of our decoding process, and then write a program to exhaust all node failures, giving the data recovery capability under any node loss.
+Take the approximate code ($3, 2, 2, 1/3$) as an example.
+
+\iffalse
+\subsection{Reconstruct Cost}
+In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
+\subsubsection{Single node failure}
+When any one data node fails, the reconstruction cost of minor data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write.
+So the total amount of data that needs to be transferred is
+$$ (1-a)*(k+1) + a*(h+1) $$.
+
+For example, when node $X_0$ is lost in case of Approximate Codes $(3,2,2,1/3)$. The amount of data required to rebuild a node is:$\frac{2}{3}*4+\frac{1}{3}*3=\frac{11}{3}$
+\fi
+
+\begin{table}[ht]
+\centering 
+\caption{Comparison of storage overhead and reconstruction cost between Approximate Code, RS and RAID-6.}\label{tab-AS-RS-AP}
+\begin{tabular}{|c|c|c|}
+\hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Reconstruction Cost\\ (single data node failure)\end{tabular} \\ \hline
+RS($k,r$) & $\frac{k+r}{k}$ & $k$ \\ \hline
+RAID-6($k,2$) & $\frac{k+2}{k}$ & $k$ \\ \hline
+\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h,a$)\end{tabular} & $\frac{(k+r)h+ak}{kh}$ & $(1-a)*(k+1) + a*(h+1)$ \\ \hline
+\end{tabular}
+\end{table}
 

### 2019-04-15 ApproximateCode.tex
version 3.4

@@
 In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy.
-Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead.
+Approximate Code aims to ensure different reliability of important and unimportant data by means of erasure coding, thereby reducing storage overhead.
 It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures.
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems.
-\textcolor{blue}{The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide higher reliability of important data.}
+The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide high reliability of important data.
 
@@
 Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice.
-In contrast, cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data.
+In contrast, the amount of cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data.
 It provides lower storage overhead and write bandwidth than replication with the same fault tolerance.
@@
 Typical erasure codes configuration use three-disk fault tolerant array (3DFTS).
-However, its overhead is still too high and is excessive because simultaneous damage of triple disks is relatively rare.
+However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.
 
 The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy.
-Common methods are to ensure the reliability of important data while storing the minor data on relatively unreliable media or reducing their error correction coding.
+Common methods are to ensure the reliability of important data while storing the unimportant data on relatively unreliable media or reducing their error correction coding.
 Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data.
@@
 Also, some pixel errors in the image data do not affect the information of the entire picture.
-However, the direct application of approximate storage in a cloud storage system will result in minor data being unacceptable volatile.
+However, the direct application of approximate storage in a cloud storage system will result in the unimportant data being unacceptable volatile.
 
@@
 $D_I$   & the zone of important data sectors   \\ \hline
-$D_M$   & the zone of minor data sectors       \\ \hline
+$D_M$   & the zone of unimportant data sectors       \\ \hline
 $Q$     & the zone of important parity sectors \\ \hline
-$P$     & the zone of minor parity sectors     \\ \hline
+$P$     & the zone of unimportant parity sectors     \\ \hline
 \end{tabular}
@@
 \subsection{Existing Erasure Codes}
-
-\textcolor{orange}{Here we give some introduction to existing erasure codes
-Specifically, we need to illustrate the existing erasure codes for video applications in detail.
-Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}
 
@@
 
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
+Reed Solomon Code (RS code) is a kind of Maximum Distance Separable (MDS) Codes, which have the optimal storage efficiency.
+The encoding and decoding operations of RS code are based on Galois Field, which leads to a higher computational complexity comparing to XOR-based codes.
+
+However, due to its high scalability, RS code has been widely applied in traditional cloud storage systems. In a RS code which is delegated by RS($k$, $r$), $n = k + r$ denotes the total number
+of nodes participating in the erasure coding schema, $k$ stands for the number of data nodes, and $r$ is the number of parity nodes.
+Generally data is organized and encoded/decoded with the minimum coding unit block.
+RS($k$, $r$) can tolerate at most $r$ failures at the same time, and single node failure can be recovered from any $k$ survivors.
+The encoding case of RS code and the failure tolerance processus are shown in Figure 1.
+
+\begin{figure}[ht]
+\centering
+\begin{minipage}[b]{0.3\textwidth}
+\includegraphics[width=0.52\textwidth]{photo/RS1.jpg}
+\includegraphics[width=0.4\textwidth]{photo/RS2.jpg}
+\end{minipage}
+\caption{Encoding process of RS($5$, $3$)}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.3\textwidth]{photo/RS3.jpg}
+\caption{Recovery processing of RS($5$, $3$) in the case of 3 random failure}
+\end{figure}
+
+\textcolor{red}{In our case, RS code could be applied.
+As the important data are uniformly-distributed in every node, the data in every node could be considered independent to each other.
+The principal of video storage divides the data into a small part of important frame and other subordinate frames.
+If a storage failure occurs in a node that stores largely the important frame, the data recovery may not be complete because the loss of the important frame could lead to a video quality degradation.
+In this way, this kind of uniformly-distribution would not allow the failure causing the data loss bigger than expected.}
+
+\textcolor{red}{The data distribution assures the independency of nodes, the recovery of data could follow nearly the theoretical case.
+The recovery processus need the reversible matrix of original matrix.
+The calculation is shown in Figure 2.}
+
+Another type of erasure code worth mentioning is XOR based codes, which uses purely XOR operations.
+There are two different approaches to implement XOR codes.
+One is to use generator matrix\cite{plank2004practical} for encoding/decoding operations, and the other is done by using specific algorithm for each code\cite{huang2008star}.
+In nowadays cloud storage systems, erasure codes for correcting two or three disk failures are widely used to ensure the reliability, and XOR-based codes show great advantages on encoding/decoding speed when the storage system is recovering from failures.
+XOR-based codes can be further categorized as XOR-based codes used in RAID-6 and ones to backup triple disk failure.
+
+When it comes to RAID-6, Maximum Distance Separable (MDS) \cite{jin2009p} \cite{cassuto2009cyclic} \cite{blaum1999lowest} \cite{corbett2004row} \cite{blaum1995evenodd} \cite{bloemer1995xor} codes are frequently discussed.
+There are two types of MDS codes with different properties.
+One of them is called horizontal MDS codes, but it suffers from high write complexity and unbalanced I/O distribution.
+Accordingly, the other is called vertical MDS codes which has a common disadvantage of having resource-consuming partial strip write to continuous data.
+
+A novel and efficient XOR-based RAID-6 code, named hybrid code(h-code) \cite{inproceedings}, is introduced a few years ago.
+This type of codes exploits the benefits of both horizontal and vertical MDS codes, therefore achieving optimization of partial stripe writes for RAID-6 in addition.
+H code can be applied to any array of (p+1) disks, where p is a prime number.
+The parities in H-Code are typical row parity and anti-diagonal parity.
+H-code does not have a specialized anti-diagonal parity strip, while it distributes the anti-diagonal parity elements among all the disks.
+Its horizontal parity ensures a partial stripe write to continuous data elements in a row share the same row parity chain, which achieves optimal partial stripe write performance.
+H code can be applied to any array of (p+1) disks, where p is a prime number.
+The analysis shows that H-Code achieves excellent performance in storage efficiency, encoding/decoding computational complexity and single write complexity.
 
@@
 \centering 
-\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-RS-AP}
+\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
- & Minor &  & medium & medium \\ \hline
+ & unimportant &  & medium & medium \\ \hline
 \end{tabular}
@@
 \subsection{Our Motivation}
-Based on Table \ref{tab-AS-RS-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
 
@@
 \subsubsection{Decoding Process}
-Approximate Code decodes important and minor data in different ways. Since the minor data is only encoded in local way, its decoding process is on the contrary.
+Approximate Code decodes important and unimportant data in different ways. Since the unimportant data is only encoded in local way, its decoding process is on the contrary.
 The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
@@
 \subsection{Recovery Mode}
-When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}.
-If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
 
@@
 \subsection{RS-based Approximate Code}
+
 \subsection{XOR-based Approximate Code}
@@
 \subsection{Fault Tolerance}
-In this section we give the fault tolerance of important and secondary data in the approximate code.
-We first prove the correctness of our decoding process, and then write a program to exhaust all node failures, giving the data recovery capability under any node loss.
-Take the approximate code ($3, 2, 2, 1/3$) as an example.
+In this section we give the fault tolerance of important and unimportant data in the Approximate Code.
+We first prove the correctness of our decoding process, and then use a program to 
+iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.
+
+For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.
+
+For important data, We consider the \emph{full recovery mode} and the \emph{approximate recovery mode} separately.
+When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}.
+If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
+
+We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.
+
+Important data nodes can tolerate the loss of any 2r+1 data nodes
+At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.
+
+First consider only the data nodes:
+Second, for the case of all nodes:
 
@@
 \subsubsection{Single node failure}
-When any one data node fails, the reconstruction cost of minor data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write.
+When any one data node fails, the reconstruction cost of unimportant data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write.
 So the total amount of data that needs to be transferred is
@@
 
-For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as minor data based on the analysis in section \ref{video storage}.
+For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}.
 In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
@@
 The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
-For example, Data 3 is represnted by blue, and its key segment (10\%) and part of minor segment (10\%) are settled in $D_I$.
+For example, Data 3 is represnted by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
 The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$.
@@
 \begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (unimportant Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
 \end{tabular}
@@
 \hline
-\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (unimportant)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
 (6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline

### 2019-04-15 ApproximateCode.tex
version 3.5

@@
 Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in Figure \ref{fig-Ap-322}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
+In the scenario shown in Figure \ref{fig-ap-41425}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
 Other $s \times t$ sectors are encoded for important data thus raise its reliability.
@@
 \subsection{Existing Erasure Codes}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.3\textwidth]{photo/chunk.pdf}
-\caption{A sample of chunks and stripes}
-\label{fig-chunk}
-\end{figure}
 
@@
 \multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
-\multicolumn{2}{|c|}{Ap-Storage}& low & very low & high \\ \hline
+\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
 \multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
- & unimportant &  & medium & medium \\ \hline
+ & unimportant &  & medium & high \\ \hline
 \end{tabular}
@@
 In this section, we introduce the design of Approximate Code and its properties through a few simple examples. 
-For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in Section \ref{evaluation}.
+\textcolor{red}{For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
+A more optimized parameter selection scheme for practical applications will be introduced in Section} \ref{evaluation}.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.35\textwidth]{photo/chunk-block.pdf}
+\caption{A sample of chunks, stripes and blocks}
+\label{fig-chunk-block}
+\end{figure}
 
 \subsection{Design of Approximate Code}
-The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $a$. 
-The nodes are divided into $h$ layers, and in each layer, $k$ data nodes generate $r$ local parity nodes. 
-We assume that each data node is composed of multiple chunks, while important data occupies $a$ of them.
-The global parity chunks are calculated by the important data chunks from $h$ nodes between layers so they only occupy $a \times k$ nodes of storage space.
-The construction of Approximate Code(3,2,2,1/3) can be illustrated by Figure \ref{fig-Ap-322}, where $X_i$ and $Y_i$ are data nodes, $P_{X/Yi}$ are local parity nodes and $G_i$ are global parity chunks.
-In this example, global parity chunks only consume 1 node of storage space.
+The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $h$, $g$ and $s$.
+
+First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper.
+In a system of $n$ nodes, $k$ of them are data nodes and $r=n-k$ nodes are for parity.
+Each node can be divided into multiple blocks.
+We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}.
+The $n$ chunks constitute a \emph{stripe}.
+Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
+For the latter situation, we specifically use \emph{layer} instead of stripe, since these two cases will result in different performance and reliability.
+
+For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of unimportant data to important data is $a-1$.
+In addition, there is another $g$ global chunks, which are calculated only by the important data blocks.
+It should be point out that $g$ global parity chunks should be placed in $g$ different nodes and should be different from the data nodes.
+The number of important data block is $h \times k$, and they generate $h \times g$ global parity blocks.
+
+To sum up, the number of blocks involved in the approximate code is 
+$$((k+r)s + g) \times h$$
+
+Approximate Code guarantees that for each stripe, the unimportant data can tolerate any $r$ node failures.
+Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios.
+Important data are provided $r+g$ node failure tolerance, and $g$ is usually configured as $3-r$ to achieve tipical 3DFTS.
+
+The construction of Approximate Code (4,1,4,2,5) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
+This example includes 22 nodes.
+
+As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 layers with 22 nodes.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{photo/AP-kmha-v4.pdf}
-\caption{A sample of Approximate Codes $(3,2,2,1/3)$ with $h=2$ layers of devices, where each layer contains $k=3$ data devices and $r=2$ parity devices.
-The important data occupies $1/3$ of the total data node.
-Data nodes are marked as water green and the more important data is marked in darker color. Local parity nodes are marked orange and global parity chunks are marked red.}
-\label{fig-Ap-322}
+\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v5.pdf}
+\caption{A sample of Approximate Codes $(4,1,4,2,5)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
+The important data (marked as blue) occupies $1/5$ of the total data node, and generate $g=2$ global parity chunks (marked as red).}
+\label{fig-ap-41425}
 \end{figure}
 
-\subsection{Overview of the Coding Scheme}
+\iffalse
+\subsection{Encoding and Decoding Process}
 \subsubsection{Encoding Process}
-
 The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
-The local encoding process takes place in the layer, where data are encoded in node level.
+The local encoding process takes place in the stripe, where data are encoded in node level.
 In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
-The global encoding process is independent of the local encoding process and is only for important data.
-It is designed to encode important data across layers in the simplest way, so we use XOR to generate global parity chunks.
-The global parity chunks can be stored in another layer or other nodes. The data layer and the global parity layer can be rotated to avoid uneven distribution of data.
-
+The global encoding process is only for important data. It is designed to encode important data across stripes. There are also several ways to implement it.
 \subsubsection{Decoding Process}
@@
 \subsection{Recovery Mode}
-
 \subsubsection{Full Recovery Mode}
@@
 Therefore, important data blocks tend to recover data using global parity blocks whenever possible, which makes the Approximate Code have low overall computational overhead and reconstruction costs in \emph{full recovery mode}.
-
 \subsubsection{Approximate Recovery Mode}
+\fi
 
 \subsection{RS-based Approximate Code}
+We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,2,5)$ and its properties.
+The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks.
+It is easy to find appropriate coefficient to ensure important data forms the form of RS(4,3) and tolerate any 3 chunk failure.
+Figure \ref{fig-ap-rs} shows the generate matrix of Layer 0 in Figure \ref{fig-ap-41425}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
+\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$.
+$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
+\label{fig-ap-rs}
+\end{figure}
 
 \subsection{XOR-based Approximate Code}
+We introduce the construction of XOR-based Approximate Code $(4,1,4,2,5)$ and Approximate Code $(4,1,4,2,5)$
 
+Since we mainly provide 3DFTS for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{photo/AP-TIP.pdf}
+\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$.
+$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
+\label{fig-ap-TIP}
+\end{figure}
+
+\iffalse
 \subsection{Fault Tolerance}
@@
 Second, for the case of all nodes:
+\fi
 

### 2019-04-16 ApproximateCode.tex
version 3.6

@@
 
-\title{Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems}
+\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems}
 
@@
 \begin{abstract}
-Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space.
-Meanwhile, to ensure the data reliability, distributed file systems often use erasure codes to backup data.
-However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive.
-On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.
+Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
+Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
+Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems.
+Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.
 
-In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy.
-Approximate Code aims to ensure different reliability of important and unimportant data by means of erasure coding, thereby reducing storage overhead.
-It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures.
-To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems.
-The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide high reliability of important data.
+To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems.
+The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance.
+On one hand, for important data, Approximate Code provides triple parities to provide high reliability.
+On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process.
+To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
 
@@
 Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud [].
-Typical erasure codes configuration use three-disk fault tolerant array (3DFTS).
+Typical erasure codes configuration use three-disk fault tolerant array (3DFTs).
 However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.
@@
 The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy.
-Common methods are to ensure the reliability of important data while storing the unimportant data on relatively unreliable media or reducing their error correction coding.
+Common methods are to ensure the reliability of important data (marked as ID) while storing the unimportant data (marked as UD) on relatively unreliable media or reducing their error correction coding.
 Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data.
@@
 
-First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks.
+First, existing erasure codes generally reach or exceed 3DFTs, and use more than 3 parity disks.
 However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
@@
 \subsection{Design of Approximate Code}
-The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $h$, $g$ and $s$.
-
-First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper.
+The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $s$. 
+We use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper.
 In a system of $n$ nodes, $k$ of them are data nodes and $r=n-k$ nodes are for parity.
@@
 
-For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of unimportant data to important data is $a-1$.
-In addition, there is another $g$ global chunks, which are calculated only by the important data blocks.
-It should be point out that $g$ global parity chunks should be placed in $g$ different nodes and should be different from the data nodes.
+For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of important data to the whole chunk is $1/s$.
+In addition, there are another $3-r$ global chunks, which are calculated only by the important data blocks.
+It should be point out that the global parity chunks should be placed in several different nodes and should be different from the data nodes.
 The number of important data block is $h \times k$, and they generate $h \times g$ global parity blocks.
-
 To sum up, the number of blocks involved in the approximate code is 
-$$((k+r)s + g) \times h$$
+$$((k+r)s + 3-r) \times h$$
 
 Approximate Code guarantees that for each stripe, the unimportant data can tolerate any $r$ node failures.
-Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios.
-Important data are provided $r+g$ node failure tolerance, and $g$ is usually configured as $3-r$ to achieve tipical 3DFTS.
+Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.
 
-The construction of Approximate Code (4,1,4,2,5) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
+The construction of Approximate Code (4,1,4,3) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
 This example includes 22 nodes.
@@
 \centering
-\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v5.pdf}
-\caption{A sample of Approximate Codes $(4,1,4,2,5)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
-The important data (marked as blue) occupies $1/5$ of the total data node, and generate $g=2$ global parity chunks (marked as red).}
+\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v6.pdf}
+\caption{A sample of Approximate Codes $(4,1,4,3)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
+The important data (marked as blue) occupies $1/5$ of the total data node, and generate 2 global parity chunks (marked as red).}
 \label{fig-ap-41425}
@@
 \end{enumerate}
-
 \subsection{Recovery Mode}
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
+\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,3)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$.
+$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
+\label{fig-ap-rs}
+\end{figure}
+
 \subsection{RS-based Approximate Code}
-We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,2,5)$ and its properties.
+We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,3)$ and its properties.
 The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks.
@@
 
+\subsection{XOR-based Approximate Code}
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
+This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6,6$) and $(4,2,4,4)$.
+
+\subsubsection{RAID5-TIP Approximate Code}
 \begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
-\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$.
-$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
-\label{fig-ap-rs}
+\includegraphics[width=0.35\textwidth]{photo/AP-TIP-v2.pdf}
+\caption{The XOR-based Approximate Code ($5,1,6,6$), constructed based on RAID5 and TIP-code.}
+\label{fig-ap-TIP}
 \end{figure}
 
-\subsection{XOR-based Approximate Code}
-We introduce the construction of XOR-based Approximate Code $(4,1,4,2,5)$ and Approximate Code $(4,1,4,2,5)$
+Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6,6$) based on RAID5 and TIP-code \cite{zhang2015tip}.
+RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
+In each layer, local parity blocks provide horizontal XOR parity, and between layers, global parity provide diagonal parity and anti-diagonal parity.
 
-Since we mainly provide 3DFTS for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
+The local (horizontal) parity elements are calculated by the following encoding equations.
+\begin{align}
+    LP_{i,0} &= \bigoplus_{j=0}^{k-1} ID_{i,j} (0 \leqslant i < h)\\
+    LP_{i,p}(0<p<s) &= \bigoplus_{j=k(p-1)}^{kp-1} UD_{i,j} (0 \leqslant i < h)
+\end{align}
+
+When generating global parity blocks, the important data block, the local parity block, and the global parity block should be arranged as the encoding form of TIP-code.
+Figure \ref{fig-TIP} shows the coding method of diagonal and anti-diagonal parity blocks.
+Since the encoding process of important data blocks can be seen as RAID5 plus TIP-code, it is obvious that they achieve 3DFTs.
+
+\begin{figure}[h]
+\subfigure[Diagonal parity $GP_0$ to $GP_5$, (e.g., $GP_0=ID_{0,0} \oplus ID_{1,4} \oplus ID_{2,3} \oplus ID_{4,2} \oplus ID_{5,1}$]{
+    \includegraphics[width=0.2\textwidth]{photo/TIP-diag.pdf}
+}
+\subfigure[Anti-diagonal parity $GP_6$ to $GP_{11}$, (e.g., $GP_7=ID_{0,0} \oplus ID_{1,1} \oplus ID_{2,2} \oplus ID_{4,3} \oplus ID_{5,4}$)]{
+    \includegraphics[width=0.2\textwidth]{photo/TIP-anti-diag.pdf}
+}
+\caption{Encoding pf TIP-code}
+\label{fig-TIP}
+\end{figure}
+
+\subsubsection{EVENODD-STAR Approximate Code}
+Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($4,2,4,4$) based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
+EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
+In this case, important data blocks are distributed in Layer 0, while unimportant data blocks occupy the rest layers.
+Because the STAR code is constructed just by adding a reverse check chain to the EVENODD code. In this case, we design a global check block to store this check chain, so 3DFTs can be guaranteed.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/AP-TIP.pdf}
-\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,2,5)$, where $ID_i$ and $UD_i$ represnt the important and unimportant data in $N_i$.
-$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
-\label{fig-ap-TIP}
+\includegraphics[width=0.35\textwidth]{photo/AP-EVEN-star-v2.pdf}
+\caption{The XOR-based Approximate Code ($4,2,4,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
+\label{fig-ap-STAR}
 \end{figure}
@@
 iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.
-
 For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.
@@
 If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
-
 We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.
-
 Important data nodes can tolerate the loss of any 2r+1 data nodes
 At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.
-
 First consider only the data nodes:
 Second, for the case of all nodes:
-\fi
-
-\iffalse
 \subsection{Reconstruct Cost}
@@
 \centering 
-\caption{Comparison of storage overhead and reconstruction cost between Approximate Code, RS and RAID-6.}\label{tab-AS-RS-AP}
+\caption{Comparison of storage overhead and fault tolerance between Approximate Code, RS and several XOR-based codes.}\label{tab-AS-RS-AP}
 \begin{tabular}{|c|c|c|}
 \hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Reconstruction Cost\\ (single data node failure)\end{tabular} \\ \hline
-RS($k,r$) & $\frac{k+r}{k}$ & $k$ \\ \hline
-RAID-6($k,2$) & $\frac{k+2}{k}$ & $k$ \\ \hline
-\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h,a$)\end{tabular} & $\frac{(k+r)h+ak}{kh}$ & $(1-a)*(k+1) + a*(h+1)$ \\ \hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Fault Tolerance \\ \hline
+RS($k,r$) & $(k+r)/k$ & $r$ \\ \hline
+RAID-5($k,1$) & $(k+1)/k$ & 1 \\ \hline
+EVENODD($k,2$) & $(k+2)/k$ & 2 \\ \hline
+TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 \\ \hline
+\begin{tabular}[c]{@{}c@{}}Approximate Code\\ ($k,r,h,s$)\end{tabular} & $\frac {(k+r)s+3-r}{k*s}$ & r to 3 \\ \hline
 \end{tabular}
@@
     \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-    \item High reliability for important data. The Approximate Code guarantees the fault tolerance of the important data $m+s$.
-    \item Flexibility.
-The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the Approximate Code can also be used for encoding such as LRC or MSR.
+    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
+    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
 \end{itemize}
@@
 \section{Implementation}\label{Implementation}
-
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
+\includegraphics[height = 6.5cm]{photo/implementation-V2.pdf}
 \caption{Overview of Approximate Code implementation}
@@
 Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data.
-We call it the approximate storage layer.
-The approximate storage layer is responsible for the identification and allocation of data. It controls the EC module and implements the encoding and decoding work of the Approximate Code.
+We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
 
-\subsection{Data Identification}
+\subsection{Data Segmentation and Distribution Process}
 The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer.
@@
 For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}.
-In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
+\textcolor{orange}{In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
 We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space.
-The feasibility of this definition will be confirmed in \ref{evaluation}.
+The feasibility of this definition will be confirmed in} \ref{evaluation}.
 
@@
 The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
-For example, Data 3 is represnted by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
+For example, Data 3 is represented by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
 The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$.
@@
 In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution.
-Since 3DFTS is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
+Since 3DFTs is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
 We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.

### 2019-04-17 ApproximateCode.tex
version 3.6.1

@@
 \section{Introduction}
-Multimedia data consumes massive storage space in cloud storage systems, and this trend is exacerbated as applications demand higher resolution and frame rates.
-On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded.
-Rapidly growing data imposes very high requirements of reliability and availability on large-scale storage systems as well as low cost.
+For typical cloud storage systems such as Windows Azure [CITE] and Amazon AWS [CITE], erasure coding is a popular technique to provide both high reliability and low monetary cost [CITE EC], where triple disk failure fault tolerant arrays (3DFTs) are widely used.
+Typical erasure codes can be divided into two categories, RS-based Codes [CITE] and XOR-based codes [CITE].
+RS-based codes [CITE] are encoded according the Galois Field Computation in Reed Solomon Code [CITE], which allow flexible configuration and have a little higher computation cost.
+XOR-based codes [CITE] simplify the computation, but the scalability is a significant issue in previous literatures.
 
-Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice.
-In contrast, the amount of cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data.
-It provides lower storage overhead and write bandwidth than replication with the same fault tolerance.
-Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud [].
-Typical erasure codes configuration use three-disk fault tolerant array (3DFTs).
-However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.
+With the increasing demand on higher resolution and frame rate for video data, tremendous storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
+On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded [DESCRIBE AND CITE YOUTUBE].
+Therefore, in this paper, we set out to answer the following question,
+In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?
 
-The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy.
-Common methods are to ensure the reliability of important data (marked as ID) while storing the unimportant data (marked as UD) on relatively unreliable media or reducing their error correction coding.
-Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data.
-For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames.
-Also, some pixel errors in the image data do not affect the information of the entire picture.
-However, the direct application of approximate storage in a cloud storage system will result in the unimportant data being unacceptable volatile.
+To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage.
+[DESCRIBE AND CITE APPROXIMATE STORAGE] but the data reliability cannot be guaranteed.
+Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance should be sacrificed.
+Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
 
-//////////////////////
+To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
+The key idea of Approximate Code is treating the important/unimportant data in different ways.
+For important data, we add additional parities to provide high capability of fault tolerance.
+On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery.
+When triple disks fail, the lost data can be reconstructed via a fuzzy manner.
 
-Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors.
-In the scenario shown in Figure \ref{fig-ap-41425}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
-Other $s \times t$ sectors are encoded for important data thus raise its reliability.
-Approximate Codes ensure that the important data can tolerate $m+s$ device failures while all data can tolerate $m$ device failures.
-When more than $s$ disks fails, Approximate Code recovers the important data and then transfer the surviving data to the upper layer for recovery.
-
-//////////////////////
-
-With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage, distinguishing data importance.
-This work is traditionally done by experienced programmers.
-Fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being more important than others.
-For example, in the progressive transform codec (PTC) compressed image, control and run-length bits are much more important than refinement bits.
-Therefore, this work can be done automatically by a system tailored to specific encodings.
-
-Our work contributions include:
+We have the following contributions of this work,
 \begin{enumerate}
-\item We propose Approximation Code that reduces storage overhead and improves the reliability and availability of important data with the approximate strategy.
-\item We prove the mathematical correctness of the Approximation Code.
-\item We perform a series of experiments and show that Approximate Code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
+\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
+\item Approximate Code can be implemented by combining most erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
+\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
 \end{enumerate}
@@
 In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
-Section \ref{Implementation} introduce the implementation of our design.
+Section \ref{Implementation} introduce the implementation of our design, and section \ref{as-analysis} analysis the performance of approximate video storage.
 The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
@@
 In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
-\textcolor{red}{For convenience of description and without loss of generalizability, we use fewer data blocks (resulting in greater storage overhead).
-A more optimized parameter selection scheme for practical applications will be introduced in Section} \ref{evaluation}.
+
+The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $s$. 
+First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block} and \emph{stripe} we use in this paper.
+In a $n$-node system, $k$ of them are data nodes and $r=n-k$ nodes are for parity.
+Each node can be divided into multiple blocks.
+We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}.
+The $n$ chunks constitute a \emph{stripe}.
+Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
+%Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
+%We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.
 
@@
 \subsection{Design of Approximate Code}
-The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $s$. 
-We use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block}, \emph{stripe} and \emph{layer} we use in this paper.
-In a system of $n$ nodes, $k$ of them are data nodes and $r=n-k$ nodes are for parity.
-Each node can be divided into multiple blocks.
-We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}.
-The $n$ chunks constitute a \emph{stripe}.
-Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
-For the latter situation, we specifically use \emph{layer} instead of stripe, since these two cases will result in different performance and reliability.
+Approximate Code distribute important and unimportant data separately and mainly in two structure.
+As shown in Figure \ref{fig-ap-4143}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each chunk, and in \emph{Structure 2}, it occupies 1 of all $h$ data stripes.
+So, in \emph{Structure 1}, important data accounts for $1/s$ of all data, and $1/h$ in \emph{Structure 2}.
+In each stripe, $r$ chunks are local parity chunks, which is encoded by the rest $k$ data chunks in the stripe.
+In addition, there are another $3-r$ global chunks, which are calculated only by the important data blocks.
+It should be point out that the global parity chunks should be placed in different nodes and should be different from the data nodes.
 
-For $s$ blocks in each chunk, we assume that important data occupies 1 block, so the ratio of important data to the whole chunk is $1/s$.
-In addition, there are another $3-r$ global chunks, which are calculated only by the important data blocks.
-It should be point out that the global parity chunks should be placed in several different nodes and should be different from the data nodes.
-The number of important data block is $h \times k$, and they generate $h \times g$ global parity blocks.
+The number of important data block is $h \times k$ in \emph{Structure 1} and $s \times k$ in \emph{Structure 2}, so they generate $h \times (3-r))$ or $s \times (3-r))$ global parity blocks.
 To sum up, the number of blocks involved in the approximate code is 
-$$((k+r)s + 3-r) \times h$$
+\begin{itemize}
+    \item Structure 1: $(k+r)sh + (3-r) h$
+    \item Structure 2: $(k+r)sh + (3-r) s$
+\end{itemize}
 
@@
 
-The construction of Approximate Code (4,1,4,3) can be illustrated by Figure \ref{fig-ap-41425}, where $N_i$ are data nodes, $P_{i}$ are local parity nodes and $G_i$ are global parity chunks. 
-This example includes 22 nodes.
+The construction of Approximate Code (4,1,4,3,\emph{Structure 1}) and Approximate (3,1,3,3,\emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-4143},
 
-As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 layers with 22 nodes.
+As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 stripes with 22 nodes.
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{photo/AP-kmha-v6.pdf}
-\caption{A sample of Approximate Codes $(4,1,4,3)$ with $h=4$ layers of nodes, where each layer contains $k=4$ data nodes (marked as water green) and $r=1$ parity nodes(marked as orange).
-The important data (marked as blue) occupies $1/5$ of the total data node, and generate 2 global parity chunks (marked as red).}
-\label{fig-ap-41425}
+\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
+\caption{A sample of Approximate Codes $(4,1,4,3)$ in \emph{Structure 1}, and Approximate Code $(3,1,3,3)$ in \emph{Structure 2}.
+Data chunks are marked as $N_i$, important data are marked as water green, local parity chunks are marked as orange and global parity chunks are marked as red.
+}
+\label{fig-ap-4143}
 \end{figure}
-
-\iffalse
-\subsection{Encoding and Decoding Process}
-\subsubsection{Encoding Process}
-The encoding process of Approximate Code is simple, which can be divided into 2 parts: local and global.
-The local encoding process takes place in the stripe, where data are encoded in node level.
-In fact, EC methods such as RS-based, XOR-based, MSR, MDS or PMDS codes can all be used to construct the local parity nodes for different advantages.
-The global encoding process is only for important data. It is designed to encode important data across stripes. There are also several ways to implement it.
-\subsubsection{Decoding Process}
-Approximate Code decodes important and unimportant data in different ways. Since the unimportant data is only encoded in local way, its decoding process is on the contrary.
-The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
-\begin{enumerate}
-\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
-\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
-\item Inter-layer check again, reconstruct using the global parity chunks.
-\end{enumerate}
-\subsection{Recovery Mode}
-\subsubsection{Full Recovery Mode}
-In general, our parameter settings guarantee $h<k$, so the global parity chain is shorter than the local one and has a lower reconstruct overhead.
-In addition, the global parity chunks are encoded by XOR, which results in high decoding speed.
-Therefore, important data blocks tend to recover data using global parity blocks whenever possible, which makes the Approximate Code have low overall computational overhead and reconstruction costs in \emph{full recovery mode}.
-\subsubsection{Approximate Recovery Mode}
-\fi
 
@@
 \subsection{RS-based Approximate Code}
-We still use Figure \ref{fig-ap-41425} to illustrate RS-based Approximate Code $(4,1,4,3)$ and its properties.
+We still use Figure \ref{fig-ap-4143} to illustrate RS-based Approximate Code $(4,1,4,3)$ and its properties.
 The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks.
 It is easy to find appropriate coefficient to ensure important data forms the form of RS(4,3) and tolerate any 3 chunk failure.
-Figure \ref{fig-ap-rs} shows the generate matrix of Layer 0 in Figure \ref{fig-ap-41425}.
+Figure \ref{fig-ap-rs} shows the generate matrix of stripe 0 in Figure \ref{fig-ap-4143}.
 
@@
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
-In each layer, local parity blocks provide horizontal XOR parity, and between layers, global parity provide diagonal parity and anti-diagonal parity.
+In each stripe, local parity blocks provide horizontal XOR parity, and between stripes, global parity provide diagonal parity and anti-diagonal parity.
 
@@
 EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
-In this case, important data blocks are distributed in Layer 0, while unimportant data blocks occupy the rest layers.
+In this case, important data blocks are distributed in stripe 0, while unimportant data blocks occupy the rest stripes.
 Because the STAR code is constructed just by adding a reverse check chain to the EVENODD code. In this case, we design a global check block to store this check chain, so 3DFTs can be guaranteed.
@@
 \end{figure}
-
-\iffalse
-\subsection{Fault Tolerance}
-In this section we give the fault tolerance of important and unimportant data in the Approximate Code.
-We first prove the correctness of our decoding process, and then use a program to 
-iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.
-For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.
-
-For important data, We consider the \emph{full recovery mode} and the \emph{approximate recovery mode} separately.
-When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}.
-If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.
-We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.
-Important data nodes can tolerate the loss of any 2r+1 data nodes
-At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.
-First consider only the data nodes:
-Second, for the case of all nodes:
-\subsection{Reconstruct Cost}
-In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
-\subsubsection{Single node failure}
-When any one data node fails, the reconstruction cost of unimportant data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write.
-So the total amount of data that needs to be transferred is
-$$ (1-a)*(k+1) + a*(h+1) $$.
-
-For example, when node $X_0$ is lost in case of Approximate Codes $(3,2,2,1/3)$. The amount of data required to rebuild a node is:$\frac{2}{3}*4+\frac{1}{3}*3=\frac{11}{3}$
-\fi
 
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data.
-We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
+Compared with the traditional scheme that does not consider the meaning of the upper stripe data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate stripe between the upper stripe application and the underlying distributed storage system is necessary to preprocess the data.
+We call it the approximate storage stripe, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
 
-\subsection{Data Segmentation and Distribution Process}
-The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer.
-We focus on the latter and take video file as an example to introduce our method of automatically distinguishing importance.
+\subsection{Data Segmentation and Distribution module}
+The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data.
+A natural approach is to follow the GOP segmentation.
+According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important parts) and other data.
+(unimportant part).
 
-For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}.
-\textcolor{orange}{In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio.
-We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space.
-The feasibility of this definition will be confirmed in} \ref{evaluation}.
+The data distribution module distributes important data and unimportant data in different blocks and records the location.
+This location information is also defined as important data.
+This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
 
-\subsection{Data Distribution and Reorganization}
-Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames.
-Therefore, we store data in units of GOPs.
-Our main purpose is to store I frames and other frames separately.
-For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame.
-In the following description, we no longer consider such data especially and simply refer to them as I-frames.
-We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size.
-We also define $\omega_{act}$ as the actual important rate the code can provide by equation \ref{eq-ome-act}.
-\begin{equation}\label{eq-ome-act}
-    \omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}
-\end{equation}
+\subsection{Approximate Code module}
+The Approximate Code implements local and global encoding of $k*h$ data chunks and is responsible for reconstructing the wrong data chunk.
+When no more than $r$ chunks are corrupted, Approximation Code uses the local check block to recover all data, both important and minor.
+When there is no more than 3 loss of important data,
+2 forms
+Form 1: Important data and unimportant data are distributed at the same node.
+When there are no more than r blocks lost in a single stripe, the local check block completely recovers all data.
+When more than r but no more than 3 blocks are lost in a single stripe, the global check block recovers all important data, and the surviving unimportant data block and important data blocks are sent to the video recovery module.
+Form 2: The important data is distributed in a stripe, and the minor number is distributed on H-1 stripes. . .
+Important data stripe loses no more than 3 blocks and is fully recovered.
+The unimportant data stripe loses no more than r blocks and is fully recovered.
+The unimportant data stripe loses more than r, and the video is restored.
+The approximate code module is also responsible for allocating data blocks to ensure that the chunks of each stripe are distributed to different nodes, while ensuring that the global check chunk and the data chunk are not on one node.
 
-  Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.
+\subsection{Data Fuzzification and Video Recovery}
+In the approximate recovery mode, the recoverable and remaining data is passed to this module, and the blurred video is recovered through various video recovery techniques, and the upper application is notified.
+Through the content of the second chapter, we can approximate the data recovery.
+.
+.
 
-\begin{algorithm}[htb] 
-\caption{Data Distribution Algorithm} 
-\label{alg-data-dist} 
-\begin{algorithmic}[1]
+\section{Approximate Storage Analysis}\label{as-analysis}
 
-\Require  $n$, $m$ and $s$ from the settings of approximate storage layer. Get the type of erasure code.
-\Ensure $D_I$, $D_M$, $Q$ and $G$.
-\While {true}
-\State Divide data into several segments (several GOPs for video data);
-\State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
-\State Adjust $t$ to find the closest $\omega_{act}$ to $\omega_{max}$;
-\Repeat 
-\State Divide each GOP into two parts: $\omega_{act}$ and $1-\omega_{act}$;
-\State Store the former in $D_I$, the latter in $D_M$;
-\Until All GOPs are classified;
-\EndWhile
+\begin{figure*}
+\subfigure{
+    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
+}
+\subfigure{
+    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
+}
+\subfigure{
+    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
+}
+\subfigure{
+    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
+}
+\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}
+\end{figure*}
 
-\end{algorithmic} 
-\end{algorithm}
+In this chapter, we mainly discuss the number of video frames saved in Mode 1 when the unimportant data corruption is greater than the fault tolerance of the local calibration and the important data can be fully recovered.
+This proves that if the video data is not distinguished, in a typical
+This compares the ability of the approximation code to secure video data.
 
-\begin{algorithm}[htb] 
-\caption{Data Reorganization Algorithm} 
-\label{alg-data-reor} 
-\begin{algorithmic}[1] 
-\Require $D_I$ and $D_M$;
-\Ensure A stripe of video data;
-\State Find the parameter $(n,m,r,s,t)$ and calculate $\omega_{act}$.
-\Repeat
-\State Read an I frame from $D_I$ and record its length as $l$.
-\State Read $l \times \frac{1-\omega_{act}}{\omega_{act}}$ in $D_M$ and combine two parts.
-\Until All blocks are read.
-\end{algorithmic} 
-\end{algorithm}
+Indicator: number of frames restored
+Test situation:
+Test set:
 
-The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
-For example, Data 3 is represented by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
-The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$.
-This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time.
-Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.
+Our experiments analyzed a series of videos. We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).
+Since the approximation code stores the I frame as important data, the integrity of the I frame is always guaranteed in our scheme.
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.32 \textwidth]{photo/Data-distribution-v2.pdf}
-\caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area.
-Here for each data segment, $\omega_1=15\%$, $\omega_2=20\%$ and $\omega_3=10\%$, so the $\omega_{max}=20\%$.}
-\label{Data-distribution-v2}
-\end{figure}
+The experimental results are shown in Figure x. The approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.
 
-In addition, our approach can be applied to a variety of other data types.
-In fact, encoded multimedia data mostly has the property of coexisting important data and non-essential data, such as PTC encoding used in image storage[][].
-
-\section{Experimental Setup}
-
-\subsection{Evaluation methodology}
-In our evaluation, we first compare the Approximate Code with the RS code and some XOR-based codes to demonstrate the performance benefits of our solution.
-Since 3DFTs is a typical erasure code configuration, we use it as a baseline and set the minimum fault tolerance of important data to 3 ($ m + s \geqslant 3 $).
-We will then demonstrate the quality loss of multimedia data under the traditional and approximate recovery models of severe disk failure to assess the benefits of our approximate storage scheme.
-We use mathematical analysis and experiments to prove the effectiveness of the Approximate Code.
-
-\subsubsection{Erasure Codes in Our Comparisons}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
-\subsubsection{Platforms and Configurations}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
-\subsubsection{Metrics}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-\subsubsection{Parameters and Assumption in Our Evaluation}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
+Our experiments prove that if data is stored indiscriminately, the loss of important data will seriously affect the security of all data, and our scheme will control the data loss near the theoretical limit, ensuring video recovery and fuzzification.
+feasibility.
 
 \section{Evaluation}\label{evaluation}
-This section introduces a series of experiments we have conducted to verify the efficiendy of the Approximate Code.
 
-\begin{table*}[ht]
-\centering
-\caption{Summary on Various Erasure Codes}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
-RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
-MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
-Raid 6 & 2 & 2 & low & high & low \\ \hline
-SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (unimportant Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
-\end{tabular}
-\end{table*}
+Our experiment is mainly divided into two parts: erasure code and approximate storage analysis.
+The former mainly analyzes the performance of the approximate code and compares our scheme with the typical erasure code configuration; the latter mainly analyzes the data protection capability of the approximate code and other schemes in the case of data loss.
 
-\begin{table}[htbp]
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (unimportant)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
-(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
-(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
-(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
-(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
-(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
-(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
-(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
-(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
-(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
-(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
-\end{tabular}
-\end{table}
+In this section, we use mathematical analysis and a series of experiments to demonstrate the performance of the approximate code.
+Evaluation method: We choose RS code, TIP-code, EVENODD, STAR, RAID5 for comparison.
 
-\subsection{Results}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
+Mathematical analysis: We use the storage efficiency, fault tolerance and reconstruction cost defined above as a measure.
 
-\subsection{Analysis}
-\textcolor{orange}{Illustrate why Approximate Code achieve high reliability with low cost}
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
+In short, for each stripe, the unimportant data can tolerate any r node failures, while important data can tolerate any three node failures. However, the actual scene will be more complicated:
+For mode one. . .
+
+For fault tolerance, Mode 1 and Mode 2 will be different. Not only that, Mode 1 provides minimal fault tolerance, while Mode 2 provides near-code maximum fault tolerance.
+
+Obviously, for mode one, the approximate code can tolerate any r node failures, and the fault tolerance of important data is 3.
+For mode two, the approximate code provides an arbitrary level of r-node failure, and only if
+
+For mode two, if all chunks are distributed across different nodes, the approximate code provides the greatest degree of reliability. That is,
+
+We calculated the recovery efficiency and reconstruction cost of the approximate code in the case of single-node, two-node and three-node failures.
+Since the approximate code can be constructed in many forms, we mainly focus on it.
+.
+.
+.
+.
+.
 

### 2019-04-17 ApproximateCode.tex
version 3.6.2

@@
 In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
-Section \ref{Implementation} introduce the implementation of our design, and section \ref{as-analysis} analysis the performance of approximate video storage.
+Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
 The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
@@
 
-The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $h$ and $s$. 
+The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
 First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block} and \emph{stripe} we use in this paper.
@@
 Approximate Code distribute important and unimportant data separately and mainly in two structure.
-As shown in Figure \ref{fig-ap-4143}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each chunk, and in \emph{Structure 2}, it occupies 1 of all $h$ data stripes.
-So, in \emph{Structure 1}, important data accounts for $1/s$ of all data, and $1/h$ in \emph{Structure 2}.
+As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each chunk, and in \emph{Structure 2}, it occupies 1 of all $h$ data stripes.
+We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.
+
 In each stripe, $r$ chunks are local parity chunks, which is encoded by the rest $k$ data chunks in the stripe.
@@
 
-The number of important data block is $h \times k$ in \emph{Structure 1} and $s \times k$ in \emph{Structure 2}, so they generate $h \times (3-r))$ or $s \times (3-r))$ global parity blocks.
+The number of important data blocks is $h \times k$, and they generate $h \times (3-r)$ global parity blocks.
 To sum up, the number of blocks involved in the approximate code is 
-\begin{itemize}
-    \item Structure 1: $(k+r)sh + (3-r) h$
-    \item Structure 2: $(k+r)sh + (3-r) s$
-\end{itemize}
+$$(k+r)h^2 + (3-r) h$$
 
@@
 
-The construction of Approximate Code (4,1,4,3,\emph{Structure 1}) and Approximate (3,1,3,3,\emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-4143},
+The construction of Approximate Code (4,1,4, \emph{Structure 1}) and Approximate (3,1,3, \emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-414},
 
-As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 stripes with 22 nodes.
+%As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 stripes with 22 nodes.
 
@@
 \includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
-\caption{A sample of Approximate Codes $(4,1,4,3)$ in \emph{Structure 1}, and Approximate Code $(3,1,3,3)$ in \emph{Structure 2}.
+\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
 Data chunks are marked as $N_i$, important data are marked as water green, local parity chunks are marked as orange and global parity chunks are marked as red.
 }
-\label{fig-ap-4143}
+\label{fig-ap-414}
 \end{figure}
@@
 \includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
-\caption{The generate matrix of RS-based Approximate Codes $(4,1,4,3)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$.
+\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$.
 $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
@@
 \subsection{RS-based Approximate Code}
-We still use Figure \ref{fig-ap-4143} to illustrate RS-based Approximate Code $(4,1,4,3)$ and its properties.
-The local parity chunks are encoded by RS(4,1), and the important data generate another 2 global parity chunks.
-It is easy to find appropriate coefficient to ensure important data forms the form of RS(4,3) and tolerate any 3 chunk failure.
-Figure \ref{fig-ap-rs} shows the generate matrix of stripe 0 in Figure \ref{fig-ap-4143}.
+The construction of the Approximate Code based on RS is simple.
+In \emph{Structure 1}, the encoding unit is block.
+A horizontal RS parity is performed on the corresponding block in each chunk to generate a local parity block.
+At the same time, the important data blocks is horizontally verified by RS and generate multiple global check blocks.
+
+In \emph{Structure 2}, the encoding unit is chunk.
+We perform horizontal RS parity in each stripe to generate local parity chunks. The global parity chunk is generated only by the important data stripe.
+
+Figure \ref{fig-ap-rs} is the RS generation matrix with $k=4$ and $r=1$.
+It shows that to ensure that the coefficients of the local and the global parity are linearly independent is easy.
+If necessary, Approximation Code can easily achieve higher reliability guarantees based on RS, but in most cases this is excessive, so we will not discuss it here.
 
@@
 Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6,6$) and $(4,2,4,4)$.
+This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}) and ($4,2,4$, \emph{Structure 2}).
 
@@
 \includegraphics[width=0.35\textwidth]{photo/AP-TIP-v2.pdf}
-\caption{The XOR-based Approximate Code ($5,1,6,6$), constructed based on RAID5 and TIP-code.}
+\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
 \label{fig-ap-TIP}
@@
 
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6,6$) based on RAID5 and TIP-code \cite{zhang2015tip}.
+Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6,6$) in \emph{Structure 1}, based on RAID5 and TIP-code \cite{zhang2015tip}.
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
@@
 \subsubsection{EVENODD-STAR Approximate Code}
-Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($4,2,4,4$) based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
+Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($4,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
 EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
 In this case, important data blocks are distributed in stripe 0, while unimportant data blocks occupy the rest stripes.
-Because the STAR code is constructed just by adding a reverse check chain to the EVENODD code. In this case, we design a global check block to store this check chain, so 3DFTs can be guaranteed.
+Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code. In this case, we design a global parity block to store this parity chain, so 3DFTs can be guaranteed.
 
@@
 
-\begin{table}[ht]
-\centering 
-\caption{Comparison of storage overhead and fault tolerance between Approximate Code, RS and several XOR-based codes.}\label{tab-AS-RS-AP}
-\begin{tabular}{|c|c|c|}
-\hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Fault Tolerance \\ \hline
-RS($k,r$) & $(k+r)/k$ & $r$ \\ \hline
-RAID-5($k,1$) & $(k+1)/k$ & 1 \\ \hline
-EVENODD($k,2$) & $(k+2)/k$ & 2 \\ \hline
-TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 \\ \hline
-\begin{tabular}[c]{@{}c@{}}Approximate Code\\ ($k,r,h,s$)\end{tabular} & $\frac {(k+r)s+3-r}{k*s}$ & r to 3 \\ \hline
-\end{tabular}
-\end{table}
+\subsection{Case Study}
+We introduce
 
@@
 \begin{itemize}
-    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
+    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
+    \item Low Write Overhead: Approximate Code only needs to write $r*h$ local parity blocks and only $3-r$ global parity chunks, while tipical 3DFTs EC methods should write $3*h$ parity chunks.
     \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
@@
 \end{itemize}
+
+\begin{table}[ht]
+\centering 
+\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
+\begin{tabular}{|c|c|c|c|}
+\hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Write\\ Overhead\end{tabular} \\ \hline
+RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
+EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
+TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
+\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k*h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
+\end{tabular}
+\end{table}
 
@@
 A natural approach is to follow the GOP segmentation.
-According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important parts) and other data.
+According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data.
 (unimportant part).
@@
 
-\section{Approximate Storage Analysis}\label{as-analysis}
+\section{Approximate Recovery}\label{ap-recovery}
 
@@
 \section{Evaluation}\label{evaluation}
+
+Storage overhead
+
+Encoding and decoding performance
+
+write performance
+
+recovery Overhead
+
+Recovery Frame
 

### 2019-04-17 ApproximateCode.tex
version 3.6.3

@@
 
-\subsection{Case Study}
-We introduce
+\subsection{Decoding Case Study}
+This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.
+
+\subsubsection{Reconstruction cases in Structure 1}
+Under \emph{Structure 1}, important data and unimportant data are distributed in
+
+\subsubsection{Reconstruction cases in Structure 2}
 
@@
     \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-    \item Low Write Overhead: Approximate Code only needs to write $r*h$ local parity blocks and only $3-r$ global parity chunks, while tipical 3DFTs EC methods should write $3*h$ parity chunks.
+    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity chunks and only $3-r$ global parity chunks, while tipical 3DFTs EC methods should write $3 \times h$ parity chunks.
     \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
@@
 \hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Write\\ Overhead\end{tabular} \\ \hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
 RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
@@
 TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
-\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k*h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
+\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
 \end{tabular}

### 2019-04-17 ApproximateCode.tex
version 3.6.4

@@
 \multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
- & unimportant &  & medium & high \\ \hline
+ & Unimp &  & medium & high \\ \hline
 \end{tabular}
@@
 The $n$ chunks constitute a \emph{stripe}.
-Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
-%Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
+%Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
+Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or in different $n$-node systems.
 %We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.
@@
 \subsubsection{Reconstruction cases in Structure 1}
-Under \emph{Structure 1}, important data and unimportant data are distributed in
+Under \emph{Structure 1}, important data and unimportant data are distributed in the same chunks, so they suffer the same risk of device failures. 
+When $r$ or less nodes fail, all the data can be reconstructed by local parity.
+When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, where the important data are recovered by global parity chunks and the damaged video data will be processed by the video recovery and fuzzy algorithm.
 
 \subsubsection{Reconstruction cases in Structure 2}
+Under \emph{Structure 2}, we consider important and unimportant data chunks separately.
 

### 2019-04-17 ApproximateCode.tex
version 3.6.5

@@
 The $n$ chunks constitute a \emph{stripe}.
-%Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
-Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or in different $n$-node systems.
+Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
+%Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or in different $n$-node systems, which is controlled by the distributed file system.
 %We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.
@@
 \subsubsection{RAID5-TIP Approximate Code}
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.35\textwidth]{photo/AP-TIP-v2.pdf}
-\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
-\label{fig-ap-TIP}
-\end{figure}
 
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6,6$) in \emph{Structure 1}, based on RAID5 and TIP-code \cite{zhang2015tip}.
+Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure 1}, based on RAID5 and TIP-code \cite{zhang2015tip}.
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
@@
 \begin{figure}[h]
+\centering
+\includegraphics[width=0.3\textwidth]{photo/AP-TIP-v2.pdf}
+\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
+\label{fig-ap-TIP}
+\end{figure}
+
+\begin{figure}[h]
 \subfigure[Diagonal parity $GP_0$ to $GP_5$, (e.g., $GP_0=ID_{0,0} \oplus ID_{1,4} \oplus ID_{2,3} \oplus ID_{4,2} \oplus ID_{5,1}$]{
@@
 \subsubsection{EVENODD-STAR Approximate Code}
-Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($4,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
+Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($5,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
 EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
 In this case, important data blocks are distributed in stripe 0, while unimportant data blocks occupy the rest stripes.
-Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code. In this case, we design a global parity block to store this parity chain, so 3DFTs can be guaranteed.
+$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity chunks and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity chunks for stripe $i$.
+So the form of every stripe fit the construction of EVENODD.
+Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
+The $GP$ is the anti-diagonal parity chunk and guarantee important data chunks form the construction method of STAR, which ensures the 3DFTs.
 
@@
 \includegraphics[width=0.35\textwidth]{photo/AP-EVEN-star-v2.pdf}
-\caption{The XOR-based Approximate Code ($4,2,4,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
+\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
 \label{fig-ap-STAR}
@@
 
-\subsection{Decoding Case Study}
+\begin{figure}[ht]
+\subfigure[]{
+    \includegraphics[width = 0.3 \linewidth]{photo/star-hori.pdf}
+}
+\subfigure{
+    \includegraphics[width = 0.3 \linewidth]{photo/star-diag.pdf}
+}
+\subfigure{
+    \includegraphics[width = 0.3 \linewidth]{photo/star-anti.pdf}
+}
+\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity chunk based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
+\end{figure}
+
+\subsection{Case Study}
 This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.
@@
 When $r$ or less nodes fail, all the data can be reconstructed by local parity.
-When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, where the important data are recovered by global parity chunks and the damaged video data will be processed by the video recovery and fuzzy algorithm.
+When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity chunks and the damaged video data will be processed by the video recovery and fuzzy algorithm.
 
@@
 
-\subsection{Properties of Approximate Code}
+For node level failure, the fault tolerance of \emph{Structure 2} is exactly as \emph{Structure 1},When it comes to chunk level failures, \emph{Structure 2} can tolerate more unimportant data chunk failures than \emph{Structure 1}.
+The parity chain of important data does not pass through the unimportant data, so the damage of these chunks does not affect the recovery of important data.
+
+///////////////////////
+Under the random probability model of chunks, the probability of failure of the Approximate Code under 4 chunk damage is
+\begin{equation}
+    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
+\end{equation}
+which is the 4 chunk failure situation in $k$ important data chunks and 3 important parity chunks.
+For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
+
+\subsection{Properties of Approximate Code}\label{properties}
 
@@
 \subsection{Approximate Code module}
-The Approximate Code implements local and global encoding of $k*h$ data chunks and is responsible for reconstructing the wrong data chunk.
-When no more than $r$ chunks are corrupted, Approximation Code uses the local check block to recover all data, both important and minor.
-When there is no more than 3 loss of important data,
-2 forms
-Form 1: Important data and unimportant data are distributed at the same node.
-When there are no more than r blocks lost in a single stripe, the local check block completely recovers all data.
-When more than r but no more than 3 blocks are lost in a single stripe, the global check block recovers all important data, and the surviving unimportant data block and important data blocks are sent to the video recovery module.
-Form 2: The important data is distributed in a stripe, and the minor number is distributed on H-1 stripes. . .
-Important data stripe loses no more than 3 blocks and is fully recovered.
-The unimportant data stripe loses no more than r blocks and is fully recovered.
-The unimportant data stripe loses more than r, and the video is restored.
-The approximate code module is also responsible for allocating data blocks to ensure that the chunks of each stripe are distributed to different nodes, while ensuring that the global check chunk and the data chunk are not on one node.
+The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance.
+For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
+
+Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
 \subsection{Data Fuzzification and Video Recovery}
-In the approximate recovery mode, the recoverable and remaining data is passed to this module, and the blurred video is recovered through various video recovery techniques, and the upper application is notified.
-Through the content of the second chapter, we can approximate the data recovery.
-.
-.
+In the approximate recovery mode, the remaining data and important data are transferred to this module.
+Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.
 
@@
 
-\begin{figure*}
+\begin{figure*}\label{fig-node-lost}
 \subfigure{
@@
 }
-\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}
+\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
 \end{figure*}
 
-In this chapter, we mainly discuss the number of video frames saved in Mode 1 when the unimportant data corruption is greater than the fault tolerance of the local calibration and the important data can be fully recovered.
-This proves that if the video data is not distinguished, in a typical
-This compares the ability of the approximation code to secure video data.
+In the approximate recovery mode, since unimportant data suffers unrecoverable loss, the recovery of damaged video files must be considered.
+Therefore, we evaluate the recovery of the video file in this section.
 
-Indicator: number of frames restored
-Test situation:
-Test set:
+\subsection{Experimental Setup}
+\subsubsection{Coding Algorithm} 
+We evaluate the condition of the video of H.264 encoding [] under approximate recovery.
+Mainly because H.264 is an advanced video coding algorithm widely used at present, at the same time, the common advanced coding algorithms have similar coding processes.
 
-Our experiments analyzed a series of videos. We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).
+\subsubsection{Data Set}
+We choose 100 videos from xxx data set[]. All videos are stored in ``.mp4'' format at 1280*720 HD resolution.
+
+\subsubsection{Metrics}
+We use the number of frames saved as an indicator to evaluate the ability of the approximate storage and normal scheme to preserve data in the event of an unrecoverable node failure.
+
+We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).
+
 Since the approximation code stores the I frame as important data, the integrity of the I frame is always guaranteed in our scheme.
 
-The experimental results are shown in Figure x. The approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.
+\subsubsection{Simulation}
+We store the video files on a single disk according to the approximate storage scheme and the common scheme, while traversing the damage of all the disks, from 1 to n-1, and counting the number of damaged p-frames and b-frames.
+We use this to get the number of P and B frames that can be completely saved in the case of m out of n disks.
 
+\subsection{Results}
+The experimental results are shown in Figure \ref{fig-node-lost}, where $n$ is 4,5,6 and 8.
+In a 8-node array, when 2 nodes are unrecoverable, the approximate recovery method protects nearly 1/4 P or B frames, while the common method lost more than half of these frames.
+In addition, the approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.
+
+\subsection{Analysis}
 Our experiments prove that if data is stored indiscriminately, the loss of important data will seriously affect the security of all data, and our scheme will control the data loss near the theoretical limit, ensuring video recovery and fuzzification.
@@
 
+\subsection{Frame Recovery ????}
+
 \section{Evaluation}\label{evaluation}
+In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code in HDFS. 
+\subsection{Evaluation Methodology }
+We choose the RS code to compare with several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6.
+Since 3DFTs are typical configurations, we set the number of check nodes for the RS to 3.
+Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
 
-Storage overhead
+\subsubsection{Metrics and Methods for Mathematical Analysis: }
+We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Write(update) Cost} defined in Section \ref{properties} as measure.
+We first analyze the impact of the settings of the three parameters on these metrics, then we compare these matrics with several EC methods.
 
-Encoding and decoding performance
+\subsubsection{Metrics and Methods for Experiments: }
+We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
 
-write performance
+Our experiment includes the calculation of these two metrics and can mainly be divided into several cases.
+We measure the encoding time by calculating the time to generate all parity blocks, and we measure the recovery time by calculating the time to fully or approximately recover the failure nodes.
+Both of them should be divided into 3 situation: single, double and triple node, so we discuss them separately.
+Also, the encoding and recovery time consist of computation time, I/O time and transimission time in distributed file system, which should be considered separately.
 
-recovery Overhead
+The environment of our experiments are shown in Table \ref{tab-platform}.
+We set a Hadoop system with one NameNode and 4 DataNodes.
+\textcolor{gray}{text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
 
-Recovery Frame
+\begin{table}[ht]
+\begin{tabular}{|l|l|}
+\hline
+Description & DELL R730 Server \\ \hline
+CPU & Intel Xeon 3.0GHz \\ \hline
+NIC 1Gbps & 1Gbps \\ \hline
+Memory & 32GB \\ \hline
+Disk & 8TB HDD \\ \hline
+OS & Linux 3.19 \\ \hline
+Platform & Hadoop HDFS 3.0.3 \\ \hline
+\end{tabular}
+\caption{Details of Our Evaluation Platform}\label{tab-platform}
+\end{table}
 
-Our experiment is mainly divided into two parts: erasure code and approximate storage analysis.
-The former mainly analyzes the performance of the approximate code and compares our scheme with the typical erasure code configuration; the latter mainly analyzes the data protection capability of the approximate code and other schemes in the case of data loss.
+\subsection{Results of Mathematical Analysis }
+In Figure X, we summarize the storage overhead and fault tolerance of the approximate code. It also shows the theoretical overhead of a single node write or update.
 
-In this section, we use mathematical analysis and a series of experiments to demonstrate the performance of the approximate code.
-Evaluation method: We choose RS code, TIP-code, EVENODD, STAR, RAID5 for comparison.
+\begin{itemize}
+    \item Storage efficiency. . .
+    \item Fault tolerance. . .
+    \item Write overhead. . .
+\end{itemize}
 
-Mathematical analysis: We use the storage efficiency, fault tolerance and reconstruction cost defined above as a measure.
+\subsection{Encoding Performance}
+We use Approximate Code (4,2,4) and (5,1,6)...
 
-In short, for each stripe, the unimportant data can tolerate any r node failures, while important data can tolerate any three node failures. However, the actual scene will be more complicated:
-For mode one. . .
+\subsection{Recovery Time}
+We use Approximate Code (4,2,4) and (5,1,6)...
 
-For fault tolerance, Mode 1 and Mode 2 will be different. Not only that, Mode 1 provides minimal fault tolerance, while Mode 2 provides near-code maximum fault tolerance.
-
-Obviously, for mode one, the approximate code can tolerate any r node failures, and the fault tolerance of important data is 3.
-For mode two, the approximate code provides an arbitrary level of r-node failure, and only if
-
-For mode two, if all chunks are distributed across different nodes, the approximate code provides the greatest degree of reliability. That is,
-
-We calculated the recovery efficiency and reconstruction cost of the approximate code in the case of single-node, two-node and three-node failures.
-Since the approximate code can be constructed in many forms, we mainly focus on it.
-.
-.
-.
-.
-.
-
+\subsection{Analysis}
 \section{Conclusion}\label{Conclusion}

### 2019-04-19 ApproximateCode.tex
version 3.7.1

@@
 \section{Related Work and Our Motivation}\label{RelatedWork}
-This section presents background on erasure codes, related video storage methods, approximate storage, and our motivation.
+In this section, we introduce the background of Video frame recovery, existing solutions to reduce storage cost and the motivation of this paper.
+To facilitate the discussion, we summarize the symbols used in this paper in Table \ref{parameter}.
 
-\iffalse
 \begin{table}[]
+\caption{The symbols used in this paper.}\label{parameter}
+\centering
 \begin{tabular}{|c|l|}
 \hline
-Symbols & Description                          \\ \hline\hline
-$n$     & the number of chunks in a stripe     \\ \hline
-$m$     & the number of parity chunks          \\ \hline
-$r$     & the number of sectors in a chunk     \\ \hline
-$s$     & the number of columns of $D_I$       \\ \hline
-$t$     & the number of rows of $D_I$          \\ \hline
-$D_I$   & the zone of important data sectors   \\ \hline
-$D_M$   & the zone of unimportant data sectors       \\ \hline
-$Q$     & the zone of important parity sectors \\ \hline
-$P$     & the zone of unimportant parity sectors     \\ \hline
+Symbols & Description \\ \hline
+$k$ & the number of data nodes in an array \\ \hline
+$r$ & the number of local parity nodes in an array \\ \hline
+$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
+$h$ & the number of arrays \\ \hline
+$s$ & the number of blocks in a node \\ \hline
+LP & local parity nodes \\ \hline
+GP & global parity nodes \\ \hline
+ID & important data \\ \hline
+UD & unimportant data \\ \hline
+ &  \\ \hline
 \end{tabular}
 \end{table}
-\fi
 
 \subsection{Existing Erasure Codes}
+Reliability is a critical issue since disk failures are typical in storage systems.
+To improve the reliability of storage systems, several RAID forms (e.g., RAID-5, RAID-6, 3DFTs) and erasure codes are proposed by researchers.
+Traditional erasure codes can be categorized into two classes, Maximum Distance Separable (MDS) codes and non-MDS codes.
+MDS codes aim to offer data protection with optimal storage efficiency.
+On the other hand, non-MDS codes improve the performance or reliability by consuming extra storage space.
 
-Reed Solomon Code (RS code) is a kind of Maximum Distance Separable (MDS) Codes, which have the optimal storage efficiency.
-The encoding and decoding operations of RS code are based on Galois Field, which leads to a higher computational complexity comparing to XOR-based codes.
+In the past two decades, several
+famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD
+code [1], RDP code [8], Blaum-Roth code[3], X-code [44], Liberation code [28], Liber8tion code [27], Cyclic [7] code, B-Code [45], Code-M [40], H-code [43], P-code [20] and HVcode [36], etc.
 
-However, due to its high scalability, RS code has been widely applied in traditional cloud storage systems. In a RS code which is delegated by RS($k$, $r$), $n = k + r$ denotes the total number
-of nodes participating in the erasure coding schema, $k$ stands for the number of data nodes, and $r$ is the number of parity nodes.
-Generally data is organized and encoded/decoded with the minimum coding unit block.
-RS($k$, $r$) can tolerate at most $r$ failures at the same time, and single node failure can be recovered from any $k$ survivors.
-The encoding case of RS code and the failure tolerance processus are shown in Figure 1.
+In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [33], Cauchy-RS codes [4], STAR code [19], Triple-Star code [41], Triple-Parity code [9], HDD1 code [39], RSL-code [10], RL-code [11], and so on.
+Typical non-MDS codes contain WEAVER codes [14], HoVer
+codes [13], T-code [38], HDD2 code [39], Pyramid codes [18], Local Reconstruction Codes [16], Locally Repairable Codes [34], etc.
 
-\begin{figure}[ht]
-\centering
-\begin{minipage}[b]{0.3\textwidth}
-\includegraphics[width=0.52\textwidth]{photo/RS1.jpg}
-\includegraphics[width=0.4\textwidth]{photo/RS2.jpg}
-\end{minipage}
-\caption{Encoding process of RS($5$, $3$)}
-\end{figure}
+Several classic erasure codes are illustrated in detail as below,
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.3\textwidth]{photo/RS3.jpg}
-\caption{Recovery processing of RS($5$, $3$) in the case of 3 random failure}
-\end{figure}
+%从这里开始简单讲解几种RAID-6或三盘容错阵列的纠删码，如RS，EVENODD，RDP，STAR，LRC, H-Code，TIP-Code等，并且用编码图来说明（主要是实验中用到的几种编码）。
 
-\textcolor{red}{In our case, RS code could be applied.
-As the important data are uniformly-distributed in every node, the data in every node could be considered independent to each other.
-The principal of video storage divides the data into a small part of important frame and other subordinate frames.
-If a storage failure occurs in a node that stores largely the important frame, the data recovery may not be complete because the loss of the important frame could lead to a video quality degradation.
-In this way, this kind of uniformly-distribution would not allow the failure causing the data loss bigger than expected.}
-
-\textcolor{red}{The data distribution assures the independency of nodes, the recovery of data could follow nearly the theoretical case.
-The recovery processus need the reversible matrix of original matrix.
-The calculation is shown in Figure 2.}
-
-Another type of erasure code worth mentioning is XOR based codes, which uses purely XOR operations.
-There are two different approaches to implement XOR codes.
-One is to use generator matrix\cite{plank2004practical} for encoding/decoding operations, and the other is done by using specific algorithm for each code\cite{huang2008star}.
-In nowadays cloud storage systems, erasure codes for correcting two or three disk failures are widely used to ensure the reliability, and XOR-based codes show great advantages on encoding/decoding speed when the storage system is recovering from failures.
-XOR-based codes can be further categorized as XOR-based codes used in RAID-6 and ones to backup triple disk failure.
-
-When it comes to RAID-6, Maximum Distance Separable (MDS) \cite{jin2009p} \cite{cassuto2009cyclic} \cite{blaum1999lowest} \cite{corbett2004row} \cite{blaum1995evenodd} \cite{bloemer1995xor} codes are frequently discussed.
-There are two types of MDS codes with different properties.
-One of them is called horizontal MDS codes, but it suffers from high write complexity and unbalanced I/O distribution.
-Accordingly, the other is called vertical MDS codes which has a common disadvantage of having resource-consuming partial strip write to continuous data.
-
-A novel and efficient XOR-based RAID-6 code, named hybrid code(h-code) \cite{inproceedings}, is introduced a few years ago.
-This type of codes exploits the benefits of both horizontal and vertical MDS codes, therefore achieving optimization of partial stripe writes for RAID-6 in addition.
-H code can be applied to any array of (p+1) disks, where p is a prime number.
-The parities in H-Code are typical row parity and anti-diagonal parity.
-H-code does not have a specialized anti-diagonal parity strip, while it distributes the anti-diagonal parity elements among all the disks.
-Its horizontal parity ensures a partial stripe write to continuous data elements in a row share the same row parity chain, which achieves optimal partial stripe write performance.
-H code can be applied to any array of (p+1) disks, where p is a prime number.
-The analysis shows that H-Code achieves excellent performance in storage efficiency, encoding/decoding computational complexity and single write complexity.
-
-\subsection{Video Storage}\label{video storage}
-For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage.
-Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, and that is why we focus on such algorithms.
-
-H.264 is one of the advanced algorithms for this type of work.
-This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
-For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
-
-H.264 classifies all frames into three different categories:
-\begin{enumerate}
-    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
-    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
-    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
-\end{enumerate}
-In order to prevent the circumstance where a P or B frame references another distant frame, the concept of GOP is introduced.
-A GOP consists of multiple consecutive I,P and B frames which are independent of the frames in other GOPs.
-In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}.
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
-\caption{A sample of GOPs in H.264}
-\label{H264-IPB}
-\end{figure}
-
-\subsubsection{Video Frame Recovery}
+\subsection{Video Frame Recovery}
 
@@
 Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
-
-The methods are relied on the completeness of some video frame, which enhances the importance of the only intact type of frame data in commonly used H.264 standard: the I frame.
 
@@
 To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
-
-In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP.
-An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to fail.
-In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frames depend on it.
-
-Considering the vital role the I frame plays in the video coding, we therefore define I frame data as the critical data of a video file.
-Although some part of P frames may play a relatively important role in the decoding process of a video, it’s importance can not exceed that of the I frames.
+Therefore, it is very important to distinguish the importance of video data. This can usually be done by an experienced expert or automatically by a program.
 
@@
 \section{Approximate Code}\label{ApCode}
-In this section, we introduce the design of Approximate Code and its properties through a few simple examples.
+In this section, we introduce Approximate Code and its properties through a few simple examples.
 
+\subsection{Overview of Approximate Code}
 The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
-First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block} and \emph{stripe} we use in this paper.
-In a $n$-node system, $k$ of them are data nodes and $r=n-k$ nodes are for parity.
-Each node can be divided into multiple blocks.
-We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}.
-The $n$ chunks constitute a \emph{stripe}.
-Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
-%Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or in different $n$-node systems, which is controlled by the distributed file system.
-%We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.
+In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
+Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
+Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$
 
-\begin{figure}[ht]
+\subsection{Framework Design}
+The Approximate Code provides an erasure code framework for video storage in the cloud system.
+It uses an approximate strategy to split the erasure code scheme into two parts with different fault tolerances for application to important and minor data.
+It mainly includes two operations of coding segmentation and structure selection.
+
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.35\textwidth]{photo/chunk-block.pdf}
-\caption{A sample of chunks, stripes and blocks}
-\label{fig-chunk-block}
+\includegraphics[width=\linewidth]{photo/Framework.pdf}
+\caption{The framework of Approximate Code}
+\label{fig-framework}
 \end{figure}
 
-\subsection{Design of Approximate Code}
+\subsubsection{Code segmentation}
+For any type of input erasure code, we assume that its fault tolerance is $x$.
+The Approximate Code first splits its parity block into two parts: local and global parity.
+The former verifies all important and non-critical data, while the latter only verifies important data.
+Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$.
+For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.
+
+\subsubsection{Structure selection}
+The Approximate Code framework then choose the Structure for the input erasure code.
 Approximate Code distribute important and unimportant data separately and mainly in two structure.
-As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each chunk, and in \emph{Structure 2}, it occupies 1 of all $h$ data stripes.
+As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
 We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.
 
-In each stripe, $r$ chunks are local parity chunks, which is encoded by the rest $k$ data chunks in the stripe.
-In addition, there are another $3-r$ global chunks, which are calculated only by the important data blocks.
-It should be point out that the global parity chunks should be placed in different nodes and should be different from the data nodes.
+Figure \ref{fig-framework} shows the process of turning a code(assume that it is XXX) to Approximate XXX code.
+XXX-code has two parities chunks, the horizontal and the diagonal.
+Approximate Code framework define the former as local parity chunk and the latter as the global parity chunk.
+Then \emph{Structure 2} is selected and the Approximate XXX Code is a 16-node system.
+
+In each array, $r$ nodes are local parity nodes, which is encoded by the rest $k$ data nodes in the array.
+In addition, there are another $3-r$ global nodes, which are calculated only by the important data blocks.
+It should be point out that the global parity nodes should be placed in different nodes and should be different from the data nodes.
 
 The number of important data blocks is $h \times k$, and they generate $h \times (3-r)$ global parity blocks.
-To sum up, the number of blocks involved in the approximate code is 
+To sum up, the number of blocks involved in the Approximate Code is 
 $$(k+r)h^2 + (3-r) h$$
 
-Approximate Code guarantees that for each stripe, the unimportant data can tolerate any $r$ node failures.
+Approximate Code guarantees that for each array, the unimportant data can tolerate any $r$ node failures.
 Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.
@@
 
-%As mentioned before, if it is considered that the chunks from the same column belong to the same node, this example includes 4 stripes with 7 nodes; otherwise, it includes 4 stripes with 22 nodes.
+%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
 
@@
 \caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
-Data chunks are marked as $N_i$, important data are marked as water green, local parity chunks are marked as orange and global parity chunks are marked as red.
+Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
 }
@@
 In \emph{Structure 1}, the encoding unit is block.
-A horizontal RS parity is performed on the corresponding block in each chunk to generate a local parity block.
+A horizontal RS parity is performed on the corresponding block in each node to generate a local parity block.
 At the same time, the important data blocks is horizontally verified by RS and generate multiple global check blocks.
 
-In \emph{Structure 2}, the encoding unit is chunk.
-We perform horizontal RS parity in each stripe to generate local parity chunks. The global parity chunk is generated only by the important data stripe.
+In \emph{Structure 2}, the encoding unit is node.
+We perform horizontal RS parity in each array to generate local parity nodes. The global parity node is generated only by the important data array.
 
@@
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
-In each stripe, local parity blocks provide horizontal XOR parity, and between stripes, global parity provide diagonal parity and anti-diagonal parity.
+In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{photo/AP-TIP-v2.pdf}
+\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
 \caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
@@
 \begin{figure}[h]
-\subfigure[Diagonal parity $GP_0$ to $GP_5$, (e.g., $GP_0=ID_{0,0} \oplus ID_{1,4} \oplus ID_{2,3} \oplus ID_{4,2} \oplus ID_{5,1}$]{
-    \includegraphics[width=0.2\textwidth]{photo/TIP-diag.pdf}
-}
-\subfigure[Anti-diagonal parity $GP_6$ to $GP_{11}$, (e.g., $GP_7=ID_{0,0} \oplus ID_{1,1} \oplus ID_{2,2} \oplus ID_{4,3} \oplus ID_{5,4}$)]{
-    \includegraphics[width=0.2\textwidth]{photo/TIP-anti-diag.pdf}
-}
+
+    \includegraphics[width=0.48\textwidth]{photo/RAID5-TIP.pdf}
+
 \caption{Encoding pf TIP-code}
@@
 EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
-In this case, important data blocks are distributed in stripe 0, while unimportant data blocks occupy the rest stripes.
-$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity chunks and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity chunks for stripe $i$.
-So the form of every stripe fit the construction of EVENODD.
+In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays.
+$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$.
+So the form of every array fit the construction of EVENODD.
 Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
-The $GP$ is the anti-diagonal parity chunk and guarantee important data chunks form the construction method of STAR, which ensures the 3DFTs.
+The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{photo/AP-EVEN-star-v2.pdf}
+\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
 \caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
@@
 \begin{figure}[ht]
-\subfigure[]{
-    \includegraphics[width = 0.3 \linewidth]{photo/star-hori.pdf}
-}
-\subfigure{
-    \includegraphics[width = 0.3 \linewidth]{photo/star-diag.pdf}
-}
-\subfigure{
-    \includegraphics[width = 0.3 \linewidth]{photo/star-anti.pdf}
-}
-\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity chunk based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
+
+\includegraphics[width = 0.98 \linewidth]{photo/EVENODD-STAR.pdf}
+
+\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
 \end{figure}
@@
 \subsubsection{Reconstruction cases in Structure 1}
-Under \emph{Structure 1}, important data and unimportant data are distributed in the same chunks, so they suffer the same risk of device failures. 
+Under \emph{Structure 1}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures. 
 When $r$ or less nodes fail, all the data can be reconstructed by local parity.
-When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity chunks and the damaged video data will be processed by the video recovery and fuzzy algorithm.
+When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity nodes and the damaged video data will be processed by the video recovery and fuzzy algorithm.
 
 \subsubsection{Reconstruction cases in Structure 2}
-Under \emph{Structure 2}, we consider important and unimportant data chunks separately.
+Under \emph{Structure 2}, we consider important and unimportant data nodes separately.
 
-For node level failure, the fault tolerance of \emph{Structure 2} is exactly as \emph{Structure 1},When it comes to chunk level failures, \emph{Structure 2} can tolerate more unimportant data chunk failures than \emph{Structure 1}.
-The parity chain of important data does not pass through the unimportant data, so the damage of these chunks does not affect the recovery of important data.
+For node level failure, the fault tolerance of \emph{Structure 2} is exactly as \emph{Structure 1},When it comes to node level failures, \emph{Structure 2} can tolerate more unimportant data node failures than \emph{Structure 1}.
+The parity chain of important data does not pass through the unimportant data, so the damage of these nodes does not affect the recovery of important data.
 
 ///////////////////////
-Under the random probability model of chunks, the probability of failure of the Approximate Code under 4 chunk damage is
+Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
 \begin{equation}
@@
 \end{equation}
-which is the 4 chunk failure situation in $k$ important data chunks and 3 important parity chunks.
+which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes.
 For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
@@
     \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity chunks and only $3-r$ global parity chunks, while tipical 3DFTs EC methods should write $3 \times h$ parity chunks.
+    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity nodes and only $3-r$ global parity nodes, while tipical 3DFTs EC methods should write $3 \times h$ parity nodes.
     \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper stripe data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate stripe between the upper stripe application and the underlying distributed storage system is necessary to preprocess the data.
-We call it the approximate storage stripe, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
+Compared with the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data.
+We call it the approximate storage array, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
 
@@
 
-Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
+Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each array are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
@@
 
-\subsection{Results of Mathematical Analysis }
-In Figure X, we summarize the storage overhead and fault tolerance of the approximate code. It also shows the theoretical overhead of a single node write or update.
+\subsection{Metrics and Methods of Experiment}
+The metric of our experiments is time.
+The independent variable in this experiment is the number of nodes.
+We change the number of data nodes with different methods to compare the operation time.
+The experiments are divided into two parts, as one part is for measuring the encoding time of different methods, the other part is for timing the decoding time of different methods.
+The unit of the time is micro-second.\par
+
+There are mainly two ways to compare different methods.
+One is for comparing the operational time of AP code with different parameters and that of one different method as we augment the number of data nodes.
+The other is for a general comparison with five data nodes for the encoding time, the decoding time in one disk, the decoding time in two disks and the decoding time in three disks for every method with its different parameters.\par
+
+The environment of our experiment is listed below………….////////\par
+
+\subsection{Numerical Results of Mathematical Analysis}
+\subsubsection{Encoding Time Analysis}
+From the Figure xx a), we could find out that the AP code encodes largely faster than RS ($k$, $3$).
+The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes’ case) to 849.2\% (13 nodes’ case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times.
+The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and the difference between them and AP code is not very large.
+The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes’ case) to 127.3\% (17 nodes’ case).
+According to Figure xx d), we could see that AP code largely reduces the encoding time, comparing to LRC method.
+The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes’ case) to 615.8\% (13 nodes’ case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%.
+Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par
+
+\begin{figure*}[ht]
+\subfigure[AP and RS]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example1Modi2.jpg}
+}
+\subfigure[AP and STAR]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example2Modi1.jpg}
+}
+\subfigure[AP and TIP]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example3.jpg}
+}
+\subfigure[AP and LRC]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example4.jpg}
+}
+\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
+\end{figure*}
+
+\begin{figure*}[ht]
+\subfigure[AP and RS]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example5Modi1.jpg}
+}
+\subfigure[AP and STAR]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example6.jpg}
+}
+\subfigure[AP and TIP]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example7.jpg}
+}
+\subfigure[AP and LRC]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example8.jpg}
+}
+\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
+\end{figure*}
+
+\begin{figure*}[ht]
+\subfigure[AP and RS]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example9.jpg}
+}
+\subfigure[AP and STAR]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example10.jpg}
+}
+\subfigure[AP and TIP]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example11Modi1.jpg}
+}
+\subfigure[AP and LRC]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example12.jpg}
+}
+\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
+\end{figure*}
+
+According to Figure xx, we see that RS ($5$, $3$) has the longest encoding time among these methods, and the encoding time of LRC method is not short either.
+The methods whose encoding time is approaching to the AP method are Star and Tip.
+Among the AP method, AP ($5$, $1$, $6$) has the shortest encoding time.\par
+
+\subsubsection{Decoding Time in One Disk Analysis}
+From the Figure xx a), we could find out that the AP code decodes faster than RS ($k$, $3$).
+The rate of optimisation between AP method ($k$, $1$, $6$) and RS ($k$, $3$) is from 395.2\% (3 nodes’ case) to 353.0\% (13 nodes’ case).
+The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and there is nearly no difference among these three methods.
+The rate of optimisation between AP method ($k$, $2$, $6$) and Star ($k$, $3$) is from 3.867\% (3 nodes’ case) to 2.971\% (17 nodes’ case).
+According to Figure xx d), we could see that LRC ($4k$, $2$, $4$) decodes a bit faster than AP code, but LRC ($6k$, $2$, $6$) decodes slower than AP code.
+LRC ($4k$, $2$, $4$) decodes faster from 5.941\% (3 nodes’ case) to 9.542\% (13 nodes’ case) than AP ($1$, $4$); but AP ($1$, $6$) decodes faster from 0.476\% (3 nodes’ case) to 6.196\% (13 nodes’ case) than LRC ($6k$, $2$, $6$).\par
+
+According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, while other methods decoding time in one disk have no significant difference.\par
+
+\begin{figure*}[ht]
+\subfigure[Encoding Time]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarEnT.jpg}
+}
+\subfigure[Decoding Time in One Node Failure]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT1Modi1.jpg}
+}
+\subfigure[Decoding Time in Two Node Failure]{
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT2.jpg}
+}
+\caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
+\end{figure*}
+
+\subsubsection{Decoding Time in Two Disks Analysis}
+From the Figure xx a), we could find out that the AP code decodes remarkably faster than RS ($k$, $3$) in two disks.
+The rate of optimisation between AP method ($k$, $1$, $6$) and RS ($k$, $3$) is from 2782.1\% (3 nodes’ case) to 2593.9\% (13 nodes’ case).
+The Figure xx b) and c) illustrate that the effet of Star code and Tip code for decoding in two disks is similar, and the difference between them and AP ($k$, $2$, $4$ or $6$) is not very large.
+However, the difference is large when it comes to AP ($k$, $1$, $6$) The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 520.8\% (3 nodes’ case) to 508.6\% (17 nodes’ case).
+According to Figure xx d), we could see that AP code largely reduces the decoding time in two disks in comparison to LRC method.
+The rate of optimisation between AP code ($k$, $1$, $4$) and LRC ($4k$, $2$, $4$) is from 1971.5\% (3 nodes’ case) to 1265.5\% (13 nodes’ case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 2941.3\% to 1970.7\%.
+Considering the optimisation rate, AP code ($k$, $1$, $6$) is the best among the four.\par
+
+According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, the LRC method is not suitable for decoding in two disks.
+AP code, here, largely reduces the decoding time in two disks, while the AP ($5$, $1$, $6$) keeps the shortest decoding time.
 
@@
 
-\textcolor{gray}{
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text
-}
-
 \begin{acks}

### 2019-04-19 test-result-guo/Eva-guo.tex
version 3.7.1

--- 2019-04-19 ApproximateCode.tex
@@
-\documentclass[sigconf]{acmart}
-
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\usepackage{subfigure}
-\usepackage{algorithm}
-%\usepackage{algorithmic}
-\usepackage{algpseudocode}
-\usepackage{amsmath}
-\usepackage{graphics}
-\usepackage{epsfig}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{subfigure}
-
-\renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
-\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm
-
-\begin{document}
-
-\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems}
-
-\author{Huayi Jin}
-
-%-------------------------ATTANTION-------------------------%
-%                                                           %
-% orange words show the content that requires to be add     %
-% blue words need to be perfected or changed                %
-% gray words are the placeholder which is easy to fill      %
-%                                                           %
-%-----------------------------------------------------------%
-
-\begin{abstract}
-Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
-Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
-Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems.
-Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.
-
-To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems.
-The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance.
-On one hand, for important data, Approximate Code provides triple parities to provide high reliability.
-On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process.
-To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
-
-\end{abstract}
-
-%
-% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-% Please copy and paste the code instead of the example below.
-%
-\keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}
-
-\maketitle
-
-\section{Introduction}
-For typical cloud storage systems such as Windows Azure [CITE] and Amazon AWS [CITE], erasure coding is a popular technique to provide both high reliability and low monetary cost [CITE EC], where triple disk failure fault tolerant arrays (3DFTs) are widely used.
-Typical erasure codes can be divided into two categories, RS-based Codes [CITE] and XOR-based codes [CITE].
-RS-based codes [CITE] are encoded according the Galois Field Computation in Reed Solomon Code [CITE], which allow flexible configuration and have a little higher computation cost.
-XOR-based codes [CITE] simplify the computation, but the scalability is a significant issue in previous literatures.
-
-With the increasing demand on higher resolution and frame rate for video data, tremendous storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
-On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded [DESCRIBE AND CITE YOUTUBE].
-Therefore, in this paper, we set out to answer the following question,
-In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?
-
-To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage.
-[DESCRIBE AND CITE APPROXIMATE STORAGE] but the data reliability cannot be guaranteed.
-Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance should be sacrificed.
-Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
-
-To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
-The key idea of Approximate Code is treating the important/unimportant data in different ways.
-For important data, we add additional parities to provide high capability of fault tolerance.
-On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery.
-When triple disks fail, the lost data can be reconstructed via a fuzzy manner.
-
-We have the following contributions of this work,
-\begin{enumerate}
-\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
-\item Approximate Code can be implemented by combining most erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
-\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
-\end{enumerate}
-
-The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. 
-In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
-Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
-The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
-
-\section{Related Work and Our Motivation}\label{RelatedWork}
-In this section, we introduce the background of Video frame recovery, existing solutions to reduce storage cost and the motivation of this paper.
-To facilitate the discussion, we summarize the symbols used in this paper in Table \ref{parameter}.
-
-\begin{table}[]
-\caption{The symbols used in this paper.}\label{parameter}
-\centering
-\begin{tabular}{|c|l|}
-\hline
-Symbols & Description \\ \hline
-$k$ & the number of data nodes in an array \\ \hline
-$r$ & the number of local parity nodes in an array \\ \hline
-$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
-$h$ & the number of arrays \\ \hline
-$s$ & the number of blocks in a node \\ \hline
-LP & local parity nodes \\ \hline
-GP & global parity nodes \\ \hline
-ID & important data \\ \hline
-UD & unimportant data \\ \hline
- &  \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection{Existing Erasure Codes}
-Reliability is a critical issue since disk failures are typical in storage systems.
-To improve the reliability of storage systems, several RAID forms (e.g., RAID-5, RAID-6, 3DFTs) and erasure codes are proposed by researchers.
-Traditional erasure codes can be categorized into two classes, Maximum Distance Separable (MDS) codes and non-MDS codes.
-MDS codes aim to offer data protection with optimal storage efficiency.
-On the other hand, non-MDS codes improve the performance or reliability by consuming extra storage space.
-
-In the past two decades, several
-famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD
-code [1], RDP code [8], Blaum-Roth code[3], X-code [44], Liberation code [28], Liber8tion code [27], Cyclic [7] code, B-Code [45], Code-M [40], H-code [43], P-code [20] and HVcode [36], etc.
-
-In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [33], Cauchy-RS codes [4], STAR code [19], Triple-Star code [41], Triple-Parity code [9], HDD1 code [39], RSL-code [10], RL-code [11], and so on.
-Typical non-MDS codes contain WEAVER codes [14], HoVer
-codes [13], T-code [38], HDD2 code [39], Pyramid codes [18], Local Reconstruction Codes [16], Locally Repairable Codes [34], etc.
-
-Several classic erasure codes are illustrated in detail as below,
-
-%从这里开始简单讲解几种RAID-6或三盘容错阵列的纠删码，如RS，EVENODD，RDP，STAR，LRC, H-Code，TIP-Code等，并且用编码图来说明（主要是实验中用到的几种编码）。
-
-\subsection{Video Frame Recovery}
-
-In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
-However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
-One of them is named video frame interpolation.
-
-Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames.
-This is a technique that can model natural motion within a video, and generate frames according to this modelling.
-Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
-
-In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
-
-\subsection{Approximate Storage}
-Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
-But not all data need high-reliability storage for its backup.
-That is when the concept of approximate storage is introduced.
-Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
-
-Use cases for approximate storage range from transient memory to embedded settings and mass storage cloud servers.
-Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance.
-On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints.
-\cite{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
-
-Approximate storage loosens the requirement of storage reliability by allowing quality loss of some specific data.
-Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
-The critical data is still safe because they are stored and sufficiently backed up by expensive and highly reliable storage devices.
-Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
-
-However, it is too naive to store data in approximate storage units indiscriminately.
-Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
-To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
-Therefore, it is very important to distinguish the importance of video data. This can usually be done by an experienced expert or automatically by a program.
-
-\begin{table}[ht]
-\centering 
-\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
-\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
-\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
-\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
-\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
- & Unimp &  & medium & high \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection{Our Motivation}
-Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
-
-First, existing erasure codes generally reach or exceed 3DFTs, and use more than 3 parity disks.
-However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
-Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
-Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.
-
-To solve these problems, we propose a new erasure code called Approximation Code.
-It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.
-
-\section{Approximate Code}\label{ApCode}
-In this section, we introduce Approximate Code and its properties through a few simple examples.
-
-\subsection{Overview of Approximate Code}
-The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
-In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
-Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
-Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$
-
-\subsection{Framework Design}
-The Approximate Code provides an erasure code framework for video storage in the cloud system.
-It uses an approximate strategy to split the erasure code scheme into two parts with different fault tolerances for application to important and minor data.
-It mainly includes two operations of coding segmentation and structure selection.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{photo/Framework.pdf}
-\caption{The framework of Approximate Code}
-\label{fig-framework}
-\end{figure}
-
-\subsubsection{Code segmentation}
-For any type of input erasure code, we assume that its fault tolerance is $x$.
-The Approximate Code first splits its parity block into two parts: local and global parity.
-The former verifies all important and non-critical data, while the latter only verifies important data.
-Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$.
-For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.
-
-\subsubsection{Structure selection}
-The Approximate Code framework then choose the Structure for the input erasure code.
-Approximate Code distribute important and unimportant data separately and mainly in two structure.
-As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
-We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.
-
-Figure \ref{fig-framework} shows the process of turning a code(assume that it is XXX) to Approximate XXX code.
-XXX-code has two parities chunks, the horizontal and the diagonal.
-Approximate Code framework define the former as local parity chunk and the latter as the global parity chunk.
-Then \emph{Structure 2} is selected and the Approximate XXX Code is a 16-node system.
-
-In each array, $r$ nodes are local parity nodes, which is encoded by the rest $k$ data nodes in the array.
-In addition, there are another $3-r$ global nodes, which are calculated only by the important data blocks.
-It should be point out that the global parity nodes should be placed in different nodes and should be different from the data nodes.
-
-The number of important data blocks is $h \times k$, and they generate $h \times (3-r)$ global parity blocks.
-To sum up, the number of blocks involved in the Approximate Code is 
-$$(k+r)h^2 + (3-r) h$$
-
-Approximate Code guarantees that for each array, the unimportant data can tolerate any $r$ node failures.
-Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.
-
-The construction of Approximate Code (4,1,4, \emph{Structure 1}) and Approximate (3,1,3, \emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-414},
-
-%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
-\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
-Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
-}
-\label{fig-ap-414}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
-\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$.
-$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
-\label{fig-ap-rs}
-\end{figure}
-
-\subsection{RS-based Approximate Code}
-The construction of the Approximate Code based on RS is simple.
-In \emph{Structure 1}, the encoding unit is block.
-A horizontal RS parity is performed on the corresponding block in each node to generate a local parity block.
-At the same time, the important data blocks is horizontally verified by RS and generate multiple global check blocks.
-
-In \emph{Structure 2}, the encoding unit is node.
-We perform horizontal RS parity in each array to generate local parity nodes. The global parity node is generated only by the important data array.
-
-Figure \ref{fig-ap-rs} is the RS generation matrix with $k=4$ and $r=1$.
-It shows that to ensure that the coefficients of the local and the global parity are linearly independent is easy.
-If necessary, Approximation Code can easily achieve higher reliability guarantees based on RS, but in most cases this is excessive, so we will not discuss it here.
-
-\subsection{XOR-based Approximate Code}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}) and ($4,2,4$, \emph{Structure 2}).
-
-\subsubsection{RAID5-TIP Approximate Code}
-
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure 1}, based on RAID5 and TIP-code \cite{zhang2015tip}.
-RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
-In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.
-
-The local (horizontal) parity elements are calculated by the following encoding equations.
-\begin{align}
-    LP_{i,0} &= \bigoplus_{j=0}^{k-1} ID_{i,j} (0 \leqslant i < h)\\
-    LP_{i,p}(0<p<s) &= \bigoplus_{j=k(p-1)}^{kp-1} UD_{i,j} (0 \leqslant i < h)
-\end{align}
-
-When generating global parity blocks, the important data block, the local parity block, and the global parity block should be arranged as the encoding form of TIP-code.
-Figure \ref{fig-TIP} shows the coding method of diagonal and anti-diagonal parity blocks.
-Since the encoding process of important data blocks can be seen as RAID5 plus TIP-code, it is obvious that they achieve 3DFTs.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
-\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
-\label{fig-ap-TIP}
-\end{figure}
-
-\begin{figure}[h]
-
-    \includegraphics[width=0.48\textwidth]{photo/RAID5-TIP.pdf}
-
-\caption{Encoding pf TIP-code}
-\label{fig-TIP}
-\end{figure}
-
-\subsubsection{EVENODD-STAR Approximate Code}
-Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($5,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
-EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
-In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays.
-$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$.
-So the form of every array fit the construction of EVENODD.
-Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
-The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
-\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
-\label{fig-ap-STAR}
-\end{figure}
-
-\begin{figure}[ht]
-
-\includegraphics[width = 0.98 \linewidth]{photo/EVENODD-STAR.pdf}
-
-\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
-\end{figure}
-
-\subsection{Case Study}
-This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.
-
-\subsubsection{Reconstruction cases in Structure 1}
-Under \emph{Structure 1}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures. 
-When $r$ or less nodes fail, all the data can be reconstructed by local parity.
-When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity nodes and the damaged video data will be processed by the video recovery and fuzzy algorithm.
-
-\subsubsection{Reconstruction cases in Structure 2}
-Under \emph{Structure 2}, we consider important and unimportant data nodes separately.
-
-For node level failure, the fault tolerance of \emph{Structure 2} is exactly as \emph{Structure 1},When it comes to node level failures, \emph{Structure 2} can tolerate more unimportant data node failures than \emph{Structure 1}.
-The parity chain of important data does not pass through the unimportant data, so the damage of these nodes does not affect the recovery of important data.
-
-///////////////////////
-Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
-\begin{equation}
-    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
-\end{equation}
-which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes.
-For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
-
-\subsection{Properties of Approximate Code}\label{properties}
-
-We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
-\begin{itemize}
-    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity nodes and only $3-r$ global parity nodes, while tipical 3DFTs EC methods should write $3 \times h$ parity nodes.
-    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
-    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
-\end{itemize}
-
-\begin{table}[ht]
-\centering 
-\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
-\begin{tabular}{|c|c|c|c|}
-\hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
-RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
-EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
-TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
-\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
-\end{tabular}
-\end{table}
-
-\section{Implementation}\label{Implementation}
-\begin{figure}[htb]
-\centering
-\includegraphics[height = 6.5cm]{photo/implementation-V2.pdf}
-\caption{Overview of Approximate Code implementation}
-\label{fig-implementation}
-\end{figure}
-
-Compared with the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data.
-We call it the approximate storage array, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
-
-\subsection{Data Segmentation and Distribution module}
-The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data.
-A natural approach is to follow the GOP segmentation.
-According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data.
-(unimportant part).
-
-The data distribution module distributes important data and unimportant data in different blocks and records the location.
-This location information is also defined as important data.
-This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
-
-\subsection{Approximate Code module}
-The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance.
-For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
-
-Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each array are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
-
-\subsection{Data Fuzzification and Video Recovery}
-In the approximate recovery mode, the remaining data and important data are transferred to this module.
-Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.
-
-\section{Approximate Recovery}\label{ap-recovery}
-
-\begin{figure*}\label{fig-node-lost}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
-}
-\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
-\end{figure*}
-
-In the approximate recovery mode, since unimportant data suffers unrecoverable loss, the recovery of damaged video files must be considered.
-Therefore, we evaluate the recovery of the video file in this section.
-
-\subsection{Experimental Setup}
-\subsubsection{Coding Algorithm} 
-We evaluate the condition of the video of H.264 encoding [] under approximate recovery.
-Mainly because H.264 is an advanced video coding algorithm widely used at present, at the same time, the common advanced coding algorithms have similar coding processes.
-
-\subsubsection{Data Set}
-We choose 100 videos from xxx data set[]. All videos are stored in ``.mp4'' format at 1280*720 HD resolution.
-
-\subsubsection{Metrics}
-We use the number of frames saved as an indicator to evaluate the ability of the approximate storage and normal scheme to preserve data in the event of an unrecoverable node failure.
-
-We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).
-
-Since the approximation code stores the I frame as important data, the integrity of the I frame is always guaranteed in our scheme.
-
-\subsubsection{Simulation}
-We store the video files on a single disk according to the approximate storage scheme and the common scheme, while traversing the damage of all the disks, from 1 to n-1, and counting the number of damaged p-frames and b-frames.
-We use this to get the number of P and B frames that can be completely saved in the case of m out of n disks.
-
-\subsection{Results}
-The experimental results are shown in Figure \ref{fig-node-lost}, where $n$ is 4,5,6 and 8.
-In a 8-node array, when 2 nodes are unrecoverable, the approximate recovery method protects nearly 1/4 P or B frames, while the common method lost more than half of these frames.
-In addition, the approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.
-
-\subsection{Analysis}
-Our experiments prove that if data is stored indiscriminately, the loss of important data will seriously affect the security of all data, and our scheme will control the data loss near the theoretical limit, ensuring video recovery and fuzzification.
-feasibility.
-
-\subsection{Frame Recovery ????}
-
-\section{Evaluation}\label{evaluation}
-In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code in HDFS. 
-\subsection{Evaluation Methodology }
-We choose the RS code to compare with several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6.
-Since 3DFTs are typical configurations, we set the number of check nodes for the RS to 3.
-Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
-
-\subsubsection{Metrics and Methods for Mathematical Analysis: }
-We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Write(update) Cost} defined in Section \ref{properties} as measure.
-We first analyze the impact of the settings of the three parameters on these metrics, then we compare these matrics with several EC methods.
-
-\subsubsection{Metrics and Methods for Experiments: }
-We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
-
-Our experiment includes the calculation of these two metrics and can mainly be divided into several cases.
-We measure the encoding time by calculating the time to generate all parity blocks, and we measure the recovery time by calculating the time to fully or approximately recover the failure nodes.
-Both of them should be divided into 3 situation: single, double and triple node, so we discuss them separately.
-Also, the encoding and recovery time consist of computation time, I/O time and transimission time in distributed file system, which should be considered separately.
-
-The environment of our experiments are shown in Table \ref{tab-platform}.
-We set a Hadoop system with one NameNode and 4 DataNodes.
-\textcolor{gray}{text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
-
-\begin{table}[ht]
-\begin{tabular}{|l|l|}
-\hline
-Description & DELL R730 Server \\ \hline
-CPU & Intel Xeon 3.0GHz \\ \hline
-NIC 1Gbps & 1Gbps \\ \hline
-Memory & 32GB \\ \hline
-Disk & 8TB HDD \\ \hline
-OS & Linux 3.19 \\ \hline
-Platform & Hadoop HDFS 3.0.3 \\ \hline
-\end{tabular}
-\caption{Details of Our Evaluation Platform}\label{tab-platform}
-\end{table}
-
+\section{Evaluation}
 \subsection{Metrics and Methods of Experiment}
@@
 Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par
-
-\begin{figure*}[ht]
-\subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example1Modi2.jpg}
-}
-\subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example2Modi1.jpg}
-}
-\subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example3.jpg}
-}
-\subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example4.jpg}
-}
-\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
-\end{figure*}
-
-\begin{figure*}[ht]
-\subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example5Modi1.jpg}
-}
-\subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example6.jpg}
-}
-\subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example7.jpg}
-}
-\subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example8.jpg}
-}
-\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
-\end{figure*}
-
-\begin{figure*}[ht]
-\subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example9.jpg}
-}
-\subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example10.jpg}
-}
-\subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example11Modi1.jpg}
-}
-\subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example12.jpg}
-}
-\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
-\end{figure*}
+\begin{figure}[H]
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example1Modi2.jpg}
+\caption{Encoding Time Comparison between AP method and RS method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example2Modi1.jpg}
+\caption{Encoding Time Comparison between AP method and Star method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example3.jpg}
+\caption{Encoding Time Comparison between AP method and Tip method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example4.jpg}
+\caption{Encoding Time Comparison between AP method and LRC method}
+\end{minipage}
+\end{figure}\par
 
@@
 Among the AP method, AP ($5$, $1$, $6$) has the shortest encoding time.\par
+\begin{figure}[H]
+\centering
+\includegraphics{BarEnT.jpg}
+\caption{Comparison of Encoding Time for 5 Nodes with Different Methods}
+\end{figure}
 
@@
 
+\begin{figure}[H]
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example5Modi1.jpg}
+\caption{Decoding Time Comparison in One Disk between AP method and RS method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example6.jpg}
+\caption{Decoding Time Comparison in One Disk between AP method and Star method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example7.jpg}
+\caption{Decoding Time Comparison in One Disk between AP method and Tip method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example8.jpg}
+\caption{Decoding Time Comparison in One Disk between AP method and LRC method}
+\end{minipage}
+\end{figure}\par
+
 According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, while other methods decoding time in one disk have no significant difference.\par
-
-\begin{figure*}[ht]
-\subfigure[Encoding Time]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarEnT.jpg}
-}
-\subfigure[Decoding Time in One Node Failure]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT1Modi1.jpg}
-}
-\subfigure[Decoding Time in Two Node Failure]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT2.jpg}
-}
-\caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
-\end{figure*}
+\begin{figure}[H]
+\centering
+\includegraphics{BarDeT1Modi1.jpg}
+\caption{Comparison of Decoding Time for 5 Nodes in One Disk with Different Methods}
+\end{figure}
 
@@
 
+\begin{figure}[H]
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example9.jpg}
+\caption{Decoding Time Comparison in Two Disks between AP method and RS method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example10.jpg}
+\caption{Decoding Time Comparison in Two Disks between AP method and Star method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example11Modi1.jpg}
+\caption{Decoding Time Comparison in Two Disks between AP method and Tip method}
+\end{minipage}
+\begin{minipage}{0.25\lineWidth}
+\centering
+\includegraphics{Example12.jpg}
+\caption{Decoding Time Comparison in Two Disks between AP method and LRC method}
+\end{minipage}
+\end{figure}\par
+
 According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, the LRC method is not suitable for decoding in two disks.
 AP code, here, largely reduces the decoding time in two disks, while the AP ($5$, $1$, $6$) keeps the shortest decoding time.
-
-\begin{itemize}
-    \item Storage efficiency. . .
-    \item Fault tolerance. . .
-    \item Write overhead. . .
-\end{itemize}
-
-\subsection{Encoding Performance}
-We use Approximate Code (4,2,4) and (5,1,6)...
-
-\subsection{Recovery Time}
-We use Approximate Code (4,2,4) and (5,1,6)...
-
-\subsection{Analysis}
-\section{Conclusion}\label{Conclusion}
-
-\begin{acks}
-
-\end{acks}
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{ApproximateCode}
-
-\end{document}
+\begin{figure}[H]
+\centering
+\includegraphics{BarDeT2.jpg}
+\caption{Comparison of Decoding Time for 5 Nodes in Two Disks with Different Methods}
+\end{figure}

### 2019-04-19 ApproximateCode.tex
version 3.8

@@
 
-\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems}
+\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems}
 
@@
 
-With the increasing demand on higher resolution and frame rate for video data, tremendous storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
-On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded [DESCRIBE AND CITE YOUTUBE].
+With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
 Therefore, in this paper, we set out to answer the following question,
-In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?
+\textbf{In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?}
 
 To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage.
-[DESCRIBE AND CITE APPROXIMATE STORAGE] but the data reliability cannot be guaranteed.
-Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance should be sacrificed.
+Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups [CITE APPROXIMATE STORAGE], thus the data reliability cannot be guaranteed.
+Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance would be sacrificed.
+Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal} \cite{ziv1978compression} \cite{deutsch1996deflate}.
+However, the compression and decompression process results in very large computational overhead, high recovery speed and high response time, which is not suitable for video applications.
 Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
@@
 In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
-Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
+%Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
 The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
@@
 \section{Related Work and Our Motivation}\label{RelatedWork}
-In this section, we introduce the background of Video frame recovery, existing solutions to reduce storage cost and the motivation of this paper.
+In this section, we introduce the background of video storage, existing solutions to reduce storage cost and the motivation of this paper.
 To facilitate the discussion, we summarize the symbols used in this paper in Table \ref{parameter}.
@@
 $h$ & the number of arrays \\ \hline
-$s$ & the number of blocks in a node \\ \hline
+$g$ & the number of global parity nodes \\ \hline
 LP & local parity nodes \\ \hline
@@
 UD & unimportant data \\ \hline
- &  \\ \hline
 \end{tabular}
 \end{table}
+
+\subsection{Basis of Video Storage}\label{video storage}
+For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy algorithms before storage.
+
+\subsubsection{Video coding}
+H.264 is one of the advanced algorithms for this type of work.
+This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
+For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
+
+H.264 classifies all frames into three different categories:
+\begin{enumerate}
+    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
+    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
+    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
+\end{enumerate}
+A GOP consists of multiple consecutive I, P, and B frames that are independent of frames in other GOPs to prevent bit error spread.
+%In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}. 
+Therefore, within each GOP, the I frame has the highest importance because other frames rely on it for recovery; the importance of the P frame is second, and the B frame has the least importance.
+Based on this feature, a special program can be designed to distinguish the importance of video frames.
+
+\iffalse
+\begin{figure}[]
+\centering
+\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
+\caption{A sample of GOPs in H.264}
+\label{H264-IPB}
+\end{figure}
+\fi
+
+\subsubsection{Video Frame Recovery}
+In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
+However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
+One of them is named video frame interpolation [CITE][CITE].
+
+Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.This is a technique that can model natural motion within a video, and generate frames according to this modelling.
+
+In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
+Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
 
@@
 In the past two decades, several
-famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD
-code [1], RDP code [8], Blaum-Roth code[3], X-code [44], Liberation code [28], Liber8tion code [27], Cyclic [7] code, B-Code [45], Code-M [40], H-code [43], P-code [20] and HVcode [36], etc.
+famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code [CITE], RDP code [CITE], Blaum-Roth code[CITE], X-code [CITE], Liberation code [CITE], Liber8tion code [CITE], Cyclic [CITE] code, B-Code [CITE], Code-M [CITE], H-code [CITE], P-code [CITE] and HVcode [CITE], etc.
 
-In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [33], Cauchy-RS codes [4], STAR code [19], Triple-Star code [41], Triple-Parity code [9], HDD1 code [39], RSL-code [10], RL-code [11], and so on.
-Typical non-MDS codes contain WEAVER codes [14], HoVer
-codes [13], T-code [38], HDD2 code [39], Pyramid codes [18], Local Reconstruction Codes [16], Locally Repairable Codes [34], etc.
+In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [CITE], Cauchy-RS codes [CITE], STAR code [CITE], Triple-Star code [CITE], Triple-Parity code [CITE], HDD1 code [CITE], RSL-code [CITE], RL-code [CITE], and so on.
+Typical non-MDS codes contain WEAVER codes [CITE], HoVer
+codes [CITE], T-code [CITE], HDD2 code [CITE], Pyramid codes [CITE], Local Reconstruction Codes [CITE], Locally Repairable Codes [CITE], etc.
 
@@
 
-\subsection{Video Frame Recovery}
-
-In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
-However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
-One of them is named video frame interpolation.
-
-Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames.
-This is a technique that can model natural motion within a video, and generate frames according to this modelling.
-Artificially increasing the frame-rate of videos enables the possibility of frame recovery.
-
-In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
-
 \subsection{Approximate Storage}
-Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
+%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
 But not all data need high-reliability storage for its backup.
-That is when the concept of approximate storage is introduced.
+That is why the concept of approximate storage is introduced.
 Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
@@
 
-However, it is too naive to store data in approximate storage units indiscriminately.
+%However, it is too naive to store data in approximate storage units indiscriminately.
 Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
 To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
-Therefore, it is very important to distinguish the importance of video data. This can usually be done by an experienced expert or automatically by a program.
+Therefore, it is very important to distinguish the importance of video data.
 
@@
 \centering 
-\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
+\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code. (``Appr.'' is short for ``Approximate'')}\label{tab-AS-EC-AP}
 \begin{tabular}{|c|c|c|c|c|}
 \hline
-\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
+\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
 \multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
-\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
-\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
-\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
- & Unimp &  & medium & high \\ \hline
+ & RAID-6 & medium & medium & high \\ \hline
+\multicolumn{2}{|c|}{Appr. Storage} & low & low & high \\ \hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr.\\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
+ & UD &  & medium & high \\ \hline
 \end{tabular}
@@
 
-First, existing erasure codes generally reach or exceed 3DFTs, and use more than 3 parity disks.
-However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large.
-Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust.
-Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.
+First, the overhead of existing 3DFTs erasure codes is too high.
+Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
+Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.
 
-To solve these problems, we propose a new erasure code called Approximation Code.
-It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.
+Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
+Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[]
 \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[]
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[]
 
@@
 
-\begin{table}[ht]
+\begin{table}[]
 \centering 
@@
 \hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
+EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
 RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
@@
 TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
-\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
+\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
 \end{tabular}
@@
 
-\begin{table}[ht]
+\begin{table}[]
 \begin{tabular}{|l|l|}
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[]
 \subfigure[AP and RS]{
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[]
 \subfigure[Encoding Time]{

### 2019-04-19 ApproximateCode.tex
version 3.8.1

@@
 
-\section{Approximate Code}\label{ApCode}
-In this section, we introduce Approximate Code and its properties through a few simple examples.
-
-\subsection{Overview of Approximate Code}
-The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
-In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
-Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
-Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$
-
-\subsection{Framework Design}
-The Approximate Code provides an erasure code framework for video storage in the cloud system.
-It uses an approximate strategy to split the erasure code scheme into two parts with different fault tolerances for application to important and minor data.
-It mainly includes two operations of coding segmentation and structure selection.
-
-\begin{figure}[]
+\begin{figure*}[ht!]
 \centering
-\includegraphics[width=\linewidth]{photo/Framework.pdf}
+\includegraphics[width=\linewidth]{photo/Framework-v2.pdf}
 \caption{The framework of Approximate Code}
 \label{fig-framework}
-\end{figure}
+\end{figure*}
 
-\subsubsection{Code segmentation}
+\section{Approximate Code}\label{ApCode}
+In this section, we introduce the Approximate Code Framework and its properties through a few simple examples.
+
+\subsection{Overview of Approximate Code Framework}
+The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
+
+\subsubsection{Code Segmentation}
 For any type of input erasure code, we assume that its fault tolerance is $x$.
-The Approximate Code first splits its parity block into two parts: local and global parity.
+The Approximate Code first splits its parity block into two parts: local and global.
 The former verifies all important and non-critical data, while the latter only verifies important data.
@@
 
-\subsubsection{Structure selection}
+\subsubsection{Structure Selection}
 The Approximate Code framework then choose the Structure for the input erasure code.
@@
 Then \emph{Structure 2} is selected and the Approximate XXX Code is a 16-node system.
+
+\subsubsection{Code Generation}
+
+The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
+In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
+Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
+Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$
 
@@
 %As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
-
+\iffalse
 \begin{figure}[]
@@
 \end{figure}
+\fi
 

### 2019-04-20 ApproximateCode.tex
version 3.8.2

@@
+% !TEX TS-program = pdflatex
 \documentclass[sigconf]{acmart}
@@
 The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
-
+                                                                    q
 \end{abstract}
@@
 \subsection{Overview of Approximate Code Framework}
-The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
+The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation. We use Figure \ref{fig-framework} to illustrate our design.
 
 \subsubsection{Code Segmentation}
-For any type of input erasure code, we assume that its fault tolerance is $x$.
+For an input erasure code, we assume that its fault tolerance is $x$.
 The Approximate Code first splits its parity block into two parts: local and global.
@@
 
+In the example, a 3DFTs erasure code with 4 data chunks and 3 parity chunks is input, and its 3 parity chunks are separated into two local and one global parity chunks.
+
 \subsubsection{Structure Selection}
-The Approximate Code framework then choose the Structure for the input erasure code.
-Approximate Code distribute important and unimportant data separately and mainly in two structure.
-As shown in Figure \ref{fig-ap-414}, in \emph{Structure 1}, important data occupies 1 of $s$ blocks in each node, and in \emph{Structure 2}, it occupies 1 of all $h$ data arrays.
-We define that $h=s$, so in \emph{Structure 1} and \emph{Structure 2},important data accounts for $1/h$ of all data.
+The Approximate Code framework then choose the structure for the input erasure code.
+There are two main structures that distribute important and unimportant data in different ways.
+As shown in Figure \ref{fig-framework}, in \emph{Structure 1}, important data occupies 1 block in each node, and in \emph{Structure 2}, it occupies 1 data arrays.
+We specify that in \emph{Structure 1}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure 1} and \emph{Structure 2} just fills up $k$ nodes.
 
-Figure \ref{fig-framework} shows the process of turning a code(assume that it is XXX) to Approximate XXX code.
-XXX-code has two parities chunks, the horizontal and the diagonal.
-Approximate Code framework define the former as local parity chunk and the latter as the global parity chunk.
-Then \emph{Structure 2} is selected and the Approximate XXX Code is a 16-node system.
+Since \emph{Structure 1} distributes important data across each node, it guarantees a more balanced load.
+\emph{Structure 2} concentrates important data into an array, and provides greater reliability for important data.
+A detailed analysis of this will be presented in \ref{evaluation}.
 
 \subsubsection{Code Generation}
+After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
 
-The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
-In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks, and we label the number of blocks in a node as $s$.
-Approximate Code are designed for $h$ arrays, therefore it includes $k*n$ data nodes and $r*h$ local parity nodes.
-Besides them, $3-r$ nodes are designed for global parity, and the total number of nodes in Approximate Code ($k,r,h$) is $$h*(k+r) +3-r$$
+The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$ and $h$. 
+In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
+Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
+Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks. The total number of nodes in Approximate Code ($k,r,g,h$) is 
+$h*(k+r) + g$.
 
-In each array, $r$ nodes are local parity nodes, which is encoded by the rest $k$ data nodes in the array.
-In addition, there are another $3-r$ global nodes, which are calculated only by the important data blocks.
-It should be point out that the global parity nodes should be placed in different nodes and should be different from the data nodes.
+Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
+Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually set to 1 or 2.
 
-The number of important data blocks is $h \times k$, and they generate $h \times (3-r)$ global parity blocks.
-To sum up, the number of blocks involved in the Approximate Code is 
-$$(k+r)h^2 + (3-r) h$$
-
-Approximate Code guarantees that for each array, the unimportant data can tolerate any $r$ node failures.
-Usually, $r$ is equal to 1 or 2, which covers most node failure scenarios, while important data are provided 3DFTs.
-
-The construction of Approximate Code (4,1,4, \emph{Structure 1}) and Approximate (3,1,3, \emph{Structure 2}) can be illustrated by Figure \ref{fig-ap-414},
-
-%As mentioned before, if it is considered that the nodes from the same column belong to the same node, this example includes 4 arrays with 7 nodes; otherwise, it includes 4 arrays with 22 nodes.
 \iffalse
@@
 
-\subsection{RS-based Approximate Code}
-The construction of the Approximate Code based on RS is simple.
-In \emph{Structure 1}, the encoding unit is block.
-A horizontal RS parity is performed on the corresponding block in each node to generate a local parity block.
-At the same time, the important data blocks is horizontally verified by RS and generate multiple global check blocks.
+\subsection{Approximate RS Code}
+For RS(k,p), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes.
+Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$.
+RS also supports both two structures.
 
-In \emph{Structure 2}, the encoding unit is node.
-We perform horizontal RS parity in each array to generate local parity nodes. The global parity node is generated only by the important data array.
-
-Figure \ref{fig-ap-rs} is the RS generation matrix with $k=4$ and $r=1$.
-It shows that to ensure that the coefficients of the local and the global parity are linearly independent is easy.
-If necessary, Approximation Code can easily achieve higher reliability guarantees based on RS, but in most cases this is excessive, so we will not discuss it here.
+For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS(4,3).
+It is divided into two local parities and one global parities with the \emph{Structure 2} and it generate Approximate RS Code (4,2,1,3,\emph{Structure 2}).
+As a result, the unimportant data constitutes RS(4,2), and the important data constitutes RS(4,3).
 
 \subsection{XOR-based Approximate Code}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several RAID6-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce tipical cases of the construction of XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}) and ($4,2,4$, \emph{Structure 2}).
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS.
+This section introduce two tipical construction of XOR-based Approximate Code, Approximate STAR Code and Approximate TIP Code.
 
-\subsubsection{RAID5-TIP Approximate Code}
+\subsubsection{Approximate STAR Code}
+Figure \ref{fig-ap-STAR} shows the construction of Approximate STAR Code ($5,2,1,3$) in \emph{Structure 2}
+
+based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
+EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
+In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays.
+$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$.
+So the form of every array fit the construction of EVENODD.
+Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
+The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.
+
+\begin{figure}[]
+\centering
+\includegraphics[width=0.6\linewidth]{photo/AP-523.pdf}
+\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
+\label{fig-ap-STAR}
+\end{figure}
+
+\begin{figure}[]
+
+\includegraphics[width =\linewidth]{photo/EVENODD-STAR.pdf}
+
+\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
+\end{figure}
+
+\subsubsection{Approximate TIP Code}
 
@@
 
-\subsubsection{EVENODD-STAR Approximate Code}
-Figure \ref{fig-ap-STAR} shows the construction of Approximate Code ($5,2,4$) in \emph{Structure 2} based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
-EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
-In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays.
-$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$.
-So the form of every array fit the construction of EVENODD.
-Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
-The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.
-
-\begin{figure}[]
-\centering
-\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
-\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
-\label{fig-ap-STAR}
-\end{figure}
-
-\begin{figure}[]
-
-\includegraphics[width = 0.98 \linewidth]{photo/EVENODD-STAR.pdf}
-
-\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
-\end{figure}
-
+\iffalse
 \subsection{Case Study}
@@
 For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
+\fi
 
@@
 EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
-RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
+RS($k,q$) & $(k+q)/k$ & $q$ & q \\ \hline
 EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
@@
 
-\section{Implementation}\label{Implementation}
+\subsection{Implementation}\label{Implementation}
 \begin{figure}[htb]
 \centering
-\includegraphics[height = 6.5cm]{photo/implementation-V2.pdf}
+\includegraphics[height = 5cm]{photo/implementation-V2.pdf}
 \caption{Overview of Approximate Code implementation}
@@
 
-\subsection{Data Segmentation and Distribution module}
+\subsubsection{Data Segmentation and Distribution module}
 The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data.
@@
 
-\subsection{Approximate Code module}
+\subsubsection{Approximate Code module}
 The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance.
@@
 
-\subsection{Data Fuzzification and Video Recovery}
+\subsubsection{Data Fuzzification and Video Recovery}
 In the approximate recovery mode, the remaining data and important data are transferred to this module.
@@
 
+\iffalse
 \section{Approximate Recovery}\label{ap-recovery}
-
 \begin{figure*}\label{fig-node-lost}
@@
 \subsection{Frame Recovery ????}
+\fi
 
@@
 
-The environment of our experiment is listed below………….////////\par
+The environment of our experiment is listed below.
 
@@
 From the Figure xx a), we could find out that the AP code encodes largely faster than RS ($k$, $3$).
-The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes’ case) to 849.2\% (13 nodes’ case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times.
+The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes case) to 849.2\% (13 nodes case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times.
 The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and the difference between them and AP code is not very large.
-The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes’ case) to 127.3\% (17 nodes’ case).
+The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes case) to 127.3\% (17 nodes case).
 According to Figure xx d), we could see that AP code largely reduces the encoding time, comparing to LRC method.
-The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes’ case) to 615.8\% (13 nodes’ case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%.
+The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes case) to 615.8\% (13 nodes case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%.
 Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par

### 2019-04-20 ApproximateCode.tex
Update ApproximateCode.tex

--- 2019-04-19 ApproximateCode.tex
@@
 \section{Introduction}
-For typical cloud storage systems such as Windows Azure [CITE] and Amazon AWS [CITE], erasure coding is a popular technique to provide both high reliability and low monetary cost [CITE EC], where triple disk failure fault tolerant arrays (3DFTs) are widely used.
-Typical erasure codes can be divided into two categories, RS-based Codes [CITE] and XOR-based codes [CITE].
-RS-based codes [CITE] are encoded according the Galois Field Computation in Reed Solomon Code [CITE], which allow flexible configuration and have a little higher computation cost.
-XOR-based codes [CITE] simplify the computation, but the scalability is a significant issue in previous literatures.
+For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used.
+Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, HCODE, STAR, tip}.
+RS-based codes are encoded according the Galois Field Computation in Reed Solomon Code \cite{RS}, which allow flexible configuration and have a little higher computation cost.
+XOR-based codes simplify the computation, but the scalability is a significant issue in previous literatures.
 
@@
 To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage.
-Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups [CITE APPROXIMATE STORAGE], thus the data reliability cannot be guaranteed.
-Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance would be sacrificed.
-Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal} \cite{ziv1978compression} \cite{deutsch1996deflate}.
+Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
+Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance would be sacrificed.
+Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}.
 However, the compression and decompression process results in very large computational overhead, high recovery speed and high response time, which is not suitable for video applications.
@@
 However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
-One of them is named video frame interpolation [CITE][CITE].
+One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context}.
 
@@
 
-In the past two decades, several
-famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code [CITE], RDP code [CITE], Blaum-Roth code[CITE], X-code [CITE], Liberation code [CITE], Liber8tion code [CITE], Cyclic [CITE] code, B-Code [CITE], Code-M [CITE], H-code [CITE], P-code [CITE] and HVcode [CITE], etc.
+In the past two decades, several famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code \cite{EVENODD}, RDP code \cite{RDP}, Blaum-Roth code\cite{BlaumRoth}, X-code \cite{XCode}, Liberation code \cite{Liberation}, Liber8tion code \cite{Liber8tion}, Cyclic \cite {Cyclic} code, B-Code \cite{BCode}, Code-M \cite{Code-M}, H-code \cite{hcode}, P-code \cite{PCode} and HVcode \cite{HVCode}, etc.
 
-In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [CITE], Cauchy-RS codes [CITE], STAR code [CITE], Triple-Star code [CITE], Triple-Parity code [CITE], HDD1 code [CITE], RSL-code [CITE], RL-code [CITE], and so on.
-Typical non-MDS codes contain WEAVER codes [CITE], HoVer
-codes [CITE], T-code [CITE], HDD2 code [CITE], Pyramid codes [CITE], Local Reconstruction Codes [CITE], Locally Repairable Codes [CITE], etc.
+In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, RL-code \cite{RL}, and so on.
+Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.
 
-Several classic erasure codes are illustrated in detail as below,
+Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating.
+Several attempts have been made to address this issue.
+Local Construction Code (LRC) \cite{LRC} is one of these attempts which succeeds in reducing the bandwidth and I/Os required for repair reads at the expense of higher storage overhead.
+
+Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures.
+This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed.
+XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures.
+More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.
+
+STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code.
+It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
+\begin{figure}[!ht]
+ \centering
+ \subfigure[Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
+  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
+ }
+ \hspace{5pt}
+ \subfigure[Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
+  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
+ } \\
+ \subfigure[Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
+  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
+ }
+ \hspace{5pt}
+ \caption{Encoding of STAR code ($p = 5$).}
+ \label{fig:star-enc}
+\end{figure}
+
+TIP-code \cite{tip} is a solution for p or p+1 disks, where p is a prime number.
+Compared to STAR, Tip's input of the diagonal and anti-diagonal parity is modified so they are evenly distributed among all the data blocks.
+This minor modification has enabled TIP-code to achieve optimal update complexity.
 

### 2019-04-20 ApproximateCode.tex
version 3.8.3

--- 2019-04-20 ApproximateCode.tex
@@
 
-\subsection{Existing Erasure Codes}
+\subsection{Existing Erasure Codes}\label{existEC}
 Reliability is a critical issue since disk failures are typical in storage systems.
@@
 There are two main structures that distribute important and unimportant data in different ways.
-As shown in Figure \ref{fig-framework}, in \emph{Structure 1}, important data occupies 1 block in each node, and in \emph{Structure 2}, it occupies 1 data arrays.
-We specify that in \emph{Structure 1}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure 1} and \emph{Structure 2} just fills up $k$ nodes.
+As shown in Figure \ref{fig-framework}, in \emph{Structure I}, important data occupies 1 block in each node, and in \emph{Structure II}, it occupies 1 data arrays.
+We specify that in \emph{Structure I}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure I} and \emph{Structure II} just fills up $k$ nodes.
 
-Since \emph{Structure 1} distributes important data across each node, it guarantees a more balanced load.
-\emph{Structure 2} concentrates important data into an array, and provides greater reliability for important data.
+Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load.
+\emph{Structure II} concentrates important data into an array, and provides greater reliability for important data.
 A detailed analysis of this will be presented in \ref{evaluation}.
@@
 
-The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$ and $h$. 
+The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and $Structure$. 
+We define the naming rules of the output Approximate Code as \textbf{``Approximate XXX Code ($k,r,g,h, Structure$)''}, where ``XXX'' is the name of input erasure code.
+Paremeter $Structure$ is I or II and it can be omitted when not focusing on the specific construction.
+
 In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
 Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
-Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks. The total number of nodes in Approximate Code ($k,r,g,h$) is 
+Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes in Approximate Code ($k,r,g,h$) is 
 $h*(k+r) + g$.
@@
 \includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
-\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
+\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure I}, and Approximate Code $(3,1,3)$ in \emph{Structure II}.
 Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
@@
 For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS(4,3).
-It is divided into two local parities and one global parities with the \emph{Structure 2} and it generate Approximate RS Code (4,2,1,3,\emph{Structure 2}).
+It is divided into two local parities and one global parities with the \emph{Structure II} and it generate Approximate RS Code (4,2,1,3,II).
 As a result, the unimportant data constitutes RS(4,2), and the important data constitutes RS(4,3).
@@
 
-\subsubsection{Approximate STAR Code}
-Figure \ref{fig-ap-STAR} shows the construction of Approximate STAR Code ($5,2,1,3$) in \emph{Structure 2}
-
-based on EVENODD \cite{blaum1995evenodd} and STAR \cite{huang2008star}. 
-EVENODD is a tipical RAID6 erasure code scheme, while STAR is a 3DFTs extension scheme of EVENODD.
-In this case, important data blocks are distributed in array 0, while unimportant data blocks occupy the rest arrays.
-$LP_{i,0}$ to $LP_{i,3}$ consist the horizontal parity nodes and $LP_{i,4}$ to $LP_{i,7}$ consist diagonal parity nodes for array $i$.
-So the form of every array fit the construction of EVENODD.
-Because the STAR code is constructed just by adding a reverse parity chain to the EVENODD code.
-The $GP$ is the anti-diagonal parity node and guarantee important data nodes form the construction method of STAR, which ensures the 3DFTs.
-
-\begin{figure}[]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=0.6\linewidth]{photo/AP-523.pdf}
-\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
-\label{fig-ap-STAR}
+\includegraphics[width=0.8\linewidth]{photo/AP-5214.pdf}
+\caption{Construction of Approximate STAR Code (5,2,1,4,II)}
+\label{fig-ap-5214}
 \end{figure}
 
-\begin{figure}[]
+\begin{figure}[ht]
+\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
+\caption{EVENODD only consist horizontal and diagonal parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
+\end{figure}
 
-\includegraphics[width =\linewidth]{photo/EVENODD-STAR.pdf}
+\subsubsection{Approximate STAR Code}
+Figure \ref{fig-ap-5214} shows the construction of Approximate STAR Code (5,2,1,4,II).
 
-\caption{EVENODD only consist horizontal and diagonaol parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
-\end{figure}
+As introduced in \ref{existEC}, STAR Code \cite{huang2008star} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
+%We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
+Since STAR is a direct extension of EVENODD\cite{blaum1995evenodd}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
+As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
+According to the construction requirements of STAR, each node is divided into 4 blocks.
+
+Briefly, Approximate STAR Code (5,2,1,4,II) can be thought of as important data encoded by the full STAR, while unimportant data is encoded by a part of STAR, EVENODD.
+It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
 
@@
 
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure 1}, based on RAID5 and TIP-code \cite{zhang2015tip}.
+optimal update complexity.
+
+Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{zhang2015tip}.
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
@@
 
-\begin{figure}[]
+\begin{figure}[ht]
 \centering
 \includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
-\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
+\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure I}), constructed based on RAID5 and TIP-code.}
 \label{fig-ap-TIP}
@@
 
-\begin{figure}[]
+\begin{figure}[ht]
+\subfigure[]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics[width=0.8\linewidth]{photo/RAID5.pdf}        
+\end{minipage}
+}
+\subfigure[]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics[width=0.8\linewidth]{photo/legend.pdf}        
+\end{minipage}
+}
 
-    \includegraphics[width=0.48\textwidth]{photo/RAID5-TIP.pdf}
-
+\subfigure[]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics[width=\linewidth]{photo/TIP-di.pdf}        
+\end{minipage}
+}
+\subfigure[]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics[width=\linewidth]{photo/TIP-an.pdf}        
+\end{minipage}
+}
 \caption{Encoding pf TIP-code}
@@
 \subsection{Case Study}
-This section describe the decoding methods in different cases of node failure based on \emph{Structure 1} and \emph{Structure 2}.
+This section describe the decoding methods in different cases of node failure based on \emph{Structure I} and \emph{Structure II}.
 
 \subsubsection{Reconstruction cases in Structure 1}
-Under \emph{Structure 1}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures. 
+Under \emph{Structure I}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures. 
 When $r$ or less nodes fail, all the data can be reconstructed by local parity.
@@
 \subsubsection{Reconstruction cases in Structure 2}
-Under \emph{Structure 2}, we consider important and unimportant data nodes separately.
+Under \emph{Structure II}, we consider important and unimportant data nodes separately.
 
-For node level failure, the fault tolerance of \emph{Structure 2} is exactly as \emph{Structure 1},When it comes to node level failures, \emph{Structure 2} can tolerate more unimportant data node failures than \emph{Structure 1}.
+For node level failure, the fault tolerance of \emph{Structure II} is exactly as \emph{Structure I},When it comes to node level failures, \emph{Structure II} can tolerate more unimportant data node failures than \emph{Structure I}.
 The parity chain of important data does not pass through the unimportant data, so the damage of these nodes does not affect the recovery of important data.
@@
 which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes.
-For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure 2}) probability is 0.478\%.
+For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure II}) probability is 0.478\%.
 \fi

### 2019-04-20 ApproximateCode.tex

@@
 \subsection{Existing Erasure Codes}\label{existEC}
+
 Reliability is a critical issue since disk failures are typical in storage systems.

### 2019-04-20 ApproximateCode.tex
till row 290

@@
 This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed.
-XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures.
-More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.
+Typical XOR-based MDS codes are EVENODD code \cite{EVENODD}, H-code \cite{hcode}, STAR code \cite{STAR} and TIP-code \cite{tip}.
+Some of them will be discussed in detail below.
 
@@
 First, the overhead of existing 3DFTs erasure codes is too high.
-Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
+Secondly, the 2DFTs erasure codes sacrifice part of the necessary reliability, and that of approximate storage schemes is much lower since they cannot tolerate disk-level failures.
 Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.
 
-Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
+Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, named Approximate Code.
 Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.
@@
 Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load.
-\emph{Structure II} concentrates important data into an array, and provides greater reliability for important data.
+\emph{Structure II} aggregates important data into an array, and provides greater reliability for important data.
 A detailed analysis of this will be presented in \ref{evaluation}.
@@
 
-In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
+In an $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
 Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
@@
 
-As introduced in \ref{existEC}, STAR Code \cite{huang2008star} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
+As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
 %We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
-Since STAR is a direct extension of EVENODD\cite{blaum1995evenodd}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
+Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
 As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
@@
 
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{zhang2015tip}.
+Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{tip}.
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.

### 2019-04-20 ApproximateCode.tex
Update ApproximateCode.tex

@@
 
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{tip}.
+Figure \ref{fig-ap-TIP} is a typical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{tip}.
 RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data.
+Compared to the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data.
 We call it the approximate storage array, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
@@
 A natural approach is to follow the GOP segmentation.
-According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data.
-(unimportant part).
+According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data (unimportant part).
 
@@
 \subsubsection{Coding Algorithm} 
-We evaluate the condition of the video of H.264 encoding [] under approximate recovery.
-Mainly because H.264 is an advanced video coding algorithm widely used at present, at the same time, the common advanced coding algorithms have similar coding processes.
+Since H.264 is an advanced video coding algorithm widely used at present, and in the meanwhile the common advanced coding algorithms have similar coding processes, We evaluate the condition of the video in H.264 encoding [] under approximate recovery.
 

### 2019-04-20 ApproximateCode.tex
Version 4! The draft

--- 2019-04-20 ApproximateCode.tex
@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
-                                                                    q
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
 \end{abstract}
@@
 For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used.
-Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, HCODE, STAR, tip}.
+Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}.
 RS-based codes are encoded according the Galois Field Computation in Reed Solomon Code \cite{RS}, which allow flexible configuration and have a little higher computation cost.
@@
 
-To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
+To address the above problem, in this paper, we propose Approximate Code\footnote{This article abbreviates ``Approximate'' to ``Appr.
+'' when necessary.}, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
 The key idea of Approximate Code is treating the important/unimportant data in different ways.
@@
 $g$ & the number of global parity nodes \\ \hline
+$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline 
 LP & local parity nodes \\ \hline
@@
  \centering
- \subfigure[Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
+ \subfigure[Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
   \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
@@
  \hspace{5pt}
- \subfigure[Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
+ \subfigure[Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
   \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
  } \\
- \subfigure[Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
+ \subfigure[Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
   \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
@@
 \centering 
-\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code. (``Appr.'' is short for ``Approximate'')}\label{tab-AS-EC-AP}
+\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code.}\label{tab-AS-EC-AP}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \multicolumn{2}{|c|}{Appr.  Storage} & low & low & high \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr.\\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr. \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
  & UD &  & medium & high \\ \hline
@@
 \emph{Structure II} concentrates important data into an array, and provides greater reliability for important data.
-A detailed analysis of this will be presented in \ref{evaluation}.
+A detailed analysis of this will be presented in Section +\ref{ReconstructionFT}.
 
-\subsubsection{Code Generation}
+\subsubsection{Code Generation}\label{code-gen}
 After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{photo/AP-5214.pdf}
+\includegraphics[width=0.7\linewidth]{photo/AP-5214.pdf}
 \caption{Construction of Approximate STAR Code (5,2,1,4,II)}
@@
 \includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
-\caption{EVENODD only consist horizontal and diagonal parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
+\caption{Encoding process of Approximate STAR Code (5,2,1,4,II), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
 \end{figure}
@@
 
-As introduced in \ref{existEC}, STAR Code \cite{huang2008star} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
-%We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
-Since STAR is a direct extension of EVENODD\cite{blaum1995evenodd}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
+As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
+Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
 As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
@@
 
-Briefly, Approximate STAR Code (5,2,1,4,II) can be thought of as important data encoded by the full STAR, while unimportant data is encoded by a part of STAR, EVENODD.
+Briefly, Approximate STAR Code (5,2,1,4,II) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD.
 It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
@@
 \subsubsection{Approximate TIP Code}
-
-optimal update complexity.
-
-Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{zhang2015tip}.
-RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code.
-In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.
-
-The local (horizontal) parity elements are calculated by the following encoding equations.
-\begin{align}
-    LP_{i,0} &= \bigoplus_{j=0}^{k-1} ID_{i,j} (0 \leqslant i < h)\\
-    LP_{i,p}(0<p<s) &= \bigoplus_{j=k(p-1)}^{kp-1} UD_{i,j} (0 \leqslant i < h)
-\end{align}
-
-When generating global parity blocks, the important data block, the local parity block, and the global parity block should be arranged as the encoding form of TIP-code.
-Figure \ref{fig-TIP} shows the coding method of diagonal and anti-diagonal parity blocks.
-Since the encoding process of important data blocks can be seen as RAID5 plus TIP-code, it is obvious that they achieve 3DFTs.
+We then intorduce the generation of Approximate TIP Code (5,1,2,6,I).
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
-\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure I}), constructed based on RAID5 and TIP-code.}
+\includegraphics[width=0.3\textwidth]{photo/AP-5126.pdf}
+\caption{Construction of Approximate TIP Code (5,1,2,6,I)}
 \label{fig-ap-TIP}
@@
 \begin{figure}[ht]
-\subfigure[]{
-\begin{minipage}[t]{0.45\linewidth}
 \centering
-\includegraphics[width=0.8\linewidth]{photo/RAID5.pdf}        
-\end{minipage}
-}
-\subfigure[]{
-\begin{minipage}[t]{0.45\linewidth}
-\centering
-\includegraphics[width=0.8\linewidth]{photo/legend.pdf}        
-\end{minipage}
-}
-
-\subfigure[]{
-\begin{minipage}[t]{0.45\linewidth}
-\centering
-\includegraphics[width=\linewidth]{photo/TIP-di.pdf}        
-\end{minipage}
-}
-\subfigure[]{
-\begin{minipage}[t]{0.45\linewidth}
-\centering
-\includegraphics[width=\linewidth]{photo/TIP-an.pdf}        
-\end{minipage}
-}
-\caption{Encoding pf TIP-code}
+\includegraphics[width=0.8\linewidth]{photo/RAID5-TIP-v2.pdf}        
+\caption{Encoding process of Approximate TIP Code (5,1,2,6,I), which can be divided into TIP (encode important data) and RAID-5 (encode unimportant data).
+(e.g., the diagonal parity block marked as a square $E_{4,5} = E_{4,0} \oplus E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$)}
 \label{fig-TIP}
@@
 
-\iffalse
-\subsection{Case Study}
-This section describe the decoding methods in different cases of node failure based on \emph{Structure I} and \emph{Structure II}.
+The horizontal parity block of TIP code is defined as the local parity and the remaining two as the global parities.
 
-\subsubsection{Reconstruction cases in Structure 1}
+As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 layers, where important data accounting for 1/6 of each node.
+All data nodes generate 6 local parity nodes.
+Important data blocks are rearranged to fit the parity form of TIP Code and generate two global parity nodes.
+The encoding process of Approximate TIP Code (5,1,2,6,I) is shown in Figure \ref{fig-TIP}.
+
+\subsection{Reconstruction Process and Fault Tolerance}\label{ReconstructionFT}
+When $r$ or less nodes fail, all the data can be reconstructed by local parities.
+When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.
+However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$. 
+The former exceeds the fault tolerance of unimportant data, while the latter exceeds the fault tolerance of important data. As mentioned in \ref{code-gen}, $r+g$ is set to 3.
+Approximate Codes based on different structures have different fault tolerance and reconstruction cases, so we discuss \emph{Structure I} and \emph{Structure II} respectively.
+
+\subsubsection{Structure I}
 Under \emph{Structure I}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures.
-When $r$ or less nodes fail, all the data can be reconstructed by local parity.
-When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity nodes and the damaged video data will be processed by the video recovery and fuzzy algorithm.
 
-\subsubsection{Reconstruction cases in Structure 2}
-Under \emph{Structure II}, we consider important and unimportant data nodes separately.
+For unimportant data, it is recoverable as long as the node loss per line does not exceed $r$. Therefore, the unrecoverable scenarios account for
+$$\frac{kh}{\binom{(k+r)h+g}{r+1}}.$$
+of all $r+1$ node failure cases. 
+For important data, when 4 nodes fail, the unrecoverable scenarios account for
+$$h*\frac{\sum_{i=0}^{g} {\binom{4-i}{k+r}*\binom{i}{g}} }{\binom{4}{(k+r)*h+g}}  (g=0,1)$$
 
-For node level failure, the fault tolerance of \emph{Structure II} is exactly as \emph{Structure I},When it comes to node level failures, \emph{Structure II} can tolerate more unimportant data node failures than \emph{Structure I}.
-The parity chain of important data does not pass through the unimportant data, so the damage of these nodes does not affect the recovery of important data.
+In Approximate Code (3,1,2,3,I), 90.11\% 2-node failure is recoverable for unimportant data nodes and 95.50\% 4-node failure is recoverable for important data nodes.
 
-///////////////////////
-Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
-\begin{equation}
-    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
-\end{equation}
-which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes.
-For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure II}) probability is 0.478\%.
-\fi
+\subsubsection{Structure II}
+Important and unimportant data are storaged in different nodes under \emph{Structure II}.
+When $r+1$ nodes fail, the unrecoverable scenarios for unimportant data account for
+$$\frac{k(h-1)}{\binom{(k+r)h+g}{r+1}}.$$
+When 4 nodes fail, the unrecoverable scenarios for important data account for
+$$\frac{\binom{k+3}{4}}{\binom{(k+r)h+g}{4}}.$$
+In Approximate Code (3,1,2,3,II), 93.41\% 2-node failure is recoverable for unimportant data nodes, and 98.50\% 4-node failure is recoverable for important data nodes.
 
@@
 \begin{itemize}
-    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
-    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity nodes and only $3-r$ global parity nodes, while tipical 3DFTs EC methods should write $3 \times h$ parity nodes.
+    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies.
+This property is more pronounced for data with a smaller proportion of important data.
+    \item Optimal Update Complexity: When one node is updated, Approximate RS Code only needs to write $r$ local parity nodes and only $g/h$ global parity nodes on average besides the write of data node.
     \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
@@
 
-\begin{table}[]
+\begin{table}[htb]
 \centering 
-\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP}\label{tab-AS-RS-AP}
 \begin{tabular}{|c|c|c|c|}
 \hline
-EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
-RS($k,q$) & $(k+q)/k$ & $q$ & q \\ \hline
-EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
-TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
-\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Write\\ Performance(Average)\end{tabular} \\ \hline
+RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
+STAR($k,3$) & $(k+3)/k$ & $3$ & $6-\frac{4}{k}$ \\ \hline
+TIP-code($k,3$) & $(k+3)/k$ & $3$ & 4 \\ \hline
+\begin{tabular}[c]{@{}c@{}}Appr. RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4} 
+\begin{tabular}[c]{@{}c@{}}Appr. STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4} 
+\begin{tabular}[c]{@{}c@{}}Appr. TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
 \end{tabular}
@@
 \includegraphics[height = 5cm]{photo/implementation-V2.pdf}
-\caption{Overview of Approximate Code implementation}
+\caption{Overview of Approximate Storage Layer}
 \label{fig-implementation}
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data.
-We call it the approximate storage array, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
+Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary.
+We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
 
@@
 (unimportant part).
-
-The data distribution module distributes important data and unimportant data in different blocks and records the location.
-This location information is also defined as important data.
+%The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data. 
 This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
@@
 For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
-
-Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each array are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
+%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each layer are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
@@
 
-\iffalse
-\section{Approximate Recovery}\label{ap-recovery}
-\begin{figure*}\label{fig-node-lost}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
-}
-\subfigure{
-    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
-}
-\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
-\end{figure*}
+\section{Evaluation}\label{evaluation}
+In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code. 
+\subsection{Evaluation Methodology }
+To compared with Approximate Code, We choose several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6, RS code and LRC codes which are widely used in cloud storage systems.
+Since 3DFTs are typical configurations, we set the number of parity nodes to 3 for all kinds of codes in this evaluation.
 
-In the approximate recovery mode, since unimportant data suffers unrecoverable loss, the recovery of damaged video files must be considered.
-Therefore, we evaluate the recovery of the video file in this section.
-
-\subsection{Experimental Setup}
-\subsubsection{Coding Algorithm} 
-We evaluate the condition of the video of H.264 encoding [] under approximate recovery.
-Mainly because H.264 is an advanced video coding algorithm widely used at present, at the same time, the common advanced coding algorithms have similar coding processes.
-
-\subsubsection{Data Set}
-We choose 100 videos from xxx data set[]. All videos are stored in ``.mp4'' format at 1280*720 HD resolution.
-
-\subsubsection{Metrics}
-We use the number of frames saved as an indicator to evaluate the ability of the approximate storage and normal scheme to preserve data in the event of an unrecoverable node failure.
-
-We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).
-
-Since the approximation code stores the I frame as important data, the integrity of the I frame is always guaranteed in our scheme.
-
-\subsubsection{Simulation}
-We store the video files on a single disk according to the approximate storage scheme and the common scheme, while traversing the damage of all the disks, from 1 to n-1, and counting the number of damaged p-frames and b-frames.
-We use this to get the number of P and B frames that can be completely saved in the case of m out of n disks.
-
-\subsection{Results}
-The experimental results are shown in Figure \ref{fig-node-lost}, where $n$ is 4,5,6 and 8.
-In a 8-node array, when 2 nodes are unrecoverable, the approximate recovery method protects nearly 1/4 P or B frames, while the common method lost more than half of these frames.
-In addition, the approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.
-
-\subsection{Analysis}
-Our experiments prove that if data is stored indiscriminately, the loss of important data will seriously affect the security of all data, and our scheme will control the data loss near the theoretical limit, ensuring video recovery and fuzzification.
-feasibility.
-
-\subsection{Frame Recovery ????}
-\fi
-
-\section{Evaluation}\label{evaluation}
-In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code in HDFS. 
-\subsection{Evaluation Methodology }
-We choose the RS code to compare with several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6.
-Since 3DFTs are typical configurations, we set the number of check nodes for the RS to 3.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
@@
 We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
-
-Our experiment includes the calculation of these two metrics and can mainly be divided into several cases.
-We measure the encoding time by calculating the time to generate all parity blocks, and we measure the recovery time by calculating the time to fully or approximately recover the failure nodes.
-Both of them should be divided into 3 situation: single, double and triple node, so we discuss them separately.
-Also, the encoding and recovery time consist of computation time, I/O time and transimission time in distributed file system, which should be considered separately.
+\textbf{Encoding Time} is the time for generating all parity nodes and \textbf{Recovery Time} is the time for recovering the lost nodes.
+Several codes are chosen to compared with Approximate Code with the same data nodes $k$.
+Attention that Approximate Code can only recover the important data nodes in some cases and we only keep the lost data nodes to be the same for all codes which means Approximate Code may recover less data than other codes.
 
 The environment of our experiments are shown in Table \ref{tab-platform}.
-We set a Hadoop system with one NameNode and 4 DataNodes.
-\textcolor{gray}{text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }
+We set a Hadoop system with one NameNode and $h$ DataNodes.
+Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes.
+We set $h=4,6$ and node size equal $1GB$ here as two common configurations.
 
-\begin{table}[]
+Our experiment can mainly be divided into five cases.
+In the first part, we evaluate the encoding time for all kinds of codes.
+In the next three parts we measure the recovery time under single, double and triple failure nodes condition respectively.
+Finally we conduct the experiment of frame interpolation to prove that the lost of video frames is recoverable to some extent.
+
+\begin{table}[!ht]
 \begin{tabular}{|l|l|}
@@
 
-\subsection{Metrics and Methods of Experiment}
-The metric of our experiments is time.
-The independent variable in this experiment is the number of nodes.
-We change the number of data nodes with different methods to compare the operation time.
-The experiments are divided into two parts, as one part is for measuring the encoding time of different methods, the other part is for timing the decoding time of different methods.
-The unit of the time is micro-second.\par
+\subsection{Numerical Results of Mathematical Analysis}
+\subsubsection{Storage Overhead}
+We compare the storage overhead between RS (k,3), Appr.
+RS (k,1,2,h) and Appr.
+RS (k,2,1,h), where h = 4 or 6.
+As shown in Figure \ref{fig-Storage}, the results shows that Appr.
+RS Code has lower storage overhead than RS Code.
+The ratio of optimization is up to 21.4\% when h=4, k=4 and 23.8\% when h=6, k=4.
 
-There are mainly two ways to compare different methods.
-One is for comparing the operational time of AP code with different parameters and that of one different method as we augment the number of data nodes.
-The other is for a general comparison with five data nodes for the encoding time, the decoding time in one disk, the decoding time in two disks and the decoding time in three disks for every method with its different parameters.\par
+\subsubsection{Fault Tolerance}
+All the erasure codes we evaluate in this Section are 3DFTs.
 
-The environment of our experiment is listed below.
+\subsubsection{Single Write Performance}
+We compare the single write performance between RS, STAR, Appr.
+RS and Appr.
+STAR, where h = 4 or 6.
+As shown in Figure \ref{fig-Sig-Write}, the results shows that Appr.
+RS Code has lower single write performance than RS Code and STAR Code.
+The ratio of optimization is up to 41.3\% when h=6 and 25\% when h=4.
+As $k$ increases, the performance of Appr.
+STAR is close to RS and always better than STAR.
 
-\subsection{Numerical Results of Mathematical Analysis}
+\begin{figure}[]
+\subfigure[h=4]{
+    \label{fig-storage4}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-4.eps}
+}
+\subfigure[h=6]{
+    \label{fig-storage6}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-6.eps}
+}
+\caption{Storage Overhead}\label{fig-Storage}
+\end{figure}
+
+\begin{figure}[]
+\subfigure[h=4]{
+    \label{fig-Sig-Write4}
+    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-4.eps}
+}
+\subfigure[h=6]{
+    \label{fig-Sig-Write6}
+    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-6.eps}
+}
+\caption{Single Write Performance}\label{fig-Sig-Write}
+\end{figure}
+
+\subsection{Experimental Results Results and Analysis}
+
 \subsubsection{Encoding Time Analysis}
-From the Figure xx a), we could find out that the AP code encodes largely faster than RS ($k$, $3$).
-The rate of optimisation between AP($k$, $1$, $6$) and RS ($k$, $3$) is from 976.4\% (3 nodes case) to 849.2\% (13 nodes case), as the encoding time of AP codes multiplies about 4.7 times and that of RS code multiplies about 4.2 times.
-The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and the difference between them and AP code is not very large.
-The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 125.6\% (3 nodes case) to 127.3\% (17 nodes case).
-According to Figure xx d), we could see that AP code largely reduces the encoding time, comparing to LRC method.
-The rate of optimisation between AP code (k, 1, 4) and LRC (4k, 2, 4) is from 596.0\% (3 nodes case) to 615.8\% (13 nodes case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 684.0\% to 443.1\%.
-Considering the optimisation rate, AP code ($k$, $1$, $4$) is the best among the four.\par
+In this part, we compared the encoding time of Approximate Code with Tip code, STAR code, RS code and LRC codes, respectively.
+Here we use Tip and STAR code to generate parities in Approximate Code.
+Thus we can cover all the code configurations from $k$ = 5 to $k$ = 17.
+\begin{itemize}
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-encodingSTAR } illustrates that Approximate Code encodes faster than STAR code and the rate of optimization is up to 56.3\% (between Appr.
+STAR (k,1,2,6) and STAR (k, 3) when k = 5).
+    \item Appr.
+TIP(k,1,2,4), Appr.
+TIP(k,2,1,4), Appr.
+TIP(k,1,2,6), Appr.
+TIP(k,2,1,6) and TIP(k,3): the effet of Tip code is similar to STAR  code.
+From Figure \ref{fig-encodingTIP}, the rate of optimization is up to 58.1\% (between Appr.
+TIP(k,1,2,6) and TIP(k, 3) when k = 9).
+    \item Appr.
+TIP/STAR (k,1,2,4), Appr.
+TIP/STAR (k,2,1,4), Appr.
+TIP/STAR (k,1,2,6), Appr.
+TIP/STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-encodingRS}, we could find out that the AP code encodes largely faster than RS code.
+The rate of optimization is up to 91.1\% (between Appr.
+TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
+    \item Appr.
+TIP/STAR (k,1,2,4), Appr.
+TIP/STAR (k,2,1,4), Appr.
+TIP/STAR (k,1,2,6), Appr.
+TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3):  According to Figure \ref{fig-encodingLRC}, we could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
+The rate of optimization is up to 88.9\% (between Appr.
+TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
+\end{itemize}
+
+We combined the encoding time of five codes in Figure \ref{fig-encoding-combine} with $k$=5.
+The results show that Approximate Code has the best encoding performance among five codes.
+There are two reasons for this condition:1) Approximate Code only generates 3 parities for important data which lead to the less size of total parity nodes, comparing with other codes.
+2)Approximate Code use XOR-based codes (Tip and star code) which have lower computational overhead than RS -based codes.\par
 
@@
 \subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example1Modi2.jpg}
+    \label{fig-encodingSTAR}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Star.eps}
 }
 \subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example2Modi1.jpg}
+    \label{fig-encodingTIP}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Tip.eps}
 }
 \subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example3.jpg}
+    \label{fig-encodingRS}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-RS.eps}
 }
 \subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example4.jpg}
+    \label{fig-encodingLRC}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-LRC.eps}
 }
@@
 \subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example5Modi1.jpg}
+    \label{fig-decoding-1-STAR}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Star.eps}
 }
 \subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example6.jpg}
+    \label{fig-decoding-1-TIP}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Tip.eps}
 }
 \subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example7.jpg}
+    \label{fig-decoding-1-RS}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-RS.eps}
 }
 \subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example8.jpg}
+    \label{fig-decoding-1-LRC}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-LRC.eps}
 }
@@
 \subfigure[AP and RS]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example9.jpg}
+    \label{fig-decoding-2-STAR}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Star.eps}
 }
 \subfigure[AP and STAR]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example10.jpg}
+    \label{fig-decoding-2-TIP}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Tip.eps}
 }
 \subfigure[AP and TIP]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example11Modi1.jpg}
+    \label{fig-decoding-2-RS}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-RS.eps}
 }
 \subfigure[AP and LRC]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example12.jpg}
+    \label{fig-decoding-2-LRC}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-LRC.eps}
 }
@@
 
-According to Figure xx, we see that RS ($5$, $3$) has the longest encoding time among these methods, and the encoding time of LRC method is not short either.
-The methods whose encoding time is approaching to the AP method are Star and Tip.
-Among the AP method, AP ($5$, $1$, $6$) has the shortest encoding time.\par
+\begin{figure*}[]
+    \subfigure[AP and RS]{
+        \label{fig-decoding-3-STAR}
+        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Star.eps}
+    }
+    \subfigure[AP and STAR]{
+        \label{fig-decoding-3-TIP}
+        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Tip.eps}
+    }
+    \subfigure[AP and TIP]{
+        \label{fig-decoding-3-RS}
+        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-RS.eps}
+    }
+    \subfigure[AP and LRC]{
+        \label{fig-decoding-3-LRC}
+        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-LRC.eps}
+    }
+    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
+    \end{figure*}
 
-\subsubsection{Decoding Time in One Disk Analysis}
-From the Figure xx a), we could find out that the AP code decodes faster than RS ($k$, $3$).
-The rate of optimisation between AP method ($k$, $1$, $6$) and RS ($k$, $3$) is from 395.2\% (3 nodes’ case) to 353.0\% (13 nodes’ case).
-The Figure xx b) and c) illustrate that the effet of Star code and Tip code is similar, and there is nearly no difference among these three methods.
-The rate of optimisation between AP method ($k$, $2$, $6$) and Star ($k$, $3$) is from 3.867\% (3 nodes’ case) to 2.971\% (17 nodes’ case).
-According to Figure xx d), we could see that LRC ($4k$, $2$, $4$) decodes a bit faster than AP code, but LRC ($6k$, $2$, $6$) decodes slower than AP code.
-LRC ($4k$, $2$, $4$) decodes faster from 5.941\% (3 nodes’ case) to 9.542\% (13 nodes’ case) than AP ($1$, $4$); but AP ($1$, $6$) decodes faster from 0.476\% (3 nodes’ case) to 6.196\% (13 nodes’ case) than LRC ($6k$, $2$, $6$).\par
+\subsubsection{Decoding Time under One Failure Node Condition Analysis}
 
-According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, while other methods decoding time in one disk have no significant difference.\par
+In this section, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17. 
+\begin{itemize}
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-1-STAR} illustrates that the decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between Appr.
+STAR (k,1,2,4) and STAR (k, 3) when k = 5).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and TIP(k,3): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as Tip code when sinlge node fails and the rate of optimization is up to 8.8\% (between Appr.
+TIP(k,1,2,4) and TIP(k, 3) when k = 17).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-1-RS}, we could find out that the Approximate Code decodes largely faster than RS code.
+The rate of optimization is up to 80.2\% (between Appr.
+TIP/STAR (k,1,2,4) and RS(k, 3) when k = 5).
+    \item Appr.
+TIP/STAR (k,1,2,4), Appr.
+TIP/STAR (k,2,1,4), Appr.
+TIP/STAR (k,1,2,6), Appr.
+TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3):  According to Figure \ref{fig-decoding-1-LRC}, we could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
+The rate of optimization is up to 5.8\% (between Appr.
+TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 13).
+\end{itemize}
+
+We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-decoding-1-combine} with $k$=5.
+The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
+The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par
 
@@
 \subfigure[Encoding Time]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarEnT.jpg}
+    \label{fig-encoding-combine}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Encoding.eps}
 }
 \subfigure[Decoding Time in One Node Failure]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT1Modi1.jpg}
+    \label{fig-decoding-1-combine}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-1.eps}
 }
 \subfigure[Decoding Time in Two Node Failure]{
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT2.jpg}
+    \label{fig-decoding-2-combine}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-2.eps}
+}
+\subfigure[Decoding Time in Three Node Failure]{
+    \label{fig-decoding-3-combine}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-3.eps}
 }
@@
 
-\subsubsection{Decoding Time in Two Disks Analysis}
-From the Figure xx a), we could find out that the AP code decodes remarkably faster than RS ($k$, $3$) in two disks.
-The rate of optimisation between AP method ($k$, $1$, $6$) and RS ($k$, $3$) is from 2782.1\% (3 nodes’ case) to 2593.9\% (13 nodes’ case).
-The Figure xx b) and c) illustrate that the effet of Star code and Tip code for decoding in two disks is similar, and the difference between them and AP ($k$, $2$, $4$ or $6$) is not very large.
-However, the difference is large when it comes to AP ($k$, $1$, $6$) The rate of optimisation between AP ($k$, $1$, $6$) and Star ($k$, $3$) is from 520.8\% (3 nodes’ case) to 508.6\% (17 nodes’ case).
-According to Figure xx d), we could see that AP code largely reduces the decoding time in two disks in comparison to LRC method.
-The rate of optimisation between AP code ($k$, $1$, $4$) and LRC ($4k$, $2$, $4$) is from 1971.5\% (3 nodes’ case) to 1265.5\% (13 nodes’ case); and the rate of optimisation between AP code ($k$, $1$, $6$) and LRC ($6k$, $2$, $6$) is from 2941.3\% to 1970.7\%.
-Considering the optimisation rate, AP code ($k$, $1$, $6$) is the best among the four.\par
-
-According to Figure xx, we see that RS ($5$, $3$) has the longest decoding time among these methods, the LRC method is not suitable for decoding in two disks.
-AP code, here, largely reduces the decoding time in two disks, while the AP ($5$, $1$, $6$) keeps the shortest decoding time.
-
+\subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
+In this part, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17. 
 \begin{itemize}
-    \item Storage efficiency. . .
-    \item Fault tolerance. . .
-    \item Write overhead. . .
+    \item Appr. STAR (k,1,2,4), Appr. STAR (k,2,1,4), \\
+    Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-2-STAR} illustrates that the rate of optimization is up to 83.9\% (between Appr.
+STAR (k,1,2,6) and STAR (k, 3) when k = 5).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4),  \\ Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and TIP(k,3): This condition is similar to STAR code.
+Figure \ref{fig-decoding-2-TIP} illustrates that the rate of optimization is up to 84.8\% (between Appr.
+TIP(k,1,2,6) and TIP(k, 3) when k = 9).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4),  \\ Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-2-RS}, we could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
+The rate of optimization is up to 96.9\% (between Appr.
+TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
+    \item Appr. TIP/STAR (k,1,2,4), Appr. TIP/STAR (k,2,1,4),  \\ Appr. TIP/STAR (k,1,2,6), Appr. TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3): 
+    According to Figure \ref{fig-decoding-2-LRC}, we could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
+The rate of optimization is up to 97.2\% (between Appr.
+TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
 \end{itemize}
 
-\subsection{Encoding Performance}
-We use Approximate Code (4,2,4) and (5,1,6)...
+The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-decoding-2-combine} (k=5).
+The results show that RS code and LRC codes has the worst two failure nodes decoding performance while Appr.
+TIP/STAR (k,1,2,6) and Appr.
+TIP/STAR (k,1,2,4) perform best among all kinds of codes.
+The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while Appr.
+TIP/STAR (k,1,2,6) and Appr.
+TIP/STAR (k,1,2,4) do the approximate recovery which means they only recover important data at this time.\par
 
-\subsection{Recovery Time}
-We use Approximate Code (4,2,4) and (5,1,6)...
+\subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
+In this part, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under three failure nodes condition, respectively. k changes from 5 to 17. 
+\begin{itemize}
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-3-STAR} illustrates that the rate of optimization is up to 83.5\% (between Appr.
+STAR (k,1,2,6) and STAR (k, 3) when k = 5).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and TIP(k,3): This condition is similar to STAR code.
+Figure \ref{fig-decoding-3-TIP} illustrates that the rate of optimization is up to 82.2\% (between Appr.
+TIP(k,1,2,6) and TIP(k, 3) when k = 5).
+    \item Appr.
+STAR (k,1,2,4), Appr.
+STAR (k,2,1,4), Appr.
+STAR (k,1,2,6), Appr.
+STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-3-RS}, we could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
+The rate of optimization is up to 96.7\% (between Appr.
+TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
+    \item Appr. TIP/STAR (k,1,2,4), Appr. TIP/STAR (k,2,1,4), Appr. TIP/STAR (k,1,2,6), Appr. TIP/STAR (k,2,1,6)  \\
+    and LRC(k,4,3), LRC(k,6,3): 
+    According to Figure \ref{fig-decoding-3-LRC}, we could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes.
+The rate of optimization is up to 98.3\%  (between Appr.
+TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
+\end{itemize}
 
-\subsection{Analysis}
+The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-decoding-3-combine} ($k$=5).
+The results show that LRC has the worst three failure nodes decoding performance.
+The main reasons are that: On three failure nodes condition, LRC codes decode data through the global parities which has a longer parity chain.
+For example $LRC(44,4,2)$ use 44 nodes to recover the three lost nodes.
+the computational cost of GF operations is also larger than XOR operations.
+On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.\par
+
+\subsection{Frame Recovery}
+Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
+As shown in Figure\ref{fig:frameRecovery}, The top 3 figures are the original frames.
+When frame 2 lost, the interpolation techniques can output \ref{fig-recoverof2} by the input of \ref{fig-interop1} and \ref{fig-interop3}.
+The recovered frame has a lower resolution and may differ from the original image, but since the unconstrained frame contains most of the context information, the video is still available, which validates the fact that the video can tolerate a certain amount of data loss.
+
+\begin{figure}[ht]
+\centering
+\subfigure[Frame 1]{
+\includegraphics[width=0.3\linewidth]{photo/Frame/1.jpg}\label{fig-interop1}
+}
+\subfigure[Frame 2]{
+\includegraphics[width=0.3\linewidth]{photo/Frame/2.jpg}\label{fig-interop2}
+}
+\subfigure[Frame 3]{
+\includegraphics[width=0.3\linewidth]{photo/Frame/3.jpg}\label{fig-interop3}
+}
+
+\subfigure[Recovery of Frame 2]{
+\includegraphics[width=0.5\linewidth]{photo/Frame/2_1.jpg}\label{fig-recoverof2}
+}
+\caption{Frame Recovery Result using Frame Interpolation}
+\label{fig:frameRecovery}
+\end{figure}
+
 \section{Conclusion}\label{Conclusion}
+In this paper, we present the Approximate Code, which is the framework for video tiered storage in cloud systems.
+The Approximate Code can segment the input erasure codes and provide different fault tolerance for data of different importance.
+For important data, the Approximate Code provides 3DFTS, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery, while having good update write performance.
+We conducted several experiments in the Hadoop system and found that compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
 

### 2019-04-21 ApproximateCode.tex
version 4.0

@@
-% !TEX TS-program = pdflatex
 \documentclass[sigconf]{acmart}
@@
 \usepackage{subfigure}
-
-\renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
-\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm
+\usepackage{array}
 
@@
 \author{Huayi Jin}
+\email{keplar_gd@sjtu.edu.cn}
+\affiliation{%
+  \institution{Shanghai Jiao Tong University}
+}
 
-%-------------------------ATTANTION-------------------------%
-%                                                           %
-% orange words show the content that requires to be add     %
-% blue words need to be perfected or changed                %
-% gray words are the placeholder which is easy to fill      %
-%                                                           %
-%-----------------------------------------------------------%
+\author{Chentao Wu}
+
+\author{Xin Xie}
+
+\author{Jie Li}
+
+\author{Minyi Guo}
+
+\author{Xubin He}
+\affiliation{%
+  \institution{}
+}
+
+\author{Yuanyuan Dong}
+\author{Hao Lin}
+\author{Jianfeng Zhang}
+\authornotemark[1]
+\email{webmaster@marysville-ohio.com}
+\affiliation{%
+  \institution{The Alibaba Group}
+}
 
@@
 
-To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems.
+To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems.
 The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance.
@@
 \end{abstract}
+
+\ccsdesc[500]{Information systems~Distributed storage}
+\ccsdesc[500]{Computer systems organization~Dependable and fault-tolerant systems and networks}
 
@@
 With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
-Therefore, in this paper, we set out to answer the following question,
-\textbf{In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?}
+Therefore, in this paper, we set out to answer the following question:
+
+\textbf{In a cloud storage system, how to efficiently store tremendous video data in 3DFTs?}
 
@@
 Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
-Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance would be sacrificed.
-Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}.
-However, the compression and decompression process results in very large computational overhead, high recovery speed and high response time, which is not suitable for video applications.
+Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
+Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}.
+\textcolor{red}{However, the compression and decompression processes result in a large amount of computational overhead, which decreases their efficiency in frequent failure scenarios like cloud.}
 Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
 
-To address the above problem, in this paper, we propose Approximate Code\footnote{This article abbreviates ``Approximate'' to ``Appr.
-'' when necessary.}, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
+To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
 The key idea of Approximate Code is treating the important/unimportant data in different ways.
@@
 \item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
-\item Approximate Code can be implemented by combining most erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
+\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
 \item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
@@
 \caption{The symbols used in this paper.}\label{parameter}
-\centering
-\begin{tabular}{|c|l|}
-\hline
-Symbols & Description \\ \hline
-$k$ & the number of data nodes in an array \\ \hline
-$r$ & the number of local parity nodes in an array \\ \hline
-$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
-$h$ & the number of arrays \\ \hline
+\centering\small
+\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
+\hline \hline
+Symbols & \multicolumn{1}{c|}{Description} \\ \hline
+$k$ & the number of data nodes in a local stripe \\ \hline
+$r$ & the number of local parity nodes in a local stripe \\ \hline
+$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
+$h$ & the number of local stripes to construct a global stripe \\ \hline
 $g$ & the number of global parity nodes \\ \hline
+$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
 $E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
+$D_i$ & data nodes \\ \hline
+$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
+$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
 LP & local parity nodes \\ \hline
 GP & global parity nodes \\ \hline
-ID & important data \\ \hline
-UD & unimportant data \\ \hline
+ID & important data in a video file \\ \hline
+UD & unimportant data in a video file \\ \hline
 \end{tabular}
@@
 \subsection{Basis of Video Storage}\label{video storage}
-For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy algorithms before storage.
+For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy compression algorithms before storage.
 
 \subsubsection{Video coding}
-H.264 is one of the advanced algorithms for this type of work.
+H.264 \cite{wiegand2003overview} is one of the advanced algorithms.
 This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
-For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.
+For a normal HD video file metioned as above, H.264 can reduce its size by about 10 times, only 443.27MB.
 
@@
 \end{enumerate}
-A GOP consists of multiple consecutive I, P, and B frames that are independent of frames in other GOPs to prevent bit error spread.
+A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames that are independent of the frames in other GOPs to prevent bit error spread, as shown in Figure \ref{H264-IPB}.
 %In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}. 
@@
 
-\iffalse
-\begin{figure}[]
+\begin{figure}[ht]
 \centering
@@
 \end{figure}
-\fi
 
@@
 In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
-However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques.
+However, the lost frames can still be recoverable with the benefit of nowadays powerful deep learning techniques.
 One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context}.
 
-Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.This is a technique that can model natural motion within a video, and generate frames according to this modelling.
+Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.
+This is a technique that can model natural motion within a video, and generate frames according to the model.
 
 In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.
+Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of PSNR, and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of middlebury benchmark.
 
@@
 Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.
+In the following we mainly introduce the classic erasure codes used in this paper.
 
@@
 Several attempts have been made to address this issue.
-Local Construction Code (LRC) \cite{LRC} is one of these attempts which succeeds in reducing the bandwidth and I/Os required for repair reads at the expense of higher storage overhead.
 
-Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures.
-This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed.
-XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures.
-More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.
+\textcolor{red}{Need to update}
+Local Construction Code (LRC) \cite{LRC} divides the data nodes into multiple local groups, each with a local parity node, and the global parity is calculated by all data nodes.
+Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
+LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{LRC}.
+
+\begin{figure}
+    \centering
+    \includegraphics[height=2.5cm]{photo/LRC.pdf}
+    \caption{LRC}
+\end{figure}
 
 STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code.
-It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
+It employs a novice diagonal redundancy as shown in the left of Figure \ref{fig-star-tip}.
+
+In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.
+
 \begin{figure}[!ht]
 \centering
- \subfigure[Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
-  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
+\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
+\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
 }
 \hspace{5pt}
- \subfigure[Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
-  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
- } \\
- \subfigure[Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
-  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
+\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
+\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
+}
+
+\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
+\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
 }
 \hspace{5pt}
- \caption{Encoding of STAR code ($p = 5$).}
- \label{fig:star-enc}
+\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
+\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
+}
+
+\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
+\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
+}
+\hspace{5pt}
+\subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
+\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
+}
+\caption{Encoding of STAR (subfigure (a),(c) and (e)) and TIP (subfigure (b),(d) and (f)) code ($p = 5$).
+Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
+\label{fig-star-tip}
 \end{figure}
 
-TIP-code \cite{tip} is a solution for p or p+1 disks, where p is a prime number.
-Compared to STAR, Tip's input of the diagonal and anti-diagonal parity is modified so they are evenly distributed among all the data blocks.
-This minor modification has enabled TIP-code to achieve optimal update complexity.
+TIP code is also an XOR-based 3DFTs erasure code.
+Compared with STAR code, the encoding and data arrangement of TIP code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.
+
+STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.
 
@@
 That is why the concept of approximate storage is introduced.
-Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
+Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
 
@@
 \centering 
-\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code.}\label{tab-AS-EC-AP}
+\caption{
+\textcolor{red}{Need to update}
+Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
+\small
 \begin{tabular}{|c|c|c|c|c|}
@@
  & RAID-6 & medium & medium & high \\ \hline
-\multicolumn{2}{|c|}{Appr.  Storage} & low & low & high \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr. \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
+\multicolumn{2}{|c|}{Approximate Storage} & low & low & high \\ \hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
  & UD &  & medium & high \\ \hline
@@
 \subsection{Our Motivation}
-Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
 
-First, the overhead of existing 3DFTs erasure codes is too high.
+%Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
+%First, the overhead of existing 3DFTs erasure codes is too high.
 Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
@@
 
-Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
-Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.
+From the summary of Table \ref{tab-AS-EC-AP}, we can find that existing solutions have high storage cost for video storage.
+Although approximate storage achieves low cost, the reliability cannot be satisfied in cloud environment.
+A feasible solution is combining the existing solutions together with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.
 
@@
 \subsection{Overview of Approximate Code Framework}
-The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation. We use Figure \ref{fig-framework} to illustrate our design.
+The Approximate Code framework contains four main steps, code input, code segementation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
+
+\subsubsection{Code Input}
+Acquire an erasure coding input and get the corresponding parameters.
+Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted by Approximate Code.
+Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.
 
 \subsubsection{Code Segmentation}
-For an input erasure code, we assume that its fault tolerance is $x$.
-The Approximate Code first splits its parity block into two parts: local and global.
+For an inputted erasure code, we assume that its fault tolerance is $x$.
+The Approximate Code first splits its parities into two parts: local and global parities.
 The former verifies all important and non-critical data, while the latter only verifies important data.
@@
 
-In the example, a 3DFTs erasure code with 4 data chunks and 3 parity chunks is input, and its 3 parity chunks are separated into two local and one global parity chunks.
+For example, several erasure codes in 3DFTs like STAR have three types of parities, horizontal, diagonal and anti-diagonal parities.
+In the code segmentation step, the horizontal parities are separated from other two parities.
 
@@
 There are two main structures that distribute important and unimportant data in different ways.
-As shown in Figure \ref{fig-framework}, in \emph{Structure I}, important data occupies 1 block in each node, and in \emph{Structure II}, it occupies 1 data arrays.
-We specify that in \emph{Structure I}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure I} and \emph{Structure II} just fills up $k$ nodes.
+As shown in Figure \ref{fig-framework}, in Even structure, important data occupies 1 block in each node, and in Uneven structure, it occupies 1 data stripe.
+We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.
 
-Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load.
-\emph{Structure II} concentrates important data into an array, and provides greater reliability for important data.
-A detailed analysis of this will be presented in Section +\ref{ReconstructionFT}.
+Since Even structure distributes important data across each node, it guarantees a more balanced load.
+Uneven structure concentrates important data into a stripe, and provides greater reliability for important data.
+A detailed analysis of this will be presented in Section \ref{ReconstructionFT}.
 
@@
 After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
+The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and Structure.
 
-The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and $Structure$. 
-We define the naming rules of the output Approximate Code as \textbf{``Approximate XXX Code ($k,r,g,h, Structure$)''}, where ``XXX'' is the name of input erasure code.
-Paremeter $Structure$ is I or II and it can be omitted when not focusing on the specific construction.
+We define the naming rules of the output Approximate Code as \textbf{APPR.CodeName} ($k,r,g,h$,Structure), where ``CodeName'' is the name of the input erasure code.
+Paremeter $Structure$ is Even or Uneven and it can be omitted when not focusing on the specific construction.
 
-In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
-Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
-Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes in Approximate Code ($k,r,g,h$) is 
-$h*(k+r) + g$.
+In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
+Approximate Code are designed for $h$ stripes, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
+Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes $N$ in Approximate Code ($k,r,g,h$) is 
+$N= h*(k+r) + g$.
 
 Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
-Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually set to 1 or 2.
+Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually 1 or 2.
+
+\subsection{\textcolor{red}{Approximate RS Code}}
+For RS($k,p$), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes.
+Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$.
+RS also supports both two structures.
+
+For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS($4,3$).
+It is divided into two local parities and one global parities with the Uneven structure and it generate Approximate RS Code ($4,2,1,3$,Uneven).
+As a result, the unimportant data constitutes RS($4,2$), and the important data constitutes RS($4,3$).
+
+\subsection{Approximate XOR-based Codes}
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS.
+This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP Code.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{photo/AP-5214-v2.pdf}
+\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
+\label{fig-ap-5214}
+\end{figure}
 
 \iffalse
-\begin{figure}[]
-\centering
-\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
-\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure I}, and Approximate Code $(3,1,3)$ in \emph{Structure II}.
-Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
-}
-\label{fig-ap-414}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
-\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$.
-$G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
-\label{fig-ap-rs}
+\begin{figure}[ht]
+\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
+\caption{Encoding process of APPR.STAR($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
 \end{figure}
@@
 
-\subsection{Approximate RS Code}
-For RS(k,p), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes.
-Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$.
-RS also supports both two structures.
+\subsubsection{Approximate STAR Code}
+Figure \ref{fig-ap-5214} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
+As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
+Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
+As shown in Figure \ref{fig-ap-5214}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
+According to the construction requirements of STAR, each node is divided into 4 blocks.
 
-For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS(4,3).
-It is divided into two local parities and one global parities with the \emph{Structure II} and it generate Approximate RS Code (4,2,1,3,II).
-As a result, the unimportant data constitutes RS(4,2), and the important data constitutes RS(4,3).
+Briefly, APPR.STAR($5,2,1,4$,Uneven) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD.
+It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
 
-\subsection{XOR-based Approximate Code}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce two tipical construction of XOR-based Approximate Code, Approximate STAR Code and Approximate TIP Code.
+\subsubsection{Approximate TIP Code}
 
@@
 \centering
-\includegraphics[width=0.7\linewidth]{photo/AP-5214.pdf}
-\caption{Construction of Approximate STAR Code (5,2,1,4,II)}
-\label{fig-ap-5214}
-\end{figure}
-
-\begin{figure}[ht]
-\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
-\caption{Encoding process of Approximate STAR Code (5,2,1,4,II), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
-\end{figure}
-
-\subsubsection{Approximate STAR Code}
-Figure \ref{fig-ap-5214} shows the construction of Approximate STAR Code (5,2,1,4,II).
-
-As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
-Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
-As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
-According to the construction requirements of STAR, each node is divided into 4 blocks.
-
-Briefly, Approximate STAR Code (5,2,1,4,II) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD.
-It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
-
-\subsubsection{Approximate TIP Code}
-We then intorduce the generation of Approximate TIP Code (5,1,2,6,I).
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.3\textwidth]{photo/AP-5126.pdf}
-\caption{Construction of Approximate TIP Code (5,1,2,6,I)}
+\includegraphics[width=\linewidth]{photo/AP-5126-v2.pdf}
+\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
 \label{fig-ap-TIP}
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.8\linewidth]{photo/RAID5-TIP-v2.pdf}        
-\caption{Encoding process of Approximate TIP Code (5,1,2,6,I), which can be divided into TIP (encode important data) and RAID-5 (encode unimportant data).
-(e.g., the diagonal parity block marked as a square $E_{4,5} = E_{4,0} \oplus E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$)}
-\label{fig-TIP}
-\end{figure}
+We then intorduce the generation of APPR.TIP($5,1,2,6$,Even).
 
-The horizontal parity block of TIP code is defined as the local parity and the remaining two as the global parities.
+In the code segmentation phase, we split TIP code into horizontal, diagonal and anti-diagonal parity.
+The important data is arranged in Even structure.
+However, since the parity block of the TIP is distributed over a series of nodes, the code generation process is different from that of the STAR.
 
-As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 layers, where important data accounting for 1/6 of each node.
+We first generate local parity nodes by the horizontal parity for the important and unimportant data in each node. Then, we arrange the important data blocks as the type of Figure \ref{fig-tip-1}.
+We use diagonal and anti-diagonal parity to encode the important data and define the last 2 node (Node 5 and 6) as the global parity nodes.
+
+As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 stripes, where important data accounting for 1/6 of each node.
 All data nodes generate 6 local parity nodes.
 Important data blocks are rearranged to fit the parity form of TIP Code and generate two global parity nodes.
-The encoding process of Approximate TIP Code (5,1,2,6,I) is shown in Figure \ref{fig-TIP}.
 
@@
 When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.
+
 However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$. 
-The former exceeds the fault tolerance of unimportant data, while the latter exceeds the fault tolerance of important data. As mentioned in \ref{code-gen}, $r+g$ is set to 3.
-Approximate Codes based on different structures have different fault tolerance and reconstruction cases, so we discuss \emph{Structure I} and \emph{Structure II} respectively.
+The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
+As mentioned in Section\ref{code-gen}, $r+g$ is set to 3.
 
-\subsubsection{Structure I}
-Under \emph{Structure I}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures.
+We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
+Approximate Codes based on different structures also have different fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structure respectively.
 
-For unimportant data, it is recoverable as long as the node loss per line does not exceed $r$. Therefore, the unrecoverable scenarios account for
-$$\frac{kh}{\binom{(k+r)h+g}{r+1}}.$$
-of all $r+1$ node failure cases. 
-For important data, when 4 nodes fail, the unrecoverable scenarios account for
-$$h*\frac{\sum_{i=0}^{g} {\binom{4-i}{k+r}*\binom{i}{g}} }{\binom{4}{(k+r)*h+g}}  (g=0,1)$$
+\subsubsection{Lost $r+1$ nodes}
+Under Even structure, the unimportant data nodes are recoverable as long as the node loss per stripe does not exceed $r$ and the global parity nodes do not need to be considered.
+There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases will result in unrecoverable of data.
 
-In Approximate Code (3,1,2,3,I), 90.11\% 2-node failure is recoverable for unimportant data nodes and 95.50\% 4-node failure is recoverable for important data nodes.
+Under Uneven structure, only $h-1$ stripes contain unimportant data, so $P_{U}$ is
+\begin{align}
+    P_{U-Even} &= 1 - \frac{h \times \binom{k+r}{r+1}}{\binom{N}{r+1}}\\
+    P_{U-Uneven} &= 1 - \frac{(h-1) \times \binom{k+r}{r+1}}{\binom{N}{r+1}}
+\end{align}
 
-\subsubsection{Structure II}
-Important and unimportant data are storaged in different nodes under \emph{Structure II}.
-When $r+1$ nodes fail, the unrecoverable scenarios for unimportant data account for
-$$\frac{k(h-1)}{\binom{(k+r)h+g}{r+1}}.$$
-When 4 nodes fail, the unrecoverable scenarios for important data account for
-$$\frac{\binom{k+3}{4}}{\binom{(k+r)h+g}{4}}.$$
-In Approximate Code (3,1,2,3,II), 93.41\% 2-node failure is recoverable for unimportant data nodes, and 98.50\% 4-node failure is recoverable for important data nodes.
+\subsubsection{Lost $4$ nodes}
+The number of all 4-node lost cases is $\binom{N}{4}$.
+We calculate the total number of cases in which all important data may be lost based on the different losses of the global parity nodes. The results are as follows:
+\begin{align}
+    P_{I-Even} = 1 - h*&\frac{\sum_{i=0}^{g} {\binom{k+r}{4-i}*\binom{g}{i}} }{\binom{N}{4}}  (g=1,2)\\
+    P_{I-Uneven} &= 1 - \frac{\binom{k+3}{4}}{\binom{N}{4}}
+\end{align}
+
+According to the equations above, in Approximate RS ($3,1,2,3$, Even), $80.21\%$ 2-node failure cases are recoverable for unimportant data nodes, and $95.50\%$ 4-node failure is recoverable for important data nodes.
+In Approximate RS ($3,1,2,3$, Uneven), $P_U=86.81\%$ $P_{I}=98.50\%$.
 
@@
 
-We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
+We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-properties}.
 \begin{itemize}
@@
 \centering 
-\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP}\label{tab-AS-RS-AP}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
 \hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Write\\ Performance(Average)\end{tabular} \\ \hline
+EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
@@
 TIP-code($k,3$) & $(k+3)/k$ & $3$ & 4 \\ \hline
-\begin{tabular}[c]{@{}c@{}}Appr. RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4} 
-\begin{tabular}[c]{@{}c@{}}Appr. STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4} 
-\begin{tabular}[c]{@{}c@{}}Appr. TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
+\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4} 
+\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4} 
+\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
 \end{tabular}
@@
 \centering
-\includegraphics[height = 5cm]{photo/implementation-V2.pdf}
+\includegraphics[height = 5.5cm]{photo/implementation-V2.pdf}
 \caption{Overview of Approximate Storage Layer}
@@
 For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
-%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each layer are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
+%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
@@
 In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code. 
-\subsection{Evaluation Methodology }
-To compared with Approximate Code, We choose several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6, RS code and LRC codes which are widely used in cloud storage systems.
-Since 3DFTs are typical configurations, we set the number of parity nodes to 3 for all kinds of codes in this evaluation.
+\subsection{Evaluation Methodology}
+The experiment is divided into two parts: the first part evaluates the performance of the Approximate Code code, and the second part evaluates the impact of the loss of the unimportant data on the video files.
 
+To compared with Approximate Code, We choose several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
 
+To prove that the lost of unimportant data is acceptable, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario.
+
 \subsubsection{Metrics and Methods for Mathematical Analysis: }
-We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Write(update) Cost} defined in Section \ref{properties} as measure.
+We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as measure.
 We first analyze the impact of the settings of the three parameters on these metrics, then we compare these matrics with several EC methods.
@@
 We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
-\textbf{Encoding Time} is the time for generating all parity nodes and \textbf{Recovery Time} is the time for recovering the lost nodes.
-Several codes are chosen to compared with Approximate Code with the same data nodes $k$.
-Attention that Approximate Code can only recover the important data nodes in some cases and we only keep the lost data nodes to be the same for all codes which means Approximate Code may recover less data than other codes.
+Encoding Time is the time for generating all parity nodes and Recovery Time is the time for recovering the lost nodes.
+
+In our experiments of recovery time, we compare Approximate Code with several other codes with the same data nodes $k$. 
+Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes.
 
@@
 Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes.
-We set $h=4,6$ and node size equal $1GB$ here as two common configurations.
+We set $h=4,6$ and node size equal $1GB$ here as two default configurations.
 
-Our experiment can mainly be divided into five cases.
-In the first part, we evaluate the encoding time for all kinds of codes.
-In the next three parts we measure the recovery time under single, double and triple failure nodes condition respectively.
-Finally we conduct the experiment of frame interpolation to prove that the lost of video frames is recoverable to some extent.
+Our experiment can mainly be divided into four cases.
+First, we evaluate the encoding time for several erasure codes.
+We then evaluate the recovery time of the scenarios where single, double and triple nodes are corrupted.
+
+\subsubsection{\textcolor{red}{Metrics and Methods for Frame Recovery: }}
+we performed the experiment of video frame recovery with the frame interpolation technique.
+The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}.
+We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes.
+We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data.
+The average quality of the recovered pictures is commonly above 35dB in terms of PSNR (Peak Signal to Noise Ratio).
 
@@
 \subsubsection{Storage Overhead}
-We compare the storage overhead between RS (k,3), Appr.
-RS (k,1,2,h) and Appr.
-RS (k,2,1,h), where h = 4 or 6.
-As shown in Figure \ref{fig-Storage}, the results shows that Appr.
-RS Code has lower storage overhead than RS Code.
-The ratio of optimization is up to 21.4\% when h=4, k=4 and 23.8\% when h=6, k=4.
+We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.
+As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
+The ratio of optimization is up to 21.4\% when $h=4, k=4$ and $23.8\%$ when $h=6, k=4$.
+For more tipical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
 
@@
 \subsubsection{Single Write Performance}
-We compare the single write performance between RS, STAR, Appr.
-RS and Appr.
-STAR, where h = 4 or 6.
-As shown in Figure \ref{fig-Sig-Write}, the results shows that Appr.
-RS Code has lower single write performance than RS Code and STAR Code.
-The ratio of optimization is up to 41.3\% when h=6 and 25\% when h=4.
-As $k$ increases, the performance of Appr.
-STAR is close to RS and always better than STAR.
+We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$.
+As shown in Figure \ref{fig-Sig-Write}, the results shows that APPR.RS Code has lower single write performance than RS Code and STAR Code.
+The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$.
+As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
 
-\begin{figure}[]
+\begin{figure}[ht]
 \subfigure[h=4]{
     \label{fig-storage4}
-    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-4.eps}
+    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-4.eps}
 }
@@
     \label{fig-storage6}
-    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-6.eps}
+    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-6.eps}
 }
@@
 
-\begin{figure}[]
+\begin{figure}[ht]
 \subfigure[h=4]{
@@
 
-\subsubsection{Encoding Time Analysis}
-In this part, we compared the encoding time of Approximate Code with Tip code, STAR code, RS code and LRC codes, respectively.
-Here we use Tip and STAR code to generate parities in Approximate Code.
-Thus we can cover all the code configurations from $k$ = 5 to $k$ = 17.
+\subsubsection{Encoding Time}
+In this part, we compared the encoding time of Approximate Code with TIP code, STAR code, RS code and LRC codes, respectively. 
+Since these two codes have different limits on the number of data nodes, we use TIP and STAR code to generate parities in Approximate Code, so that we can cover all the code configurations from $k$ = 5 to $k$ = 17.
 \begin{itemize}
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-encodingSTAR } illustrates that Approximate Code encodes faster than STAR code and the rate of optimization is up to 56.3\% (between Appr.
-STAR (k,1,2,6) and STAR (k, 3) when k = 5).
-    \item Appr.
-TIP(k,1,2,4), Appr.
-TIP(k,2,1,4), Appr.
-TIP(k,1,2,6), Appr.
-TIP(k,2,1,6) and TIP(k,3): the effet of Tip code is similar to STAR  code.
-From Figure \ref{fig-encodingTIP}, the rate of optimization is up to 58.1\% (between Appr.
-TIP(k,1,2,6) and TIP(k, 3) when k = 9).
-    \item Appr.
-TIP/STAR (k,1,2,4), Appr.
-TIP/STAR (k,2,1,4), Appr.
-TIP/STAR (k,1,2,6), Appr.
-TIP/STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-encodingRS}, we could find out that the AP code encodes largely faster than RS code.
-The rate of optimization is up to 91.1\% (between Appr.
-TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
-    \item Appr.
-TIP/STAR (k,1,2,4), Appr.
-TIP/STAR (k,2,1,4), Appr.
-TIP/STAR (k,1,2,6), Appr.
-TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3):  According to Figure \ref{fig-encodingLRC}, we could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
-The rate of optimization is up to 88.9\% (between Appr.
-TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-encodingSTAR} illustrates that Approximate Code encodes faster than STAR code and the rate of optimization is up to $56.3\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+
+    \item APPR.TIP($k,1,2,4$), APPR.TIP($k,2,1,4$), APPR.TIP($k,1,2,6$), APPR.TIP($k,2,1,6$) and TIP($k,3$): the effet of TIP code is similar to STAR code.
+From Figure \ref{fig-encodingTIP}, the rate of optimization is up to 58.1\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
+
+    \item APPR.TIP/STAR ($k,1,2,4$), APPR.
+TIP/STAR ($k,2,1,4$), APPR.
+TIP/STAR ($k,1,2,6$), APPR.TIP/STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-encodingRS}, we could find out that the AP code encodes largely faster than RS code.
+The rate of optimization is up to 91.1\% (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+
+    \item APPR.
+TIP/STAR ($k,1,2,4$), APPR.
+TIP/STAR ($k,2,1,4$), APPR.
+TIP/STAR ($k,1,2,6$), APPR.
+TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC ($k,6,3$): According to Figure \ref{fig-encodingLRC}, we could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
+The rate of optimization is up to 88.9\% (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
 \end{itemize}
@@
 The results show that Approximate Code has the best encoding performance among five codes.
-There are two reasons for this condition:1) Approximate Code only generates 3 parities for important data which lead to the less size of total parity nodes, comparing with other codes.
-2)Approximate Code use XOR-based codes (Tip and star code) which have lower computational overhead than RS -based codes.\par
+There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while tipical 3DFTs codes generate 3 nodes.
+(2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par
 
-\begin{figure*}[]
-\subfigure[AP and RS]{
+\begin{figure*}[ht]
+\subfigure[APPR.STAR and STAR]{
     \label{fig-encodingSTAR}
@@
 }
-\subfigure[AP and STAR]{
+\subfigure[APPR.TIP and TIP]{
     \label{fig-encodingTIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Tip.eps}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-TIP.eps}
 }
-\subfigure[AP and TIP]{
+\subfigure[APPR.TIP/STAR and RS]{
     \label{fig-encodingRS}
@@
 }
-\subfigure[AP and LRC]{
+\subfigure[APPR.TIP/STAR and LRC]{
     \label{fig-encodingLRC}
@@
 
-\begin{figure*}[]
-\subfigure[AP and RS]{
+\begin{figure*}[ht]
+\subfigure[APPR.STAR and STAR]{
     \label{fig-decoding-1-STAR}
@@
 }
-\subfigure[AP and STAR]{
+\subfigure[APPR.TIP and TIP]{
     \label{fig-decoding-1-TIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Tip.eps}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-TIP.eps}
 }
-\subfigure[AP and TIP]{
+\subfigure[APPR.TIP/STAR and RS]{
     \label{fig-decoding-1-RS}
@@
 }
-\subfigure[AP and LRC]{
+\subfigure[APPR.TIP/STAR and LRC]{
     \label{fig-decoding-1-LRC}
@@
 
-\begin{figure*}[]
+\begin{figure*}[ht]
 \subfigure[AP and RS]{
@@
     \label{fig-decoding-2-TIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Tip.eps}
+    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-TIP.eps}
 }
@@
 }
-\subfigure[AP and LRC]{
+\subfigure[APPR.TIP/STAR and LRC]{
     \label{fig-decoding-2-LRC}
@@
 
-\begin{figure*}[]
+\begin{figure*}[ht]
     \subfigure[AP and RS]{
@@
         \label{fig-decoding-3-TIP}
-        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Tip.eps}
+        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-TIP.eps}
     }
@@
     }
-    \subfigure[AP and LRC]{
+    \subfigure[APPR.TIP/STAR and LRC]{
         \label{fig-decoding-3-LRC}
@@
 
-In this section, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17. 
+In this section, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17. 
 \begin{itemize}
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-1-STAR} illustrates that the decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between Appr.
-STAR (k,1,2,4) and STAR (k, 3) when k = 5).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and TIP(k,3): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as Tip code when sinlge node fails and the rate of optimization is up to 8.8\% (between Appr.
-TIP(k,1,2,4) and TIP(k, 3) when k = 17).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-1-RS}, we could find out that the Approximate Code decodes largely faster than RS code.
-The rate of optimization is up to 80.2\% (between Appr.
-TIP/STAR (k,1,2,4) and RS(k, 3) when k = 5).
-    \item Appr.
-TIP/STAR (k,1,2,4), Appr.
-TIP/STAR (k,2,1,4), Appr.
-TIP/STAR (k,1,2,6), Appr.
-TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3):  According to Figure \ref{fig-decoding-1-LRC}, we could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
-The rate of optimization is up to 5.8\% (between Appr.
-TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 13).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-1-STAR} illustrates that the decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-1-RS}, we could find out that the Approximate Code decodes largely faster than RS code.
+The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
+    \item APPR.TIP/STAR ($k,1,2,4$), APPR.
+TIP/STAR ($k,2,1,4$), APPR.
+TIP/STAR ($k,1,2,6$), APPR.
+TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC  ($k,6,3$):  According to Figure \ref{fig-decoding-1-LRC}, we could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
+The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
 \end{itemize}
 
-We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-decoding-1-combine} with $k$=5.
+We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-decoding-1-combine} with $k=5$.
 The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
@@
 
-\begin{figure*}[]
+\begin{figure*}[ht]
 \subfigure[Encoding Time]{
@@
 \subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17. 
+In this part, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17. 
 \begin{itemize}
-    \item Appr. STAR (k,1,2,4), Appr. STAR (k,2,1,4), \\
-    Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-2-STAR} illustrates that the rate of optimization is up to 83.9\% (between Appr.
-STAR (k,1,2,6) and STAR (k, 3) when k = 5).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4),  \\ Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and TIP(k,3): This condition is similar to STAR code.
-Figure \ref{fig-decoding-2-TIP} illustrates that the rate of optimization is up to 84.8\% (between Appr.
-TIP(k,1,2,6) and TIP(k, 3) when k = 9).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4),  \\ Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-2-RS}, we could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
-The rate of optimization is up to 96.9\% (between Appr.
-TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
-    \item Appr. TIP/STAR (k,1,2,4), Appr. TIP/STAR (k,2,1,4),  \\ Appr. TIP/STAR (k,1,2,6), Appr. TIP/STAR (k,2,1,6) and LRC(k,4,3), LRC(k,6,3): 
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-2-STAR} illustrates that the rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$),  APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): This condition is similar to STAR code.
+Figure \ref{fig-decoding-2-TIP} illustrates that the rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$),  APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-2-RS}, we could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
+The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item APPR.TIP/STAR ($k,1,2,4$), APPR. TIP/STAR ($k,2,1,4$),  APPR. TIP/STAR ($k,1,2,6$), APPR. TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC ($k,6,3$): 
     According to Figure \ref{fig-decoding-2-LRC}, we could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
-The rate of optimization is up to 97.2\% (between Appr.
-TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
+The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
 \end{itemize}
 
-The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-decoding-2-combine} (k=5).
-The results show that RS code and LRC codes has the worst two failure nodes decoding performance while Appr.
-TIP/STAR (k,1,2,6) and Appr.
-TIP/STAR (k,1,2,4) perform best among all kinds of codes.
-The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while Appr.
-TIP/STAR (k,1,2,6) and Appr.
-TIP/STAR (k,1,2,4) do the approximate recovery which means they only recover important data at this time.\par
+The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-decoding-2-combine} ($k=5$).
+The results show that RS code and LRC codes has the worst two failure nodes decoding performance while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) perform best among all kinds of codes.
+The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) do the approximate recovery which means they only recover important data at this time.
 
 \subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with Tip code, Star code, RS code and LRC codes under three failure nodes condition, respectively. k changes from 5 to 17. 
+In this part, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under three failure nodes condition, respectively. $k$ changes from 5 to 17. 
 \begin{itemize}
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and STAR (k,3): Figure \ref{fig-decoding-3-STAR} illustrates that the rate of optimization is up to 83.5\% (between Appr.
-STAR (k,1,2,6) and STAR (k, 3) when k = 5).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and TIP(k,3): This condition is similar to STAR code.
-Figure \ref{fig-decoding-3-TIP} illustrates that the rate of optimization is up to 82.2\% (between Appr.
-TIP(k,1,2,6) and TIP(k, 3) when k = 5).
-    \item Appr.
-STAR (k,1,2,4), Appr.
-STAR (k,2,1,4), Appr.
-STAR (k,1,2,6), Appr.
-STAR (k,2,1,6) and RS(k,3): From the Figure \ref{fig-decoding-3-RS}, we could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
-The rate of optimization is up to 96.7\% (between Appr.
-TIP/STAR (k,1,2,6) and RS(k, 3) when k = 5).
-    \item Appr. TIP/STAR (k,1,2,4), Appr. TIP/STAR (k,2,1,4), Appr. TIP/STAR (k,1,2,6), Appr. TIP/STAR (k,2,1,6)  \\
-    and LRC(k,4,3), LRC(k,6,3): 
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-3-STAR} illustrates that the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): This condition is similar to STAR code.
+Figure \ref{fig-decoding-3-TIP} illustrates that the rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-3-RS}, we could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
+The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item APPR.TIP/STAR ($k,1,2,4$), APPR. TIP/STAR ($k,2,1,4$), APPR. TIP/STAR ($k,1,2,6$), APPR. TIP/STAR ($k,2,1,6$)  \\
+    and LRC($k,4,3$), LRC ($k,6,3$): 
     According to Figure \ref{fig-decoding-3-LRC}, we could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes.
-The rate of optimization is up to 98.3\%  (between Appr.
-TIP/STAR (k,1,2,6) and LRC(k, 6, 2) when k = 5).
+The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
 \end{itemize}
@@
 The main reasons are that: On three failure nodes condition, LRC codes decode data through the global parities which has a longer parity chain.
-For example $LRC(44,4,2)$ use 44 nodes to recover the three lost nodes.
+For example $LRC (44,4,2)$ use 44 nodes to recover the three lost nodes.
 the computational cost of GF operations is also larger than XOR operations.
-On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.\par
+On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.
 
@@
 Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
-As shown in Figure\ref{fig:frameRecovery}, The top 3 figures are the original frames.
+As shown in Figure\ref{fig-frameRecovery}, The top 3 figures are the original frames.
 When frame 2 lost, the interpolation techniques can output \ref{fig-recoverof2} by the input of \ref{fig-interop1} and \ref{fig-interop3}.
@@
 \caption{Frame Recovery Result using Frame Interpolation}
-\label{fig:frameRecovery}
+\label{fig-frameRecovery}
 \end{figure}
@@
 The Approximate Code can segment the input erasure codes and provide different fault tolerance for data of different importance.
-For important data, the Approximate Code provides 3DFTS, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery, while having good update write performance.
+For important data, the Approximate Code provides 3DFTs, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery, while having good update write performance.
 We conducted several experiments in the Hadoop system and found that compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.

### 2019-04-22 Apcode-4-22/ApproximateCode.tex
version 4.1

--- 2019-04-21 ApproximateCode.tex
@@
 \author{Chentao Wu}
-
 \author{Xin Xie}
-
 \author{Jie Li}
-
 \author{Minyi Guo}
-
-\author{Xubin He}
-\affiliation{%
-  \institution{}
+\affiliation{
+  \institution{Shanghai Jiao Tong University}
 }
 
-\author{Yuanyuan Dong}
 \author{Hao Lin}
@@
 \authornotemark[1]
-\email{webmaster@marysville-ohio.com}
 \affiliation{%
@@
 \begin{abstract}
-Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
+Nowadays massive video data is stored in cloud storage systems, which is generated by various applications such as autonomous driving, news media, security monitoring, etc.
 Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
@@
 \begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
-\hline \hline
-Symbols & \multicolumn{1}{c|}{Description} \\ \hline
+\hline
+Symbols & \multicolumn{1}{c|}{Description} \\ \hline \hline
 $k$ & the number of data nodes in a local stripe \\ \hline
@@
 In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of PSNR, and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of middlebury benchmark.
+Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of Peak Signal to Noise Ratio (PSNR), and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of Middlebury benchmark.
 
@@
 \hspace{5pt}
-\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
-\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
-}
-
 \subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
 \includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
-}
-\hspace{5pt}
-\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
-\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
 }
@@
 \hspace{5pt}
+\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
+\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
+}
+
+\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
+\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
+}
+\hspace{5pt}
 \subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
@@
 }
-\caption{Encoding of STAR (subfigure (a),(c) and (e)) and TIP (subfigure (b),(d) and (f)) code ($p = 5$).
+\caption{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$).
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
@@
 STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.
-
-%从这里开始简单讲解几种RAID-6或三盘容错阵列的纠删码，如RS，EVENODD，RDP，STAR，LRC, H-Code，TIP-Code等，并且用编码图来说明（主要是实验中用到的几种编码）。
 
@@
 We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data.
-The average quality of the recovered pictures is commonly above 35dB in terms of PSNR (Peak Signal to Noise Ratio).
+The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio PSNR .
 

### 2019-04-22 ApproximateCode.tex
version 4.1

@@
 
-%
-% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-% Please copy and paste the code instead of the example below.
-%
 \keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}
-
 \maketitle
@@
 \centering
-\includegraphics[width=\linewidth]{photo/Framework-v2.pdf}
+\includegraphics[width=\linewidth]{photo/Framework-v3.pdf}
 \caption{The framework of Approximate Code}
@@
 \centering
-\includegraphics[width=\linewidth]{photo/AP-5214-v2.pdf}
+\subfigure[Structure selection of APPR.STAR Code]{
+    \label{fig-ap-tip-str}
+    \includegraphics[width = 0.5\linewidth]{photo/APPR-STAR-STR.pdf}
+}
+
+\subfigure[Generation of local parities]{
+    \label{fig-ap-tip-lP}
+    \includegraphics[width = 0.59\linewidth]{photo/APPR-STAR-LO.pdf}
+}
+\subfigure[Generation of global parities]{
+    \label{fig-ap-tip-GP}
+    \includegraphics[width = 0.35\linewidth]{photo/APPR-STAR-GL.pdf}
+}
 \caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
@@
 \end{figure}
-
-\iffalse
-\begin{figure}[ht]
-\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
-\caption{Encoding process of APPR.STAR($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
-\end{figure}
-\fi
 
@@
 \centering
-\includegraphics[width=\linewidth]{photo/AP-5126-v2.pdf}
+\subfigure[Structure selection of APPR.TIP Code]{
+    \label{fig-ap-tip-str}
+    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
+}
+\hspace{2pt}
+\subfigure[Generation of local parities]{
+    \label{fig-ap-tip-lP}
+    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
+}
+
+\subfigure[Generation of global parities]{
+    \label{fig-ap-tip-GP}
+    \includegraphics[width = 0.75\linewidth]{photo/APPR-TIP-GL.pdf}
+}
 \caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
@@
 
-We then intorduce the generation of APPR.TIP($5,1,2,6$,Even).
+We then introduce the generation of APPR.TIP($5,1,2,6$,Even).
 

### 2019-04-22 ApproximateCode.tex
version 4.2

@@
 
-\author{Huayi Jin}
-\email{keplar_gd@sjtu.edu.cn}
+\author{Huayi Jin, Chentao Wu, Xin Xie, Jie Li, Minyi Guo, Hao Lin, Jianfeng Zhang}
+%\email{keplar_gd@sjtu.edu.cn}
 \affiliation{%
@@
 
-\author{Chentao Wu}
-\author{Xin Xie}
-\author{Jie Li}
-\author{Minyi Guo}
-\affiliation{
-  \institution{Shanghai Jiao Tong University}
-}
-
-\author{Hao Lin}
-\author{Jianfeng Zhang}
+\author{Hao Lin, Jianfeng Zhang}
 \authornotemark[1]
@@
 
-\begin{table}[]
+\begin{table}[]\footnotesize
 \caption{The symbols used in this paper.}\label{parameter}
-\centering\small
-\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
+\centering
+\begin{tabular}{|p{0.7cm}<{\centering}|p{6.5cm}|}
 \hline
@@
 $r$ & the number of local parity nodes in a local stripe \\ \hline
-$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
+$n$ & the number of all data and parity nodes in a local stripe. ($n=k+r$) \\ \hline
 $h$ & the number of local stripes to construct a global stripe \\ \hline
@@
 $N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
-$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
-$D_i$ & data nodes \\ \hline
+$E_{i,j}$ & the element at the $i$-th row and $j$-th column \\ \hline
+$D_i$ & a data node \\ \hline
 $P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
 $P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
+$\oplus$ & the XOR operation symbol \\ \hline
+$\binom{n}{k}$ & The number of $k$-combinations from $n$ elements\\ \hline
 LP & local parity nodes \\ \hline
@@
 
-Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating.
-Several attempts have been made to address this issue.
+Reed Solomon Code \cite{RS} (RS code) is a classic MDS code.
+The encoding and decoding operations of RS code are based on Galois Field (GF), leading to high scalability as well as high computational complexity.
+All the parities of RS code are horizontal as shown in Figure \ref{fig-RS-1}.
 
@@
 Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
-LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{LRC}.
+LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{fig-LRC-1}.
 
@@
     \centering
-    \includegraphics[height=2.5cm]{photo/LRC.pdf}
-    \caption{LRC}
+    \subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $E_{0,5} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
+        \includegraphics[width=0.26\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
+    }
+    \hspace{3px}
+    \subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $E_{0,5} = \sum_{i=2}^3 A_{0,i}E_{0,i}$ and the global parity $E_{0,7} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
+        \includegraphics[width=0.67\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
+    }
+    \caption{Encoding of RS code and LRC}
 \end{figure}
@@
 
-\subsection{Approximate Storage}
+\subsection{Approximate Storage \textcolor[rgb]{1.00,0.00,0.00}{Compression}}
 %Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
@@
 
-\begin{table}[ht]
+\begin{table}[ht]\footnotesize
 \centering
 \caption{
-\textcolor{red}{Need to update}
 Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
-\small
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|}
 \hline
-\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
-\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5}
- & RAID-6 & medium & medium & high \\ \hline
-\multicolumn{2}{|c|}{Approximate Storage} & low & low & high \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5}
- & UD &  & medium & high \\ \hline
+\multirow{2}{*}{EC} & RS & high & high & high \\ \cline{2-5}
+ & RAID-6 & medium & medium & medium \\ \hline
+\multicolumn{2}{|c|}{Approximate Storage} & low & low & low \\ \hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate\\ Code\end{tabular}} & ID & low & high & low \\ \cline{2-5}
+ & UD & low & medium & low \\ \hline
+\multicolumn{2}{|c|}{Data Compression} & low & / & high \\ \hline
 \end{tabular}
@@
 %First, the overhead of existing 3DFTs erasure codes is too high.
-Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
-Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.
+%Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
+%Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.
 
@@
 \centering
-\includegraphics[width=\linewidth]{photo/Framework-v3.pdf}
+\includegraphics[width=0.9\linewidth]{photo/Framework-v3.pdf}
 \caption{The framework of Approximate Code}
@@
 
+\begin{figure}
+    \centering
+    \subfigure[XXX]{
+        \includegraphics[width=0.26\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+    }
+    \subfigure[XXX]{
+        \includegraphics[width=0.68\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
+    }
+    \caption{XXXX}
+\end{figure}
+
 \subsection{Approximate XOR-based Codes}
@@
 
-\subfigure[Generation of local parities]{
-    \label{fig-ap-tip-lP}
-    \includegraphics[width = 0.59\linewidth]{photo/APPR-STAR-LO.pdf}
-}
-\subfigure[Generation of global parities]{
-    \label{fig-ap-tip-GP}
-    \includegraphics[width = 0.35\linewidth]{photo/APPR-STAR-GL.pdf}
+\subfigure[Generation process]{
+    \label{fig-ap-tip-GEN}
+    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
 }
@@
     \label{fig-ap-tip-GP}
-    \includegraphics[width = 0.75\linewidth]{photo/APPR-TIP-GL.pdf}
+    \includegraphics[width = 0.8\linewidth]{photo/APPR-TIP-GL-v2.pdf}
 }
@@
     \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-LRC.eps}
-}
+}\vspace{-0.5cm}
 \caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
@@
 \begin{figure*}[ht]
-\subfigure[APPR.STAR and STAR]{
+\subfigure{
     \label{fig-decoding-1-STAR}
@@
 }
-\subfigure[APPR.TIP and TIP]{
+\subfigure{
     \label{fig-decoding-1-TIP}
@@
 }
-\subfigure[APPR.TIP/STAR and RS]{
+\subfigure{
     \label{fig-decoding-1-RS}
@@
 }
-\subfigure[APPR.TIP/STAR and LRC]{
+\subfigure{
     \label{fig-decoding-1-LRC}
     \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-LRC.eps}
-}
+}\vspace{-0.5cm}
 \caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
@@
 \begin{figure*}[ht]
-\subfigure[AP and RS]{
+\subfigure{
     \label{fig-decoding-2-STAR}
@@
 }
-\subfigure[AP and STAR]{
+\subfigure{
     \label{fig-decoding-2-TIP}
@@
 }
-\subfigure[AP and TIP]{
+\subfigure{
     \label{fig-decoding-2-RS}
@@
 }
-\subfigure[APPR.TIP/STAR and LRC]{
+\subfigure{
     \label{fig-decoding-2-LRC}
     \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-LRC.eps}
-}
+}\vspace{-0.5cm}
 \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
@@
 \begin{figure*}[ht]
-    \subfigure[AP and RS]{
+\subfigure{
     \label{fig-decoding-3-STAR}
@@
 }
-    \subfigure[AP and STAR]{
+\subfigure{
     \label{fig-decoding-3-TIP}
@@
 }
-    \subfigure[AP and TIP]{
+\subfigure{
     \label{fig-decoding-3-RS}
@@
 }
-    \subfigure[APPR.TIP/STAR and LRC]{
+\subfigure{
     \label{fig-decoding-3-LRC}
     \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-LRC.eps}
-    }
+}\vspace{-0.5cm}
 \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
@@
 
+\iffalse
+\begin{figure}[ht]
+\centering
+\subfigure[]{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
+}\hspace{-0.4cm}
+\subfigure[]{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
+}
+\caption{Recovery time Result using Frame Interpolation}
+\label{fig-recoverytime}
+\end{figure}
+\fi
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{photo/experiment/Recovery-2-3.pdf}\label{fig-rec-3}
+\caption{Recovery time Result using Frame Interpolation}
+\label{fig-recoverytime}
+\end{figure}
+
 The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-decoding-3-combine} ($k$=5).
@@
 
-\begin{acks}
-
-\end{acks}
-
 \bibliographystyle{ACM-Reference-Format}

### 2019-04-22 ApproximateCode.tex
version 4.3

@@
     \institution{Shanghai Jiao Tong University}
-}
-
-\author{Hao Lin, Jianfeng Zhang}
-\authornotemark[1]
-\affiliation{%
     \institution{The Alibaba Group}
@@
 \begin{abstract}
-Nowadays massive video data is stored in cloud storage systems, which is generated by various applications such as autonomous driving, news media, security monitoring, etc.
+Nowadays massive video data is stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
 Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
 Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems.
-Although there are several solutions like approximate storage technique for storage devices, it cannot guarantee low storage cost and high data reliability in storage systems concurrently.
+Although there are several solutions like approximate storage technique, they cannot guarantee low storage cost and high data reliability concurrently.
 
-To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems.
-The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance.
+To address this challenge, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems.
+The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance.
 On one hand, for important data, Approximate Code provides triple parities to provide high reliability.
@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
 \end{abstract}
@@
 Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}.
-RS-based codes are encoded according the Galois Field Computation in Reed Solomon Code \cite{RS}, which allow flexible configuration and have a little higher computation cost.
-XOR-based codes simplify the computation, but the scalability is a significant issue in previous literatures.
+RS-based codes are encoded according the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost.
+XOR-based codes simplify the computation, but they suffer other issues like scalability.
+\textcolor{red}{[CITE GSR SDM]}
 
@@
 Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
-Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
-Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}.
-\textcolor{red}{However, the compression and decompression processes result in a large amount of computational overhead, which decreases their efficiency in frequent failure scenarios like cloud.}
+The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
+Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.}
+is the third strategy to reduce the storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}, which needs to be collaborated with erasure codes for high reliability.
+However, the compression/decompression processes result in a large amount of computational overhead, which limits their usage in cloud systems.
 Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
 
-To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems.
+To address the above challenge, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for tiered video data storage in cloud systems.
 The key idea of Approximate Code is treating the important/unimportant data in different ways.
@@
 On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery.
-When triple disks fail, the lost data can be reconstructed via a fuzzy manner.
+When triple disks fail, the lost unimportant data can be reconstructed via a fuzzy manner.
 
@@
 $N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
-$E_{i,j}$ & the element at the $i$-th row and $j$-th column \\ \hline
+$C_{i,j}$ & the element at the $i$-th row and $j$-th column \\ \hline
+$A_{i,j}$ &  the coefficient of $C_{ij}$ in the Galois Field \\ \hline
 $D_i$ & a data node \\ \hline
@@
 \end{tabular}
+\vspace{-3mm}
 \end{table}
@@
 This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
-For a normal HD video file metioned as above, H.264 can reduce its size by about 10 times, only 443.27MB.
+For a normal HD video file as mentioned above, H.264 can reduce its size by about 10 times, only 443.27MB.
 
@@
 \begin{enumerate}
-    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
-    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
-    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
+    \item I frame: A frame that is not depend on other frame data, which means it can be decoded independently of other frames.
+    \item P frame: A frame holds the changes compared to the previous frame, which saves the storage space by leaving out redundant information.
+    \item B frame: A frame decreases the storage space as well by utilizing the data of both the preceding and following frames.
 \end{enumerate}
-A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames that are independent of the frames in other GOPs to prevent bit error spread, as shown in Figure \ref{H264-IPB}.
-%In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}.
-Therefore, within each GOP, the I frame has the highest importance because other frames rely on it for recovery; the importance of the P frame is second, and the B frame has the least importance.
+A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames, as shown in Figure \ref{H264-IPB}.
+Within each GOP, the I frame is the most significant because all other frames rely on if for recovery. P frames are the second important, and B frames have the least value.
 Based on this feature, a special program can be designed to distinguish the importance of video frames.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
+\includegraphics[width=0.4\textwidth]{photo/H264_IPB.pdf}
+\vspace{-3mm}
 \caption{A sample of GOPs in H.264}
+\vspace{-3mm}
 \label{H264-IPB}
@@
 In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
-However, the lost frames can still be recoverable with the benefit of nowadays powerful deep learning techniques.
-One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context}.
+However, the lost frames can still be recoverable with the benefit of powerful deep learning techniques.
+One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context, van2017frame}.
 
@@
 This is a technique that can model natural motion within a video, and generate frames according to the model.
-
-In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow.
-Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of Peak Signal to Noise Ratio (PSNR), and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of Middlebury benchmark.
 
@@
 
-Reed Solomon Code \cite{RS} (RS code) is a classic MDS code.
+Reed Solomon (RS) Code \cite{RS} is a classic MDS code, as shown in Figure \ref{fig-RS-1}.
 The encoding and decoding operations of RS code are based on Galois Field (GF), leading to high scalability as well as high computational complexity.
-All the parities of RS code are horizontal as shown in Figure \ref{fig-RS-1}.
 
-\textcolor{red}{Need to update}
-Local Construction Code (LRC) \cite{LRC} divides the data nodes into multiple local groups, each with a local parity node, and the global parity is calculated by all data nodes.
-Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
-LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{fig-LRC-1}.
+Local Construction Code (LRC) \cite{LRC} 
+is shown in Figure \ref{fig-LRC-1}.
+It divides the data nodes into several groups, which are called local stripes.
+Typically, each local stripe contains one parity node, which is calculated via the data nodes in the same stripe.
+Global stripe is generated via crossing multiple local stripes.
 
@@
 \centering
-    \subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $E_{0,5} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
-        \includegraphics[width=0.26\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
+\subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
+    \includegraphics[width=0.92\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
 }
-    \hspace{3px}
-    \subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $E_{0,5} = \sum_{i=2}^3 A_{0,i}E_{0,i}$ and the global parity $E_{0,7} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
-        \includegraphics[width=0.67\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
-    }
+
+\subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
+    \includegraphics[width=0.8\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
+}\vspace{-3mm}
 \caption{Encoding of RS code and LRC}
+\vspace{-3mm}
 \end{figure}
 
-STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code.
-It employs a novice diagonal redundancy as shown in the left of Figure \ref{fig-star-tip}.
+STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
 
@@
 \centering
-\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
+\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
 \includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
@@
 \hspace{5pt}
-\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
+\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
 \includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
@@
 
-\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
+\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
 \includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
@@
 \hspace{5pt}
-\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
+\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
 \includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
@@
 
-\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
+\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
 \includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
@@
 \hspace{5pt}
-\subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
+\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
 \includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
@@
 
-TIP code is also an XOR-based 3DFTs erasure code.
-Compared with STAR code, the encoding and data arrangement of TIP code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.
+TIP-Code is also an XOR-based 3DFTs erasure code.
+Compared with STAR code, the encoding and data arrangement of TIP-Code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.
 
@@
 
+\iffalse
 \begin{table}[ht]\footnotesize
@@
 \end{table}
+\fi
+
+\begin{table}[ht]\footnotesize
+\centering
+\caption{
+Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
+\begin{tabular}{|p{1.2cm}<{\centering}|p{2.1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|}
+\hline
+Layer & Schemes & Storage Overhead & Fault Tolerance & Computing Overhead \\ \hline
+\begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} & Data Compression & low & / & high \\ \hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}} & RS-based EC for 3DFTs & high & high & high \\ \cline{2-5} 
+ & XOR-based EC for 3DFTs & high & high & low \\ \cline{2-5} 
+ & RAID-6 & low & low & low \\ \cline{2-5} 
+ & RAID-5 & medium & medium & low \\ \cline{2-5} 
+ & Approximate Storage & very low & very low & low \\ \cline{2-5} 
+ & Approximate Code & low & high & low \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-%Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
-%First, the overhead of existing 3DFTs erasure codes is too high.
-%Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
-%Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.
+From the summary of Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance.
+Although approximate storage achieves low cost, its reliability cannot be satisfied in cloud environment.
+Application layer methods such as compression algorithms have high computational overhead and need to be used together with erasure codes to ensure reliability.
+Therefore, the existing solution cannot guarantee high reliability and low overhead at the same time of video storage.
 
-From the summary of Table \ref{tab-AS-EC-AP}, we can find that existing solutions have high storage cost for video storage.
-Although approximate storage achieves low cost, the reliability cannot be satisfied in cloud environment.
 A feasible solution is combining the existing solutions together with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.
@@
 \centering
-\includegraphics[width=0.9\linewidth]{photo/Framework-v3.pdf}
+\includegraphics[width=0.95\linewidth]{photo/Framework-v3.pdf}
 \caption{The framework of Approximate Code}
@@
 
-\subsection{\textcolor{red}{Approximate RS Code}}
+\subsection{Approximate RS-based Codes}
 For RS($k,p$), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes.
@@
     \subfigure[XXX]{
-        \includegraphics[width=0.26\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
     }
+
     \subfigure[XXX]{
-        \includegraphics[width=0.68\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
+        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
     }
-    \caption{XXXX}
+    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
 \end{figure}
@@
 Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP Code.
+This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP-Code.
 
@@
 
-\subsubsection{Approximate TIP Code}
+\subsubsection{Approximate TIP-Code}
 
@@
 \centering
-\subfigure[Structure selection of APPR.TIP Code]{
+\subfigure[Structure selection of APPR.TIP-Code]{
     \label{fig-ap-tip-str}
@@
 }
-\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
+\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}
 \label{fig-ap-TIP}
@@
 
-In the code segmentation phase, we split TIP code into horizontal, diagonal and anti-diagonal parity.
+In the code segmentation phase, we split TIP-Code into horizontal, diagonal and anti-diagonal parity.
 The important data is arranged in Even structure.
@@
 All data nodes generate 6 local parity nodes.
-Important data blocks are rearranged to fit the parity form of TIP Code and generate two global parity nodes.
+Important data blocks are rearranged to fit the parity form of TIP-Code and generate two global parity nodes.
 
@@
     \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
-    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
+    \item Flexibility. The implementation of the Approximate Code can be based on any erasure codes in 3DFTs.
 \end{itemize}
@@
 \centering
-\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP}\label{tab-properties}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
@@
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
-STAR($k,3$) & $(k+3)/k$ & $3$ & $6-\frac{4}{k}$ \\ \hline
-TIP-code($k,3$) & $(k+3)/k$ & $3$ & 4 \\ \hline
+STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
+TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
 \begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
@@
 \centering
-\includegraphics[height = 5.5cm]{photo/implementation-V2.pdf}
+\includegraphics[width=0.8\linewidth]{photo/implementation-V2.pdf}
 \caption{Overview of Approximate Storage Layer}
@@
 
-To compared with Approximate Code, We choose several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
+To compared with Approximate Code, We choose several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
@@
 \subsubsection{Encoding Time}
-In this part, we compared the encoding time of Approximate Code with TIP code, STAR code, RS code and LRC codes, respectively.
+In this part, we compared the encoding time of Approximate Code with TIP-Code, STAR code, RS code and LRC codes, respectively.
 Since these two codes have different limits on the number of data nodes, we use TIP and STAR code to generate parities in Approximate Code, so that we can cover all the code configurations from $k$ = 5 to $k$ = 17.
@@
 
-    \item APPR.TIP($k,1,2,4$), APPR.TIP($k,2,1,4$), APPR.TIP($k,1,2,6$), APPR.TIP($k,2,1,6$) and TIP($k,3$): the effet of TIP code is similar to STAR code.
+    \item APPR.TIP($k,1,2,4$), APPR.TIP($k,2,1,4$), APPR.TIP($k,1,2,6$), APPR.TIP($k,2,1,6$) and TIP($k,3$): the effet of TIP-Code is similar to STAR code.
 From Figure \ref{fig-encodingTIP}, the rate of optimization is up to 58.1\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
@@
 
-In this section, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17.
+In this section, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17.
 \begin{itemize}
     \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-1-STAR} illustrates that the decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
+    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as TIP-Code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
     \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-1-RS}, we could find out that the Approximate Code decodes largely faster than RS code.
@@
 \subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17.
+In this part, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17.
 \begin{itemize}
@@
 \subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with TIP code, Star code, RS code and LRC codes under three failure nodes condition, respectively. $k$ changes from 5 to 17.
+In this part, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under three failure nodes condition, respectively. $k$ changes from 5 to 17.
 \begin{itemize}

### 2019-04-23 ApproximateCode.tex
version 4.5

@@
 \begin{abstract}
-Nowadays massive video data is stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
+Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
 Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
@@
 However, the compression/decompression processes result in a large amount of computational overhead, which limits their usage in cloud systems.
-Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.
+Therefore, existing solutions are difficult to provide low storage cost and high reliability simultaneously.
 
@@
 \item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
-\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
+\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves a small number of parities, low storage cost, high single write performance, and fast data recovery under various failure scenarios.
 \end{enumerate}
@@
 \begin{enumerate}
-    \item I frame: A frame that is not depend on other frame data, which means it can be decoded independently of other frames.
+    \item I frame: A frame that is self-contained, which means it can be decoded independently.
     \item P frame: A frame holds the changes compared to the previous frame, which saves the storage space by leaving out redundant information.
@@
 It divides the data nodes into several groups, which are called local stripes.
-Typically, each local stripe contains one parity node, which is calculated via the data nodes in the same stripe.
+Typically, each local stripe contains one local parity node, which is calculated via the data nodes in the same stripe.
 Global stripe is generated via crossing multiple local stripes.
@@
 \centering
-\subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
+\subfigure[RS Code for arbitrary storage nodes ($k=4, r=3$). The figure shows the encoding of different horizontal parities. (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
     \includegraphics[width=0.92\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
@@
 
-\subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
+\subfigure[LRC Code for arbitrary storage nodes ($k=4, r=2, g=2$), where 4 nodes are divided into 2 local groups and each of them has a local parity.The figure shows the encoding of local and global parities.
+(e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
     \includegraphics[width=0.8\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
@@
 STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
-
 In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.
@@
 }
-
+\vspace{-3mm}
 \subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
@@
 }
-
+\vspace{-3mm}
 \subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
@@
 \includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
-}
-\caption{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$).
-Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
+}\vspace{-3mm}
+\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$).
+Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
+STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
+\vspace{-3mm}
 \label{fig-star-tip}
@@
 TIP-Code is also an XOR-based 3DFTs erasure code.
-Compared with STAR code, the encoding and data arrangement of TIP-Code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.
+Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.
 
-STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.
-
-\subsection{Approximate Storage \textcolor[rgb]{1.00,0.00,0.00}{Compression}}
+\subsection{Approximate Storage}
 %Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
@@
 
-\iffalse
-\begin{table}[ht]\footnotesize
-\centering
-\caption{
-Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
-\begin{tabular}{|c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|}
-\hline
-\multirow{2}{*}{EC} & RS & high & high & high \\ \cline{2-5}
- & RAID-6 & medium & medium & medium \\ \hline
-\multicolumn{2}{|c|}{Approximate Storage} & low & low & low \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate\\ Code\end{tabular}} & ID & low & high & low \\ \cline{2-5}
- & UD & low & medium & low \\ \hline
-\multicolumn{2}{|c|}{Data Compression} & low & / & high \\ \hline
-\end{tabular}
-\end{table}
-\fi
-
 \begin{table}[ht]\footnotesize
@@
 \subsection{Our Motivation}
-
-From the summary of Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance.
+We summarize various methods to reduce storage cost for video files in Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance.
 Although approximate storage achieves low cost, its reliability cannot be satisfied in cloud environment.
@@
 
-A feasible solution is combining the existing solutions together with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.
+From the summary of Table \ref{tab-AS-EC-AP}, existing solutions have their drawbacks on providing high reliability with low storage cost. 
+A feasible solution is combining various erasure codes with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.
 
@@
 Acquire an erasure coding input and get the corresponding parameters.
-Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted by Approximate Code.
+Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted as the input.
 Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.
@@
 For an inputted erasure code, we assume that its fault tolerance is $x$.
-The Approximate Code first splits its parities into two parts: local and global parities.
-The former verifies all important and non-critical data, while the latter only verifies important data.
-Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$.
-For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.
+The Approximate Code first splits its parities into two parts, local and global parities.
+The local parities are used for all data, while the global parities focus on the important data.
+Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of unimportant data is $r$.
+For important data, the code segmentation ensures that the important data have the capabilities of fault tolerance by up to $x$ nodes.
 
 For example, several erasure codes in 3DFTs like STAR have three types of parities, horizontal, diagonal and anti-diagonal parities.
-In the code segmentation step, the horizontal parities are separated from other two parities.
+In the code segmentation step, the horizontal parities are regarded as local parities, which are separated from the diagonal/anti-diagonal parities (shown in Fig.
+\ref{fig-appr-star} and illustrated in \ref{APPRXOR} in detail).
 
 \subsubsection{Structure Selection}
-The Approximate Code framework then choose the structure for the input erasure code.
+The framework choose the structure after code segmentation.
 There are two main structures that distribute important and unimportant data in different ways.
-As shown in Figure \ref{fig-framework}, in Even structure, important data occupies 1 block in each node, and in Uneven structure, it occupies 1 data stripe.
-We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.
+As shown in Figure \ref{fig-framework}, in Even structure, important data are distributed uniformly among all data nodes.
+The other structure is Uneven structure, which stores the important data among several nodes dedicatedly.
+%We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.
 
-Since Even structure distributes important data across each node, it guarantees a more balanced load.
-Uneven structure concentrates important data into a stripe, and provides greater reliability for important data.
-A detailed analysis of this will be presented in Section \ref{ReconstructionFT}.
+Since Even structure distributes important data across each node, it guarantees a balanced workload.
+Uneven structure concentrates important data into several dedicated nodes, and provides better reliability based on failure locality.
+\textcolor{red}{[CITE FAILURE MODEL]}.
 
 \subsubsection{Code Generation}\label{code-gen}
-After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
-The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and Structure.
+After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the inputted erasure code.
+The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$, $h$ and the structure type.
 
-We define the naming rules of the output Approximate Code as \textbf{APPR.CodeName} ($k,r,g,h$,Structure), where ``CodeName'' is the name of the input erasure code.
-Paremeter $Structure$ is Even or Uneven and it can be omitted when not focusing on the specific construction.
+We define the output Approximate Code as \textbf{APPR.CodeName ($k,r,g,h$, Structure Type)}, where ``CodeName'' is the name of the input erasure code.
+Structure type is Even or Uneven and the default configuration selects both two structures.
 
-In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
-Approximate Code are designed for $h$ stripes, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
-Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes $N$ in Approximate Code ($k,r,g,h$) is
+According to these parameters, Approximate Code framework divides the data/parity nodes into several local stripes. Each local stripe has $n$ nodes,  
+In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are local parity nodes.
+Assume the ratio of important data is $1/h$, the framework utilizes $h$ local stripes to construct a global stripe, which includes $k*h$ data nodes and $r*h$ local parity nodes in total.
+In a global stripe, $g$ additional nodes are designed for global parities, which are calculated by the important data, so the total number of nodes $N$ in APPR.CodeName ($k,r,g,h$) is
 $N= h*(k+r) + g$.
@@
 Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
-Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually 1 or 2.
+Since the 3DFTs is a typical configuration, we mainly discuss the situation of $r+g=3$ in the rest of our paper, so $r$ is usually $1$ or $2$.%, except section \ref{appr-rsbased}.
 
-\subsection{Approximate RS-based Codes}
-For RS($k,p$), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes.
-Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$.
+\subsection{Approximate RS-based Codes}\label{appr-rsbased}
+The operation of RS($k,m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes.
+Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$.
 RS also supports both two structures.
+We then introduce the construction of Approximate RS Code and Approximate LRC.
 
-For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS($4,3$).
-It is divided into two local parities and one global parities with the Uneven structure and it generate Approximate RS Code ($4,2,1,3$,Uneven).
-As a result, the unimportant data constitutes RS($4,2$), and the important data constitutes RS($4,3$).
+\subsubsection{Approximate RS Code}
+We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}.
+Three horizontal parities are divided into one local and two global parities with the Uneven structure and it generate Approximate RS Code ($4,1,2,3$,Uneven).
+As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS($4,3$).
+
+\subsubsection{Approximate LRC}
 
@@
     \centering
-    \subfigure[XXX]{
+    \subfigure[The generation of APPR.RS Code]{
         \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
@@
 
-    \subfigure[XXX]{
+    \subfigure[The generation of APPR.LRC]{
         \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
@@
 
-\subsection{Approximate XOR-based Codes}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS.
-This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP-Code.
+\subsection{Approximate XOR-based Codes}\label{APPRXOR}
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS-based codes.
+Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.
 
@@
 }
-\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
-\label{fig-ap-5214}
+\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven)}
+\label{fig-appr-star}
 \end{figure}
@@
 \subsubsection{Approximate STAR Code}
-Figure \ref{fig-ap-5214} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
+Figure \ref{fig-appr-star} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
 As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
 Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
-As shown in Figure \ref{fig-ap-5214}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
+As shown in Figure \ref{fig-appr-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
 According to the construction requirements of STAR, each node is divided into 4 blocks.
@@
 \centering
-\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
@@
 
-To compared with Approximate Code, We choose several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code.
+In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
 
-To prove that the lost of unimportant data is acceptable, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario.
+In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.
 
-\subsubsection{Metrics and Methods for Mathematical Analysis: }
-We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as measure.
-We first analyze the impact of the settings of the three parameters on these metrics, then we compare these matrics with several EC methods.
+\subsubsection{Metrics}
+We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.
 
-\subsubsection{Metrics and Methods for Experiments: }
-We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
-Encoding Time is the time for generating all parity nodes and Recovery Time is the time for recovering the lost nodes.
-
-In our experiments of recovery time, we compare Approximate Code with several other codes with the same data nodes $k$.
+We use \textbf{Encoding Time}, \textbf{Recovery Time} and \textbf{Decoding Time} as the metrics in our experiments.
+Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes.
 Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes.
-
+Recovery time consists of computation time, I/O overhead and transmission time
+\subsubsection{Experiments Environment}
 The environment of our experiments are shown in Table \ref{tab-platform}.
@@
 Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes.
-We set $h=4,6$ and node size equal $1GB$ here as two default configurations.
+We set $h=4,6$ and node size equal $1GB$ here as two default configurations.Our experiment can mainly be divided into four cases.
+First, we evaluate the encoding time for several erasure codes.
+We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
 
-Our experiment can mainly be divided into four cases.
-First, we evaluate the encoding time for several erasure codes.
-We then evaluate the recovery time of the scenarios where single, double and triple nodes are corrupted.
-
-\subsubsection{\textcolor{red}{Metrics and Methods for Frame Recovery: }}
 we performed the experiment of video frame recovery with the frame interpolation technique.
@@
 \subsection{Numerical Results of Mathematical Analysis}
-\subsubsection{Storage Overhead}
-We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.
-As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
+In this section, we show the mathematical analysis of Approximate Code and compare it with Star Code, Tip Code, LRC and RS codes.
+\begin{itemize}
+    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
 The ratio of optimization is up to 21.4\% when $h=4, k=4$ and $23.8\%$ when $h=6, k=4$.
 For more tipical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
-
-\subsubsection{Fault Tolerance}
-All the erasure codes we evaluate in this Section are 3DFTs.
-
-\subsubsection{Single Write Performance}
-We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$.
+    \item \textbf{Fault Tolerance:} All the erasure codes we evaluate in this Section are 3DFTs.
+    \item \textbf{Single Write Performance:} We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$.
 As shown in Figure \ref{fig-Sig-Write}, the results shows that APPR.RS Code has lower single write performance than RS Code and STAR Code.
@@
 As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
+\end{itemize}
 
@@
 \subsection{Experimental Results Results and Analysis}
+In this part, we compared the encoding and decoding time of Approximate Code with TIP code, STAR code, RS code and LRC codes, respectively. The code configuration is as follow,
+\begin{itemize}
+    \item \textbf{Approximate Code:} APPR.TIP/STAR ($k,1,2,4$), APPR.
+TIP/STAR ($k,2,1,4$), APPR.
+TIP/STAR ($k,1,2,6$), APPR.TIP/STAR ($k,2,1,6$).
+Since TIP and STAR code have different limits on the number of data nodes, we use these two codes to generate parities in Approximate Code, so that we can cover all the code configurations from $k$ = 5 to $k$ = 17.
+When we compare Approximate Code with STAR, we only choose APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and so do the TIP Code.
+    \item \textbf{RS Code:} RS($k,3$). $k = 5,7,9,11,13$.
+    \item \textbf{LRC Codes:} LRC ($k,4,3$), LRC ($k,6,3$). $k = 5,7,9,11,13$.
+    \item \textbf{TIP Code:} TIP($k,3$). $k = 5,9,11,15,17$.
+    \item \textbf{STAR Code:} STAR($k,3$). $k = 5,7,11,13,17$.
+\end{itemize}
+\subsubsection{Encoding Time}
+The results are shown in Figure \ref{fig-encoding}.
+\begin{itemize}
+    \item STAR Code: Approximate Code encodes faster than STAR code and the rate of optimization is up to $56.3\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
 
-\subsubsection{Encoding Time}
-In this part, we compared the encoding time of Approximate Code with TIP-Code, STAR code, RS code and LRC codes, respectively.
-Since these two codes have different limits on the number of data nodes, we use TIP and STAR code to generate parities in Approximate Code, so that we can cover all the code configurations from $k$ = 5 to $k$ = 17.
-\begin{itemize}
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-encodingSTAR} illustrates that Approximate Code encodes faster than STAR code and the rate of optimization is up to $56.3\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item TIP Code: the effet of TIP code is similar to STAR code. The rate of optimization is up to 58.1\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
 
-    \item APPR.TIP($k,1,2,4$), APPR.TIP($k,2,1,4$), APPR.TIP($k,1,2,6$), APPR.TIP($k,2,1,6$) and TIP($k,3$): the effet of TIP-Code is similar to STAR code.
-From Figure \ref{fig-encodingTIP}, the rate of optimization is up to 58.1\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
+    \item RS Code: We could find out that the AP code encodes largely faster than RS code. The rate of optimization is up to 91.1\% (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
 
-    \item APPR.TIP/STAR ($k,1,2,4$), APPR.
-TIP/STAR ($k,2,1,4$), APPR.
-TIP/STAR ($k,1,2,6$), APPR.TIP/STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-encodingRS}, we could find out that the AP code encodes largely faster than RS code.
-The rate of optimization is up to 91.1\% (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-
-    \item APPR.
-TIP/STAR ($k,1,2,4$), APPR.
-TIP/STAR ($k,2,1,4$), APPR.
-TIP/STAR ($k,1,2,6$), APPR.
-TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC ($k,6,3$): According to Figure \ref{fig-encodingLRC}, we could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
+    \item LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
 The rate of optimization is up to 88.9\% (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
@@
 
-We combined the encoding time of five codes in Figure \ref{fig-encoding-combine} with $k$=5.
+We combined the encoding time of five codes in Figure \ref{fig-BAR} with $k$=5.
 The results show that Approximate Code has the best encoding performance among five codes.
@@
 
-\begin{figure*}[ht]
-\subfigure[APPR.STAR and STAR]{
+\begin{figure}[ht]
+\subfigure{
     \label{fig-encodingSTAR}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Star.eps}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-Star.eps}
 }
-\subfigure[APPR.TIP and TIP]{
+\subfigure{
     \label{fig-encodingTIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-TIP.eps}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-TIP.eps}
 }
-\subfigure[APPR.TIP/STAR and RS]{
+\subfigure{
     \label{fig-encodingRS}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-RS.eps}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-RS.eps}
 }
-\subfigure[APPR.TIP/STAR and LRC]{
+\subfigure{
     \label{fig-encodingLRC}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-LRC.eps}
-}\vspace{-0.5cm}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-LRC.eps}
+}
+\vspace{-0.3cm}
 \caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[ht]
+\subsubsection{Decoding Time under One Failure Node Condition Analysis}
+The results are shown in Figure \ref{fig-decoding-1}.
+\begin{itemize}
+    \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
+    \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
+    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code.
+The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
+    \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
+The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
+\end{itemize}
+
+We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$.
+The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
+The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par
+
+\begin{figure}[ht]
     \subfigure{
         \label{fig-decoding-1-STAR}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Star.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
     }
@@
         \label{fig-decoding-1-TIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-TIP.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
     }
@@
         \label{fig-decoding-1-RS}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-RS.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
     }
@@
         \label{fig-decoding-1-LRC}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-LRC.eps}
-}\vspace{-0.5cm}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
+    }
+    \vspace{-0.3cm}
     \caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
-\end{figure*}
+    \end{figure}
 
-\begin{figure*}[ht]
+\subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
+The results are shown in Figure \ref{fig-decoding-2}.
+\begin{itemize}
+    \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
+The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item LRC Codes:
+    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
+The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
+\end{itemize}
+
+The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-BAR} ($k=5$).
+The results show that RS code and LRC codes has the worst two failure nodes decoding performance while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) perform best among all kinds of codes.
+The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) do the approximate recovery which means they only recover important data at this time.
+
+\begin{figure}[ht]
     \subfigure{
         \label{fig-decoding-2-STAR}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Star.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-Star.eps}
     }
@@
         \label{fig-decoding-2-TIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-TIP.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-TIP.eps}
     }
@@
         \label{fig-decoding-2-RS}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-RS.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-RS.eps}
     }
@@
         \label{fig-decoding-2-LRC}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-LRC.eps}
-}\vspace{-0.5cm}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-LRC.eps}
+    }
+    \vspace{-0.3cm}
     \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
-\end{figure*}
+    \end{figure}
 
-\begin{figure*}[ht]
+\subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
+The results are shown in Figure \ref{fig-decoding-3}.
+\begin{itemize}
+    \item STAR Code: the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
+    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
+The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item LRC Codes:
+    We could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes.
+The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
+\end{itemize}
+
+The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-BAR} ($k$=5).
+The results show that LRC has the worst three failure nodes decoding performance.
+The main reasons are that: On three failure nodes condition, LRC codes decode data through the global parities which has a longer parity chain.
+For example $LRC (44,4,2)$ use 44 nodes to recover the three lost nodes.
+the computational cost of GF operations is also larger than XOR operations.
+On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.
+
+\begin{figure}[ht]
     \subfigure{
         \label{fig-decoding-3-STAR}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Star.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-Star.eps}
     }
@@
         \label{fig-decoding-3-TIP}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-TIP.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-TIP.eps}
     }
@@
         \label{fig-decoding-3-RS}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-RS.eps}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-RS.eps}
     }
@@
         \label{fig-decoding-3-LRC}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-LRC.eps}
-}\vspace{-0.5cm}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-LRC.eps}
+    }
+    \vspace{-0.3cm}
     \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
-\end{figure*}
+    \end{figure}
 
-\subsubsection{Decoding Time under One Failure Node Condition Analysis}
-
-In this section, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under single failure node condition, respectively. $k$ changes from 5 to 17.
-\begin{itemize}
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-1-STAR} illustrates that the decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): Figure \ref{fig-decoding-1-TIP} illustrates that the decoding time of Approximate Code is almost the same as TIP-Code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-1-RS}, we could find out that the Approximate Code decodes largely faster than RS code.
-The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
-    \item APPR.TIP/STAR ($k,1,2,4$), APPR.
-TIP/STAR ($k,2,1,4$), APPR.
-TIP/STAR ($k,1,2,6$), APPR.
-TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC  ($k,6,3$):  According to Figure \ref{fig-decoding-1-LRC}, we could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
-The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
-\end{itemize}
-
-We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-decoding-1-combine} with $k=5$.
-The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
-The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par
-
-\begin{figure*}[ht]
-\subfigure[Encoding Time]{
+\begin{figure*}[!ht]
+    \subfigure{
         \label{fig-encoding-combine}
@@
     }
-\subfigure[Decoding Time in One Node Failure]{
+    \subfigure{
         \label{fig-decoding-1-combine}
@@
     }
-\subfigure[Decoding Time in Two Node Failure]{
+    \subfigure{
         \label{fig-decoding-2-combine}
@@
     }
-\subfigure[Decoding Time in Three Node Failure]{
+    \subfigure{
         \label{fig-decoding-3-combine}
@@
 
-\subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under two failure nodes condition, respectively. $k$ changes from 5 to 17.
-\begin{itemize}
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-2-STAR} illustrates that the rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$),  APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): This condition is similar to STAR code.
-Figure \ref{fig-decoding-2-TIP} illustrates that the rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$),  APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-2-RS}, we could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
-The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-    \item APPR.TIP/STAR ($k,1,2,4$), APPR. TIP/STAR ($k,2,1,4$),  APPR. TIP/STAR ($k,1,2,6$), APPR. TIP/STAR ($k,2,1,6$) and LRC ($k,4,3$), LRC ($k,6,3$):
-    According to Figure \ref{fig-decoding-2-LRC}, we could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
-The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
-\end{itemize}
+\subsubsection{Recovery Time Analysis}
 
-The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-decoding-2-combine} ($k=5$).
-The results show that RS code and LRC codes has the worst two failure nodes decoding performance while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) perform best among all kinds of codes.
-The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) do the approximate recovery which means they only recover important data at this time.
-
-\subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
-In this part, we compared the decoding time of Approximate Code with TIP-Code, Star code, RS code and LRC codes under three failure nodes condition, respectively. $k$ changes from 5 to 17.
-\begin{itemize}
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and STAR ($k,3$): Figure \ref{fig-decoding-3-STAR} illustrates that the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and TIP($k,3$): This condition is similar to STAR code.
-Figure \ref{fig-decoding-3-TIP} illustrates that the rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
-    \item APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and RS($k,3$): From the Figure \ref{fig-decoding-3-RS}, we could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
-The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-    \item APPR.TIP/STAR ($k,1,2,4$), APPR. TIP/STAR ($k,2,1,4$), APPR. TIP/STAR ($k,1,2,6$), APPR. TIP/STAR ($k,2,1,6$)  \\
-    and LRC($k,4,3$), LRC ($k,6,3$):
-    According to Figure \ref{fig-decoding-3-LRC}, we could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes.
-The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
-\end{itemize}
-
-\iffalse
-\begin{figure}[ht]
-\centering
-\subfigure[]{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
-}\hspace{-0.4cm}
-\subfigure[]{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
-}
-\caption{Recovery time Result using Frame Interpolation}
-\label{fig-recoverytime}
-\end{figure}
-\fi
+Figure \ref{fig-recovery} shows the recovery time of Approximate Code and other ECs under two and three failure nodes
+condition.
+We can see that Approximate Code owns the best recovery performance in all ECs.
+The optimization ratio can be up to 97.7\% between APPR.TIP/STAR(5,1,2,6) and LRC(30,2,6).
+The main reason is that Approximate Code only recover important data under multiple failure nodes condition which can significantly reduce computation time, I/O overhead and transmission time.
 
 \begin{figure}[ht]
-\centering
-\includegraphics[width=\linewidth]{photo/experiment/Recovery-2-3.pdf}\label{fig-rec-3}
-\caption{Recovery time Result using Frame Interpolation}
-\label{fig-recoverytime}
+    \subfigure{
+        \label{fig-recovery-2}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
+    }
+    \subfigure{
+        \label{fig-recovery-3}
+        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
+    }
+    \vspace{-0.3cm}
+    \caption{Recovery time comparison in two and three disk between Approximate Code and other ECs}\label{fig-recovery}
     \end{figure}
-
-The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-decoding-3-combine} ($k$=5).
-The results show that LRC has the worst three failure nodes decoding performance.
-The main reasons are that: On three failure nodes condition, LRC codes decode data through the global parities which has a longer parity chain.
-For example $LRC (44,4,2)$ use 44 nodes to recover the three lost nodes.
-the computational cost of GF operations is also larger than XOR operations.
-On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.
 
@@
 
+\subsection{Analysis}
+The improvements of Approximate Code over STAR/TIP/RS/LRC codes are listed in Table \ref{tab-summary}.
+From the table, we discover that Approximate Code can obtain a better encoding/decoding performance in all experiments.
+There are several reasons to achieve these gains.
+First, Approximate Code only provides three parities for important data and this method leads to the improvements of storage efficiency and encoding/decoding performance.
+Secondly Approximate Code uses XOR-Based codes to generate parities which reduce the computation overhead.
+Finally, the parity chain of Approximate Code is shorter than other ECs and takes advantage of transmission time and I/O overhead in cloud storage systems.
+
+\begin{table}[]\footnotesize
+\caption{Summary on various of configurations of APPR.TIP/STAR Code}\label{tab-summary}
+\begin{tabular}{|p{1.5cm}<{\centering}|p{1.2cm}<{\centering}|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Experiment\\ scenario\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Coding\\ Method\end{tabular}} & \multicolumn{5}{c|}{Number of Nodes $k$} \\ \cline{3-7}
+ &  & \multicolumn{1}{c|}{5} & \multicolumn{1}{c|}{7} & \multicolumn{1}{c|}{9} & \multicolumn{1}{c|}{11} & \multicolumn{1}{c|}{13} \\ \hline
+\multirow{4}{*}{Encoding} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
+ & RS (k,3) & 89.7\% & 89.5\% & 88.7\% & 89.2\% & 88.3\% \\ \cline{2-7} 
+ & Star (k,3) & 51.6\% & 51.0\% & 48.4\% & 46.9\% & 51.7\% \\ \cline{2-7} 
+ & LRC (20,2,4) & 87.5\% & 86.8\% & 85.9\% & 86.1\% & 86.0\% \\ \hline
+\multirow{4}{*}{Encoding} & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
+ & RS (k,3) & 91.1\% & 90.7\% & 90.5\% & 90.3\% & 89.5\% \\ \cline{2-7} 
+ & Star (k,3) & 56.3\% & 54.2\% & / & 55.8\% & 55.6\% \\ \cline{2-7} 
+ & LRC (30,2,6) & 88.9\% & 88.0\% & 85.6\% & 85.2\% & 81.6\% \\ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Single Node \\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
+ & RS (k,3) & 79.6\% & 79.3\% & 78.7\% & 78.2\% & 78.0\% \\ \cline{2-7} 
+ & Star (k,3) & 5.5\% & 3.7\% & -2.1\% & -5.3\% & 3.7\% \\ \cline{2-7} 
+ & LRC (20,2,4) & 1.3\% & -0.8\% & -0.9\% & -3.5\% & -9.5\% \\ \cline{2-7} 
+ & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
+ & RS (k,3) & 80.1\% & 79.4\% & 78.7\% & 77.6\% & 76.0\% \\ \cline{2-7} 
+ & Star (k,3) & 5.1\% & -0.5\% & / & 2.1\% & 1.4\% \\ \cline{2-7} 
+ & LRC (30,2,6) & -1.9\% & -5.4\% & -1.9\% & 3.5\% & 5.8\% \\ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Double Node\\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
+ & RS (k,3) & 94.9\% & 94.5\% & 94.6\% & 94.8\% & 94.8\% \\ \cline{2-7} 
+ & Star (k,3) & 76.5\% & 76.0\% & 74.5\% & 73.7\% & 76.0\% \\ \cline{2-7} 
+ & LRC (20,2,4) & 96.0\% & 95.5\% & 94.1\% & 93.0\% & 92.0\% \\ \cline{2-7} 
+ & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
+ & RS (k,3) & 96.9\% & 96.5\% & 96.5\% & 96.5\% & 96.3\% \\ \cline{2-7} 
+ & Star (k,3) & 83.9\% & 83.1\% & / & 83.6\% & 83.5\% \\ \cline{2-7} 
+ & LRC (30,2,6) & 97.2\% & 96.8\% & 96.3\% & 95.5\% & 95.2\% \\ \hline
+\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Triple Node\\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
+ & RS (k,3) & 94.9\% & 94.8\% & 94.7\% & 94.7\% & 94.3\% \\ \cline{2-7} 
+ & Star (k,3) & 75.1\% & 74.9\% & 75.1\% & 75.0\% & 75.1\% \\ \cline{2-7} 
+ & LRC (20,2,4) & 97.5\% & 97.3\% & 97.2\% & 97.3\% & 97.2\% \\ \cline{2-7} 
+ & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
+ & RS (k,3) & 96.7\% & 96.2\% & 96.5\% & 96.4\% & 96.0\% \\ \cline{2-7} 
+ & Star (k,3) & 83.5\% & 81.4\% & / & 83.0\% & 82.6\% \\ \cline{2-7} 
+ & LRC (30,2,6) & 98.3\% & 98.1\% & 98.3\% & 98.3\% & 98.4\% \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[ht]
+\centering
+\subfigure{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
+}\hspace{-0.4cm}
+\subfigure{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
+}
+\caption{Recovery time Result using Frame Interpolation}
+\label{fig-recoverytime}
+\end{figure}
+
 \section{Conclusion}\label{Conclusion}

### 2019-04-23 ApproximateCode.tex
version 4.6

@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 1.25X when double disks fail.
 \end{abstract}
@@
 \subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
-\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
-}
-\hspace{5pt}
-\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
-\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
-}
-\vspace{-3mm}
-\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
-\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
-}
-\hspace{5pt}
-\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
-\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
-}
-\vspace{-3mm}
-\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
-\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
+\includegraphics[height=6cm]{photo/STAR.pdf}\label{fig-star}
 }
@@
 \subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
-\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
+\includegraphics[height=6cm]{photo/TIP.pdf}\label{fig-tip}
 }\vspace{-3mm}
-\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$).
+\caption{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$).
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
-STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
+STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}
 \vspace{-3mm}
@@
 \subsection{Approximate Storage}
-%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources.
-But not all data need high-reliability storage for its backup.
-That is why the concept of approximate storage is introduced.
-Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.
+Approximate storage is an innovative approach for storage devices \cite{zhao2017approximate, sampson2014approximate, guo2016high, jevdjic2017approximate}, which enable applications to store data approximately.
+It can improve the performance, lifetime, or reduce the power consumption of different storage devices.
 
-Use cases for approximate storage range from transient memory to embedded settings and mass storage cloud servers.
-Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance.
-On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints.
-\cite{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.
-
-Approximate storage loosens the requirement of storage reliability by allowing quality loss of some specific data.
-Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks.
-The critical data is still safe because they are stored and sufficiently backed up by expensive and highly reliable storage devices.
-Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.
-
-%However, it is too naive to store data in approximate storage units indiscriminately.
-Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution.
-To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
-Therefore, it is very important to distinguish the importance of video data.
+Specifically, for video applications, there are several approximate storage methods \cite{guo2016high, jevdjic2017approximate} for bit-level reliability in progressively encoded multimedia data.
+\cite{guo2016high} identifies the relative importance of the encoded bits on the image quality and apply different levels of error correction.
+\cite{jevdjic2017approximate} shows how reliability of video storage can be traded for density and achieves the optimal quality/density points by tracking visual and metadata dependencies within the encoded bit stream.
 
@@
 Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
-\begin{tabular}{|p{1.2cm}<{\centering}|p{2.1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|}
+\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
 \hline
-Layer & Schemes & Storage Overhead & Fault Tolerance & Computing Overhead \\ \hline
-\begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} & Data Compression & low & / & high \\ \hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}} & RS-based EC for 3DFTs & high & high & high \\ \cline{2-5} 
- & XOR-based EC for 3DFTs & high & high & low \\ \cline{2-5} 
- & RAID-6 & low & low & low \\ \cline{2-5} 
- & RAID-5 & medium & medium & low \\ \cline{2-5} 
- & Approximate Storage & very low & very low & low \\ \cline{2-5} 
- & Approximate Code & low & high & low \\ \hline
+Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
+Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
+RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
+XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
+RAID-6 & low & low & low & \\ \cline{1-4} 
+RAID-5 & medium & medium & low & \\ \cline{1-4} 
+Approximate Storage & very low & very low & low & \\ \cline{1-4} 
+Approximate Code & low & high & low & \\ \hline
 \end{tabular}
@@
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
+LRC($k,l,r$) & $1+(l+r)/k$ & $r+1$ & $r+2$ \\ \hline
 STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
@@
 
-\subsubsection{Decoding Time under One Failure Node Condition Analysis}
+\subsubsection{Decoding Time under Single Node Failure Condition Analysis}
 The results are shown in Figure \ref{fig-decoding-1}.
@@
     \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
+    \caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}
     \end{figure}
 
-\subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
+\subsubsection{Decoding Time under Double Node Failure Condition Analysis}
 The results are shown in Figure \ref{fig-decoding-2}.
@@
     \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
+    \caption{Decoding Time Comparison in Double Node Failure between Approximate Code and other method}\label{fig-decoding-2}
     \end{figure}
 
-\subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
+\subsubsection{Decoding Time under Triple Node Failure Condition Analysis}
 The results are shown in Figure \ref{fig-decoding-3}.
@@
     \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
+    \caption{Decoding Time Comparison in Triple Node Failure between Approximate Code and other method}\label{fig-decoding-3}
     \end{figure}
@@
     }
-    \caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
+    \caption{Comparison of several matrics between different methods when the number of data nodes is 5}\label{fig-BAR}
     \end{figure*}
@@
     \vspace{-0.3cm}
-    \caption{Recovery time comparison in two and three disk between Approximate Code and other ECs}\label{fig-recovery}
+    \caption{Recovery time comparison in double and triple node failures between Approximate Code and other ECs}\label{fig-recovery}
     \end{figure}

### 2019-04-23 ApproximateCode-4-23-1557-wu.tex
version Final

--- 2019-04-23 ApproximateCode.tex
@@
 \subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
-\includegraphics[height=6cm]{photo/STAR.pdf}\label{fig-star}
+\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
+}
+\hspace{5pt}
+\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
+\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
+}
+\vspace{-3mm}
+\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
+\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
+}
+\hspace{5pt}
+\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
+\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
+}
+\vspace{-3mm}
+\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
+\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
 }
@@
 \subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
-\includegraphics[height=6cm]{photo/TIP.pdf}\label{fig-tip}
+\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
 }\vspace{-3mm}
-\caption{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$).
+\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$).
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
-STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}
+STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
 \vspace{-3mm}
@@
 Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
-\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
+\begin{tabular}{|p{1.2cm}<{\centering}|p{2.1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|}
 \hline
-Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
-Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
-RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
-XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
-RAID-6 & low & low & low & \\ \cline{1-4} 
-RAID-5 & medium & medium & low & \\ \cline{1-4} 
-Approximate Storage & very low & very low & low & \\ \cline{1-4} 
-Approximate Code & low & high & low & \\ \hline
+Layer & Schemes & Storage Overhead & Fault Tolerance & Computing Overhead \\ \hline
+\begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} & Data Compression & low & / & high \\ \hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}} & RS-based EC for 3DFTs & high & high & high \\ \cline{2-5} 
+ & XOR-based EC for 3DFTs & high & high & low \\ \cline{2-5} 
+ & RAID-6 & low & low & low \\ \cline{2-5} 
+ & RAID-5 & medium & medium & low \\ \cline{2-5} 
+ & Approximate Storage & very low & very low & low \\ \cline{2-5} 
+ & Approximate Code & low & high & low \\ \hline
 \end{tabular}
@@
 \centering
-\includegraphics[width=0.95\linewidth]{photo/Framework-v3.pdf}
+\includegraphics[width=0.8\linewidth]{photo/Framework-v3.pdf}
 \caption{The framework of Approximate Code}
@@
 \subsection{Approximate RS-based Codes}\label{appr-rsbased}
-The operation of RS($k,m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes.
+RS-based codes are based the calculation of Galois Field (GF), which are designed for arbitrary number of data nodes.
+Therefore, in the code segmentation step of  Approximate Code framework, we divide the RS-based codes into two parts, $r$ parties and $g$ parities.
+For structure selection step, the important data can be distributed in both two structures.
+Here we take RS and LRC codes to show how Approximate Code framework work.
+
+%The operation of RS($k, m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes.
 Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$.
@@
 We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}.
-Three horizontal parities are divided into one local and two global parities with the Uneven structure and it generate Approximate RS Code ($4,1,2,3$,Uneven).
-As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS($4,3$).
+Three horizontal parities are divided into one local and two global parities with the Uneven structure, and finally we generate APPR.RS ($4,1,2,3$,Uneven).
+As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS ($4,3$).
+
+\begin{figure}
+    \centering
+    \subfigure[The generation of APPR.RS ($4,1,2,3$,Uneven) ]{
+        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+    }
+
+    \subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
+        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
+    }
+    \caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \subfigure[The generation of APPR.RS Code]{
-        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
-    }
-
-    \subfigure[The generation of APPR.LRC]{
-        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
-    }
-    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
-\end{figure}
+We take LRC ($4, 3, 1$) \cite{LRC} as an example (shown in Figure \ref{fig-LRC-2}), which means that three local parities and one global parities are generated initially.
+Similar to the construction of RS code, two local parities and two global parities are reorganized in the code segmentation step.
+At last we get the APPR.LRC ($4, 2, 2, 3$, Even).
 
 \subsection{Approximate XOR-based Codes}\label{APPRXOR}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS-based codes.
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding/decoding speed than RS-based codes.
 Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.
+
+\subsubsection{Approximate STAR Code}
+
+As introduced in Section \ref{existEC}, STAR Code \cite{STAR} is a typical XOR-based erasure code for 3DFTs.
+STAR is a direct extension of EVENODD\cite{EVENODD} (RAID-6 code) by adding the anti-diagonal parities.
+Figure \ref{fig-appr-star} shows the construction of APPR.STAR ($5,2,1,4$,Uneven).
+In this case, the horizontal and diagonal parities are regarded as local parities,  the anti-diagonal parities are defined as global parities in Approximate Code framework.
+
+Briefly, according to the construction of APPR.STAR ($5,2,1,4$, Uneven), the important data are encoded by STAR code while the unimportant data are generated by EVENODD code.
+It is clear that the important/unimportant data can tolerate triple/double nodes fail, respectively.
 
@@
 \centering
-\subfigure[Structure selection of APPR.STAR Code]{
+\subfigure[Structure selection.]{
     \label{fig-ap-tip-str}
@@
 
-\subfigure[Generation process]{
+\subfigure[Generation of APPR.STAR.]{
     \label{fig-ap-tip-GEN}
@@
 }
-\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven)}
+\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}
 \label{fig-appr-star}
@@
 
-\subsubsection{Approximate STAR Code}
-Figure \ref{fig-appr-star} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
-As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
-Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
-As shown in Figure \ref{fig-appr-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
-According to the construction requirements of STAR, each node is divided into 4 blocks.
-
-Briefly, APPR.STAR($5,2,1,4$,Uneven) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD.
-It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
-
-\subsubsection{Approximate TIP-Code}
-
 \begin{figure}[ht]
 \centering
-\subfigure[Structure selection of APPR.TIP-Code]{
+\subfigure[Structure selection.]{
     \label{fig-ap-tip-str}
@@
 \hspace{2pt}
-\subfigure[Generation of local parities]{
+\subfigure[Local parity generation.]{
     \label{fig-ap-tip-lP}
@@
 
-\subfigure[Generation of global parities]{
+\subfigure[Global parity generation.]{
     \label{fig-ap-tip-GP}
@@
 }
-\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}
+\caption{Construction of APPR.TIP ($5,1,2,6$,Even) via Approximate Code framework.}
 \label{fig-ap-TIP}
@@
 
-We then introduce the generation of APPR.TIP($5,1,2,6$,Even).
+\subsubsection{Approximate TIP-Code}
 
-In the code segmentation phase, we split TIP-Code into horizontal, diagonal and anti-diagonal parity.
-The important data is arranged in Even structure.
-However, since the parity block of the TIP is distributed over a series of nodes, the code generation process is different from that of the STAR.
+We use the generation of APPR.TIP ($5,1,2,6$,Even) as an example (shown in Figure \ref{fig-ap-TIP}).
+In the code segmentation phase, we split TIP-Code into two parts, the horizontal parity part, and the diagonal/anti-diagonal parities part.
+The important data are arranged in Even structure.
+Since the parities of the TIP-Code are distributed among several nodes, the code generation process is different from APPR.STAR.
 
-We first generate local parity nodes by the horizontal parity for the important and unimportant data in each node. Then, we arrange the important data blocks as the type of Figure \ref{fig-tip-1}.
-We use diagonal and anti-diagonal parity to encode the important data and define the last 2 node (Node 5 and 6) as the global parity nodes.
+We first generate local parity nodes by the horizontal parities for all data.
+Then, we reorganize the important data to construct new global stripes, where the diagonal and anti-diagonal parities are used to encode the important data.
+The number of global stripes are based on the ratio of important data ($1/h$).
+Assume $h=6$, which means that the framework utilizes the important data from six local stripes to generate one global stripe.
 
-As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 stripes, where important data accounting for 1/6 of each node.
-All data nodes generate 6 local parity nodes.
-Important data blocks are rearranged to fit the parity form of TIP-Code and generate two global parity nodes.
+\subsection{Reconstruction and Capability of Fault Tolerance}\label{ReconstructionFT}
 
-\subsection{Reconstruction Process and Fault Tolerance}\label{ReconstructionFT}
-When $r$ or less nodes fail, all the data can be reconstructed by local parities.
-When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.
+Existing work \cite{LRC} has demonstrated that when we have $r$ local parities and $g$ global parities, the capability of fault tolerance is at least $r+g$ in typical.
+Thus the reconstruction (less than $r+g$ nodes fail) of the framework are classified into two cases,
 
-However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$.
+(1) When $r$ or less nodes fail, all data (both important and unimportant data) are reconstructed via local parities.
+
+(2) When $r+g$ or less nodes fail, the important data are reconstructed via both local and global parities.
+
+Under some special cases, for important/unimportant data, exceeding $r+g$/$r+1$ failure nodes is recoverable as well. 
+Here we only consider two situations: $r+1$ and $r+g+1$.
+Assume the recovery probabilities of these two cases are $P_{I}$/$P_{U}$, respectively.
+Because in this paper we focus on the 3DFTs, $r+g$ is set to 3.
+
 The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
@@
 
-We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
-Approximate Codes based on different structures also have different fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structure respectively.
+%We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
+Approximate Codes based on different structures also have different capabilities of fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structures in the following subsection.
 
 \subsubsection{Lost $r+1$ nodes}
-Under Even structure, the unimportant data nodes are recoverable as long as the node loss per stripe does not exceed $r$ and the global parity nodes do not need to be considered.
-There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases will result in unrecoverable of data.
+Under Even structure, the unimportant data nodes are recoverable as long as the node losses don't exceed $r$.
+There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases result in unrecoverable data.
 
@@
 
-\subsubsection{Lost $4$ nodes}
-The number of all 4-node lost cases is $\binom{N}{4}$.
-We calculate the total number of cases in which all important data may be lost based on the different losses of the global parity nodes. The results are as follows:
+\subsubsection{Lost $r+g+1$ nodes ($4$ nodes)}
+The number of all quad nodes fail cases is $\binom{N}{4}$.
+We calculate the total number of cases on losing the important data, which are based on the different losses of the global parity nodes. The results are as follows,
 \begin{align}
@@
 
-According to the equations above, in Approximate RS ($3,1,2,3$, Even), $80.21\%$ 2-node failure cases are recoverable for unimportant data nodes, and $95.50\%$ 4-node failure is recoverable for important data nodes.
-In Approximate RS ($3,1,2,3$, Uneven), $P_U=86.81\%$ $P_{I}=98.50\%$.
+According to the above equations, for APPR.RS ($3,1,2,3$, Even), $80.21\%$ double failures cases are recoverable for unimportant data, and $95.50\%$ quad failures is recoverable for important data nodes.
+For APRR.RS ($3,1,2,3$, Uneven), $P_U=86.81\%$, $P_{I}=98.50\%$.
 
@@
 
-We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-properties}.
+We analyze the nature of the Approximate Code from the following aspects, and summarize the results shown in Table \ref{tab-properties}.
 \begin{itemize}
-    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies.
-This property is more pronounced for data with a smaller proportion of important data.
-    \item Optimal Update Complexity: When one node is updated, Approximate RS Code only needs to write $r$ local parity nodes and only $g/h$ global parity nodes on average besides the write of data node.
-    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
-    \item Flexibility. The implementation of the Approximate Code can be based on any erasure codes in 3DFTs.
+    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies for important/unimportant data. 
+    \item Low Update Complexity: When one node is updated, APPR. CodeName needs to write $r$ local parity nodes and only $g/h$ global parity nodes, which are less than typical erasure codes.
+    \item High reliability for important data. important data can be recovered in all triple nodes failure and most quad nodes failure environment.
+    \item High Flexibility. Approximate Code framework can be applied with any erasure codes in 3DFTs, and various parameters can be set.
 \end{itemize}
@@
 \centering
-\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance among typical erasure codes and their approximate codes.}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
@@
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
-LRC($k,l,r$) & $1+(l+r)/k$ & $r+1$ & $r+2$ \\ \hline
 STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
@@
 
-\subsection{Implementation}\label{Implementation}
+\subsection{Implementation in Storage Systems}\label{Implementation}
 \begin{figure}[htb]
@@
 
-Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary.
-We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.
+Due to classification of important/unimportant data, the implementation of Approximate Code in storage systems includes three modules (shown in Figure \ref{fig-implementation}), data identification and distribution, approximate code and video recovery.
 
-\subsubsection{Data Segmentation and Distribution module}
-The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data.
+\subsubsection{Data Identification and Distribution Module}
+This module splits the video stream files into multiple data segments, and automatically identifies the important data.
 A natural approach is to follow the GOP segmentation.
-According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data.
-(unimportant part).
+According to Section \ref{video storage}, the GOP of the encoded video starts with an I frame, and the remaining data in the GOP depends on it for decoding.
+Therefore, we define the I frames as the important data, the reminder are unimportant data.
 %The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data.
-This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
+%This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
 
-\subsubsection{Approximate Code module}
-The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance.
-For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
+\subsubsection{Approximate Code Module}
+The Approximate Code module is responsible for encoding/decoding the video data and completely recovering the data.
+For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module.
 %Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
-\subsubsection{Data Fuzzification and Video Recovery}
-In the approximate recovery mode, the remaining data and important data are transferred to this module.
-Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.
+\subsubsection{Video Recovery Module}
+For unrecovered data, the video recovery module using advanced video recovery strategies illustrated in Section \label{video storage}.
+Generally, the lost frames are recovered using the interpolation algorithms, where the corrupted frames are processed into fuzzy images and approximately recovered by superpixel techniques.
 

### 2019-04-23 ApproximateCode.tex
version Final

@@
 \usepackage{array}
+\usepackage{fancyhdr}
 
@@
 \affiliation{%
-    \institution{Shanghai Jiao Tong University}
-    \institution{The Alibaba Group}
+    \institution{Shanghai Jiao Tong University, The Alibaba Group}
 }
@@
 Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc.
-Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
-Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems.
+Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability and low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice.
+Therefore, how to minimize the storage cost of video data in 3DFTs is a challenge for cloud storage systems.
 Although there are several solutions like approximate storage technique, they cannot guarantee low storage cost and high data reliability concurrently.
@@
 The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance.
-On one hand, for important data, Approximate Code provides triple parities to provide high reliability.
+On one hand, for important data, Approximate Code provides triple parities to ensure high reliability.
 On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process.
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 1.25X when double disks fail.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double disks fail.
 \end{abstract}
@@
 
+\thispagestyle{fancy} 
+\pagestyle{fancy}
+\cfoot{\thepage}
+
 \section{Introduction}
@@
 Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}.
-RS-based codes are encoded according the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost.
-XOR-based codes simplify the computation, but they suffer other issues like scalability.
-\textcolor{red}{[CITE GSR SDM]}
+RS-based codes are encoded based on the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost.
+XOR-based codes simplify the computation, but they suffer other issues like scalability \cite{wu2012sdm, jiang2016bdr}.
 
@@
 Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
-The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
+The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance is sacrificed.
 Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.}
@@
 
-To address the above challenge, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for tiered video data storage in cloud systems.
+To address the challenge, in this paper, we propose Approximate Code, which is an erasure coding framework to provide a comprehensive solution for tiered video data storage in cloud systems.
 The key idea of Approximate Code is treating the important/unimportant data in different ways.
@@
 \item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
-\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
-\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves a small number of parities, low storage cost, high single write performance, and fast data recovery under various failure scenarios.
+\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, LRC, STAR Code, TIP-Code, etc.
+\item We conduct several quantitative analysis and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves a small number of parities, low storage cost, high single write performance, and fast data recovery under various failure scenarios.
 \end{enumerate}
@@
 The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation.
-In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail.
+In Section \ref{ApCode}, the design of Approximate Code Framework will be illustrated in detail.
 %Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
@@
 \centering
-\begin{tabular}{|p{0.7cm}<{\centering}|p{6.5cm}|}
+\begin{tabular}{|p{0.8cm}<{\centering}|p{6.4cm}|}
 \hline
 Symbols & \multicolumn{1}{c|}{Description} \\ \hline \hline
-$k$ & the number of data nodes in a local stripe \\ \hline
-$r$ & the number of local parity nodes in a local stripe \\ \hline
+$k$ & the number of data nodes (in a local stripe) \\ \hline
+$r$ & the number of parity nodes (in a local stripe) \\ \hline
 $n$ & the number of all data and parity nodes in a local stripe. ($n=k+r$) \\ \hline
@@
 $g$ & the number of global parity nodes \\ \hline
+$p$ & a prime number \\ \hline
 $N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
@@
 A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames, as shown in Figure \ref{H264-IPB}.
-Within each GOP, the I frame is the most significant because all other frames rely on if for recovery. P frames are the second important, and B frames have the least value.
-Based on this feature, a special program can be designed to distinguish the importance of video frames.
+Within each GOP, the I frame is the most significant because all other frames rely on it for recovery. P frames are the second important, and B frames have the least value.
+Based on this feature, a special program can be designed to get the important video frames.
 
@@
 \includegraphics[width=0.4\textwidth]{photo/H264_IPB.pdf}
-\vspace{-3mm}
 \caption{A sample of GOPs in H.264}
-\vspace{-3mm}
 \label{H264-IPB}
@@
 
-Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.
+%Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.
 This is a technique that can model natural motion within a video, and generate frames according to the model.
@@
 }
-
 \subfigure[LRC Code for arbitrary storage nodes ($k=4, r=2, g=2$), where 4 nodes are divided into 2 local groups and each of them has a local parity.The figure shows the encoding of local and global parities.
@@
 STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
-In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.
+In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which leads to a long parity chain.
 
@@
 \centering
-\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
-\includegraphics[height=6cm]{photo/STAR.pdf}\label{fig-star}
+\subfigure[\textbf{STAR Code:} For example, in the diagonal parity $S = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S$.]{
+\includegraphics[height=6.3cm, width = 3.8cm]{photo/STAR.pdf}\label{fig-star}
 }
 \hspace{5pt}
-\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
-\includegraphics[height=6cm]{photo/TIP.pdf}\label{fig-tip}
+\subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$]{
+\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-tip}
 }\vspace{-3mm}
-\caption{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$).
+\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$).
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
-STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}
+STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$.}}
 \vspace{-3mm}
@@
 \subsection{Approximate Storage}
-Approximate storage is an innovative approach for storage devices \cite{zhao2017approximate, sampson2014approximate, guo2016high, jevdjic2017approximate}, which enable applications to store data approximately.
+Approximate storage is an innovative approach for storage devices \cite{zhao2017approximate, sampson2014approximate, guo2016high, jevdjic2017approximate}, which enables applications to store data approximately.
 It can improve the performance, lifetime, or reduce the power consumption of different storage devices.
@@
 Specifically, for video applications, there are several approximate storage methods \cite{guo2016high, jevdjic2017approximate} for bit-level reliability in progressively encoded multimedia data.
-\cite{guo2016high} identifies the relative importance of the encoded bits on the image quality and apply different levels of error correction.
+\cite{guo2016high} identifies the relative importance of the encoded bits on the image quality and applys different levels of error correction.
 \cite{jevdjic2017approximate} shows how reliability of video storage can be traded for density and achieves the optimal quality/density points by tracking visual and metadata dependencies within the encoded bit stream.
 
-\begin{table}[ht]\footnotesize
+\begin{table}[ht]\small
 \centering
@@
 \end{tabular}
+\vspace{-5mm}
 \end{table}
@@
 \subsection{Our Motivation}
-We summarize various methods to reduce storage cost for video files in Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance.
-Although approximate storage achieves low cost, its reliability cannot be satisfied in cloud environment.
+We summarize various methods to reduce storage cost for video files in Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifices fault tolerance.
+Although approximate storage achieves low cost, its reliability cannot satisfy cloud environment.
 Application layer methods such as compression algorithms have high computational overhead and need to be used together with erasure codes to ensure reliability.
-Therefore, the existing solution cannot guarantee high reliability and low overhead at the same time of video storage.
+Therefore, the existing solutions cannot guarantee high reliability and low overhead at the same time of video storage.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{photo/Framework-v3.pdf}
-\caption{The framework of Approximate Code}
-\label{fig-framework}
+\includegraphics[width=0.8\linewidth]{photo/Framework-v3.pdf}
+\caption{The framework of Approximate Code}\label{fig-framework}
+\vspace{-2mm}
 \end{figure*}
@@
 \subsection{Overview of Approximate Code Framework}
-The Approximate Code framework contains four main steps, code input, code segementation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
+The Approximate Code framework contains four main steps, code input, code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
 
@@
 \subsubsection{Structure Selection}
-The framework choose the structure after code segmentation.
+The framework chooses the structure after code segmentation.
 There are two main structures that distribute important and unimportant data in different ways.
@@
 Since Even structure distributes important data across each node, it guarantees a balanced workload.
-Uneven structure concentrates important data into several dedicated nodes, and provides better reliability based on failure locality.
-\textcolor{red}{[CITE FAILURE MODEL]}.
+Uneven structure aggregates important data into several dedicated nodes, and provides better reliability (illustrated in Section \ref{ReconstructionFT}).
 
 \subsubsection{Code Generation}\label{code-gen}
-After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the inputted erasure code.
+After the code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the inputted erasure code.
 The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$, $h$ and the structure type.
@@
 \subsection{Approximate RS-based Codes}\label{appr-rsbased}
-The operation of RS($k,m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes.
-Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$.
-RS also supports both two structures.
-We then introduce the construction of Approximate RS Code and Approximate LRC.
+RS-based codes are based the calculation of Galois Field (GF), which are designed for arbitrary number of data nodes.
+Therefore, in the code segmentation step of  Approximate Code framework, we divide the RS-based codes into two parts, $r$ parties and $g$ parities.
+For structure selection step, the important data can be distributed in both two structures.
+Here we take RS and LRC codes to show how Approximate Code framework work.
 
@@
 We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}.
-Three horizontal parities are divided into one local and two global parities with the Uneven structure and it generate Approximate RS Code ($4,1,2,3$,Uneven).
-As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS($4,3$).
+Three horizontal parities are divided into one local and two global parities with the Uneven structure, and finally we generate APPR.RS ($4,1,2,3$,Uneven).
+As a result, the unimportant data and their corresponding parities constitute a RS ($4,1$) array, and the important data and their corresponding parities form a RS ($4,3$).
+
+\begin{figure}
+\centering
+\subfigure[The generation of APPR.RS ($4,1,2,3$,Uneven) ]{
+    \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+}
+
+\subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
+    \includegraphics[width=0.75\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
+}
+\caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
+\vspace{-3mm}
+\end{figure}
 
@@
 
-\begin{figure}
+We take LRC ($4, 3, 1$) \cite{LRC} as an example (shown in Figure \ref{fig-LRC-2}), which means that three local parities and one global parities are generated initially.
+Similar to the construction of RS code, two local parities and two global parities are reorganized in the code segmentation step.
+At last we get the APPR.LRC ($4, 2, 2, 3$, Even).
+
+\subsection{Approximate XOR-based Codes}\label{APPRXOR}
+Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding/decoding speed than RS-based codes.
+Here we introduce two typical constructions of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.
+
+\subsubsection{Approximate STAR Code}
+
+As introduced in Section \ref{existEC}, STAR Code \cite{STAR} is a typical XOR-based erasure code for 3DFTs.
+STAR is a direct extension of EVENODD\cite{EVENODD} (RAID-6 code) by adding the anti-diagonal parities.
+Figure \ref{fig-appr-star} shows the construction of APPR.STAR ($5,2,1,4$,Uneven).
+In this case, the horizontal and diagonal parities are regarded as local parities,  the anti-diagonal parities are defined as global parities in Approximate Code framework.
+
+Briefly, according to the construction of APPR.STAR ($5,2,1,4$, Uneven), the important data are encoded by STAR code while the unimportant data are generated by EVENODD code.
+It is clear that the important/unimportant data can tolerate triple/double nodes fail, respectively.
+
+\begin{figure}[ht]
+\vspace{-3mm}
 \centering
-    \subfigure[The generation of APPR.RS Code]{
-        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+\subfigure[Structure selection.]{
+    \label{fig-ap-tip-str}
+    \includegraphics[width = 0.45\linewidth]{photo/APPR-STAR-STR.pdf}
 }
 
-    \subfigure[The generation of APPR.LRC]{
-        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
-    }
-    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
+\subfigure[Generation of APPR.STAR.]{
+    \label{fig-ap-tip-GEN}
+    \includegraphics[width = 0.95\linewidth]{photo/APPR-STAR-GEN.pdf}
+}\vspace{-3mm}
+\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}\label{fig-appr-star}
+\vspace{-3mm}
 \end{figure}
-
-\subsection{Approximate XOR-based Codes}\label{APPRXOR}
-Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS-based codes.
-Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.
-
-\begin{figure}[ht]
-\centering
-\subfigure[Structure selection of APPR.STAR Code]{
-    \label{fig-ap-tip-str}
-    \includegraphics[width = 0.5\linewidth]{photo/APPR-STAR-STR.pdf}
-}
-
-\subfigure[Generation process]{
-    \label{fig-ap-tip-GEN}
-    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
-}
-\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven)}
-\label{fig-appr-star}
-\end{figure}
-
-\subsubsection{Approximate STAR Code}
-Figure \ref{fig-appr-star} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
-As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
-Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD.
-As shown in Figure \ref{fig-appr-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
-According to the construction requirements of STAR, each node is divided into 4 blocks.
-
-Briefly, APPR.STAR($5,2,1,4$,Uneven) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD.
-It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.
-
-\subsubsection{Approximate TIP-Code}
 
@@
     \label{fig-ap-tip-GP}
-    \includegraphics[width = 0.8\linewidth]{photo/APPR-TIP-GL-v2.pdf}
+    \includegraphics[width = 0.9\linewidth]{photo/APPR-TIP-GL-v2.pdf}
 }
-\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}
-\label{fig-ap-TIP}
+\vspace{-3mm}
+\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}\label{fig-ap-TIP}
+\vspace{-3mm}
 \end{figure}
 
-We then introduce the generation of APPR.TIP($5,1,2,6$,Even).
+\subsubsection{Approximate TIP-Code}
 
-In the code segmentation phase, we split TIP-Code into horizontal, diagonal and anti-diagonal parity.
-The important data is arranged in Even structure.
-However, since the parity block of the TIP is distributed over a series of nodes, the code generation process is different from that of the STAR.
+We use the generation of APPR.TIP ($5,1,2,6$,Even) as an example (shown in Figure \ref{fig-ap-TIP}).
+In the code segmentation phase, we split TIP-Code into two parts, the horizontal parity part, and the diagonal/anti-diagonal parities part.
+The important data are arranged in Even structure.
+Since the parities of the TIP-Code are distributed among several nodes, the code generation process is different from APPR.STAR.
 
-We first generate local parity nodes by the horizontal parity for the important and unimportant data in each node. Then, we arrange the important data blocks as the type of Figure \ref{fig-tip-1}.
-We use diagonal and anti-diagonal parity to encode the important data and define the last 2 node (Node 5 and 6) as the global parity nodes.
-
-As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 stripes, where important data accounting for 1/6 of each node.
-All data nodes generate 6 local parity nodes.
-Important data blocks are rearranged to fit the parity form of TIP-Code and generate two global parity nodes.
+We first generate local parity nodes by the horizontal parities for all data.
+Then, we reorganize the important data to construct new global stripes, where the diagonal and anti-diagonal parities are used to encode the important data.
+The number of global stripes are based on the ratio of important data ($1/h$).
+Assume $h=6$, which means that the framework utilizes the important data from six local stripes to generate one global stripe.
 
 \subsection{Reconstruction Process and Fault Tolerance}\label{ReconstructionFT}
-When $r$ or less nodes fail, all the data can be reconstructed by local parities.
-When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.
+Existing work \cite{LRC} has demonstrated that when we have $r$ local parities and $g$ global parities, the capability of fault tolerance is at least $r+g$ in typical.
+Thus the reconstruction (less than $r+g$ nodes fail) of the framework are classified into two cases,
 
-However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$.
+(1) When $r$ or less nodes fail, all data (both important and unimportant data) are reconstructed via local parities.
+
+(2) When $r+g$ or less nodes fail, the important data are reconstructed via both local and global parities.
+
+Under some special cases, for important/unimportant data, exceeding $r+g$/$r+1$ failure nodes is recoverable as well. 
+Here we only consider two situations: $r+1$ and $r+g+1$.
+Assume the recovery probabilities of these two cases are $P_{I}$/$P_{U}$, respectively.
+Because in this paper we focus on the 3DFTs, $r+g$ is set to 3.
+
 The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
@@
 
-We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-properties}.
+We analyze the nature of the Approximate Code from the following aspects, and summarize the results shown in Table \ref{tab-properties}.
 \begin{itemize}
-    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies.
-This property is more pronounced for data with a smaller proportion of important data.
-    \item Optimal Update Complexity: When one node is updated, Approximate RS Code only needs to write $r$ local parity nodes and only $g/h$ global parity nodes on average besides the write of data node.
-    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
-    \item Flexibility. The implementation of the Approximate Code can be based on any erasure codes in 3DFTs.
+    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies for important/unimportant data. 
+    \item Low Update Complexity: When one node is updated, APPR. CodeName needs to write $r$ local parity nodes and only $g/h$ global parity nodes, which are less than typical erasure codes.
+    \item High reliability for important data. important data can be recovered in all triple nodes failure and most quad nodes failure environment.
+    \item High Flexibility. Approximate Code framework can be applied with any erasure codes in 3DFTs, and various parameters can be set.
 \end{itemize}
 
-\begin{table}[htb]
+\begin{table}[htb]\small
 \centering
-\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance among typical erasure codes and their approximate codes.}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
 \hline
-EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
+Erasure Coding & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault Tolerance\\ Capability\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg.
+Single Write\\ Overhead \end{tabular} \\ \hline
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
-LRC($k,l,r$) & $1+(l+r)/k$ & $r+1$ & $r+2$ \\ \hline
+LRC($k,l,r$) & $1+\frac{l+r}{k}$ & $r+1$ & $r+2$ \\ \hline
 STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
@@
 
-\subsection{Implementation}\label{Implementation}
+\subsection{Implementation in Storage Systems}\label{Implementation}
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.8\linewidth]{photo/implementation-V2.pdf}
+\includegraphics[width=0.85\linewidth]{photo/implementation-V2.pdf}
+\vspace{-3mm}
 \caption{Overview of Approximate Storage Layer}
+\vspace{-3mm}
 \label{fig-implementation}
@@
 \subsection{Evaluation Methodology}
-The experiment is divided into two parts: the first part evaluates the performance of the Approximate Code code, and the second part evaluates the impact of the loss of the unimportant data on the video files.
+The experiment is divided into two parts: the first part evaluates the performance of the Approximate Code, and the second part evaluates the impact of the loss of the unimportant data on the video files.
 
-In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
+In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
@@
 \subsubsection{Metrics}
-We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.
+We use the \textbf{Storage Efficiency} and \textbf{Single Write (update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.
 
-We use \textbf{Encoding Time}, \textbf{Recovery Time} and \textbf{Decoding Time} as the metrics in our experiments.
+We use \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
 Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes.
 Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes.
-Recovery time consists of computation time, I/O overhead and transmission time
+Recovery time consists of computation time, I/O overhead and transmission time.
 \subsubsection{Experiments Environment}
@@
 We set a Hadoop system with one NameNode and $h$ DataNodes.
-Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes.
-We set $h=4,6$ and node size equal $1GB$ here as two default configurations.Our experiment can mainly be divided into four cases.
+Each DataNodes storage the data of one stripe of Approximate Code and the global parities are distributed at each DataNodes.
+We set $h=4,6$ and node size equal $1GB$ here as two default configurations.
+Our experiment can mainly be divided into four cases.
 First, we evaluate the encoding time for several erasure codes.
-We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
+Then we evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
 
@@
 We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data.
-The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio PSNR .
+The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).
 
-\begin{table}[!ht]
+\begin{table}[!ht]\small
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
+\vspace{3mm}
 \caption{Details of Our Evaluation Platform}\label{tab-platform}
+\vspace{-10mm}
 \end{table}
@@
 \subsection{Numerical Results of Mathematical Analysis}
-In this section, we show the mathematical analysis of Approximate Code and compare it with Star Code, Tip Code, LRC and RS codes.
+In this section, we show the mathematical analysis of Approximate Code and compare it with STAR Code, TIP-Code, LRC and RS codes.
 \begin{itemize}
-    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
+    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.
+As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
 The ratio of optimization is up to 21.4\% when $h=4, k=4$ and $23.8\%$ when $h=6, k=4$.
-For more tipical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
-    \item \textbf{Fault Tolerance:} All the erasure codes we evaluate in this Section are 3DFTs.
+For more typical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
+    \item \textbf{Fault Tolerance:} The fault tolerance of Approximate Code is the same as the inputted erasure codes. All the erasure codes we evaluate in this Section are 3DFTs.
     \item \textbf{Single Write Performance:} We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$.
@@
 
-\subsection{Experimental Results Results and Analysis}
-In this part, we compared the encoding and decoding time of Approximate Code with TIP code, STAR code, RS code and LRC codes, respectively. The code configuration is as follow,
+\subsection{Experimental Results and Analysis}
+In this part, we compared the encoding and decoding time of Approximate Code with TIP-Code, STAR code, RS code and LRC codes, respectively. The code configuration is as follow,
 \begin{itemize}
-    \item \textbf{Approximate Code:} APPR.TIP/STAR ($k,1,2,4$), APPR.
-TIP/STAR ($k,2,1,4$), APPR.
-TIP/STAR ($k,1,2,6$), APPR.TIP/STAR ($k,2,1,6$).
-Since TIP and STAR code have different limits on the number of data nodes, we use these two codes to generate parities in Approximate Code, so that we can cover all the code configurations from $k$ = 5 to $k$ = 17.
-When we compare Approximate Code with STAR, we only choose APPR.STAR ($k,1,2,4$), APPR.STAR ($k,2,1,4$), APPR.STAR ($k,1,2,6$), APPR.STAR ($k,2,1,6$) and so do the TIP Code.
+    \item We use ($k,1,2,4$), ($k,2,1,4$), ($k,1,2,6$) and ($k,2,1,6$) as the parameter used in the generation process of APPR.RS Code, APPR.TIP-Code and APPR.STAR Code.
+We also use ($k,1,2,4$) and ($k,1,2,6$) as the parameter used in generating APPR.LRC.
     \item \textbf{RS Code:} RS($k,3$). $k = 5,7,9,11,13$.
     \item \textbf{LRC Codes:} LRC ($k,4,3$), LRC ($k,6,3$). $k = 5,7,9,11,13$.
-    \item \textbf{TIP Code:} TIP($k,3$). $k = 5,9,11,15,17$.
+    \item \textbf{TIP-Code:} TIP($k,3$). $k = 5,9,11,15,17$.
     \item \textbf{STAR Code:} STAR($k,3$). $k = 5,7,11,13,17$.
 \end{itemize}
+
 \subsubsection{Encoding Time}
@@
 
-    \item TIP Code: the effet of TIP code is similar to STAR code. The rate of optimization is up to 58.1\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
+    \item TIP-Code: the result of TIP-Code is similar to STAR code. The rate of optimization is up to 58.1\% (between APPR.TIP ($k,1,2,6$) and TIP ($k,3$) when $k$ = 9).
 
-    \item RS Code: We could find out that the AP code encodes largely faster than RS code. The rate of optimization is up to 91.1\% (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item RS Code: We could find out that the  (between APPR.RS ($k,1,2,6$) and RS($k,3$) when $k = 5$).
 
@@
 The results show that Approximate Code has the best encoding performance among five codes.
-There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while tipical 3DFTs codes generate 3 nodes.
+There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while typical 3DFTs codes generate 3 nodes.
 (2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par
@@
 \vspace{-0.3cm}
-\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
+\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}\vspace{-3mm}
 \end{figure}
@@
     \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
-    \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
+    \item TIP-Code: The decoding time of Approximate Code is almost the same as TIP-Code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
     \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code.
@@
 \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}
+\caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}\vspace{-3mm}
 \end{figure}
@@
     \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item TIP-Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
     \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
@@
 \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in Double Node Failure between Approximate Code and other method}\label{fig-decoding-2}
+\caption{Decoding Time Comparison in Double Node Failure between Approximate Code and other method}\label{fig-decoding-2}\vspace{-3mm}
 \end{figure}
@@
     \item STAR Code: the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
+    \item TIP-Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
     \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
@@
 \vspace{-0.3cm}
-    \caption{Decoding Time Comparison in Triple Node Failure between Approximate Code and other method}\label{fig-decoding-3}
+\caption{Decoding Time Comparison in Triple Node Failure between Approximate Code and other method}\label{fig-decoding-3}\vspace{-3mm}
 \end{figure}
@@
 }
-    \caption{Comparison of several matrics between different methods when the number of data nodes is 5}\label{fig-BAR}
+\vspace{-3mm}
+\caption{Comparison of several matrics between different methods when the number of data nodes is 5}\label{fig-BAR}\vspace{-3mm}
 \end{figure*}
@@
 \caption{Recovery time comparison in double and triple node failures between Approximate Code and other ECs}\label{fig-recovery}
+\vspace{-3mm}
 \end{figure}
 
-\subsection{Frame Recovery}
-Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
-As shown in Figure\ref{fig-frameRecovery}, The top 3 figures are the original frames.
-When frame 2 lost, the interpolation techniques can output \ref{fig-recoverof2} by the input of \ref{fig-interop1} and \ref{fig-interop3}.
-The recovered frame has a lower resolution and may differ from the original image, but since the unconstrained frame contains most of the context information, the video is still available, which validates the fact that the video can tolerate a certain amount of data loss.
+\begin{table}[]\footnotesize
+\caption{Summary on comparison between RS, LRC, STAR and TIP-Code and their Approximate Codes.}\label{tab-summary}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Experiment\\ Scenario\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Coding\\ Method\end{tabular}} & \multicolumn{5}{c|}{Number of Data Nodes} \\ \cline{3-7}
+ &  & 5 & 7 & 9 & 11 & 13 \\ \hline \hline
+\multirow{4}{*}{Encoding} & RS(k,3) & 48.8\% & 48.9\% & 54.0\% & 50.8\% & 51.9\% \\ \cline{2-7} 
+ & STAR(p) & 51.7\% & 51.0\% & / & 48.5\% & 46.9\% \\ \cline{2-7} 
+ & TIP(k) & 51.7\% & / & 54.3\% & 48.4\% & / \\ \cline{2-7} 
+ & LRC(20,2,4) & 61.7\% & 56.8\% & 58.0\% & 54.6\% & 54.7\% \\ \hline
+\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under \\ Single Node \\ Failure\end{tabular}} & RS(k,3) & 0.1\% & 0.9\% & 0.2\% & 0.6\% & 0.6\% \\ \cline{2-7} 
+ & STAR(p) & 5.5\% & 3.7\% & / & -2.5\% & -5.2\% \\ \cline{2-7} 
+ & TIP(k) & 8.8\% & / & 10.8\% & -1.7\% & / \\ \cline{2-7} 
+ & LRC(20,2,4) & 1.3\% & -0.8\% & -0.9\% & -3.4\% & -9.5\% \\ \hline
+\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Double Node\\ Failure\end{tabular}} & RS(k,3) & 75.0\% & 75.4\% & 75.1\% & 75.2\% & 75.2\% \\ \cline{2-7} 
+ & STAR(p) & 76.5\% & 76.0\% & / & 74.5\% & 73.7\% \\ \cline{2-7} 
+ & TIP(k) & 77.1\% & / & 77.6\% & 74.5\% & / \\ \cline{2-7} 
+ & LRC(20,2,4) & 77.8\% & 78.7\% & 78.5\% & 77.4\% & 77.6\% \\ \hline
+\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Triple Node\\ Failure\end{tabular}} & RS(k,3) & 75.0\% & 75.0\% & 75.0\% & 75.0\% & 75.0\% \\ \cline{2-7} 
+ & STAR(p) & 75.1\% & 74.9\% & / & 75.1\% & 75.0\% \\ \cline{2-7} 
+ & TIP(k) & 74.9\% & / & 75.6\% & 73.2\% & / \\ \cline{2-7} 
+ & LRC(20,2,4) & 87.6\% & 87.4\% & 87.0\% & 87.3\% & 87.9\% \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[ht]
+\centering
+\subfigure{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
+}\hspace{-0.4cm}
+\subfigure{
+\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
+}
+\vspace{-3mm}
+\caption{Recovery time Result using Frame Interpolation}
+\label{fig-recoverytime}
+\vspace{-3mm}
+\end{figure}
 
@@
 \subfigure[Recovery of Frame 2]{
-\includegraphics[width=0.5\linewidth]{photo/Frame/2_1.jpg}\label{fig-recoverof2}
+\includegraphics[width=0.4\linewidth]{photo/Frame/2_1.jpg}\label{fig-recoverof2}
 }
+\vspace{-3mm}
 \caption{Frame Recovery Result using Frame Interpolation}
+\vspace{-3mm}
 \label{fig-frameRecovery}
 \end{figure}
+
+\subsection{Frame Recovery}
+Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
+As shown in Figure\ref{fig-frameRecovery}, The top 3 figures are the original frames.
+When frame 2 lost, the interpolation techniques can output \ref{fig-recoverof2} by the input of \ref{fig-interop1} and \ref{fig-interop3}.
+The recovered frame has a lower resolution and may differ from the original image, but since the unconstrained frame contains most of the context information, the video is still available, which validates the fact that the video can tolerate a certain amount of data loss.
 
@@
 
-\begin{table}[]\footnotesize
-\caption{Summary on various of configurations of APPR.TIP/STAR Code}\label{tab-summary}
-\begin{tabular}{|p{1.5cm}<{\centering}|p{1.2cm}<{\centering}|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Experiment\\ scenario\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Coding\\ Method\end{tabular}} & \multicolumn{5}{c|}{Number of Nodes $k$} \\ \cline{3-7}
- &  & \multicolumn{1}{c|}{5} & \multicolumn{1}{c|}{7} & \multicolumn{1}{c|}{9} & \multicolumn{1}{c|}{11} & \multicolumn{1}{c|}{13} \\ \hline
-\multirow{4}{*}{Encoding} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
- & RS (k,3) & 89.7\% & 89.5\% & 88.7\% & 89.2\% & 88.3\% \\ \cline{2-7} 
- & Star (k,3) & 51.6\% & 51.0\% & 48.4\% & 46.9\% & 51.7\% \\ \cline{2-7} 
- & LRC (20,2,4) & 87.5\% & 86.8\% & 85.9\% & 86.1\% & 86.0\% \\ \hline
-\multirow{4}{*}{Encoding} & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
- & RS (k,3) & 91.1\% & 90.7\% & 90.5\% & 90.3\% & 89.5\% \\ \cline{2-7} 
- & Star (k,3) & 56.3\% & 54.2\% & / & 55.8\% & 55.6\% \\ \cline{2-7} 
- & LRC (30,2,6) & 88.9\% & 88.0\% & 85.6\% & 85.2\% & 81.6\% \\ \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Single Node \\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
- & RS (k,3) & 79.6\% & 79.3\% & 78.7\% & 78.2\% & 78.0\% \\ \cline{2-7} 
- & Star (k,3) & 5.5\% & 3.7\% & -2.1\% & -5.3\% & 3.7\% \\ \cline{2-7} 
- & LRC (20,2,4) & 1.3\% & -0.8\% & -0.9\% & -3.5\% & -9.5\% \\ \cline{2-7} 
- & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
- & RS (k,3) & 80.1\% & 79.4\% & 78.7\% & 77.6\% & 76.0\% \\ \cline{2-7} 
- & Star (k,3) & 5.1\% & -0.5\% & / & 2.1\% & 1.4\% \\ \cline{2-7} 
- & LRC (30,2,6) & -1.9\% & -5.4\% & -1.9\% & 3.5\% & 5.8\% \\ \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Double Node\\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
- & RS (k,3) & 94.9\% & 94.5\% & 94.6\% & 94.8\% & 94.8\% \\ \cline{2-7} 
- & Star (k,3) & 76.5\% & 76.0\% & 74.5\% & 73.7\% & 76.0\% \\ \cline{2-7} 
- & LRC (20,2,4) & 96.0\% & 95.5\% & 94.1\% & 93.0\% & 92.0\% \\ \cline{2-7} 
- & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
- & RS (k,3) & 96.9\% & 96.5\% & 96.5\% & 96.5\% & 96.3\% \\ \cline{2-7} 
- & Star (k,3) & 83.9\% & 83.1\% & / & 83.6\% & 83.5\% \\ \cline{2-7} 
- & LRC (30,2,6) & 97.2\% & 96.8\% & 96.3\% & 95.5\% & 95.2\% \\ \hline
-\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Triple Node\\ Failure\end{tabular}} & \multicolumn{6}{c|}{APPR.TIP/STAR(5,1,2,4)} \\ \cline{2-7} 
- & RS (k,3) & 94.9\% & 94.8\% & 94.7\% & 94.7\% & 94.3\% \\ \cline{2-7} 
- & Star (k,3) & 75.1\% & 74.9\% & 75.1\% & 75.0\% & 75.1\% \\ \cline{2-7} 
- & LRC (20,2,4) & 97.5\% & 97.3\% & 97.2\% & 97.3\% & 97.2\% \\ \cline{2-7} 
- & \multicolumn{6}{c|}{APPR.TIP/STAR (5,1,2,6)} \\ \cline{2-7} 
- & RS (k,3) & 96.7\% & 96.2\% & 96.5\% & 96.4\% & 96.0\% \\ \cline{2-7} 
- & Star (k,3) & 83.5\% & 81.4\% & / & 83.0\% & 82.6\% \\ \cline{2-7} 
- & LRC (30,2,6) & 98.3\% & 98.1\% & 98.3\% & 98.3\% & 98.4\% \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{figure}[ht]
-\centering
-\subfigure{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
-}\hspace{-0.4cm}
-\subfigure{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
-}
-\caption{Recovery time Result using Frame Interpolation}
-\label{fig-recoverytime}
-\end{figure}
-
 \section{Conclusion}\label{Conclusion}
-In this paper, we present the Approximate Code, which is the framework for video tiered storage in cloud systems.
-The Approximate Code can segment the input erasure codes and provide different fault tolerance for data of different importance.
-For important data, the Approximate Code provides 3DFTs, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery, while having good update write performance.
-We conducted several experiments in the Hadoop system and found that compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
+In this paper, we present the Approximate Code, which is the framework for tiered video storage in cloud systems.
+The Approximate Code can segment the inputted erasure codes and provide different fault tolerance for data of different importance.
+For important data, the Approximate Code provides 3DFTs, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery as well as having good update write performance.
+We conducted several experiments in the Hadoop system and found that compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 4.70X when double disk fail.
 

### 2019-04-26 ApproximateCode.tex
Paper submittion!

@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double disks fail.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double nodes fail.
 \end{abstract}
@@
 For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used.
-Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}.
+Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, TIP}.
 RS-based codes are encoded based on the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost.
@@
 
-STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
+STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star}.
 In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which leads to a long parity chain.
@@
 \subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$]{
-\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-tip}
+\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-TIP}
 }\vspace{-3mm}
-\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$).
+\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-TIP}) code ($p = 5$).
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
@@
 \vspace{-3mm}
-\label{fig-star-tip}
+\label{fig-star-TIP}
 \end{figure}
 
-TIP-Code is also an XOR-based 3DFTs erasure code.
+TIP-Code is also an XOR-based 3DFTs erasure code, as shown in Figure \ref{fig-TIP}.
 Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.
@@
 Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
-\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
+\begin{tabular}{|p{1.8cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.4cm}<{\centering}|}
 \hline
 Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
-Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
+Data Compression & low & / & high & Application Level\\ \hline
 RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
@@
 \end{tabular}
-\vspace{-5mm}
 \end{table}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{photo/Framework-v3.pdf}
+\includegraphics[width=0.83\linewidth]{photo/Framework-v3.pdf}
 \caption{The framework of Approximate Code}\label{fig-framework}
-\vspace{-2mm}
 \end{figure*}
@@
 \caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
-\vspace{-3mm}
 \end{figure}
@@
 \begin{figure}[ht]
-\vspace{-3mm}
 \centering
 \subfigure[Structure selection.]{
-    \label{fig-ap-tip-str}
+    \label{fig-ap-TIP-str}
     \includegraphics[width = 0.45\linewidth]{photo/APPR-STAR-STR.pdf}
@@
 \subfigure[Generation of APPR.STAR.]{
-    \label{fig-ap-tip-GEN}
+    \label{fig-ap-TIP-GEN}
     \includegraphics[width = 0.95\linewidth]{photo/APPR-STAR-GEN.pdf}
-}\vspace{-3mm}
+}
 \caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}\label{fig-appr-star}
-\vspace{-3mm}
 \end{figure}
@@
 \subfigure[Structure selection of APPR.TIP-Code]{
-    \label{fig-ap-tip-str}
+    \label{fig-ap-TIP-str}
     \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
@@
 \subfigure[Generation of local parities]{
-    \label{fig-ap-tip-lP}
+    \label{fig-ap-TIP-lP}
     \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
@@
 \subfigure[Generation of global parities]{
-    \label{fig-ap-tip-GP}
+    \label{fig-ap-TIP-GP}
     \includegraphics[width = 0.9\linewidth]{photo/APPR-TIP-GL-v2.pdf}
@@
 \section{Evaluation}\label{evaluation}
-In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code.
+In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code framework.
+
 \subsection{Evaluation Methodology}
-The experiment is divided into two parts: the first part evaluates the performance of the Approximate Code, and the second part evaluates the impact of the loss of the unimportant data on the video files.
+The experiments consist of two parts.
+The first part we evaluate the performance/reliability of the Approximate Code, which include encoding/decoding performance, single write performance, etc.
+The second part we verify the capability of interpolation algorithm to recover the lost video frames.
+The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}.
+We define a $1\%$ data loss on the unimportant video frames.
+The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).
 
-In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code.
+%In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
 Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
 
-In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.
+%In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.
+
+\subsubsection{Erasure Codes}
+We select several erasure codes and their corresponding approximate codes in our evaluation as below ($k = 5,7,9,11,13,15,17$), which can tolerant concurrent triple node failures and be used in typical cloud storage systems.
+\begin{itemize}
+    \item \textbf{Approximate Code:} APPR.
+RS/LRC/TIP/STAR ($k,1,2,4$), APPR.
+RS/LRC/TIP/STAR ($k,1,2,6$).
+If an approximate code has two structures (Even/Uneven), we use the average value as the result in our comparison.
+    \item \textbf{RS Code \cite{RS}:} RS($k,3$).
+    \item \textbf{LRC Codes \cite{LRC}:} LRC ($k,4,3$), LRC ($k,6,3$). 
+    \item \textbf{TIP Code \cite{TIP}:} TIP($k,3$). 
+    \item \textbf{STAR Code \cite{STAR}:} STAR($k,3$).
+\end{itemize}
 
 \subsubsection{Metrics}
-We use the \textbf{Storage Efficiency} and \textbf{Single Write (update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.
+We select the \textbf{Storage Overhead}, \textbf{Single Write Cost}, \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our evaluation.
 
-We use \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our experiments.
+Storage overhead is the ratio between the total amount of data (all data and parities) and the original data.
+Single write cost is the average number of I/O operations to handle a single write.
 Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes.
-Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes.
-Recovery time consists of computation time, I/O overhead and transmission time.
-\subsubsection{Experiments Environment}
-The environment of our experiments are shown in Table \ref{tab-platform}.
+Recovery time is the total number to recover a lost data, which consists of computation time, I/O overhead, transmission time, etc.
+
+\subsubsection{Experimental Environment}
+The experimental environment is shown in Table \ref{tab-platform}.
 We set a Hadoop system with one NameNode and $h$ DataNodes.
-Each DataNodes storage the data of one stripe of Approximate Code and the global parities are distributed at each DataNodes.
-We set $h=4,6$ and node size equal $1GB$ here as two default configurations.
-Our experiment can mainly be divided into four cases.
+Each DataNodes are the same as data nodes in Approximate Code, and the global parities are distributed on each DataNodes.
+We set $h=4,6$, and the size of each node is $1GB$.
+
+%Our experiment can mainly be divided into four cases.
 First, we evaluate the encoding time for several erasure codes.
-Then we evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
+We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
 
-we performed the experiment of video frame recovery with the frame interpolation technique.
-The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}.
-We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes.
-We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data.
-The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).
-
-\begin{table}[!ht]\small
+\begin{table}[!ht]\footnotesize
 \begin{tabular}{|l|l|}
@@
 CPU & Intel Xeon 3.0GHz \\ \hline
-NIC 1Gbps & 1Gbps \\ \hline
+NIC & 10Gbps \\ \hline
 Memory & 32GB \\ \hline
@@
 \end{tabular}
-\vspace{3mm}
 \caption{Details of Our Evaluation Platform}\label{tab-platform}
-\vspace{-10mm}
+\vspace{-4mm}
 \end{table}
 
-\subsection{Numerical Results of Mathematical Analysis}
-In this section, we show the mathematical analysis of Approximate Code and compare it with STAR Code, TIP-Code, LRC and RS codes.
+\subsection{Mathematical Analysis}
+In this section, we show the numerical results of mathematical analysis by comparing the Approximate Code with its corresponding original code.
+
 \begin{itemize}
-    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$.
-As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code.
-The ratio of optimization is up to 21.4\% when $h=4, k=4$ and $23.8\%$ when $h=6, k=4$.
-For more typical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
-    \item \textbf{Fault Tolerance:} The fault tolerance of Approximate Code is the same as the inputted erasure codes. All the erasure codes we evaluate in this Section are 3DFTs.
-    \item \textbf{Single Write Performance:} We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$.
-As shown in Figure \ref{fig-Sig-Write}, the results shows that APPR.RS Code has lower single write performance than RS Code and STAR Code.
-The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$.
-As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
+    \item \textbf{Storage Overhead:} We compare the storage overhead among RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), and the results are shown in Figure \ref{fig-Storage}.
+It is clear that APPR.RS has much lower storage overhead than RS Code.
+The degradation is up to 21.4\% when $h=4, k=4$, and $23.8\%$ when $h=6, k=4$.
+When $k=6$, APPR.RS ($6,1,2,4$) reduces the average number of parity nodes from $3$ to $1.33$.
+    \item \textbf{Single Write Performance:} We compare the single write cost among different erasure codes, and the results are shown in Figure \ref{fig-Sig-Write}.
+We notice that APPR.RS has the lowest single write performance, which decreases the average number of I/Os by up to  $41.3\%$.
+%The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$. As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
 \end{itemize}
@@
     \label{fig-storage4}
-    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-4.eps}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-4.eps}
 }
@@
     \label{fig-storage6}
-    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-6.eps}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-6.eps}
 }
-\caption{Storage Overhead}\label{fig-Storage}
+\caption{Storage overhead comparison between RS and APPR.RS}\label{fig-Storage}
 \end{figure}
@@
     \label{fig-Sig-Write4}
-    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-4.eps}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Single-4.eps}
 }
@@
     \label{fig-Sig-Write6}
-    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-6.eps}
+    \includegraphics[width = 0.42\linewidth]{photo/experiment/Single-6.eps}
 }
-\caption{Single Write Performance}\label{fig-Sig-Write}
+\caption{Single write performance comparison among RS, STAR, APPR.RS and APPR.STAR.}\label{fig-Sig-Write}
 \end{figure}
 
-\subsection{Experimental Results and Analysis}
-In this part, we compared the encoding and decoding time of Approximate Code with TIP-Code, STAR code, RS code and LRC codes, respectively. The code configuration is as follow,
-\begin{itemize}
-    \item We use ($k,1,2,4$), ($k,2,1,4$), ($k,1,2,6$) and ($k,2,1,6$) as the parameter used in the generation process of APPR.RS Code, APPR.TIP-Code and APPR.STAR Code.
-We also use ($k,1,2,4$) and ($k,1,2,6$) as the parameter used in generating APPR.LRC.
-    \item \textbf{RS Code:} RS($k,3$). $k = 5,7,9,11,13$.
-    \item \textbf{LRC Codes:} LRC ($k,4,3$), LRC ($k,6,3$). $k = 5,7,9,11,13$.
-    \item \textbf{TIP-Code:} TIP($k,3$). $k = 5,9,11,15,17$.
-    \item \textbf{STAR Code:} STAR($k,3$). $k = 5,7,11,13,17$.
-\end{itemize}
+\subsection{Experimental Results}
+In this subsection, we show the experimental results of various codes in terms of encoding/decoding time and recovery time.
 
@@
 \begin{itemize}
-    \item STAR Code: Approximate Code encodes faster than STAR code and the rate of optimization is up to $56.3\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item Compared to STAR/TIP Codes: Approximate Code encodes faster than STAR/TIP code by up to $51.7\%$, $54.3\%$, respectively.
 
-    \item TIP-Code: the result of TIP-Code is similar to STAR code. The rate of optimization is up to 58.1\% (between APPR.TIP ($k,1,2,6$) and TIP ($k,3$) when $k$ = 9).
+ %. (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
 
-    \item RS Code: We could find out that the  (between APPR.RS ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+ %   \item Compare to TIP Code: The acceleration over original TIP code is similar to STAR code. The enhancement is up to $58.1\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
 
-    \item LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
-The rate of optimization is up to 88.9\% (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
+    \item Compared to RS/LRC Code: Approximate Code improve the encoding significantly. The optimization ratios are up to $54.0\%$ for RS code,  $61.7\%$ for LRC codes, respectively.
+
+ %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+
+ %   \item Compare to LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
+The rate of optimization is up to $88.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
 \end{itemize}
 
-We combined the encoding time of five codes in Figure \ref{fig-BAR} with $k$=5.
-The results show that Approximate Code has the best encoding performance among five codes.
-There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while typical 3DFTs codes generate 3 nodes.
+%There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while tipical 3DFTs codes generate 3 nodes.
 (2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par
@@
 \vspace{-0.3cm}
-\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}\vspace{-3mm}
+\caption{Encoding Time Comparison among various erasure coding methods.}\label{fig-encoding}
 \end{figure}
 
-\subsubsection{Decoding Time under Single Node Failure Condition Analysis}
+\subsubsection{Decoding Time under Single Node Failure Condition}
 The results are shown in Figure \ref{fig-decoding-1}.
 \begin{itemize}
-    \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
-    \item TIP-Code: The decoding time of Approximate Code is almost the same as TIP-Code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
-    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code.
-The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
-    \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
+    \item Compared to STAR/TIP Codes: The decoding time of Approximate Code is almost the same as original code when single node fails, with an increment by up to $5.5\%$ for STAR code, up to $10.8\%$ for TIP Code, respectively.
+  %   (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
+ %   \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
+    \item Compared to RS/LRC Codes: Approximate Code decodes nearly the same as RS code (improvement by up to $0.9\%$) and LRC codes (enhancement by up to $1.3\%$).
+In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
+    \item In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
+ %The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
+  % \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
 The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
@@
 
-We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$.
+%We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$.
 The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
@@
     \vspace{-0.3cm}
-\caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}\vspace{-3mm}
+    \caption{Single Node Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-1}
     \end{figure}
 
-\subsubsection{Decoding Time under Double Node Failure Condition Analysis}
+\subsubsection{Decoding Time under Double Nodes Failure Condition}
 The results are shown in Figure \ref{fig-decoding-2}.
 \begin{itemize}
-    \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item TIP-Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
-    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition.
-The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-    \item LRC Codes:
-    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
+    \item Compared to STAR/TIP Codes: The recovery acceleration is up to $76.5\%$ for STAR, up to $77.6\%$, respectively.
+    %((between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    %\item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item Compared to RS/LRC Codes: Approximate Code reconstruct the lost data faster than original erasure codes, which improve the reconstruction by up to $75.4\%$ for RS code, and $78.7\%$ for LRC codes, respectively.
+    %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+%    \item LRC Codes:
+%    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
 The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
@@
 
-The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-BAR} ($k=5$).
+%The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-BAR} ($k=5$).
 The results show that RS code and LRC codes has the worst two failure nodes decoding performance while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) perform best among all kinds of codes.
@@
     \vspace{-0.3cm}
-\caption{Decoding Time Comparison in Double Node Failure between Approximate Code and other method}\label{fig-decoding-2}\vspace{-3mm}
+    \caption{Double Nodes Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-2}
     \end{figure}
 
-\subsubsection{Decoding Time under Triple Node Failure Condition Analysis}
+\subsubsection{Decoding Time under Triple Nodes Failure Condition}
 The results are shown in Figure \ref{fig-decoding-3}.
 \begin{itemize}
-    \item STAR Code: the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item TIP-Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
-    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition.
-The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-    \item LRC Codes:
-    We could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes.
-The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
+    \item Compared to STAR Code: The maximum optimization ratio is $75.1\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
+    \item Compared to TIP Code: This condition is similar to STAR code with an optimization ratio is up to $75.6\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item Compared to RS Code: Approximate Code decodes largely faster than RS code under three failure nodes condition by up to $75.0\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item Compared to LRC Codes: Approximate Code largely reduces the decoding time  by up to $87.9\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
 \end{itemize}
 
-The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-BAR} ($k$=5).
+%The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-BAR} ($k$=5).
 The results show that LRC has the worst three failure nodes decoding performance.
@@
 On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.
+
+We combined the encoding/decoding time of all erasure codes in Figure \ref{fig-BAR} when $k=5$.
+The results show that Approximate Code has the best encoding/decoding performance among all erasure codes.
 
@@
     \vspace{-0.3cm}
-\caption{Decoding Time Comparison in Triple Node Failure between Approximate Code and other method}\label{fig-decoding-3}\vspace{-3mm}
+    \caption{Triple Nodes Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-3}
     \end{figure}
@@
     \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Encoding.eps}
-}
+}\hspace{-2mm}
 \subfigure{
@@
 \vspace{-3mm}
-\caption{Comparison of several matrics between different methods when the number of data nodes is 5}\label{fig-BAR}\vspace{-3mm}
+\caption{Comparison of several metrics with five data nodes ($k=5$).}\label{fig-BAR}
+\vspace{-3mm}
 \end{figure*}
 
-\subsubsection{Recovery Time Analysis}
+\subsubsection{Recovery Time}
 
-Figure \ref{fig-recovery} shows the recovery time of Approximate Code and other ECs under two and three failure nodes
-condition.
-We can see that Approximate Code owns the best recovery performance in all ECs.
-The optimization ratio can be up to 97.7\% between APPR.TIP/STAR(5,1,2,6) and LRC(30,2,6).
+Figure \ref{fig-recovery} shows the recovery time of various erasure codes (ECs) under two and three failure nodes
+condition. We can see that Approximate Code owns the best recovery performance in all ECs. The optimization ratio is up to $95.9\%$.
+% between APPR.TIP/STAR(5,1,2,6) and LRC(30,2,6).
 The main reason is that Approximate Code only recover important data under multiple failure nodes condition which can significantly reduce computation time, I/O overhead and transmission time.
@@
 \begin{table}[]\footnotesize
-\caption{Summary on comparison between RS, LRC, STAR and TIP-Code and their Approximate Codes.}\label{tab-summary}
+\caption{Improvement of approximate codes over their corresponding erasure codes.}\label{tab-summary}
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \begin{figure}[ht]
-\centering
 \subfigure{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
-}\hspace{-0.4cm}
+    \label{fig-recovery-2}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
+}
 \subfigure{
-\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
+    \label{fig-recovery-3}
+    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
 }
-\vspace{-3mm}
-\caption{Recovery time Result using Frame Interpolation}
-\label{fig-recoverytime}
+\vspace{-0.3cm}
+\caption{Recovery time comparison under double/triple nodes failure among various erasure coding methods.}\label{fig-recovery}
 \vspace{-3mm}
@@
 \subfigure[Recovery of Frame 2]{
-\includegraphics[width=0.4\linewidth]{photo/Frame/2_1.jpg}\label{fig-recoverof2}
+\includegraphics[width=0.3\linewidth]{photo/Frame/2_1.jpg}\label{fig-recoverof2}
 }
-\vspace{-3mm}
-\caption{Frame Recovery Result using Frame Interpolation}
-\vspace{-3mm}
+\caption{Video Recovery Result using Frame Interpolation.}
 \label{fig-frameRecovery}
+\vspace{-2mm}
 \end{figure}
 
-\subsection{Frame Recovery}
+\subsection{Video Recovery}
 Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
 As shown in Figure\ref{fig-frameRecovery}, The top 3 figures are the original frames.
-When frame 2 lost, the interpolation techniques can output \ref{fig-recoverof2} by the input of \ref{fig-interop1} and \ref{fig-interop3}.
-The recovered frame has a lower resolution and may differ from the original image, but since the unconstrained frame contains most of the context information, the video is still available, which validates the fact that the video can tolerate a certain amount of data loss.
+When frame 2 is lost, the interpolation technique can output Figure \ref{fig-recoverof2} via the input of Figures \ref{fig-interop1} and \ref{fig-interop3}.
+The recovered frame has a lower resolution and differs from the original image, but the unconstrained frame contains most of the context information.
+Therefore, the video is still available and useful for several recovery scenarios.
+It validates the fact that the video can tolerate a certain amount of data loss (e.g., more than $r+g+1$ nodes).
 
 \subsection{Analysis}
-The improvements of Approximate Code over STAR/TIP/RS/LRC codes are listed in Table \ref{tab-summary}.
-From the table, we discover that Approximate Code can obtain a better encoding/decoding performance in all experiments.
+The improvements of Approximate Code over typical erasure codes are listed in Table \ref{tab-summary}.
+From the table, we notice that Approximate Code is a cost-effective solution for 3DFTs.
 There are several reasons to achieve these gains.
-First, Approximate Code only provides three parities for important data and this method leads to the improvements of storage efficiency and encoding/decoding performance.
-Secondly Approximate Code uses XOR-Based codes to generate parities which reduce the computation overhead.
-Finally, the parity chain of Approximate Code is shorter than other ECs and takes advantage of transmission time and I/O overhead in cloud storage systems.
+First, Approximate Code only provides triple parities for important data, which leads to the degradation of storage cost and improvement on encoding/decoding performance.
+Second, Approximate Code simplifies the generation of local parities, which reduces the computational complexity.
+Third, the parity chains in Approximate Code are short, which decreases the transmission time and I/O overhead in cloud storage systems.
 
 \section{Conclusion}\label{Conclusion}
-In this paper, we present the Approximate Code, which is the framework for tiered video storage in cloud systems.
-The Approximate Code can segment the inputted erasure codes and provide different fault tolerance for data of different importance.
-For important data, the Approximate Code provides 3DFTs, and for non-critical data, the Approximate Code provides single or double parity, thus saving storage costs and speeding up recovery as well as having good update write performance.
-We conducted several experiments in the Hadoop system and found that compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 4.70X when double disk fail.
+In this paper, we propose a novel erasure coding framework called Approximate Code, which is used for tiered video storage in cloud systems.
+The framework provides high reliability for important data and low reliability for unimportant.
+By this way, the storage cost can be saved.
+The experimental results show that Approximate Code have the following advantages, (1) reduces the number of parities by up to $55\%$, (2) saves the storage cost by up to $20.8\%$, (3) increases the recovery speed by up to a factor of $4.7X$ under double/triple nodes failure conditions.
 

### 2019-04-26 Apcode_reli/Hicode/main.cpp

@@ -1,417 +1,0 @@
-//
-//  main.cpp
-//  Hicode
-//
-//  Created by HY J on 2019/3/6.
-//  Copyright © 2019 HY J. All rights reserved.
-//
-#include "main.h"
-
-
-int print_map(vector< vector<int> > diskmap){
-    for(int i = 0 ; i < diskmap.size() ; ++i){
-        for(int j= 0 ; j < diskmap[i].size() ; ++j){
-            cout<<diskmap[i][j]<<"\t";
-        }
-        cout<<endl;
-    }
-    cout<<endl;
-    return 0;
-}
-
-int diskclean(vector< vector<int> > & diskmap){
-    for(int i = 0 ; i < diskmap.size() ; ++i){
-        for(int j = 0 ; j < diskmap[0].size() ; ++j){
-            diskmap[i][j]=0;
-        }
-    }
-    diskmap[diskmap.size()-1][diskmap[0].size()-1]=-2;
-    diskmap[diskmap.size()-1][diskmap[0].size()-2]=-2;
-    return 0;
-}
-
-int index2map(vector<vector<int>> & diskmap, bool* index){
-    int a = diskmap.size();
-    int b = diskmap[0].size();
-    
-    for(int i = 0 ; i < a ; ++i){
-        for(int j = 0 ; j < b ; ++j){
-            if(i == a-1 && j >= b-2){
-                continue;
-            }
-            diskmap[i][j]=index[i * b + j];
-        }
-    }
-    return 0;
-}
-
-int disk_break_RS(vector< vector<int> > &RSmap, bool* index, int & comb_num){
-    int length;
-    length = RSmap.size() * RSmap[0].size();
-    
-    if (!hasDone(index, length, DISK_BREAK_NUM))
-    {
-        //从左到右扫描数组
-        for (int i = 0; i < length - 1; i++)
-        {
-            //找到第一个“10”组合将其变成"01"组合
-            if (index[i] && !index[i + 1])
-            {
-                index[i] = false;
-                index[i + 1] = true;
-                
-                //将"01"组合左边的1移到最左边
-                int count = 0;
-                for (int j = 0; j < i; j++)
-                {
-                    if (index[j])
-                    {
-                        index[j] = false;
-                        index[count++] = true;
-                    }
-                }
-                index2map(RSmap, index);
-                //print_map(RSmap);
-                comb_num ++;
-                break;
-            }
-        }
-        return 0;
-    }
[…]

### 2019-04-26 Apcode_reli/Hicode/main.h

@@ -1,46 +1,0 @@
-//
-//  Header.h
-//  Hicode
-//
-//  Created by HY J on 2019/3/6.
-//  Copyright © 2019 HY J. All rights reserved.
-//
-#include <vector>
-#include <iostream>
-#include <time.h>
-#include <iomanip>
-
-
-#ifndef Header_h
-#define Header_h
-#define MAX 100
-#define RATE 10 //损坏率(%)
-#define TIMES 0
-#define DISK_BREAK_NUM 6
-
-
-using namespace std;
-//This project is for Hi-code
-
-/*磁盘存储形式
-            k          m
-     -------------  -------
-     |  |  |  |  |  |  |  |
-     -------------  -------
-l    |  |  |  |  |  |  |  |
-     -------------  -------
-     |  |  |  |  |  |  |  |
-     -------------  -------
- 
-     -------------
- 1   |  |  |  |  |
-     -------------
- 0表示数据正常，1表示数据损坏，-1表示无此盘。
- */
-
-int print_map(vector< vector<int> >);
-int Comb(int n, int k);
-void printRes(bool* index, int n);
-bool hasDone(bool* index, int n, int k);
-int index2map(vector<vector<int>> & diskmap, bool* index);
-#endif /* Header_h */

### 2019-06-10 ApproximateCode.tex
FinalEdition v1

@@
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage{libertine}
 \usepackage{subfigure}
@@
 
-\author{Huayi Jin, Chentao Wu, Xin Xie, Jie Li, Minyi Guo, Hao Lin, Jianfeng Zhang}
-%\email{keplar_gd@sjtu.edu.cn}
+\author{Huayi Jin$^1$,
+        Chentao Wu$^{1*}$,
+        Xin Xie$^1$,
+        Jie Li$^1$,
+        Minyi Guo$^1$,
+        Hao Lin$^2$,
+        and Jianfeng Zhang$^2$}
 \affiliation{%
-    \institution{Shanghai Jiao Tong University, The Alibaba Group}
+    \institution{$^1$MoE Key Lab of Artificial Intelligence, AI Institute \& Department of Computer Science and Engineering, \\Shanghai Jiao Tong University, China}
+    \institution{$^2$The Alibaba Group, China}
+    \institution{$^*$Corresponding  author: wuct@cs.sjtu.edu.cn}
 }
+
+\renewcommand{\shortauthors}{Huayi Jin and Chentao Wu, et al.}
 
@@
 To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems.
-The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double nodes fail.
+The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to $55\%$, saves the storage cost by up to $20.8\%$ and increase the recovery speed by up to $4.7$X when double nodes fail.
 \end{abstract}
@@
 
+\copyrightyear{2019} 
+\acmYear{2019} 
+\setcopyright{acmcopyright}
+\acmConference[ICPP 2019]{48th International Conference on Parallel Processing}{August 5--8, 2019}{Kyoto, Japan}
+\acmBooktitle{48th International Conference on Parallel Processing (ICPP 2019), August 5--8, 2019, Kyoto, Japan}
+\acmPrice{15.00}
+\acmDOI{10.1145/3337821.3337869}
+\acmISBN{978-1-4503-6295-5/19/08}
+
 \keywords{Erasure Codes, Approximate Storage, Multimedia, Cloud Storage}
 \maketitle
-
-\thispagestyle{fancy} 
-\pagestyle{fancy}
-\cfoot{\thepage}
 
@@
 Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, TIP}.
-RS-based codes are encoded based on the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost.
-XOR-based codes simplify the computation, but they suffer other issues like scalability \cite{wu2012sdm, jiang2016bdr}.
+RS-based codes are encoded based on the Galois Field(GF) computations \cite{RS}, which allow flexible configurations.
+XOR-based codes simplify the computations compared to RS-based code, but they suffer other issues like scalability \cite{wu2012sdm, jiang2016bdr}.
 
-With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
+With the increasing demand on higher resolution and frame rate for video applications such as autonomous driving, news media, security monitoring, etc., massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
 Therefore, in this paper, we set out to answer the following question:
@@
 Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
-The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance is sacrificed.
+The second solution is using disk arrays like RAID-5\cite{menon1995performance} or RAID-6 \cite{RAID}, but the capability of fault tolerance is sacrificed.
 Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.}
@@
 \begin{enumerate}
-\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
+\item We propose Approximate Code, which is a cost-effective framework to store video data in cloud storage systems.
 \item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, LRC, STAR Code, TIP-Code, etc.
@@
 In Section \ref{ApCode}, the design of Approximate Code Framework will be illustrated in detail.
-%Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
 The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.
@@
 $r$ & the number of parity nodes (in a local stripe) \\ \hline
-$n$ & the number of all data and parity nodes in a local stripe. ($n=k+r$) \\ \hline
+$n$ & the number of all data and parity nodes in a local stripe. $n=k+r$ \\ \hline
 $h$ & the number of local stripes to construct a global stripe \\ \hline
 $g$ & the number of global parity nodes \\ \hline
+$f$ & the number of failed nodes \\ \hline
 $p$ & a prime number \\ \hline
-$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
+$N$ & total number of all nodes ($N=h*(k+r)+g$) \\ \hline
 $C_{i,j}$ & the element at the $i$-th row and $j$-th column \\ \hline
@@
 $P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
-$\oplus$ & the XOR operation symbol \\ \hline
-$\binom{n}{k}$ & The number of $k$-combinations from $n$ elements\\ \hline
-LP & local parity nodes \\ \hline
-GP & global parity nodes \\ \hline
-ID & important data in a video file \\ \hline
-UD & unimportant data in a video file \\ \hline
+$\oplus$ & an XOR operation \\ \hline
+$\binom{n}{k}$ & the number of $k$-combinations from $n$ elements\\ \hline
+LP & the local parity node \\ \hline
+GP & the global parity node \\ \hline
+ID & the important data in a video file \\ \hline
+UD & the unimportant data in a video file \\ \hline
 \end{tabular}
-\vspace{-3mm}
+
 \end{table}
@@
 \subsection{Basis of Video Storage}\label{video storage}
-For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy compression algorithms before storage.
+For normal high-definition (HD, resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy compression algorithms before storage.
 
@@
 H.264 \cite{wiegand2003overview} is one of the advanced algorithms.
-This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor.
+This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessors.
 For a normal HD video file as mentioned above, H.264 can reduce its size by about 10 times, only 443.27MB.
 
-H.264 classifies all frames into three different categories:
+H.264 classifies all frames into three different categories,
 \begin{enumerate}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{photo/H264_IPB.pdf}
-\caption{A sample of GOPs in H.264}
+\includegraphics[width=0.35\textwidth]{photo/H264_IPB.pdf}
+\caption{A sample of GOPs in H.264.}
 \label{H264-IPB}
@@
 \subsubsection{Video Frame Recovery}
-In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete.
+In the circumstance of video approximate storage, it's common to lose some frames and make the video incompleted.
 However, the lost frames can still be recoverable with the benefit of powerful deep learning techniques.
@@
 \subsection{Existing Erasure Codes}\label{existEC}
-
 Reliability is a critical issue since disk failures are typical in storage systems.
@@
 In the past two decades, several famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code \cite{EVENODD}, RDP code \cite{RDP}, Blaum-Roth code\cite{BlaumRoth}, X-code \cite{XCode}, Liberation code \cite{Liberation}, Liber8tion code \cite{Liber8tion}, Cyclic \cite {Cyclic} code, B-Code \cite{BCode}, Code-M \cite{Code-M}, H-code \cite{hcode}, P-code \cite{PCode} and HVcode \cite{HVCode}, etc.
-
-In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, RL-code \cite{RL}, and so on.
-Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.
+In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, and so on.
+Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, AZ-code \cite{AZ-code}, etc.
+Besides these codes, several methods are proposed to accelerate the encoding/decoding \cite{PCM}\cite{APCM}.
 In the following we mainly introduce the classic erasure codes used in this paper.
@@
 Reed Solomon (RS) Code \cite{RS} is a classic MDS code, as shown in Figure \ref{fig-RS-1}.
-The encoding and decoding operations of RS code are based on Galois Field (GF), leading to high scalability as well as high computational complexity.
+The encoding and decoding operations of RS code are based on Galois Field (GF), leading to high scalability as well as high computational complexity \cite{Optimizing2019}.
 
@@
 \centering
-\subfigure[RS Code for arbitrary storage nodes ($k=4, r=3$). The figure shows the encoding of different horizontal parities. (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
+\subfigure[\textbf{RS Code} for arbitrary storage nodes ($k=4, r=3$). The figure shows the encoding of different horizontal parities. (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
     \includegraphics[width=0.92\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
 }
-\subfigure[LRC Code for arbitrary storage nodes ($k=4, r=2, g=2$), where 4 nodes are divided into 2 local groups and each of them has a local parity.The figure shows the encoding of local and global parities.
+\subfigure[\textbf{LRC Code} for arbitrary storage nodes ($k=4, r=2, g=2$), where 4 nodes are divided into 2 local groups (node 0-1 and node 2-3) and each of them has a local parity.
+The figure shows the encoding of local and global parities.
 (e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
     \includegraphics[width=0.8\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
-}\vspace{-3mm}
-\caption{Encoding of RS code and LRC}
-\vspace{-3mm}
+}
+\caption{Encoding of RS codes and LRC.}
 \end{figure}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[ht]
 \centering
 \subfigure[\textbf{STAR Code:} For example, in the diagonal parity $S = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S$.]{
-\includegraphics[height=6.3cm, width = 3.8cm]{photo/STAR.pdf}\label{fig-star}
+\includegraphics[height=6.3cm]{photo/STAR.pdf}\label{fig-star}
 }
-\hspace{5pt}
-\subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$]{
-\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-TIP}
-}\vspace{-3mm}
-\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-TIP}) code ($p = 5$).
+\hspace{6pt}
+\subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,5} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3}$]{
+\includegraphics[height=6.3cm]{photo/TIP.pdf}\label{fig-TIP}
+}
+\caption{\small{Encoding of STAR ($p = 5$) (Figure \ref{fig-star}) and TIP ($p = 3$) (Figure \ref{fig-TIP}) codes.
 Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.
 STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$.}}
-\vspace{-3mm}
+
 \label{fig-star-TIP}
@@
 
-TIP-Code is also an XOR-based 3DFTs erasure code, as shown in Figure \ref{fig-TIP}.
+TIP-Code\cite{TIP} is also an XOR-based 3DFTs erasure code, as shown in Figure \ref{fig-TIP}.
 Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.
@@
 
-\begin{table}[ht]\small
+\begin{table}[ht]\footnotesize
 \centering
 \caption{
-Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
-\begin{tabular}{|p{1.8cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.4cm}<{\centering}|}
+Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files.}\label{tab-AS-EC-AP}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
-Data Compression & low & / & high & Application Level\\ \hline
-RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
-XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
-RAID-6 & low & low & low & \\ \cline{1-4} 
-RAID-5 & medium & medium & low & \\ \cline{1-4} 
-Approximate Storage & very low & very low & low & \\ \cline{1-4} 
-Approximate Code & low & high & low & \\ \hline
+\multirow{2}{*}{Schemes} & \multirow{2}{*}{Layer} & Storage & Fault & Computing \\
+ &  & Overhead & Tolerance & Overhead \\ \hline
+Data& Application & \multirow{2}{*}{low} & \multirow{2}{*}{/} & \multirow{2}{*}{high} \\
+Compression & Level &  &  &  \\ \hline
+RS-based EC & \multirow{10}{*}{\begin{tabular}[c]{@{}c@{}}Device\\ Level\end{tabular}} & \multirow{2}{*}{high} & \multirow{2}{*}{high} & \multirow{2}{*}{high} \\
+for 3DFTs &  &  &  &  \\ \cline{1-1} \cline{3-5} 
+XOR-based EC &  & \multirow{2}{*}{high} & \multirow{2}{*}{high} & \multirow{2}{*}{low} \\
+for 3DFTs &  &  &  &  \\ \cline{1-1} \cline{3-5} 
+RAID-6 &  & medium & medium & low \\ \cline{1-1} \cline{3-5} 
+RAID-5 &  & low & low & low \\ \cline{1-1} \cline{3-5} 
+Approximate &  & \multirow{2}{*}{very low} & \multirow{2}{*}{very low} & \multirow{2}{*}{low} \\
+Storage &  &  &  &  \\ \cline{1-1} \cline{3-5} 
+Approximate &  & \multirow{2}{*}{low} & \multirow{2}{*}{high} & \multirow{2}{*}{low} \\
+Code &  &  &  &  \\ \hline
 \end{tabular}
@@
 
-\begin{figure*}[ht!]
+\begin{figure*}[ht]
 \centering
 \includegraphics[width=0.83\linewidth]{photo/Framework-v3.pdf}
-\caption{The framework of Approximate Code}\label{fig-framework}
+\caption{The Framework of Approximate Code.}\label{fig-framework}
 \end{figure*}
@@
 \subsection{Overview of Approximate Code Framework}
-The Approximate Code framework contains four main steps, code input, code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
+The Approximate Code Framework contains four main steps, code input, code segmentation, structure selection and code generation, as shown in Figure \ref{fig-framework}.
 
@@
 Acquire an erasure coding input and get the corresponding parameters.
-Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted as the input.
+Typically, for cloud storage systems, erasure codes used in 3DFTs are all accepted as the input.
 Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.
@@
 In the code segmentation step, the horizontal parities are regarded as local parities, which are separated from the diagonal/anti-diagonal parities (shown in Fig.
-\ref{fig-appr-star} and illustrated in \ref{APPRXOR} in detail).
+\ref{fig-ap-STAR} and illustrated in Section \ref{APPRXOR} in detail).
 
@@
 The framework chooses the structure after code segmentation.
-There are two main structures that distribute important and unimportant data in different ways.
-As shown in Figure \ref{fig-framework}, in Even structure, important data are distributed uniformly among all data nodes.
-The other structure is Uneven structure, which stores the important data among several nodes dedicatedly.
-%We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.
+There are two main structures for distributing the important and unimportant data, as shown in Figure \ref{fig-framework}.
+In Even Structure, important data are distributed uniformly among all data nodes, while in Uneven Structure, they are stored among several nodes dedicatedly.
+%We specify that in Even Structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even Structure and Uneven Structure just fills up $k$ nodes.
 
-Since Even structure distributes important data across each node, it guarantees a balanced workload.
-Uneven structure aggregates important data into several dedicated nodes, and provides better reliability (illustrated in Section \ref{ReconstructionFT}).
+Since Even Structure distributes the important data across each node, it guarantees a balanced workload.
+Meanwhile, Uneven Structure aggregates important data into several dedicated nodes, which provides better reliability (illustrated in Section \ref{ReconstructionFT}).
 
@@
 After the code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the inputted erasure code.
-The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$, $h$ and the structure type.
+The construction of the Approximate Code is determined by four parameters ($k$, $r$, $g$, $h$) and the structure type.
 
@@
 
-According to these parameters, Approximate Code framework divides the data/parity nodes into several local stripes. Each local stripe has $n$ nodes,  
-In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are local parity nodes.
-Assume the ratio of important data is $1/h$, the framework utilizes $h$ local stripes to construct a global stripe, which includes $k*h$ data nodes and $r*h$ local parity nodes in total.
-In a global stripe, $g$ additional nodes are designed for global parities, which are calculated by the important data, so the total number of nodes $N$ in APPR.CodeName ($k,r,g,h$) is
+According to these parameters, Approximate Code Framework divides the data/parity nodes into several local stripes. Each local stripe has $n$ nodes,  
+In an $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are local parity nodes.
+We define that the ratio of important data is $1/h$, and the framework utilizes $h$ local stripes to construct a global stripe, which includes $k*h$ data nodes and $r*h$ local parity nodes in total.
+In a global stripe, $g$ additional nodes are designed for global parities, which are calculated by the important data, so the total number of nodes in APPR.CodeName ($k,r,g,h$) is
 $N= h*(k+r) + g$.
 
-Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
-Since the 3DFTs is a typical configuration, we mainly discuss the situation of $r+g=3$ in the rest of our paper, so $r$ is usually $1$ or $2$.%, except section \ref{appr-rsbased}.
+Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures if the inputted erasure code is an MDS code.
+Since the 3DFTs is a typical configuration, we mainly discuss the situation of $r+g=3$ in the rest of our paper, so $r$ is usually $1$ or $2$.
 
 \subsection{Approximate RS-based Codes}\label{appr-rsbased}
-RS-based codes are based the calculation of Galois Field (GF), which are designed for arbitrary number of data nodes.
-Therefore, in the code segmentation step of  Approximate Code framework, we divide the RS-based codes into two parts, $r$ parties and $g$ parities.
-For structure selection step, the important data can be distributed in both two structures.
-Here we take RS and LRC codes to show how Approximate Code framework work.
+RS-based codes are based on the calculation of Galois Field (GF), which are designed for arbitrary number of data nodes.
+Therefore, in the code segmentation step of  Approximate Code Framework, we divide the RS-based codes into two parts, $r$ parties and $g$ parities.
+In the structure selection step, the important data can be distributed in both two structures.
+Here we take RS and LRC codes to show how Approximate Code Framework works.
 
-\subsubsection{Approximate RS Code}
-We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}.
-Three horizontal parities are divided into one local and two global parities with the Uneven structure, and finally we generate APPR.RS ($4,1,2,3$,Uneven).
+\subsubsection{Approximate RS Code (APPR.RS)}
+We consider RS($4,3$) as the inputted erasure code, as shown in Figure \ref{fig-RS-2}.
+Three horizontal parities are divided into one local and two global parities with the Uneven Structure, and finally we generate APPR.RS ($4,1,2,3$,Uneven).
 As a result, the unimportant data and their corresponding parities constitute a RS ($4,1$) array, and the important data and their corresponding parities form a RS ($4,3$).
@@
 \centering
-\subfigure[The generation of APPR.RS ($4,1,2,3$,Uneven) ]{
-    \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+\subfigure[The structure of APPR.RS ($4,1,2,3$,Uneven) ]{
+    \includegraphics[width=0.42\linewidth]{photo/RS-3.pdf}\label{fig-RS-3}
+}\hspace{3mm}
+\subfigure[The structure of APPR.LRC ($4,2,2,3$,Even)]{
+    \includegraphics[width=0.42\linewidth]{photo/LRC-3.pdf}\label{fig-LRC-3}
 }
 
+\subfigure[The generation of APPR.RS ($4,1,2,3$,Uneven) ]{
+    \includegraphics[width=0.85\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
+}
 \subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
-    \includegraphics[width=0.75\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
+    \includegraphics[width=0.85\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
 }
-\caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
+\caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code Framework.}
 \end{figure}
 
-\subsubsection{Approximate LRC}
+\subsubsection{Approximate LRC (APPR.LRC)}
 
-We take LRC ($4, 3, 1$) \cite{LRC} as an example (shown in Figure \ref{fig-LRC-2}), which means that three local parities and one global parities are generated initially.
-Similar to the construction of RS code, two local parities and two global parities are reorganized in the code segmentation step.
-At last we get the APPR.LRC ($4, 2, 2, 3$, Even).
+We take LRC ($4, 2, 2$) \cite{LRC} as an example (shown in Figure \ref{fig-LRC-2}), which means
+that two local parities and two global parities are generated initially.
+Similar to the construction of RS code, the global parities are generated only by the important data.
+At last we get the APPR.LRC ($4, 2, 2, 3$, Even)\footnote{Since LRC code is not an MDS erasure code, the fault tolerance of APPR.LRC ($4, 2, 2, 3$) is the same as APPR.RS ($4,1,2,3$)}.
 
@@
 
-\subsubsection{Approximate STAR Code}
+\subsubsection{Approximate STAR Code (APPR.STAR)}
 
-As introduced in Section \ref{existEC}, STAR Code \cite{STAR} is a typical XOR-based erasure code for 3DFTs.
-STAR is a direct extension of EVENODD\cite{EVENODD} (RAID-6 code) by adding the anti-diagonal parities.
-Figure \ref{fig-appr-star} shows the construction of APPR.STAR ($5,2,1,4$,Uneven).
-In this case, the horizontal and diagonal parities are regarded as local parities,  the anti-diagonal parities are defined as global parities in Approximate Code framework.
+As introduced in Section \ref{existEC}, STAR Code \cite{STAR} is a typical XOR-based erasure code for 3DFTs, which is a direct extension of EVENODD\cite{EVENODD} (RAID-6 code) by adding the anti-diagonal parities.
+Figure \ref{fig-ap-STAR} shows the construction of APPR.STAR ($5,2,1,4$,Uneven).
+In this case, the horizontal and diagonal parities are regarded as local parities,  the anti-diagonal parities are defined as global parities in Approximate Code Framework.
 
@@
 \subfigure[Structure selection.]{
-    \label{fig-ap-TIP-str}
-    \includegraphics[width = 0.45\linewidth]{photo/APPR-STAR-STR.pdf}
+    \label{fig-ap-STAR-str}
+    \includegraphics[width = 0.4\linewidth]{photo/APPR-STAR-STR.pdf}
 }
@@
 \subfigure[Generation of APPR.STAR.]{
-    \label{fig-ap-TIP-GEN}
-    \includegraphics[width = 0.95\linewidth]{photo/APPR-STAR-GEN.pdf}
+    \label{fig-ap-STAR-GEN}
+    \includegraphics[width = 0.85\linewidth]{photo/APPR-STAR-GEN.pdf}
 }
-\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}\label{fig-appr-star}
+
+\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code Framework.}\label{fig-ap-STAR}
 \end{figure}
@@
 \subfigure[Structure selection of APPR.TIP-Code]{
-    \label{fig-ap-TIP-str}
-    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
+    \label{fig-ap-TIP-a}
+    \includegraphics[width = 0.4\linewidth]{photo/TIP-a.pdf}
 }
-\hspace{2pt}
+\hspace{5pt}
 \subfigure[Generation of local parities]{
-    \label{fig-ap-TIP-lP}
-    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
+    \label{fig-ap-TIP-b}
+    \includegraphics[width = 0.3\linewidth]{photo/TIP-b.pdf}
 }
@@
 \subfigure[Generation of global parities]{
-    \label{fig-ap-TIP-GP}
-    \includegraphics[width = 0.9\linewidth]{photo/APPR-TIP-GL-v2.pdf}
+    \label{fig-ap-TIP-c}
+    \includegraphics[width = 0.85\linewidth]{photo/TIP-c.pdf}
 }
-\vspace{-3mm}
-\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}\label{fig-ap-TIP}
-\vspace{-3mm}
+
+\caption{The construction and the encoding process of APPR.TIP ($3,1,2,4$,Even). The node 3 and 4 in TIP-Code are defined as the global parity nodes in this case.}\label{fig-ap-TIP}
+
 \end{figure}
 
-\subsubsection{Approximate TIP-Code}
+\subsubsection{Approximate TIP-Code (APPR.TIP)}
 
-We use the generation of APPR.TIP ($5,1,2,6$,Even) as an example (shown in Figure \ref{fig-ap-TIP}).
+We use the generation of APPR.TIP ($3,1,2,4$,Even) as an example (shown in Figure \ref{fig-ap-TIP}).
 In the code segmentation phase, we split TIP-Code into two parts, the horizontal parity part, and the diagonal/anti-diagonal parities part.
-The important data are arranged in Even structure.
+The important data are arranged in an Even Structure.
 Since the parities of the TIP-Code are distributed among several nodes, the code generation process is different from APPR.STAR.
@@
 The number of global stripes are based on the ratio of important data ($1/h$).
-Assume $h=6$, which means that the framework utilizes the important data from six local stripes to generate one global stripe.
+Here $h=6$, which means that the framework utilizes the important data from six local stripes to generate one global stripe.
 
@@
 Existing work \cite{LRC} has demonstrated that when we have $r$ local parities and $g$ global parities, the capability of fault tolerance is at least $r+g$ in typical.
-Thus the reconstruction (less than $r+g$ nodes fail) of the framework are classified into two cases,
+Thus the reconstruction (less than $r+g$ nodes fail) of the framework is classified into two cases,
 
-(1) When $r$ or less nodes fail, all data (both important and unimportant data) are reconstructed via local parities.
+(1) When $f \leqslant r$, all data (both important and unimportant data) are reconstructed via local parities.
 
-(2) When $r+g$ or less nodes fail, the important data are reconstructed via both local and global parities.
+(2) When $f \leqslant r+g$, the important data are reconstructed via both local and global parities.
 
-Under some special cases, for important/unimportant data, exceeding $r+g$/$r+1$ failure nodes is recoverable as well. 
-Here we only consider two situations: $r+1$ and $r+g+1$.
-Assume the recovery probabilities of these two cases are $P_{I}$/$P_{U}$, respectively.
-Because in this paper we focus on the 3DFTs, $r+g$ is set to 3.
+However, under some special cases, important/unimportant data are also recoverable when ($f>r+g$)/($f > r+1$).
+Here we only consider two situations: $f=r+1$ and $f=r+g+1$, because the former just exceeds the fault tolerance of unimportant data so we calculate $P_U$, while the latter just exceeds the fault tolerance of important data so we calculate $P_I$.
+ Since in this paper we focus on the 3DFTs, $r+g$ is set to 3.
 
-The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
-As mentioned in Section\ref{code-gen}, $r+g$ is set to 3.
+\subsubsection{When $f=r+1$}
+Under Even Structure, the unimportant data nodes are recoverable as long as $f \leqslant r$.
+There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and there are $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases result in unrecoverable data.
 
-%We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
-Approximate Codes based on different structures also have different capabilities of fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structures in the following subsection.
-
-\subsubsection{Lost $r+1$ nodes}
-Under Even structure, the unimportant data nodes are recoverable as long as the node losses don't exceed $r$.
-There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases result in unrecoverable data.
-
-Under Uneven structure, only $h-1$ stripes contain unimportant data, so $P_{U}$ is
+Under Uneven Structure, only $h-1$ stripes contain unimportant data, so $P_{U}$ is
 \begin{align}
@@
 
-\subsubsection{Lost $r+g+1$ nodes ($4$ nodes)}
-The number of all quad nodes fail cases is $\binom{N}{4}$.
+\subsubsection{When $f=r+g+1$ ($f=4$)}
+The number of cases that $f=4$ is $\binom{N}{4}$.
 We calculate the total number of cases on losing the important data, which are based on the different losses of the global parity nodes. The results are as follows,
@@
 \begin{itemize}
-    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies for important/unimportant data. 
-    \item Low Update Complexity: When one node is updated, APPR. CodeName needs to write $r$ local parity nodes and only $g/h$ global parity nodes, which are less than typical erasure codes.
-    \item High reliability for important data. important data can be recovered in all triple nodes failure and most quad nodes failure environment.
-    \item High Flexibility. Approximate Code framework can be applied with any erasure codes in 3DFTs, and various parameters can be set.
+    \item Low Storage Overhead. Approximate Code reduces storage overhead by approximating and tiered storage strategies for important/unimportant data. 
+    \item Low Update Complexity. When one node is updated, Approximate Code needs to write $r$ local parity nodes and only $g/h$ global parity nodes, which are less than the inputted erasure codes.
+    \item High reliability for important data. Important data can be recovered in all triple nodes failure and most quad nodes failure environment.
+    \item High Flexibility. Approximate Code Framework can be applied with any erasure codes in 3DFTs, and various parameters can be set.
 \end{itemize}
 
-\begin{table}[htb]\small
+\begin{table}[htb]\footnotesize
 \centering
-\caption{Comparison of storage overhead, fault tolerance and average single write performance among typical erasure codes and their approximate codes.}\label{tab-properties}
+\caption{Comparison of storage overhead, fault tolerance and average single write performance among typical erasure codes and their Approximate Codes.}\label{tab-properties}
 \begin{tabular}{|c|c|c|c|}
 \hline
-Erasure Coding & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault Tolerance\\ Capability\end{tabular} & \begin{tabular}[c]{@{}c@{}}Avg.
-Single Write\\ Overhead \end{tabular} \\ \hline
+\multirow{2}{*}{Erasure Coding} & Storage & Fault Tolerance & Avg. Single Write \\
+ & Overhead & Capability & Overhead \\ \hline
 RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
@@
 TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
-\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
-\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
-\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
+APPR.LRC & \multirow{8}{*}{$\frac{(k+r)h+g}{kh}$} & \multirow{2}{*}{$1+g$} & \multirow{2}{*}{$2+\frac{g}{h}$} \\ 
+($k,r,g,h$) &  &  &  \\ \cline{1-1} \cline{3-4} 
+APPR.RS &  & \multirow{2}{*}{$r+g$} & \multirow{2}{*}{$1+r+\frac{g}{h}$} \\
+($k,r,g,h$) &  &  &  \\ \cline{1-1} \cline{3-4} 
+APPR.STAR &  & \multirow{2}{*}{3} & \multirow{2}{*}{$2\frac{k-h-1}{kh}+4$} \\
+($k,2,1,h$) &  &  &  \\ \cline{1-1} \cline{3-4} 
+APPR.TIP &  & \multirow{2}{*}{3} & \multirow{2}{*}{$2+\frac{2}{h}$} \\
+($k,1,2,h$) &  &  &  \\ \hline
 \end{tabular}
@@
 \subsection{Implementation in Storage Systems}\label{Implementation}
+
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.85\linewidth]{photo/implementation-V2.pdf}
-\vspace{-3mm}
-\caption{Overview of Approximate Storage Layer}
-\vspace{-3mm}
+\includegraphics[width=0.75\linewidth]{photo/implementation-V2.pdf}
+\caption{Overview of Approximate Storage Layer.}
 \label{fig-implementation}
@@
 
-Due to classification of important/unimportant data, the implementation of Approximate Code in storage systems includes three modules (shown in Figure \ref{fig-implementation}), data identification and distribution, approximate code and video recovery.
+Due to classification of important/unimportant data, the implementation of Approximate Code in storage systems includes three modules (shown in Figure \ref{fig-implementation}), data identification and distribution, Approximate Code and video recovery.
 
@@
 Therefore, we define the I frames as the important data, the reminder are unimportant data.
-%The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data.
-%This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.
 
@@
 For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module.
-%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.
 
 \subsubsection{Video Recovery Module}
-For unrecovered data, the video recovery module using advanced video recovery strategies illustrated in Section \label{video storage}.
+For unrecovered data, the video recovery module using advanced video recovery strategies illustrated in Section \ref{video storage}.
 Generally, the lost frames are recovered using the interpolation algorithms, where the corrupted frames are processed into fuzzy images and approximately recovered by superpixel techniques.
@@
 \section{Evaluation}\label{evaluation}
-In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code framework.
+In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code Framework.
 
@@
 The experiments consist of two parts.
-The first part we evaluate the performance/reliability of the Approximate Code, which include encoding/decoding performance, single write performance, etc.
-The second part we verify the capability of interpolation algorithm to recover the lost video frames.
+In the first part we evaluate the performance/reliability of the Approximate Code, which includes encoding/decoding performance, single write performance, etc.
+In the second part we verify the capability of interpolation algorithm\cite{meyer2015phase, niklaus2018context,van2017frame} to recover the lost video frames.
 The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}.
@@
 The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).
-
-%In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code.
-Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.
-
-%In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.
+The recovered frame has a lower resolution and differs from the original image, but the unconstrained frame contains most of the context information.
+Therefore, the video is still available and useful for several recovery scenarios.
+It validates the fact that the video can tolerate a certain amount of data loss (e.g., more than $r+g+1$ nodes).
 
 \subsubsection{Erasure Codes}
-We select several erasure codes and their corresponding approximate codes in our evaluation as below ($k = 5,7,9,11,13,15,17$), which can tolerant concurrent triple node failures and be used in typical cloud storage systems.
+We select several erasure codes and their corresponding Approximate Codes in our evaluation as below ($k = 5,7,9,11,13,15,17$), which can tolerant concurrent triple node failures and be used in typical cloud storage systems.
 \begin{itemize}
-    \item \textbf{Approximate Code:} APPR.
-RS/LRC/TIP/STAR ($k,1,2,4$), APPR.
-RS/LRC/TIP/STAR ($k,1,2,6$).
-If an approximate code has two structures (Even/Uneven), we use the average value as the result in our comparison.
+    \item \textbf{Approximate Code:} APPR. RS/LRC/TIP/STAR ($k,1,2,4$), APPR. RS/LRC/TIP/STAR ($k,1,2,6$). Different structures have little effect on the metrics metioned in \ref{metrics}.
+     If an Approximate Code has two structures (Even/Uneven), we use the average value as the result in our comparison.
     \item \textbf{RS Code \cite{RS}:} RS($k,3$).
-    \item \textbf{LRC Codes \cite{LRC}:} LRC ($k,4,3$), LRC ($k,6,3$). 
-    \item \textbf{TIP Code \cite{TIP}:} TIP($k,3$). 
+    \item \textbf{LRC Codes \cite{LRC}:} LRC ($k,4,2$), LRC ($k,6,2$). 
+    \item \textbf{TIP-Code \cite{TIP}:} TIP($k,3$). 
     \item \textbf{STAR Code \cite{STAR}:} STAR($k,3$).
@@
 
-\subsubsection{Metrics}
+\subsubsection{Metrics}\label{metrics}
 We select the \textbf{Storage Overhead}, \textbf{Single Write Cost}, \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our evaluation.
@@
 Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes.
-Recovery time is the total number to recover a lost data, which consists of computation time, I/O overhead, transmission time, etc.
+Recovery time is the time to recover a lost data, which consists of computation time, I/O overhead, transmission time, etc.
 
@@
 We set a Hadoop system with one NameNode and $h$ DataNodes.
-Each DataNodes are the same as data nodes in Approximate Code, and the global parities are distributed on each DataNodes.
+Each DataNode is the same as data nodes in Approximate Code, and the global parities are distributed on each DataNodes.
 We set $h=4,6$, and the size of each node is $1GB$.
 
-%Our experiment can mainly be divided into four cases.
-First, we evaluate the encoding time for several erasure codes.
-We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.
-
-\begin{table}[!ht]\footnotesize
+\begin{table}[ht]\footnotesize
+\caption{Details of Our Evaluation Platform.}\label{tab-platform}
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
-\caption{Details of Our Evaluation Platform}\label{tab-platform}
-\vspace{-4mm}
 \end{table}
-
-\subsection{Mathematical Analysis}
-In this section, we show the numerical results of mathematical analysis by comparing the Approximate Code with its corresponding original code.
-
-\begin{itemize}
-    \item \textbf{Storage Overhead:} We compare the storage overhead among RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), and the results are shown in Figure \ref{fig-Storage}.
-It is clear that APPR.RS has much lower storage overhead than RS Code.
-The degradation is up to 21.4\% when $h=4, k=4$, and $23.8\%$ when $h=6, k=4$.
-When $k=6$, APPR.RS ($6,1,2,4$) reduces the average number of parity nodes from $3$ to $1.33$.
-    \item \textbf{Single Write Performance:} We compare the single write cost among different erasure codes, and the results are shown in Figure \ref{fig-Sig-Write}.
-We notice that APPR.RS has the lowest single write performance, which decreases the average number of I/Os by up to  $41.3\%$.
-%The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$. As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
-\end{itemize}
 
@@
 }
-\caption{Storage overhead comparison between RS and APPR.RS}\label{fig-Storage}
+\caption{Storage overhead comparison between RS and APPR.RS.}\label{fig-Storage}
 \end{figure}
@@
 }
+
 \caption{Single write performance comparison among RS, STAR, APPR.RS and APPR.STAR.}\label{fig-Sig-Write}
 \end{figure}
+
+\subsection{Mathematical Analysis}
+In this section, we show the numerical results of mathematical analysis by comparing the Approximate Code with its corresponding original code.
+
+\begin{itemize}
+    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), and the results are shown in Figure \ref{fig-Storage}.
+It is clear that APPR.RS has much lower storage overhead than RS Code.
+The degradation is up to 21.4\% when $h=4, k=4$, and $23.8\%$ when $h=6, k=4$.
+When $k=6$, APPR.RS ($6,1,2,4$) reduces the average number of parity nodes from $3$ to $1.33$.
+    Table \ref{tab-SO} shows the improvements on storage overhead, note that the results also applies to other 3DFTs MDS codes.
+    \item \textbf{Single Write Performance:} We compare the single write cost among different erasure codes, and the results are shown in Figure \ref{fig-Sig-Write}.
+We notice that APPR.RS has the lowest single write time, which decreases the average number of I/Os by up to  $41.3\%$.
+\end{itemize}
+
+\begin{table}[]\footnotesize
+\caption{Improvement of APPR.RS codes over RS($k,3$) on storage overhead.}\label{tab-SO}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+Coding & \multicolumn{6}{c|}{Number of Data Nodes} \\ \cline{2-7} 
+Method & 4 & 5 & 6 & 7 & 8 & 9 \\ \hline
+APPR.RS($k,1,2,4$) & 21.4\% & 18.8\% & 16.7\% & 15.0\% & 13.6\% & 12.5\% \\ \hline
+APPR.RS($k,2,1,4$) & 10.7\% & 9.4\% & 8.3\% & 7.5\% & 6.8\% & 6.2\% \\ \hline
+APPR.RS($k,1,2,6$) & 23.8\% & 20.8\% & 18.5\% & 16.7\% & 15.2\% & 13.9\% \\ \hline
+APPR.RS($k,2,1,6$) & 11.9\% & 10.4\% & 9.3\% & 8.3\% & 7.6\% & 6.9\% \\ \hline
+\end{tabular}
+\end{table}
 
@@
     \item Compared to STAR/TIP Codes: Approximate Code encodes faster than STAR/TIP code by up to $51.7\%$, $54.3\%$, respectively. 
-
- %. (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-
- %   \item Compare to TIP Code: The acceleration over original TIP code is similar to STAR code. The enhancement is up to $58.1\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).
-
     \item Compared to RS/LRC Code: Approximate Code improve the encoding significantly. The optimization ratios are up to $54.0\%$ for RS code,  $61.7\%$ for LRC codes, respectively.
-
- %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-
- %   \item Compare to LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes.
-The rate of optimization is up to $88.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
 \end{itemize}
-
-%There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while tipical 3DFTs codes generate 3 nodes.
-(2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par
 
@@
 }
-\vspace{-0.3cm}
+
 \caption{Encoding Time Comparison among various erasure coding methods.}\label{fig-encoding}
+
 \end{figure}
@@
 \subsubsection{Decoding Time under Single Node Failure Condition}
-The results are shown in Figure \ref{fig-decoding-1}.
+The results are shown in Table \ref{tab-summary}.
 \begin{itemize}
-    \item Compared to STAR/TIP Codes: The decoding time of Approximate Code is almost the same as original code when single node fails, with an increment by up to $5.5\%$ for STAR code, up to $10.8\%$ for TIP Code, respectively.
-  %   (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
- %   \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
-    \item Compared to RS/LRC Codes: Approximate Code decodes nearly the same as RS code (improvement by up to $0.9\%$) and LRC codes (enhancement by up to $1.3\%$).
-In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
-    \item In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
- %The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
-  % \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node.
-The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
+    \item Compared to STAR/TIP Codes: The decoding time of Approximate Code is almost the same as original code when single node fails, with an increment by up to $5.5\%$ for STAR code, up to $10.8\%$ for TIP-Code, respectively.
+    \item Compared to RS/LRC Codes: Approximate Code decodes nearly the same as RS code (improvements by up to $0.9\%$) and LRC codes (enhancement by up to $1.3\%$).
+    \item In some scenarios, Approximate Codes are worse than original codes, which is affected by small differences on parameter configurations.
 \end{itemize}
-
-%We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$.
-The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same.
-The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par
-
-\begin{figure}[ht]
-    \subfigure{
-        \label{fig-decoding-1-STAR}
-        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
-    }
-    \subfigure{
-        \label{fig-decoding-1-TIP}
-        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
-    }
-    \subfigure{
-        \label{fig-decoding-1-RS}
-        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
-    }
-    \subfigure{
-        \label{fig-decoding-1-LRC}
-        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
-    }
-    \vspace{-0.3cm}
-    \caption{Single Node Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-1}
-    \end{figure}
 
@@
     \item Compared to STAR/TIP Codes: The recovery acceleration is up to $76.5\%$ for STAR, up to $77.6\%$, respectively.
-    %((between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    %\item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
     \item Compared to RS/LRC Codes: Approximate Code reconstruct the lost data faster than original erasure codes, which improve the reconstruction by up to $75.4\%$ for RS code, and $78.7\%$ for LRC codes, respectively.
-    %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-%    \item LRC Codes:
-%    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes.
-The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
 \end{itemize}
-
-%The combined decoding time of five codes under two failure node condition are shown in Figure \ref{fig-BAR} ($k=5$).
-The results show that RS code and LRC codes has the worst two failure nodes decoding performance while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) perform best among all kinds of codes.
-The main reasons are that: On two failure nodes condition, RS code and LRC codes decode data based on RS method which have heavy computational cost while APPR.TIP/STAR ($k,1,2,6$) and APPR.TIP/STAR ($k,1,2,4$) do the approximate recovery which means they only recover important data at this time.
 
@@
 }
-    \vspace{-0.3cm}
+
 \caption{Double Nodes Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-2}
@@
     \item Compared to STAR Code: The maximum optimization ratio is $75.1\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
-    \item Compared to TIP Code: This condition is similar to STAR code with an optimization ratio is up to $75.6\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
-    \item Compared to RS Code: Approximate Code decodes largely faster than RS code under three failure nodes condition by up to $75.0\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
-    \item Compared to LRC Codes: Approximate Code largely reduces the decoding time  by up to $87.9\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
+    \item Compared to TIP-Code: This condition is similar to STAR code with an optimization ratio is up to $75.6\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
+    \item Compared to RS Code: Approximate Code decodes largely faster than RS code under three failure nodes condition by up to $75.0\%$ (between APPR.RS ($k,1,2,6$) and RS($k,3$) when $k = 5$).
+    \item Compared to LRC Codes: Approximate Code largely reduces the decoding time  by up to $87.9\%$  (between APPR.LRC ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
 \end{itemize}
-
-%The combined decoding time of five codes under three failure node condition are shown in Figure \ref{fig-BAR} ($k$=5).
-The results show that LRC has the worst three failure nodes decoding performance.
-The main reasons are that: On three failure nodes condition, LRC codes decode data through the global parities which has a longer parity chain.
-For example $LRC (44,4,2)$ use 44 nodes to recover the three lost nodes.
-the computational cost of GF operations is also larger than XOR operations.
-On the other hand, All kinds of Approximate Code perform best among all kinds of codes because they only recover important data at this time.
 
@@
 }
-    \vspace{-0.3cm}
+
 \caption{Triple Nodes Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-3}
+
 \end{figure}
 
-\begin{figure*}[!ht]
+\begin{figure*}[ht]
 \subfigure{
     \label{fig-encoding-combine}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Encoding.eps}
-}\hspace{-2mm}
+    \includegraphics[width = 0.25\linewidth]{photo/experiment/Bar-Encoding.eps}
+}\hspace{-3mm}
 \subfigure{
     \label{fig-decoding-1-combine}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-1.eps}
-}
+    \includegraphics[width = 0.25\linewidth]{photo/experiment/Bar-Decoding-1.eps}
+}\hspace{-3mm}
 \subfigure{
     \label{fig-decoding-2-combine}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-2.eps}
-}
+    \includegraphics[width = 0.25\linewidth]{photo/experiment/Bar-Decoding-2.eps}
+}\hspace{-3mm}
 \subfigure{
     \label{fig-decoding-3-combine}
-    \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-3.eps}
+    \includegraphics[width = 0.25\linewidth]{photo/experiment/Bar-Decoding-3.eps}
 }
-\vspace{-3mm}
+
 \caption{Comparison of several metrics with five data nodes ($k=5$).}\label{fig-BAR}
-\vspace{-3mm}
+
 \end{figure*}
@@
 condition. We can see that Approximate Code owns the best recovery performance in all ECs. The optimization ratio is up to $95.9\%$.
-% between APPR.TIP/STAR(5,1,2,6) and LRC(30,2,6).
 The main reason is that Approximate Code only recover important data under multiple failure nodes condition which can significantly reduce computation time, I/O overhead and transmission time.
 
-\begin{figure}[ht]
-\subfigure{
-    \label{fig-recovery-2}
-    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
-}
-\subfigure{
-    \label{fig-recovery-3}
-    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
-}
-\vspace{-0.3cm}
-\caption{Recovery time comparison in double and triple node failures between Approximate Code and other ECs}\label{fig-recovery}
-\vspace{-3mm}
-\end{figure}
-
 \begin{table}[]\footnotesize
-\caption{Improvement of approximate codes over their corresponding erasure codes.}\label{tab-summary}
+\caption{Improvement of Approximate Codes ($k,1,2,4$) over their corresponding erasure codes.}\label{tab-summary}
 \begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Experiment\\ Scenario\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Coding\\ Method\end{tabular}} & \multicolumn{5}{c|}{Number of Data Nodes} \\ \cline{3-7}
- &  & 5 & 7 & 9 & 11 & 13 \\ \hline \hline
-\multirow{4}{*}{Encoding} & RS(k,3) & 48.8\% & 48.9\% & 54.0\% & 50.8\% & 51.9\% \\ \cline{2-7} 
- & STAR(p) & 51.7\% & 51.0\% & / & 48.5\% & 46.9\% \\ \cline{2-7} 
- & TIP(k) & 51.7\% & / & 54.3\% & 48.4\% & / \\ \cline{2-7} 
- & LRC(20,2,4) & 61.7\% & 56.8\% & 58.0\% & 54.6\% & 54.7\% \\ \hline
-\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under \\ Single Node \\ Failure\end{tabular}} & RS(k,3) & 0.1\% & 0.9\% & 0.2\% & 0.6\% & 0.6\% \\ \cline{2-7} 
- & STAR(p) & 5.5\% & 3.7\% & / & -2.5\% & -5.2\% \\ \cline{2-7} 
- & TIP(k) & 8.8\% & / & 10.8\% & -1.7\% & / \\ \cline{2-7} 
- & LRC(20,2,4) & 1.3\% & -0.8\% & -0.9\% & -3.4\% & -9.5\% \\ \hline
-\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Double Node\\ Failure\end{tabular}} & RS(k,3) & 75.0\% & 75.4\% & 75.1\% & 75.2\% & 75.2\% \\ \cline{2-7} 
- & STAR(p) & 76.5\% & 76.0\% & / & 74.5\% & 73.7\% \\ \cline{2-7} 
- & TIP(k) & 77.1\% & / & 77.6\% & 74.5\% & / \\ \cline{2-7} 
- & LRC(20,2,4) & 77.8\% & 78.7\% & 78.5\% & 77.4\% & 77.6\% \\ \hline
-\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Decoding under\\ Triple Node\\ Failure\end{tabular}} & RS(k,3) & 75.0\% & 75.0\% & 75.0\% & 75.0\% & 75.0\% \\ \cline{2-7} 
- & STAR(p) & 75.1\% & 74.9\% & / & 75.1\% & 75.0\% \\ \cline{2-7} 
- & TIP(k) & 74.9\% & / & 75.6\% & 73.2\% & / \\ \cline{2-7} 
- & LRC(20,2,4) & 87.6\% & 87.4\% & 87.0\% & 87.3\% & 87.9\% \\ \hline
+Experiment & Coding & \multicolumn{5}{c|}{Number of Data Nodes} \\ \cline{3-7} 
+Scenario & Method & 5 & 7 & 9 & 11 & 13 \\ \hline \hline
+\multirow{4}{*}{Encoding} & RS & 48.80\% & 48.91\% & 53.96\% & 50.79\% & 51.90\% \\ \cline{2-7} 
+ & STAR & 51.65\% & 51.04\% & / & 48.45\% & 46.92\% \\ \cline{2-7} 
+ & TIP & 51.68\% & / & 54.29\% & 48.43\% & / \\ \cline{2-7} 
+ & LRC & 61.69\% & 56.82\% & 57.95\% & 54.60\% & 54.71\% \\ \hline
+Decoding & RS & 0.09\% & 0.89\% & 0.18\% & 0.62\% & 0.57\% \\ \cline{2-7} 
+under & STAR & 5.50\% & 3.67\% & / & -2.05\% & -5.26\% \\ \cline{2-7} 
+Single Node & TIP & 8.78\% & / & 10.79\% & -1.68\% & / \\ \cline{2-7} 
+Failure & LRC & 1.32\% & -0.75\% & -0.91\% & -3.42\% & -9.54\% \\ \hline
+Decoding & RS & 75.03\% & 75.35\% & 75.10\% & 75.23\% & 75.22\% \\ \cline{2-7} 
+under & STAR & 76.46\% & 75.98\% & / & 74.54\% & 73.73\% \\ \cline{2-7} 
+Double Node & TIP & 77.11\% & / & 77.63\% & 74.53\% & / \\ \cline{2-7} 
+Failure & LRC & 77.75\% & 78.70\% & 78.53\% & 77.41\% & 77.62\% \\ \hline
+Decoding & RS & 75.00\% & 75.01\% & 74.99\% & 74.99\% & 75.02\% \\ \cline{2-7} 
+under & STAR & 75.11\% & 74.94\% & / & 75.11\% & 75.03\% \\ \cline{2-7} 
+Triple Node & TIP & 74.85\% & / & 75.57\% & 73.23\% & / \\ \cline{2-7} 
+Failure & LRC & 87.58\% & 87.40\% & 87.00\% & 87.29\% & 87.87\% \\ \hline
 \end{tabular}
@@
 \begin{figure}[ht]
-\subfigure{
+\subfigure[Double nodes recovery]{
     \label{fig-recovery-2}
-    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
+    \includegraphics[width = 0.5\linewidth]{photo/experiment/Recovery-2.eps}
+}\hspace{-4mm}
+\subfigure[Triple nodes recovery]{
+    \label{fig-recovery-3}
+    \includegraphics[width = 0.5\linewidth]{photo/experiment/Recovery-3.eps}
 }
-\subfigure{
-    \label{fig-recovery-3}
-    \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
-}
-\vspace{-0.3cm}
+
 \caption{Recovery time comparison under double/triple nodes failure among various erasure coding methods.}\label{fig-recovery}
-\vspace{-3mm}
+
 \end{figure}
 
+\iffalse
 \begin{figure}[ht]
@@
 \label{fig-frameRecovery}
-\vspace{-2mm}
 \end{figure}
-
-\subsection{Video Recovery}
-Here we present the frame recovery result by using frame interpolation \cite{meyer2015phase, niklaus2018context,van2017frame}.
-As shown in Figure\ref{fig-frameRecovery}, The top 3 figures are the original frames.
-When frame 2 is lost, the interpolation technique can output Figure \ref{fig-recoverof2} via the input of Figures \ref{fig-interop1} and \ref{fig-interop3}.
-The recovered frame has a lower resolution and differs from the original image, but the unconstrained frame contains most of the context information.
-Therefore, the video is still available and useful for several recovery scenarios.
-It validates the fact that the video can tolerate a certain amount of data loss (e.g., more than $r+g+1$ nodes).
+\fi
 
 \subsection{Analysis}
-The improvements of Approximate Code over typical erasure codes are listed in Table \ref{tab-summary}.
+The improvements of Approximate Code over typical erasure codes are listed in Table \ref{tab-SO} and Table \ref{tab-summary}.
 From the table, we notice that Approximate Code is a cost-effective solution for 3DFTs.
 There are several reasons to achieve these gains.
-First, Approximate Code only provides triple parities for important data, which leads to the degradation of storage cost and improvement on encoding/decoding performance.
+First, Approximate Code only provides triple parities for important data, which leads to the degradation of storage cost and improvements on encoding/decoding performance.
 Second, Approximate Code simplifies the generation of local parities, which reduces the computational complexity.
@@
 
+\section*{Acknowledgement}
+We thank anonymous reviewers for their insightful comments.
+This work is partially sponsored by the National Key R\&D Program of China (No.2018YFB0105203), the National 973 Program of China (No.2015CB352403), the Natural Science Foundation of Shanghai (No.18ZR1418500), the Alibaba Group through Alibaba Innovative Research (AIR) program, and the Open Research fund by Data Storage System Lab, Ministry of Education of China.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-06-11 ApproximateCode.tex
Final Version v2

@@
 
-In the past two decades, several famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code \cite{EVENODD}, RDP code \cite{RDP}, Blaum-Roth code\cite{BlaumRoth}, X-code \cite{XCode}, Liberation code \cite{Liberation}, Liber8tion code \cite{Liber8tion}, Cyclic \cite {Cyclic} code, B-Code \cite{BCode}, Code-M \cite{Code-M}, H-code \cite{hcode}, P-code \cite{PCode} and HVcode \cite{HVCode}, etc.
+In the past two decades, several famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code \cite{EVENODD}, RDP code \cite{RDP}, Blaum-Roth code\cite{BlaumRoth}, X-code \cite{XCode}, Liberation code \cite{Liberation}, Liber8tion code \cite{Liber8tion}, Cyclic \cite {Cyclic} code,
+% B-Code \cite{BCode}, Code-M \cite{Code-M},
+H-code \cite{hcode}, P-code \cite{PCode} and HVcode \cite{HVCode}, etc. 
 In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, and so on.
@@
 \subsection{Evaluation Methodology}
-The experiments consist of two parts.
-In the first part we evaluate the performance/reliability of the Approximate Code, which includes encoding/decoding performance, single write performance, etc.
-In the second part we verify the capability of interpolation algorithm\cite{meyer2015phase, niklaus2018context,van2017frame} to recover the lost video frames.
+In the experiments, we mainly evaluate the performance/reliability of the Approximate Code, which includes encoding/decoding performance, single write performance, etc.
+
+We also verify the capability of interpolation algorithm\cite{meyer2015phase, niklaus2018context,van2017frame} to recover the lost video frames.
 The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}.
@@
 It validates the fact that the video can tolerate a certain amount of data loss (e.g., more than $r+g+1$ nodes).
+Due to space limitation, we do not include these results in the paper.
 
